### 2019-10-28 _Abstract_ASHEcon_201910.Rmd
Update workflow files

---
title: "Decision Support and Health Insurance Choice"
author: Ian McCarthy & Evan Saltzman
date: October 2019
output: 
  pdf_document:
    keep_tex: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stargazer, knitr, kableExtra,
               lfe)
```

```{r, include=FALSE}
load("data/R_workspace.Rdata")
```
## Background

## Data

## Methods

## Results
As a first-order result, we establish strong evidence that decision assistance matters for insurance choice. Incorporating institutional details of the exchanges and insurance subsidies, we then identify instances in which individuals choose a strictly dominated health insurance plan. Here, we find that individuals who made an "unassited" choice were `r round(reg1$coeff[2],2)` percentage points less likely to make a dominated choice. On a base of `r round(mean.dom.choice,2)*100`%, this reflects a `r round(reg1$coeff[2]/mean.dom.choice,1)`$x$ increase in the probability of a dominated choice.

Preliminary results further suggest strong heterogeneities across different types of decision assistance, with insurance-based decision support (i.e., insurance brokers) more likely to steer patients into plans offered by the sponsoring insurer. The steering effect appears sufficiently strong such that individuals using an insurance broker are no less likely to choose a dominated plan than individuals with no decision support. The reduction in prevalence of dominated choices is therefore driven entirely by publicly provided decision assistance.

### 2019-10-28 _Abstract_ASHEcon_201910.tex
Update workflow files

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Decision Support and Health Insurance Choice},
            pdfauthor={Ian McCarthy \& Evan Saltzman},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\providecommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{Decision Support and Health Insurance Choice}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Ian McCarthy \& Evan Saltzman}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{October 2019}

\begin{document}
\maketitle

\hypertarget{background}{%
\subsection{Background}\label{background}}

\hypertarget{data}{%
\subsection{Data}\label{data}}

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

\hypertarget{results}{%
\subsection{Results}\label{results}}

As a first-order result, we establish strong evidence that decision
assistance matters for insurance choice. Incorporating institutional
details of the exchanges and insurance subsidies, we then identify
instances in which individuals choose a strictly dominated health
insurance plan. Here, we find that individuals who made an ``unassited''
choice were 0.02 percentage points less likely to make a dominated
choice. On a base of 3\%, this reflects a 0.8\(x\) increase in the
probability of a dominated choice.

Preliminary results further suggest strong heterogeneities across
different types of decision assistance, with insurance-based decision
support (i.e., insurance brokers) more likely to steer patients into
plans offered by the sponsoring insurer. The steering effect appears
sufficiently strong such that individuals using an insurance broker are
no less likely to choose a dominated plan than individuals with no
decision support. The reduction in prevalence of dominated choices is
therefore driven entirely by publicly provided decision assistance.

\end{document}

### 2019-10-28 RunRender.R

@@ -1,0 +1,23 @@
+
+# Meta --------------------------------------------------------------------
+
+## Title:         Decision Assistance and Health Insurance Choice
+## Author:        Ian McCarthy
+## Date Created:  10/28/2019
+## Date Edited:   10/28/2019
+## Description:   This file renders/runs all relevant R code for the project
+
+
+# Preliminaries -----------------------------------------------------------
+
+setwd('C:/Users/immccar/CloudStation/Professional/Research Projects/ACA Decision Support')
+##setwd("D:/CloudStation/Professional/Research Projects/ACA Decision Support")
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stargazer, knitr, kableExtra,
+               lfe)
+
+source('analysis/IanAnalysis.R')
+rmarkdown::render(input = '_Abstract_ASHEcon_201910.Rmd',
+                  output_format = 'all',
+                  output_file ='_Abstract_ASHEcon_201910')

### 2019-10-28 analysis/IanAnalysis.R

@@ -1,23 +1,19 @@
 # Meta --------------------------------------------------------------------
-# Project:       Decision Assistance and Insurance Choice
-# Author:        E. Saltzman & I. McCarthy
-# Date Created:  10/11/2019
-# Date Edited:   10/15/2019
+
+## Title:         Decision Assistance and Health Insurance Choice
+## Author:        Ian McCarthy
+## Date Created:  10/11/2019
+## Date Edited:   10/15/2019
+## Description:   Analysis file for project
 
 
-# Preliminaries -----------------------------------------------------------
+# Load data ---------------------------------------------------------------
 
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, ggplot2, dplyr, lubridate)
-
-
-## Load data
-setwd("D:/CloudStation/Professional/Research Projects/ACA Decision Support/data")
-data <- get(load("ca_enrollment_data_AUG022019")) # individual-level data
-households <- get(load("ca_household_data_AUG022019")) # household-level data
-plan_data <- read.csv("ca_plan_data2.csv") # Covered California plan data
-zip3_choices <- read.csv("zip3_choices2.csv",row.names = 1) # choice set by 3 digit zip and rating area
-product_definitions <- read.csv("product_definitions.csv",row.names = 1) # definitions of column names in zip3_choices
+data <- get(load("data/ca_enrollment_data_AUG022019")) # individual-level data
+households <- get(load("data/ca_household_data_AUG022019")) # household-level data
+plan_data <- read.csv("data/ca_plan_data2.csv") # Covered California plan data
+zip3_choices <- read.csv("data/zip3_choices2.csv",row.names = 1) # choice set by 3 digit zip and rating area
+product_definitions <- read.csv("data/product_definitions.csv",row.names = 1) # definitions of column names in zip3_choices
 
 
 
@@ -91,20 +87,6 @@ data.clean <- data.clean %>%
          metal = replace(metal, metal == "Minimum Coverage", "Catastrophic"))
 
 
-## Subsidies
-data.clean <- data.clean %>%
-  left_join( (households %>% select(household_id, year, subsidized_members)),
[…]

### 2019-10-28 _Abstract_ASHEcon_201910.Rmd
Initial analysis and abstract

@@
 date: October 2019
+geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
+fontsize: 12pt
+subparagraph: yes
+header-includes:
+   - \usepackage{setspace}
+   - \doublespacing
+   - \usepackage{titlesec}
+   - \titlespacing{\section}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
+   - \titlespacing{\subsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
+   - \titlespacing{\subsubsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
 output: 
@@
     keep_tex: TRUE
+bibliography: 'D:/CloudStation/Professional/Bibliography/BibTeX_Library.bib'
 ---
@@
 ```
-## Background
+### Background:
+Health insurance markets are unique in many respects, not least of which is the increasing complexity of choosing an optimal health insurance plan.
+Such complexity has been well-documented in studies of health insurance choice in the Medicare Advantage market [@abaluck2011; @ketcham2012; @gruber2017].
+One way to reduce the burden of this complexity is to provide professional decision support through private insurance agents or public assistance programs, both of which are available in the California health insurance exchanges created under the Affordable Care Act (ACA).
+In this paper, we examine the role of this decision assistance on health insurance plan choice and its implications for consumer welfare.
 
-## Data
+### Data:
+We have data on `r format(tot.enroll, big.mark=",")` enrollee/year observations from the California health insurance exhanges from `r first.year` to `r last.year`.
+Our data include a variety of individual and household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any).
+From these data, we can identify each household's set of possible health insurance plans, and we employ premium and cost sharing subsidy formulas to calculate health insurance costs for each possible plan for each household.
 
-## Methods
+### Methods:
+We first estimate overall demand for health insurance using a nested logit discrete choice model, as in @saltzman2019.
+We then identify specific instances in which the observed plan choice is dominated by some other plan in an individual's choice set.
+For example, Gold and Platinum tier plans are dominated for any household that is eligible for cost-sharing subsidies and with incomes below 150% of the federal poverty level.
+We estimate the effect of decision assistance on dominated choices with a linear probability model, allowing for year and household fixed effects.
 
-## Results
-As a first-order result, we establish strong evidence that decision assistance matters for insurance choice.
-Incorporating institutional details of the exchanges and insurance subsidies, we then identify instances in which individuals choose a strictly dominated health insurance plan.
-Here, we find that individuals who made an "unassited" choice were `r round(reg1$coeff[2],2)` percentage points less likely to make a dominated choice.
-On a base of `r round(mean.dom.choice,2)*100`%, this reflects a `r round(reg1$coeff[2]/mean.dom.choice,1)`$x$ increase in the probability of a dominated choice.
+### Results:
+Our nested logit models establish strong evidence that decision assistance matters for insurance choice.
+Turning specifically to dominated choices, our baseline results suggest that individuals with decision assistance are `r abs(round(reg2$coeff[1],4))*100` percentage points less likely to make a dominated choice.
+On a base of `r round(mean.dom.choice,3)*100`%, this reflects a `r abs(round(reg2$coeff[1]/mean.dom.choice,2))*100`% decrease in the probability of making a dominated choice.
 
-Preliminary results further suggest strong heterogeneities across different types of decision assistance, with insurance-based decision support (i.e., insurance brokers) more likely to steer patients into plans offered by the sponsoring insurer.
+We also find strong heterogeneities in the effects of different forms of decision assistance.
+In particular, we find that individuals using publicly provided decision assistance are `r abs(round(reg3$coeff[2],4))*100` percentage points less likely to select a dominated plan, while individuals using a private insurance agent are `r abs(round(reg3$coeff[1],4))*100` percentage points less likely to select a dominated plan.
+
+### Discussion:
+Our current results provide strong evidence that decision assistance has a significant and economically meaningful effect on health insurance plan choice.
+In terms of dominated choices, our early results suggest that this change in decision-making is welfare improving, and we continue to explore other measures of choice dominance to further confirm this result.
+
+In future work, our identification strategy will exploit the Trump administration's removal of cost-sharing subisidies from the exchanges in 2018 and the subsequent response from insurers to increase premiums on their silver plans ("silver loading").
+This response significantly changed the prevalence of dominated choices in each household's choice set, and in this way, the removal of the cost-sharing subsidies offers an exogenous change to the set of dominated plans available to each household.
+
+We are also extending our analysis of the differential effects between public decision support versus assistance from private insurance agents/brokers.
+This analysis will determine whether insurance brokers are more likely to steer patients into plans offered by the sponsoring insurer.
+
+<!-- Preliminary results further suggest strong heterogeneities across different types of decision assistance, with insurance-based decision support (i.e., insurance brokers) more likely to steer patients into plans offered by the sponsoring insurer.
 The steering effect appears sufficiently strong such that individuals using an insurance broker are no less likely to choose a dominated plan than individuals with no decision support.
 The reduction in prevalence of dominated choices is therefore driven entirely by publicly provided decision assistance.
+-->
+
+# References

### 2019-10-28 _Abstract_ASHEcon_201910.tex
Initial analysis and abstract

@@
-\documentclass[]{article}
+\documentclass[12pt,]{article}
 \usepackage{lmodern}
@@
 }{}
-\usepackage[margin=1in]{geometry}
+\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
 \usepackage{hyperref}
@@
 \setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
 
@@
 
+\usepackage{setspace}
+\doublespacing
+\usepackage{titlesec}
+\titlespacing{\section}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
+\titlespacing{\subsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
+\titlespacing{\subsubsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
+
 \begin{document}
@@
 \hypertarget{background}{%
-\subsection{Background}\label{background}}
+\subsubsection{Background:}\label{background}}
+
+Health insurance markets are unique in many respects, not least of which
+is the increasing complexity of choosing an optimal health insurance
+plan. Such complexity has been well-documented in studies of health
+insurance choice in the Medicare Advantage market (Abaluck and Gruber
+2011; Ketcham et al. 2012; Gruber 2017). One way to reduce the burden of
+this complexity is to provide professional decision support through
+private insurance agents or public assistance programs, both of which
+are available in the California health insurance exchanges created under
+the Affordable Care Act (ACA). In this paper, we examine the role of
+this decision assistance on health insurance plan choice and its
+implications for consumer welfare.
 
 \hypertarget{data}{%
-\subsection{Data}\label{data}}
+\subsubsection{Data:}\label{data}}
+
+We have data on 6,401,473 enrollee/year observations from the California
+health insurance exhanges from 2014 to 2017. Our data include a variety
+of individual and household characteristics, plan choices and plan
+characteristics, and information on the type of decision assistance used
+by the enrollee (if any). From these data, we can identify each
+household's set of possible health insurance plans, and we employ
+premium and cost sharing subsidy formulas to calculate health insurance
+costs for each possible plan for each household.
 
 \hypertarget{methods}{%
-\subsection{Methods}\label{methods}}
+\subsubsection{Methods:}\label{methods}}
+
+We first estimate overall demand for health insurance using a nested
+logit discrete choice model, as in Saltzman (2019). We then identify
+specific instances in which the observed plan choice is dominated by
+some other plan in an individual's choice set. For example, Gold and
+Platinum tier plans are dominated for any household that is eligible for
+cost-sharing subsidies and with incomes below 150\% of the federal
+poverty level. We estimate the effect of decision assistance on
+dominated choices with a linear probability model, allowing for year and
+household fixed effects.
 
 \hypertarget{results}{%
-\subsection{Results}\label{results}}
+\subsubsection{Results:}\label{results}}
 
-As a first-order result, we establish strong evidence that decision
-assistance matters for insurance choice. Incorporating institutional
-details of the exchanges and insurance subsidies, we then identify
-instances in which individuals choose a strictly dominated health
-insurance plan. Here, we find that individuals who made an ``unassited''
-choice were 0.02 percentage points less likely to make a dominated
-choice. On a base of 3\%, this reflects a 0.8\(x\) increase in the
-probability of a dominated choice.
+Our nested logit models establish strong evidence that decision
+assistance matters for insurance choice. Turning specifically to
+dominated choices, our baseline results suggest that individuals with
+decision assistance are 0.37 percentage points less likely to make a
+dominated choice. On a base of 1.9\%, this reflects a 20\% decrease in
+the probability of making a dominated choice.
 
-Preliminary results further suggest strong heterogeneities across
-different types of decision assistance, with insurance-based decision
-support (i.e., insurance brokers) more likely to steer patients into
-plans offered by the sponsoring insurer. The steering effect appears
-sufficiently strong such that individuals using an insurance broker are
-no less likely to choose a dominated plan than individuals with no
-decision support. The reduction in prevalence of dominated choices is
-therefore driven entirely by publicly provided decision assistance.
+We also find strong heterogeneities in the effects of different forms of
+decision assistance. In particular, we find that individuals using
+publicly provided decision assistance are 0.43 percentage points less
+likely to select a dominated plan, while individuals using a private
+insurance agent are 0.16 percentage points less likely to select a
+dominated plan.
+
+\hypertarget{discussion}{%
+\subsubsection{Discussion:}\label{discussion}}
+
+Our current results provide strong evidence that decision assistance has
+a significant and economically meaningful effect on health insurance
+plan choice. In terms of dominated choices, our early results suggest
+that this change in decision-making is welfare improving, and we
+continue to explore other measures of choice dominance to further
+confirm this result.
+
+In future work, our identification strategy will exploit the Trump
+administration's removal of cost-sharing subisidies from the exchanges
+in 2018 and the subsequent response from insurers to increase premiums
+on their silver plans (``silver loading''). This response significantly
+changed the prevalence of dominated choices in each household's choice
+set, and in this way, the removal of the cost-sharing subsidies offers
+an exogenous change to the set of dominated plans available to each
+household.
+
+We are also extending our analysis of the differential effects between
+public decision support versus assistance from private insurance
+agents/brokers. This analysis will determine whether insurance brokers
+are more likely to steer patients into plans offered by the sponsoring
+insurer.
+
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-abaluck2011}{}%
+Abaluck, Jason, and Jonathan Gruber. 2011. ``Heterogeneity in Choice
+Inconsistencies Among the Elderly: Evidence from Prescription Drug Plan
+Choice.'' \emph{American Economic Review} 101 (3): 377--81.
+
+\leavevmode\hypertarget{ref-gruber2017}{}%
+Gruber, Jonathan. 2017. ``Delivering Public Health Insurance Through
+Private Plan Choice in the United States.'' \emph{Journal of Economic
+Perspectives} 31 (4): 3--22.
+
+\leavevmode\hypertarget{ref-ketcham2012}{}%
+Ketcham, Jonathan D, Claudio Lucarelli, Eugenio J Miravete, and M
+Christopher Roebuck. 2012. ``Sinking, Swimming, or Learning to Swim in
+Medicare Part d.'' \emph{American Economic Review} 102 (6): 2639--73.
+
+\leavevmode\hypertarget{ref-saltzman2019}{}%
+Saltzman, Evan. 2019. ``Demand for Health Insurance: Evidence from the
+California and Washington Aca Exchanges.'' \emph{Journal of Health
+Economics} 63: 197--222.
 

### 2019-10-28 RunRender.R

@@ -10,8 +10,8 @@
 
 # Preliminaries -----------------------------------------------------------
 
-setwd('C:/Users/immccar/CloudStation/Professional/Research Projects/ACA Decision Support')
-##setwd("D:/CloudStation/Professional/Research Projects/ACA Decision Support")
+##setwd('C:/Users/immccar/CloudStation/Professional/Research Projects/ACA Decision Support')
+setwd("D:/CloudStation/Professional/Research Projects/ACA Decision Support")
 
 if (!require("pacman")) install.packages("pacman")
 pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stargazer, knitr, kableExtra,

### 2019-10-28 analysis/IanAnalysis.R

@@ -119,7 +119,7 @@ data.clean <- data.clean %>%
   mutate(
     language = case_when(
       language_spoken == "English" ~ "English",
-      language_spoken == "Spanish" ~ "Spansih",
+      language_spoken == "Spanish" ~ "Spanish",
       !(language_spoken %in% c("(nonres","English","Spanish")) ~ "Other Language",
       TRUE ~ NA_character_
     )
@@ -187,29 +187,41 @@ data.clean <- data.clean %>%
              TRUE ~ as.character(service_channel)
            ))
 
+data.pre2018 <- data.clean %>% filter(year<2018)
+
+## DD data
+data.dd <- data.clean %>%
+  group_by(individual_id) %>%
+  mutate(csr_post = (csr_eligible*(year>=2018) & subsidy_fpl_bracket %in% c("138% FPL or less","138% FPL to 150% FPL")),
+         switch_plan = (plan_number!=previous_plan_number & !is.na(previous_plan_number))) %>%
+  ungroup()
+
+
 
 # Summary Statistics ------------------------------------------------------
 
 
 ## metal by type of assistance (all enrollees)
-metal.assist.all <- data.clean %>% group_by(channel, metal) %>%
+metal.assist.all <- data.pre2018 %>% group_by(channel, metal) %>%
   summarize(metal_count=n()) %>%
   mutate(metal_pct=metal_count/sum(metal_count),
          metal_pct=round(metal_pct,3))
 
 ## metal by type of assistance (new enrollees)
-metal.assist.new <- data.clean %>% filter(is.na(previous_plan_number)) %>%
+metal.assist.new <- data.pre2018 %>% filter(is.na(previous_plan_number)) %>%
   group_by(channel, metal) %>%
   summarize(metal_count=n()) %>%
   mutate(metal_pct=metal_count/sum(metal_count),
          metal_pct=round(metal_pct))
 
+## table of assistance and tier choice
 kable(metal.assist.all[,2:4], "latex", booktabs=T, 
       col.names=c("Tier"," Count", "Percent")) %>%
   group_rows("Insurance Agent", 1, 5) %>%
   group_rows("Other Assitance", 6, 10) %>%
   group_rows("Unassisted", 11, 15)
 
+## figure of assistance and tier choice
 stack.all <- ggplot(data.clean) +
   geom_bar(mapping=aes(x=channel,fill=metal),
            position="fill", color="black") +
[…]

### 2019-10-28 RunRender.R
Upate titles and filenames

@@ -2,7 +2,7 @@
 # Meta --------------------------------------------------------------------
 
 ## Title:         Decision Assistance and Health Insurance Choice
-## Author:        Ian McCarthy
+## Author:        Ian McCarthy & Evan Saltzman
 ## Date Created:  10/28/2019
 ## Date Edited:   10/28/2019
 ## Description:   This file renders/runs all relevant R code for the project
@@ -17,7 +17,7 @@ if (!require("pacman")) install.packages("pacman")
 pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stargazer, knitr, kableExtra,
                lfe)
 
-source('analysis/IanAnalysis.R')
+source('analysis/_Analysis.R')
 rmarkdown::render(input = '_Abstract_ASHEcon_201910.Rmd',
                   output_format = 'all',
                   output_file ='_Abstract_ASHEcon_201910')

### 2019-10-28 analysis/_Analysis.R

@@ -1,9 +1,9 @@
 # Meta --------------------------------------------------------------------
 
 ## Title:         Decision Assistance and Health Insurance Choice
-## Author:        Ian McCarthy
+## Author:        Ian McCarthy & Evan Saltzman
 ## Date Created:  10/11/2019
-## Date Edited:   10/15/2019
+## Date Edited:   10/28/2019
 ## Description:   Analysis file for project
 
 

### 2019-11-07 _Abstract_ASHEcon_201910.Rmd
Split cleanup files and update analysis to household level

@@
     keep_tex: TRUE
-bibliography: 'D:/CloudStation/Professional/Bibliography/BibTeX_Library.bib'
+bibliography: 'C:/Users/immccar/CloudStation/Professional/Bibliography/BibTeX_Library.bib'
 ---
@@
 ### Data:
-We have data on `r format(tot.enroll, big.mark=",")` enrollee/year observations from the California health insurance exhanges from `r first.year` to `r last.year`.
-Our data include a variety of individual and household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any).
+Our final dataset consists of `r format(tot.enroll, big.mark=",")` household/year observations from the California health insurance exhanges from `r first.year` to `r last.year`.
+Our data include a variety of household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any).
 From these data, we can identify each household's set of possible health insurance plans, and we employ premium and cost sharing subsidy formulas to calculate health insurance costs for each possible plan for each household.
@@
 For example, Gold and Platinum tier plans are dominated for any household that is eligible for cost-sharing subsidies and with incomes below 150% of the federal poverty level.
-We estimate the effect of decision assistance on dominated choices with a linear probability model, allowing for year and household fixed effects.
+We estimate the effect of decision assistance on dominated choices with a linear probability model, allowing for year, insurer, and region fixed effects.
 
@@
 Our nested logit models establish strong evidence that decision assistance matters for insurance choice.
-Turning specifically to dominated choices, our baseline results suggest that individuals with decision assistance are `r abs(round(reg2$coeff[1],4))*100` percentage points less likely to make a dominated choice.
-On a base of `r round(mean.dom.choice,3)*100`%, this reflects a `r abs(round(reg2$coeff[1]/mean.dom.choice,2))*100`% decrease in the probability of making a dominated choice.
+Turning specifically to dominated choices, our baseline results suggest that individuals with decision assistance are `r abs(round(reg1$coeff[1],4))*100` percentage points less likely to make a dominated choice.
+On a base of `r round(mean.dom.choice,3)*100`%, this reflects a `r abs(round(reg1$coeff[1]/mean.dom.choice,2))*100`% decrease in the probability of making a dominated choice.
 
-We also find strong heterogeneities in the effects of different forms of decision assistance.
-In particular, we find that individuals using publicly provided decision assistance are `r abs(round(reg3$coeff[2],4))*100` percentage points less likely to select a dominated plan, while individuals using a private insurance agent are `r abs(round(reg3$coeff[1],4))*100` percentage points less likely to select a dominated plan.
+We also find evidence fo heterogeneities in the effects of different forms of decision assistance.
+In particular, we find that individuals using publicly provided decision assistance are `r abs(round(reg1.b$coeff[2],4))*100` percentage points less likely to select a dominated plan, while individuals using a private insurance agent are `r abs(round(reg1.b$coeff[1],4))*100` percentage points less likely to select a dominated plan.
 

### 2019-11-07 RunRender.R

@@ -4,20 +4,35 @@
 ## Title:         Decision Assistance and Health Insurance Choice
 ## Author:        Ian McCarthy & Evan Saltzman
 ## Date Created:  10/28/2019
-## Date Edited:   10/28/2019
+## Date Edited:   11/4/2019
 ## Description:   This file renders/runs all relevant R code for the project
 
 
 # Preliminaries -----------------------------------------------------------
 
-##setwd('C:/Users/immccar/CloudStation/Professional/Research Projects/ACA Decision Support')
-setwd("D:/CloudStation/Professional/Research Projects/ACA Decision Support")
+setwd('C:/Users/immccar/CloudStation/Professional/Research Projects/ACA Decision Support')
+##setwd("D:/CloudStation/Professional/Research Projects/ACA Decision Support")
 
 if (!require("pacman")) install.packages("pacman")
 pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stargazer, knitr, kableExtra,
                lfe)
 
+
+# Clean data --------------------------------------------------------------
+source('analysis/Data_Plans.R')
+source('analysis/Data_Individual.R')
+source('analysis/Data_Household.R')
+
+
+# Call analysis and set workspace for knitr -------------------------------
 source('analysis/_Analysis.R')
+rm(list=c("data", "data.ind", "households", "data.hh", "zip3.choices",
+          "plan.data", "product.definitions", "final.data", "hh.language"))
+save.image("data/R_workspace.Rdata")
+
+
+
+# Run abstract markdown ---------------------------------------------------
 rmarkdown::render(input = '_Abstract_ASHEcon_201910.Rmd',
                   output_format = 'all',
                   output_file ='_Abstract_ASHEcon_201910')

### 2019-11-07 analysis/Data_Household.R

@@ -1,0 +1,120 @@
+# Meta --------------------------------------------------------------------
+
+## Title:         Decision Assistance and Health Insurance Choice
+## Author:        Ian McCarthy & Evan Saltzman
+## Date Created:  10/11/2019
+## Date Edited:   11/4/2019
+## Description:   Clean household-level dataset
+
+
+# Load data ---------------------------------------------------------------
+
+households <- get(load("data/ca_household_data_AUG022019")) # household-level data
+zip3.choices <- read.csv("data/zip3_choices2.csv",row.names = 1) # choice set by 3 digit zip and rating area
+product.definitions <- read.csv("data/product_definitions.csv",row.names = 1) # definitions of column names in zip3_choices
+
+
+# Clean Household Data ---------------------------------------------------
+
+## Plan characteristics
+data.hh <- households %>% 
+  separate(zip_region_year, c(NA,"region",NA), sep="_") %>%
+  mutate(region = as.integer(region)) %>%
+  left_join( (plan.data %>% 
+                select(plan_name=Plan_Name, region, 
+                       year=ENROLLMENT_YEAR, 
+                       plan_network_type=PLAN_NETWORK_TYPE,
+                       metal, 
+                       insurer=Issuer_Name) %>%
+                mutate(plan_name=as.character(plan_name))),
+             by=c("plan_name","region","year")) %>%
+  mutate(plan_network_type=as.character(plan_network_type)) %>%
+  mutate( metal = replace(metal, metal == "Minimum Coverage", "Catastrophic"))
+
+
+## Income groups
+data.hh <- data.hh %>%
+  mutate(
+    subsidy_fpl_bracket = case_when(
+      FPL <= 1.38 ~ "138% FPL or less",
+      FPL > 1.38 & FPL <= 1.50 ~ "138% FPL to 150% FPL",
+      FPL > 1.50 & FPL <= 2.00 ~ "150% FPL to 200% FPL",
+      FPL > 2.00 & FPL <= 2.50 ~ "200% FPL to 250% FPL",
+      FPL > 2.50 & FPL <= 4.00 ~ "250% FPL to 400% FPL",
+      FPL > 4.00 ~ "400% FPL or greater",
+      TRUE ~ NA_character_
+    )
+  )
+
+## Language
+hh.language <- data.ind %>% 
+  mutate(lang_english = (language == "English"),
+         lang_spanish = (language == "Spanish"),
[…]

### 2019-11-07 analysis/Data_Individual.R

@@ -1,0 +1,94 @@
+# Meta --------------------------------------------------------------------
+
+## Title:         Decision Assistance and Health Insurance Choice
+## Author:        Ian McCarthy & Evan Saltzman
+## Date Created:  10/11/2019
+## Date Edited:   11/5/2019
+## Description:   Clean individual-level dataset
+
+
+# Load data ---------------------------------------------------------------
+
+data <- get(load("data/ca_enrollment_data_AUG022019")) # individual-level data
+zip3.choices <- read.csv("data/zip3_choices2.csv",row.names = 1) # choice set by 3 digit zip and rating area
+product.definitions <- read.csv("data/product_definitions.csv",row.names = 1) # definitions of column names in zip3_choices
+
+
+# Clean Individual Data ---------------------------------------------------
+
+## Drop all uninsured records for this analysis
+data.ind <- data %>%
+  filter(!is.na(plan_id))
+
+## Create Age Group Variable
+data.ind <- data.ind %>%
+  mutate(
+    age_group=case_when(
+      AGE < 18 ~ "0to17",
+      AGE >= 18 & AGE < 26 ~ "18to25",
+      AGE >= 26 & AGE < 35 ~ "26to34",
+      AGE >= 35 & AGE < 45 ~ "35to44",
+      AGE >= 45 & AGE < 55 ~ "45to54",
+      AGE >= 55 & AGE < 65 ~ "55to64",
+      AGE >= 65 & AGE < 120 ~ "65plus",
+      TRUE ~ NA_character_
+    )
+  )
+
+
+## Gender
+data.ind <- data.ind %>%
+  mutate(
+    Gender = case_when(
+      gender == 1 ~ "Male",
+      gender == 0 ~ "Female"
+    )
+  )
+
+## Metal
+data.ind <- data.ind %>%
+  mutate(metal = as.character(metal_level_enhanced),
+         metal = replace(metal, metal %in% c("Silver - Enhanced 73",
+                                             "Silver - Enhanced 87",
+                                             "Silver - Enhanced 94"), 
+                         "Silver"),
+         metal = replace(metal, metal == "Minimum Coverage", "Catastrophic"))
+
+
+## Income groups
+data.ind <- data.ind %>%
+  mutate(
+    subsidy_fpl_bracket = case_when(
+      FPL <= 1.38 ~ "138% FPL or less",
[…]

### 2019-11-07 analysis/Data_Plans.R

@@ -1,0 +1,41 @@
+# Meta --------------------------------------------------------------------
+
+## Title:         Decision Assistance and Health Insurance Choice
+## Author:        Ian McCarthy & Evan Saltzman
+## Date Created:  10/11/2019
+## Date Edited:   11/5/2019
+## Description:   Clean plan-level dataset
+
+
+# Load data ---------------------------------------------------------------
+
+plan.data <- read.csv("data/ca_plan_data2.csv") # Covered California plan data
+
+
+# Clean Plan Data ---------------------------------------------------------
+
+## rename insurers
+plan.data <- plan.data %>%
+  mutate(
+    Issuer_Name = case_when(
+      Issuer_Name == "Anthem Blue Cross" ~ "Anthem",
+      Issuer_Name == "Blue Shield" ~ "Blue_Shield",
+      Issuer_Name == "Chinese Community" ~ "Chinese_Community",
+      Issuer_Name == "Contra Costa Health Plan" ~ "Contra_Costa",
+      Issuer_Name == "Health Net" ~ "Health_Net",
+      Issuer_Name == "LA Care" ~ "LA_Care",
+      Issuer_Name == "UnitedHealthcare" ~ "United",
+      Issuer_Name == "Western Health" ~ "Western",
+      Issuer_Name == "Sharp" ~ "SHARP"
+    )
+  )
+
+
+## Metal tier
+plan.data <- plan.data %>%
+  mutate(metal = as.character(metal_level),
+         metal = replace(metal, metal %in% c("Silver - Enhanced 73",
+                                             "Silver - Enhanced 87",
+                                             "Silver - Enhanced 94"), 
+                         "Silver") )
+

### 2019-11-07 analysis/_Analysis.R

@@ -3,198 +3,33 @@
 ## Title:         Decision Assistance and Health Insurance Choice
 ## Author:        Ian McCarthy & Evan Saltzman
 ## Date Created:  10/11/2019
-## Date Edited:   10/28/2019
+## Date Edited:   11/4/2019
 ## Description:   Analysis file for project
 
 
-# Load data ---------------------------------------------------------------
 
-data <- get(load("data/ca_enrollment_data_AUG022019")) # individual-level data
-households <- get(load("data/ca_household_data_AUG022019")) # household-level data
-plan_data <- read.csv("data/ca_plan_data2.csv") # Covered California plan data
-zip3_choices <- read.csv("data/zip3_choices2.csv",row.names = 1) # choice set by 3 digit zip and rating area
-product_definitions <- read.csv("data/product_definitions.csv",row.names = 1) # definitions of column names in zip3_choices
-
-
-
-# Clean Plan Data ---------------------------------------------------------
-
-## rename insurers
-plan_data <- plan_data %>%
-  mutate(
-    Issuer_Name = case_when(
-      Issuer_Name == "Anthem Blue Cross" ~ "Anthem",
-      Issuer_Name == "Blue Shield" ~ "Blue_Shield",
-      Issuer_Name == "Chinese Community" ~ "Chinese_Community",
-      Issuer_Name == "Contra Costa Health Plan" ~ "Contra_Costa",
-      Issuer_Name == "Health Net" ~ "Health_Net",
-      Issuer_Name == "LA Care" ~ "LA_Care",
-      Issuer_Name == "UnitedHealthcare" ~ "United",
-      Issuer_Name == "Western Health" ~ "Western",
-      Issuer_Name == "Sharp" ~ "SHARP"
-    )
-  )
-
-
-## Metal tier
-plan_data <- plan_data %>%
-  mutate(metal = as.character(metal_level),
-         metal = replace(metal, metal %in% c("Silver - Enhanced 73",
-                                             "Silver - Enhanced 87",
-                                             "Silver - Enhanced 94"), 
-                         "Silver") )
-
-
-
-# Clean Individual Data ---------------------------------------------------
-
-## Drop all uninsured records for this analysis
-data.clean <- data %>%
-  filter(!is.na(plan_id))
-
-## Create Age Group Variable
-data.clean <- data.clean %>%
[…]

### 2020-06-09 _Abstract_SHESG_202006.Rmd
Big update with new files for discrete choice model and SHESG abstract

---
title: "Decision Assistance and Insurer Steering in Health Insurance"
author: Ian McCarthy & Evan Saltzman
date: June 2020
geometry: "left=2cm,right=2cm,top=1cm,bottom=2cm"
fontsize: 11pt
subparagraph: yes
header-includes:
   - \usepackage{setspace}
   - \singlespacing
   - \usepackage{titlesec}
   - \titlespacing{\section}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
   - \titlespacing{\subsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
   - \titlespacing{\subsubsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
output: 
  pdf_document2:
    keep_tex: TRUE
    toc: FALSE
    number_sections: FALSE
bibliography: 'D:/CloudStation/Professional/Bibliography/BibTeX_Library.bib'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stargazer, knitr, kableExtra,
               lfe)
```

```{r, include=FALSE}
load("data/R_workspace.Rdata")
```
### Background:
Health insurance markets are unique in many respects, not least of which is the increasing complexity of choosing an optimal health insurance plan. Such complexity has been well-documented in studies of health insurance choice in the Medicare Advantage market [@abaluck2011; @ketcham2012; @gruber2017], among others. One way to reduce the burden of this complexity is to provide professional decision support through private insurance agents or public assistance programs, both of which are available in the California health insurance exchanges created under the Affordable Care Act (ACA). The presence of private insurance brokers also introduces the potential for insurers to steer patients to insurance products indirectly through the brokers. In this paper, we examine the role of decision assistance on health insurance plan choice, the effects of commissions on insurer steering, and the broad implications of decision assistance for consumer welfare.

### Data:
Our final dataset consists of `r format(tot.enroll, big.mark=",")` household/year observations from the California health insurance exhanges from `r first.year` to `r last.year`. Our data include a variety of household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any). From these data, we can identify each household's set of possible health insurance plans, and we employ premium and cost sharing subsidy formulas to calculate health insurance costs for each possible plan for each household.

### Demand estimation:
We model health insurance purchasing with a nested logit discrete choice model, as in @saltzman2019, and we derive estimates of the causal effect of decision assistnce by embedding this discrete choice model into a standard potential outcomes framework. This analysis proceeds in three steps: 1) we estimate utility parameters on the subset of individuals without decision assistance; 2) we incorporate these parameters into the closed-form nested logit choice probabilities to estimate choices for the subset of "treated" individuals (i.e., those with some form of decision assistance); and 3) we take the difference between observed and predicted values to form our estimate of the average treatment effect on the treated. Standard errors are bootstrapped and clustered at the year/region level.

Our nested logit demand estimation reveals economically large and statistically significant effects of decision assistance on plan choice. For example, we estimate that individuals are `r round(as.numeric(metal.final[5,6]),2)*100`% more likely to select a silver plan when using some form of decision assistance. Since silver plans are the dominant plan for many choice sets, this finding suggests that decision assistance may improve plan choice.

### Dominated choices:
As a complementary empirical analysis, we identify specific instances in which the observed plan choice is dominated by some other plan in an individual's choice set, and we estimate the effects of decision assistance on the probability of making such a choice. For example, Gold and Platinum tier plans are dominated for any household that is eligible for cost-sharing subsidies and with incomes below 150% of the federal poverty level. We estimate the effect of decision assistance on dominated choices with a linear probability model, allowing for year, insurer, and region fixed effects. Analogous to our nested logit analysis, these results suggest that individuals with decision assistance are `r abs(round(reg1$coeff[1],4))*100` percentage points less likely to make a dominated choice. On a base of `r round(mean.dom.choice,3)*100`%, this reflects a `r abs(round(reg1$coeff[1]/mean.dom.choice,2))*100`% decrease in the probability of making a dominated choice.

### Steering and welfare:
We then supplement our nested logit demand analysis with data on commission payments to insurance brokers, and we incorporate a suppyl-side model of insurer commissions. Our strutural framework allows us to examine welfare implications of decision assistance and steering. Within this framework, we study several counterfactuals designed to approxmiate a variety of policy proposals, including flat commissions, banning of private insurance brokers in favor of public assistance only, and outright removal of all forms of decision assitance (e.g., defunding decision assistance entirely). Preliminary results suggest large welfare gains from removal of commission payments or restrictions to a flat commission schedule.

### Discussion:
Our results provide strong evidence that decision assistance has a significant and economically meaningful effect on health insurance plan choice. Decision assistance in general tends to improve consumer welfare, increasing the probability that enrollees select a silver plan and dramatically decreasing the probability of making a dominated choice. Gains to consumer welfare may be offset somewhat by insurer steering.

In addition to continued structural work on commissions and steering, future work will exploit the Trump administration's removal of cost-sharing subisidies from the exchanges in 2018 and the subsequent response from insurers to increase premiums on their silver plans ("silver loading"). This response significantly changed the prevalence of dominated choices in each household's choice set, and in this way, the removal of the cost-sharing subsidies offers an exogenous change to the set of dominated plans available to each household.

# References

### 2020-06-09 _Abstract_SHESG_202006.tex
Big update with new files for discrete choice model and SHESG abstract

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  11pt,
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Decision Assistance and Insurer Steering in Health Insurance},
  pdfauthor={Ian McCarthy \& Evan Saltzman},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[left=2cm,right=2cm,top=1cm,bottom=2cm]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{setspace}
\singlespacing
\usepackage{titlesec}
\titlespacing{\section}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
\titlespacing{\subsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
\titlespacing{\subsubsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}

\title{Decision Assistance and Insurer Steering in Health Insurance}
\author{Ian McCarthy \& Evan Saltzman}
\date{June 2020}

\begin{document}
\maketitle

\hypertarget{background}{%
\subsubsection{Background:}\label{background}}

Health insurance markets are unique in many respects, not least of which is the increasing complexity of choosing an optimal health insurance plan. Such complexity has been well-documented in studies of health insurance choice in the Medicare Advantage market (Abaluck and Gruber 2011; Ketcham et al. 2012; Gruber 2017), among others. One way to reduce the burden of this complexity is to provide professional decision support through private insurance agents or public assistance programs, both of which are available in the California health insurance exchanges created under the Affordable Care Act (ACA). The presence of private insurance brokers also introduces the potential for insurers to steer patients to insurance products indirectly through the brokers. In this paper, we examine the role of decision assistance on health insurance plan choice, the effects of commissions on insurer steering, and the broad implications of decision assistance for consumer welfare.

\hypertarget{data}{%
\subsubsection{Data:}\label{data}}

Our final dataset consists of 3,212,732 household/year observations from the California health insurance exhanges from 2014 to 2019. Our data include a variety of household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any). From these data, we can identify each household's set of possible health insurance plans, and we employ premium and cost sharing subsidy formulas to calculate health insurance costs for each possible plan for each household.

\hypertarget{demand-estimation}{%
\subsubsection{Demand estimation:}\label{demand-estimation}}

We model health insurance purchasing with a nested logit discrete choice model, as in Saltzman (2019), and we derive estimates of the causal effect of decision assistnce by embedding this discrete choice model into a standard potential outcomes framework. This analysis proceeds in three steps: 1) we estimate utility parameters on the subset of individuals without decision assistance; 2) we incorporate these parameters into the closed-form nested logit choice probabilities to estimate choices for the subset of ``treated'' individuals (i.e., those with some form of decision assistance); and 3) we take the difference between observed and predicted values to form our estimate of the average treatment effect on the treated. Standard errors are bootstrapped and clustered at the year/region level.

Our nested logit demand estimation reveals economically large and statistically significant effects of decision assistance on plan choice. For example, we estimate that individuals are 14\% more likely to select a silver plan when using some form of decision assistance. Since silver plans are the dominant plan for many choice sets, this finding suggests that decision assistance may improve plan choice.

\hypertarget{dominated-choices}{%
\subsubsection{Dominated choices:}\label{dominated-choices}}

As a complementary empirical analysis, we identify specific instances in which the observed plan choice is dominated by some other plan in an individual's choice set, and we estimate the effects of decision assistance on the probability of making such a choice. For example, Gold and Platinum tier plans are dominated for any household that is eligible for cost-sharing subsidies and with incomes below 150\% of the federal poverty level. We estimate the effect of decision assistance on dominated choices with a linear probability model, allowing for year, insurer, and region fixed effects. Analogous to our nested logit analysis, these results suggest that individuals with decision assistance are 1.4 percentage points less likely to make a dominated choice. On a base of 2.8\%, this reflects a 50\% decrease in the probability of making a dominated choice.

\hypertarget{steering-and-welfare}{%
\subsubsection{Steering and welfare:}\label{steering-and-welfare}}

We then supplement our nested logit demand analysis with data on commission payments to insurance brokers, and we incorporate a suppyl-side model of insurer commissions. Our strutural framework allows us to examine welfare implications of decision assistance and steering. Within this framework, we study several counterfactuals designed to approxmiate a variety of policy proposals, including flat commissions, banning of private insurance brokers in favor of public assistance only, and outright removal of all forms of decision assitance (e.g., defunding decision assistance entirely). Preliminary results suggest large welfare gains from removal of commission payments or restrictions to a flat commission schedule.

\hypertarget{discussion}{%
\subsubsection{Discussion:}\label{discussion}}

Our results provide strong evidence that decision assistance has a significant and economically meaningful effect on health insurance plan choice. Decision assistance in general tends to improve consumer welfare, increasing the probability that enrollees select a silver plan and dramatically decreasing the probability of making a dominated choice. Gains to consumer welfare may be offset somewhat by insurer steering.

In addition to continued structural work on commissions and steering, future work will exploit the Trump administration's removal of cost-sharing subisidies from the exchanges in 2018 and the subsequent response from insurers to increase premiums on their silver plans (``silver loading''). This response significantly changed the prevalence of dominated choices in each household's choice set, and in this way, the removal of the cost-sharing subsidies offers an exogenous change to the set of dominated plans available to each household.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-abaluck2011}{}%
Abaluck, Jason, and Jonathan Gruber. 2011. ``Heterogeneity in Choice Inconsistencies Among the Elderly: Evidence from Prescription Drug Plan Choice.'' \emph{American Economic Review} 101 (3): 377--81.

\leavevmode\hypertarget{ref-gruber2017}{}%
Gruber, Jonathan. 2017. ``Delivering Public Health Insurance Through Private Plan Choice in the United States.'' \emph{Journal of Economic Perspectives} 31 (4): 3--22.

\leavevmode\hypertarget{ref-ketcham2012}{}%
Ketcham, Jonathan D, Claudio Lucarelli, Eugenio J Miravete, and M Christopher Roebuck. 2012. ``Sinking, Swimming, or Learning to Swim in Medicare Part d.'' \emph{American Economic Review} 102 (6): 2639--73.

\leavevmode\hypertarget{ref-saltzman2019}{}%
Saltzman, Evan. 2019. ``Demand for Health Insurance: Evidence from the California and Washington Aca Exchanges.'' \emph{Journal of Health Economics} 63: 197--222.
\end{cslreferences}

\end{document}

### 2020-06-09 RunRender.R

@@ -4,17 +4,19 @@
 ## Title:         Decision Assistance and Health Insurance Choice
 ## Author:        Ian McCarthy & Evan Saltzman
 ## Date Created:  10/28/2019
-## Date Edited:   3/4/2020
+## Date Edited:   5/29/2020
 ## Description:   This file renders/runs all relevant R code for the project
 
 
 # Preliminaries -----------------------------------------------------------
-
 if (!require("pacman")) install.packages("pacman")
 pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stargazer, knitr, kableExtra,
-               lfe, modelr)
+               lfe, modelr, mlogit, bookdown, future, parallel, nnet, mnlogit, mixl,
+               JuliaCall, future.apply, gtsummary, emo, twilio)
 
-
+source('paths.R')
+source(paste0(common,"/common_functions.R"))
+julia_setup(JULIA_HOME=jsetup)
 
 # Load data ------------------------------------------------------------
 
@@ -36,16 +38,64 @@ source('analysis/Data_Plans.R')
 source('analysis/Data_Individual.R')
 source('analysis/Data_Household.R')
 
+final.data <- data.hh %>%
+  mutate(channel = as.factor(channel),
+         new_enrollee = is.na(previous_plan_number),
+         any_assist = (channel=="Insurance Agent" | channel=="Other Assistance"),
+         assist_agent = (channel=="Insurance Agent"),
+         assist_other = (channel=="Other Assistance"),
+         low_income = (FPL<1.5),
+         hh_single = (household_size==1),
+         hmo_ppo = (plan_network_type %in% c("HMO","PPO")),
+         bad_obs = (new_enrollee==0 & year==2014),
+         insurer = replace(insurer, 
+                           insurer %in% c("Chinese_Community","LA_Care","Western","Contra_Costa","SHARP"),
+                           "Other")) %>%
+  filter( flagged==0 & !is.na(plan_number_nocsr) & bad_obs==0 & FPL<2.0)%>%
+  select(lang_english, lang_spanish, lang_other,
+         perc_0to17, perc_18to25, perc_26to34, perc_35to44, perc_45to54,
+         perc_male, perc_asian, perc_black, perc_hispanic, perc_other, 
+         FPL, low_income, household_size, hh_single, SEP, new_enrollee, 
+         insurer, hmo_ppo, metal,
+         channel, any_assist, assist_agent, assist_other, dominated_choice, 
[…]

### 2020-06-09 analysis/Data_Choice.R

@@ -1,176 +1,0 @@
-# Meta --------------------------------------------------------------------
-
-## Date Created:  3/4/2020
-## Date Edited:   3/9/2020
-## Description:   Create dataset for choice model
-## Notes:         This file requires that we've already created the household data
-##                and the plan data.
-
-
-
-# Clean data --------------------------------------------------------------
-
-## Remove "flagged" households
-hh.clean <- data.hh %>% filter(flagged==0)
-data.clean <- data %>% filter(flagged==0)
-
-## Oldest person per household
-max.age <- data.ind %>%
-  group_by(household_id, year) %>%
-  summarize(oldest_member=max(AGE))
-
-## Add some variables
-hh.clean <- hh.clean %>%
-  mutate(FPL_bracket = case_when(
-    FPL <= 1.38 ~ "138orless",
-    FPL > 1.38 & FPL <= 2.50 ~ "138to250",
-    FPL > 2.50 & FPL <= 4 ~ "250to400",
-    FPL > 4 ~ "400ormore")) %>%
-  mutate(perc_18to34 = perc_18to25 + perc_26to34,
-         perc_35to54 = perc_35to44 + perc_45to54) %>%
-  left_join(max.age, by=c("household_id","year"))
-
-  
-
-## Predict who left market
-hh.clean <- hh.clean %>%
-  add_predictions(outside_logit, "pred_oom", type="response") %>%
-  mutate(pred_oom = ifelse(is.na(plan_number_nocsr),pred_oom,NA),
-         out_of_market = (pred_oom > mean(pred_oom, na.rm=TRUE))) %>%
-  filter(out_of_market == FALSE | !is.na(plan_number_nocsr))
-hh.clean <- as_tibble(hh.clean)
-  
-
-data.clean <- data.clean %>%
-  left_join(hh.clean %>% select(household_id, year, out_of_market), 
-            by=c("household_id","year")) %>%
-  filter(out_of_market == FALSE | !is.na(plan_number_nocsr))
-data.clean <- as_tibble(data.clean)
-
-
-# Form choice sets --------------------------------------------------------
-afford.threshold <- tibble(
-  cutoff = c(0.08, 0.0805, 0.0813, 0.0816, 0.0805, 0.0830),
-  year = c(2014, 2015, 2016, 2017, 2018, 2019)
-)
-
-zip3.choices <- zip3.choices %>%
-  mutate(outside_option=1)
-zip3 <- as_tibble(zip3.choices %>% distinct(zip3))
-
-for (t in 2014:2019) {
-  
[…]

### 2020-06-09 analysis/Data_Household.R

@@ -7,12 +7,13 @@
 
 # Clean Household Data ---------------------------------------------------
 
+
 ## Plan characteristics
 data.hh <- households %>% 
   separate(zip_region_year, c(NA,"region",NA), sep="_") %>%
   mutate(region = as.integer(region)) %>%
   left_join( (plan.data %>% 
-                select(plan_name=Plan_Name, region, 
+                select(plan_name=Plan_Name2, region, 
                        year=ENROLLMENT_YEAR, 
                        plan_network_type=PLAN_NETWORK_TYPE,
                        metal, 

### 2020-06-09 analysis/Data_Plans.R

@@ -19,7 +19,11 @@ plan.data <- plan.data %>%
       Issuer_Name == "LA Care" ~ "LA_Care",
       Issuer_Name == "UnitedHealthcare" ~ "United",
       Issuer_Name == "Western Health" ~ "Western",
-      Issuer_Name == "Sharp" ~ "SHARP"
+      Issuer_Name == "Sharp" ~ "SHARP",
+      Issuer_Name == "Kaiser" ~ "Kaiser",
+      Issuer_Name == "Oscar" ~ "Oscar",
+      Issuer_Name == "Molina" ~ "Molina",
+      Issuer_Name == "Valley" ~ "Valley"
     )
   )
 

### 2020-06-09 analysis/J_demand_bs.jl

@@ -1,0 +1,64 @@
+####################################################
+### Estimate Demand Model for Covered California ###
+####################################################
+		
+##### Load Data
+
+	# Packages
+	using DataFrames
+	using StatsBase
+	using Optim
+	using Calculus
+	using Distributions
+	using Random
+	using DelimitedFiles
+	using CSV
+	using LinearAlgebra
+	using Libdl
+	
+##### Specify simulation parameters and variables
+		
+	choices = convert(Array,data[!,:choice]);
+	household_numbers = convert(Array,data[!,:household_number]);	
+			
+	# Indicator for nested logit gradient and hessian
+	I_ex_nest = zero(choices);
+	unique_hh = unique(household_numbers);
+	for id in unique_hh
+		household_ids = findall(household_numbers .== id);
+		I_ex_nest[household_ids] .= 1 - choices[household_ids[length(household_ids)]];
+	end	
+		
+##### Form Covariate Matrixbe
+
+	X = form_X_matrix(all_covariates, data, choices, uninsured_plans);
+	
+##### Estimation with Newton-Raphson
+#	min_beta = newton_nested_logit(beta_initial,X,choices,1e-8)
+
+##### Estimation with Other methods	
+	obj_nested_logit(betap) = objective_nested_logit(betap,X,choices);
+
+#	nested_logit = optimize(obj_nested_logit, g!, beta_initial, LBFGS()) ;
+	nested_logit = try
+			optimize(obj_nested_logit, beta_initial, LBFGS(); autodiff = :forward)
+		catch
+			optimize(obj_nested_logit, beta_initial, iterations=50000)
+		end
+	min_beta = Optim.minimizer(nested_logit)
+
+
+	
+##### Output Processing
+
+	# Calculate standard errors
+	probs = simulate_nested_probabilities(min_beta,X);
+	
+	# Save output
+	param_output = DataFrame();
+	param_output[:Variable] = cat(dims=1,all_covariates,"lambda");
+	param_output[:Coef] = min_beta;
+		
+		
+		
+		

### 2020-06-09 analysis/J_demand_est.jl

@@ -1,0 +1,56 @@
+####################################################
+### Estimate Demand Model for Covered California ###
+####################################################
+		
+##### Load Data
+
+	# Packages
+	using DataFrames
+	using StatsBase
+	using Optim
+	using Calculus
+	using Distributions
+	using Random
+	using DelimitedFiles
+	using CSV
+	using LinearAlgebra
+	using Libdl
+	
+##### Specify simulation parameters and variables
+	
+	choices = convert(Array,data[!,:choice]);
+	household_numbers = convert(Array,data[!,:household_number]);	
+			
+	# Indicator for nested logit gradient and hessian
+	I_ex_nest = zero(choices);
+	unique_hh = unique(household_numbers);
+	for id in unique_hh
+		household_ids = findall(household_numbers .== id);
+		I_ex_nest[household_ids] .= 1 - choices[household_ids[length(household_ids)]];
+	end	
+		
+##### Form Covariate Matrixbe
+
+	X = form_X_matrix(all_covariates, data, choices, uninsured_plans);
+	
+##### Estimation with Nelder Mead
+	
+	obj_nested_logit(betap) = objective_nested_logit(betap,X,choices);
+	nested_logit = optimize(obj_nested_logit, beta_initial, iterations=50000, show_trace=true) ;				
+#	nested_logit = optimize(obj_nested_logit, beta_initial, BFGS(); autodiff = :forward) ;
+#	nested_logit = optimize(obj_nested_logit, g!, beta_initial, LBFGS()) ;
+	min_beta = Optim.minimizer(nested_logit)
+	
+##### Output Processing
+
+	# Calculate standard errors
+	probs = simulate_nested_probabilities(min_beta,X);
+	
+	# Save output
+	param_output = DataFrame();
+	param_output[:Variable] = cat(dims=1,all_covariates,"lambda");
+	param_output[:Coef] = min_beta;
+		
+		
+		
+		

### 2020-06-09 analysis/J_demand_fnc.jl

@@ -1,0 +1,298 @@
+### Compute Logit Gradient and Hessian
+
+		# Reference: p.18 of https://cran.r-project.org/web/packages/mlogit/vignettes/mlogit.pdf
+		
+		function compute_nested_logit_gradient(betap,X,choices,probs)
+		
+			lambda = betap[length(betap)];
+			betap = betap[1:(length(betap)-1)];
+			U = X * betap;
+			
+			inside_option_probs = zero(probs);
+			ex_probs = zero(probs);
+			N_exchange = zero(probs);
+			
+			for id in unique_hh
+				household_ids = findall(household_numbers .== id);
+				
+				inside_option_prob = 1 - probs[household_ids[length(household_ids)]];
+				inside_option_probs[household_ids] .= inside_option_prob;
+				
+				ex_probs[household_ids] = probs[household_ids]/inside_option_prob;
+				ex_probs[household_ids[length(household_ids)]] = 0;
+				
+				N_exchange[household_ids] .= sum(exp.(U[household_ids[1:(length(household_ids)-1)]]/lambda)) ;
+			end
+			
+			# Gradient wrt beta
+			gradient_beta = (1/lambda) * (transpose(X) * choices) + 
+							((lambda-1)/lambda) * (transpose(X) * (ex_probs .* I_ex_nest)) - 
+							transpose(X) * probs;
+			
+			# Gradient wrt lambda (This should be a scalar!)
+			gradient_lambda = -(1/lambda^2) * (transpose(U) * choices) + 
+							transpose(choices .* (1 .- uninsured_plans)) * log.(N_exchange) + 
+							((1 - lambda)/lambda^2) * (transpose(U) * (ex_probs .* I_ex_nest)) .- 
+							transpose(choices .* inside_option_probs) * log.(N_exchange) + 
+							(1/lambda) * (transpose(U) * probs);
+		
+			return(cat(dims=1,gradient_beta,gradient_lambda))
+		end
+
+
+		function g!(G,betap)
+		
+			probs = simulate_nested_probabilities(betap,X);
+			lambda = betap[length(betap)];
+			betap = betap[1:(length(betap)-1)];
+			U = X * betap;
+			
+			inside_option_probs = zero(probs);
+			ex_probs = zero(probs);
+			N_exchange = zero(probs);
+			
+			for id in unique_hh
+				household_ids = findall(household_numbers .== id);
+				
[…]

### 2020-06-09 analysis/_ChoiceModel.R

@@ -1,0 +1,125 @@
+# Meta --------------------------------------------------------------------
+
+## Date Created:  3/4/2020
+## Date Edited:   5/12/2020
+## Description:   Create data for discrete choice model and estimate by year and 3-digit zip
+
+## Notes:         This file requires that we've already created the household data
+##                and the plan data.
+
+
+
+# Clean data --------------------------------------------------------------
+
+## Remove "flagged" households
+hh.clean <- data.hh %>% filter(flagged==0)
+data.clean <- data %>% filter(flagged==0)
+
+## Oldest person per household
+max.age <- data.ind %>%
+  group_by(household_id, year) %>%
+  summarize(oldest_member=max(AGE))
+
+## Add some variables
+hh.clean <- hh.clean %>%
+  mutate(FPL_bracket = case_when(
+    FPL <= 1.38 ~ "138orless",
+    FPL > 1.38 & FPL <= 2.50 ~ "138to250",
+    FPL > 2.50 & FPL <= 4 ~ "250to400",
+    FPL > 4 ~ "400ormore")) %>%
+  mutate(perc_18to34 = perc_18to25 + perc_26to34,
+         perc_35to54 = perc_35to44 + perc_45to54,
+         FPL_bracket=as.factor(FPL_bracket)) %>%
+  left_join(max.age, by=c("household_id","year"))
+
+  
+
+## Predict who left market
+hh.clean <- hh.clean %>%
+  add_predictions(outside_logit, "pred_oom", type="response") %>%
+  mutate(pred_oom = ifelse(is.na(plan_number_nocsr),pred_oom,NA),
+         unif_draw=runif(n(),0,1),
+         out_of_market = (pred_oom >= unif_draw)) %>%
+  filter(out_of_market == FALSE | !is.na(plan_number_nocsr))
+hh.clean <- as_tibble(hh.clean)
+  
+
+data.clean <- data.clean %>%
+  left_join(hh.clean %>% select(household_id, year, out_of_market), 
+            by=c("household_id","year")) %>%
+  filter(out_of_market == FALSE | !is.na(plan_number_nocsr))
+data.clean <- as_tibble(data.clean)
+
+
+# Form choice sets --------------------------------------------------------
+afford.threshold <- tibble(
+  cutoff = c(0.08, 0.0805, 0.0813, 0.0816, 0.0805, 0.0830),
[…]

### 2020-06-09 analysis/_ChoiceSummary.R

@@ -1,0 +1,122 @@
+# Meta --------------------------------------------------------------------
+
+## Date Created:  6/5/2020
+## Date Edited:   6/8/2020
+## Description:   Summarize results from discrete choice models
+
+
+# Average treatment effect on the treated ---------------------------------
+
+pred.purchase <- est.prob %>% ungroup() %>%
+  mutate(plan_name=str_replace(plan_name, "G.*","G"),
+         plan_name=str_replace(plan_name, "P.*","P"),
+         plan_name=str_replace(plan_name, "CAT.*","CAT"),
+         plan_name=str_replace(plan_name, "BR.*","BR"))
+
+plan.summary <- pred.purchase %>%
+  group_by(plan_name) %>%
+  summarize(obs_purchase=sum(obs_purchase, na.rm=TRUE), 
+            pred_purchase=sum(pred_purchase, na.rm=TRUE))
+
+
+## by metal 
+metal.summary <- pred.purchase %>%
+  separate(plan_name, c("insurer","metal"), sep="_") %>%
+  mutate(metal=if_else(is.na(metal),"Uninsured",metal)) %>%
+  group_by(metal) %>%
+  summarize(obs_purchase=sum(obs_purchase, na.rm=TRUE), 
+            pred_purchase=sum(pred_purchase, na.rm=TRUE)) %>%
+  ungroup() %>%
+  mutate(e_y1 = obs_purchase/sum(obs_purchase),
+         e_y0 = pred_purchase/sum(pred_purchase),
+         att = e_y1 - e_y0)
+
+## by insurer
+ins.summary <- pred.purchase %>%
+  separate(plan_name, c("insurer","metal"), sep="_") %>%
+  group_by(insurer) %>%
+  summarize(obs_purchase=sum(obs_purchase, na.rm=TRUE), 
+            pred_purchase=sum(pred_purchase, na.rm=TRUE)) %>%
+  ungroup() %>%
+  mutate(e_y1 = obs_purchase/sum(obs_purchase),
+         e_y0 = pred_purchase/sum(pred_purchase),
+         att = e_y1 - e_y0)
+
+
+
+
+# 95% confidence intervals ------------------------------------------------
+
+bs.pred$boot <- 0
+bs.pred$boot[1] <- 1
+for (i in 2:nrow(bs.pred)) {
[…]

### 2020-06-09 analysis/_DominatedChoices.R

@@ -1,0 +1,38 @@
+# Meta --------------------------------------------------------------------
+
+## Date Created:  3/4/2020
+## Date Edited:   6/5/2020
+## Description:   Simple regressions of dominated choices
+
+
+# Initial Regressions -----------------------------------------------------
+
+
+reg1 <- felm(dominated_choice ~ any_assist + lang_english + lang_spanish +
+               low_income + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
+               perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
+               perc_other + hh_single + SEP + new_enrollee 
+             | region + year + insurer | 0 | region, 
+     data=final.data)
+
+reg2 <- felm(dominated_choice ~ any_assist + lang_english + lang_spanish +
+               low_income + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
+               perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
+               perc_other + hh_single + SEP + new_enrollee
+             | household_id + year + insurer | 0 | household_id, 
+             data=final.data)
+
+reg1.b <- felm(dominated_choice ~ assist_agent + assist_other + lang_english + lang_spanish +
+                 low_income + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
+                 perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
+                 perc_other + hh_single + SEP + new_enrollee 
+               | region + year + insurer  | 0 | region, 
+               data=final.data)
+
+
+reg2.b <- felm(dominated_choice ~ assist_agent + assist_other + lang_english + lang_spanish +
+               low_income + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
+               perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
+               perc_other + hh_single + SEP + new_enrollee
+             | household_id + year + insurer | 0 | household_id, 
+             data=final.data)

### 2020-06-09 analysis/_SummaryStats.R

@@ -1,32 +1,8 @@
 # Meta --------------------------------------------------------------------
 
 ## Date Created:  10/11/2019
-## Date Edited:   3/4/2020
-## Description:   Analysis file for project
-
-
-# Analytic Datasets -----------------------------------------------------------
-final.data <- data.hh %>%
-  mutate(channel = as.factor(channel),
-         new_enrollee = is.na(previous_plan_number),
-         any_assist = (channel=="Insurance Agent" | channel=="Other Assistance"),
-         assist_agent = (channel=="Insurance Agent"),
-         assist_other = (channel=="Other Assistance"),
-         low_income = (FPL<1.5),
-         hh_single = (household_size==1),
-         hmo_ppo = (plan_network_type %in% c("HMO","PPO")),
-         bad_obs = (new_enrollee==0 & year==2014),
-         insurer = replace(insurer, 
-                           insurer %in% c("Chinese_Community","LA_Care","Western","Contra_Costa","SHARP"),
-                           "Other")) %>%
-  filter( flagged==0 & !is.na(plan_number_nocsr) & bad_obs==0 & FPL<2.0)%>%
-  select(lang_english, lang_spanish, lang_other,
-         perc_0to17, perc_18to25, perc_26to34, perc_35to44, perc_45to54,
-         perc_male, perc_asian, perc_black, perc_hispanic, perc_other, 
-         FPL, low_income, household_size, hh_single, SEP, new_enrollee, 
-         insurer, hmo_ppo, metal,
-         channel, any_assist, assist_agent, assist_other, dominated_choice, 
-         region, rating_area, year, household_id)
+## Date Edited:   6/5/2020
+## Description:   Basic summary stats
 
 
 # Summary Statistics ------------------------------------------------------

### 2020-06-09 analysis/choice_data_function.R

@@ -1,0 +1,244 @@
+# Meta --------------------------------------------------------------------
+
+## Date Created:  5/12/2020
+## Date Edited:   5/25/2020
+## Description:   Function to create choice-level datasets and save subset for future use
+
+
+# Estimation function -----------------------------------------------------
+
+choice.data.fnc <- function(t, r) {
+  
+  a.thresh <- as.numeric(afford.threshold %>% filter(year==t) %>% select(cutoff))
+  outside=tibble(
+    plan_name="Uninsured",
+    region=r,
+    Issuer_Name="Outside_Option"
+  )
+  
+  choice.set <- plan.data %>% filter(ENROLLMENT_YEAR==t, region==r) %>%
+    select(plan_name=Plan_Name2, Issuer_Name, region, PLAN_NETWORK_TYPE, metal_level, metal, 
+           Premium, MSP, HSA) %>%
+    group_by(plan_name, region) %>%
+    summarize(Issuer_Name=first(Issuer_Name),
+              PLAN_NETWORK_TYPE=first(PLAN_NETWORK_TYPE),
+              metal_level=first(metal_level),
+              metal=first(metal),
+              Premium=mean(Premium, na.rm=TRUE),
+              MSP=min(MSP, na.rm=TRUE),
+              HSA=min(HSA, na.rm=TRUE)) %>%
+    ungroup() %>%
+    mutate(plan_name=as.character(plan_name)) %>%
+    bind_rows(outside)
+  
+  
+  full.choice.data <- hh.clean %>% filter(year==t, region==r) %>%
+    select(household_id, year, zip3, FPL, subsidized_members, hh_region=region, hh_rating=rating_factor,
+           hh_plan_number = plan_number_nocsr, hh_plan_id=plan_id, penalty, hh_insurer=insurer,
+           hh_plan_name = plan_name, oldest_member, cheapest_premium, subsidy, poverty_threshold) %>%
+    full_join(choice.set, by=c("hh_region"="region")) 
+  
+  
+  ## Remove plans that are not available for specific households.
+  ## 1. ACS eligible households not eligible for "unenhanced silver plans"
+  clean.choice.data <- full.choice.data %>%
+    mutate(acs_eligible73 = ifelse(FPL>2 & FPL<=2.5 & subsidized_members>0,1,0),
[…]

### 2020-06-09 analysis/choice_est_bs_function.R

@@ -1,0 +1,102 @@
+# Meta --------------------------------------------------------------------
+
+## Date Created:  5/12/2020
+## Date Edited:   5/20/2020
+## Description:   Function to estimate standard errors using bootstrap
+
+
+# Estimation function -----------------------------------------------------
+
+dchoice.bs <- function(time, area) {
+  
+  for (t in time) {
+    
+    a.thresh <- as.numeric(afford.threshold %>% filter(year==t) %>% select(cutoff))
+    
+    step=0
+    for (r in area) {
+      step=step+1
+    
+      julia.data <- get(paste0("julia.data.",r,".",t))
+      julia.oos <- get(paste0("julia.oos.",r,".",t))
+
+      # Select bootstrap sample (within area and year)
+      unique.hh <- julia.data %>%
+        group_by(household_number) %>%
+        mutate(hh_count=seq(n())) %>%
+        filter(hh_count==1) %>%
+        select(household_number) %>% ungroup()
+      sample.hh <- sample_n(unique.hh, size=nrow(unique.hh), replace=TRUE)
+      julia.data <- julia.data %>%
+        inner_join(sample.hh, by=c("household_number"))
+      
+      
+      # send sample to Julia and estimate with original starting values  
+      julia_assign("data",julia.data)
+      julia_assign("data_oos",julia.oos)
+      
+      all_covars <- as.list(bs.starting %>% filter(region==r, year==t, value!="lambda") %>% select(value))$value
+      beta_initial <- as.list(bs.starting %>% filter(region==r, year==t) %>% select(value1))$value1
+      
+      jpath=getwd()
+      unins.plans <- as.array(julia.data$uninsured_plan)
+      julia_assign("uninsured_plans",unins.plans)
+      julia_assign("jpath",jpath)
+      julia_assign("all_covariates",all_covars)
+      julia_assign("beta_initial",beta_initial)
+      
+      ## Estimate model in Julia and store results
+      julia_source('analysis/J_demand_bs.jl')
+      julia.out <- julia_eval('param_output')
+      coef.name <- as_tibble(julia.out$Variable)
+      coef.est <- as_tibble(julia.out$Coef)
+      coef.vals <- bind_cols(coef.name, coef.est) %>% mutate(region=r)
+      
+      ## counterfactual estimates
+      julia_assign("beta_hat",julia.out$Coef)
[…]

### 2020-06-09 analysis/choice_est_function.R

@@ -1,0 +1,170 @@
+# Meta --------------------------------------------------------------------
+
+## Date Created:  5/12/2020
+## Date Edited:   5/25/2020
+## Description:   Function to estimate demand, calls Julia within function and reports
+##                mean predicted enrollments per plan as well as coefficient estimates
+
+
+# Estimation function -----------------------------------------------------
+
+dchoice.est <- function(time, area) {
+  
+  for (t in time) {
+    
+    a.thresh <- as.numeric(afford.threshold %>% filter(year==t) %>% select(cutoff))
+    
+    step=0
+    for (r in area) {
+      step=step+1
+      
+      julia.data <- get(paste0("julia.data.",r,".",t))
+      julia.oos <- get(paste0("julia.oos.",r,".",t))
+      
+      julia_assign("data",julia.data)
+      julia_assign("data_oos",julia.oos)
+      
+        
+      ## Terms for estimation (passed to Julia)
+      all_covars=c("intercept","premium", "AV", "HMO", "HSA", "silver")
+      beta_initial = array(0,dim=length(all_covars)+1)
+        
+      ins.offer <- c(0,0,0,0)
+      cml.share <- 0
+      tot.choice <- sum(julia.data$choice==1)
+      ins.offer[1] <- sum(julia.data$Anthem==1 & julia.data$choice==1)/tot.choice
+      ins.offer[2] <- sum(julia.data$Blue_Shield==1 & julia.data$choice==1)/tot.choice
+      ins.offer[3] <- sum(julia.data$Kaiser==1 & julia.data$choice==1)/tot.choice
+      ins.offer[4] <- sum(julia.data$Health_Net==1 & julia.data$choice==1)/tot.choice
+        
+      cml.share <- ins.offer[1]
+      if (ins.offer[1]>.1 & cml.share<.9) {
+        all_covars=c(all_covars, "Anthem")
+        beta_initial=c(beta_initial,0)
+      }
+      cml.share <- cml.share+ins.offer[2]
+      if (ins.offer[2]>.1 & cml.share<.9) {
+        all_covars=c(all_covars, "Blue_Shield")
+        beta_initial=c(beta_initial,0)
+      }
+      cml.share <- cml.share+ins.offer[3]
+      if (ins.offer[3]>.1 & cml.share<.9) {
+        all_covars=c(all_covars, "Kaiser")
+        beta_initial=c(beta_initial,0)
+      }
[…]

### 2020-06-09 analysis/create.summary.stats.R

@@ -1,284 +1,0 @@
-# NOTE: you should use cleaned up data eventually here
-
-# Load Data
-setwd("C:/Users/esaltzm/OneDrive - Emory University/Google Drive/Emory/Research/Navigators/Data")  # Office computer directory
-data <- get(load("ca_enrollment_data_AUG022019")) # individual-level data
-households <- get(load("ca_household_data_AUG022019")) # household-level data
-plan_data <- read.csv("ca_plan_data2.csv") # Covered California plan data
-zip3_choices <- read.csv("zip3_choices2.csv",row.names = 1) # choice set by 3 digit zip and rating area
-product_definitions <- read.csv("product_definitions.csv",row.names = 1) # definitions of column names in zip3_choices
-library(plyr)
-
-# We can drop all uninsured records for this analysis
-data <- data[!is.na(data$plan_id),]
-
-plan_data$Issuer_Name <- as.character(plan_data$Issuer_Name)
-plan_data[plan_data$Issuer_Name == "Anthem Blue Cross","Issuer_Name"] <- "Anthem"
-plan_data[plan_data$Issuer_Name == "Blue Shield","Issuer_Name"] <- "Blue_Shield"
-plan_data[plan_data$Issuer_Name == "Chinese Community","Issuer_Name"] <- "Chinese_Community"
-plan_data[plan_data$Issuer_Name == "Contra Costa Health Plan","Issuer_Name"] <- "Contra_Costa"
-plan_data[plan_data$Issuer_Name == "Health Net","Issuer_Name"] <- "Health_Net"
-plan_data[plan_data$Issuer_Name == "LA Care","Issuer_Name"] <- "LA_Care"
-plan_data[plan_data$Issuer_Name == "UnitedHealthcare","Issuer_Name"] <- "United"
-plan_data[plan_data$Issuer_Name == "Western Health","Issuer_Name"] <- "Western"
-plan_data[plan_data$Issuer_Name == "Sharp","Issuer_Name"] <- "SHARP"
-	
-# Create Age Group Variable
-
-	data$age_group <- NA
-	data[data$AGE < 18 & !is.na(data$AGE),"age_group"] <- "0to17"
-	data[data$AGE >= 18 & data$AGE < 26 & !is.na(data$AGE),"age_group"] <- "18to25"
-	data[data$AGE >= 26 & data$AGE < 35 & !is.na(data$AGE),"age_group"] <- "26to34"
[…]

### 2020-06-11 _Abstract_SHESG_202006.Rmd
Update _Abstract_SHESG_202006.Rmd
Evan's updates to Ian's original abstract

@@
 ### Background:
-Health insurance markets are unique in many respects, not least of which is the increasing complexity of choosing an optimal health insurance plan.
-Such complexity has been well-documented in studies of health insurance choice in the Medicare Advantage market [@abaluck2011; @ketcham2012; @gruber2017], among others.
-One way to reduce the burden of this complexity is to provide professional decision support through private insurance agents or public assistance programs, both of which are available in the California health insurance exchanges created under the Affordable Care Act (ACA).
-The presence of private insurance brokers also introduces the potential for insurers to steer patients to insurance products indirectly through the brokers.
-In this paper, we examine the role of decision assistance on health insurance plan choice, the effects of commissions on insurer steering, and the broad implications of decision assistance for consumer welfare.
+In some markets such as real estate, used automobiles, and insurance, consumers face significant cognitive challenges that may require the assistance of an agent or intermediary.
+How agents influence consumer decisions and firm incentives affect agents' advice to consumers have important implications for the efficiency of these markets.
+In this paper, we study the welfare impact of agent decision assistance and firm steering of agents in health insurance.
+The complexity of choosing an optimal health insurance plan has been well-documented in studies of health insurance choice in the Medicare Advantage market [@abaluck2011; @ketcham2012; @gruber2017], among others.
+We expand on this literature by analyzing the effect of private insurance agents and publicly-financed assistors (known as navigators) on health insurance plan choices.
+We then examine the extent to which insurance firms steer consumer choices through agent commissions.
+We quantify the welfare impact of decision assistance and simulate the impact of alternative decision support policy regimes.
 
 ### Data:
-Our final dataset consists of `r format(tot.enroll, big.mark=",")` household/year observations from the California health insurance exhanges from `r first.year` to `r last.year`.
-Our data include a variety of household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any).
-From these data, we can identify each household's set of possible health insurance plans, and we employ premium and cost sharing subsidy formulas to calculate health insurance costs for each possible plan for each household.
+We obtain consumer-level enrollment data from the California Affordable Care Act (ACA) exchange.
+Our final data consist of (is this right?
+seems too low) `r format(tot.enroll, big.mark=",")` household-year observations from `r first.year` to `r last.year`.
+The data include a variety of household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any).
+Using these data, we can precisely identify each household's choice set, the premium paid for each plan in the choice set, and any premium and cost sharing subsidies for which the household is eligible.
 
-### Demand estimation:
-We model health insurance purchasing with a nested logit discrete choice model, as in @saltzman2019, and we derive estimates of the causal effect of decision assistnce by embedding this discrete choice model into a standard potential outcomes framework.
+### Model and Estimation:
+To study the effect of choice assistance and firm steering, we use our data to estimate a structural model of the California ACA exchange.
+Our model endogenizes consumer plan choices,  premiums, and commissions.
+We estimate demand for health insurance using a nested logit discrete choice model, as in @saltzman2019, and derive estimates of the causal effect of decision assistance by embedding this discrete choice model into a standard potential outcomes framework.
 This analysis proceeds in three steps: 1) we estimate utility parameters on the subset of individuals without decision assistance; 2) we incorporate these parameters into the closed-form nested logit choice probabilities to estimate choices for the subset of "treated" individuals (i.e., those with some form of decision assistance); and 3) we take the difference between observed and predicted values to form our estimate of the average treatment effect on the treated.
@@
 
-Our nested logit demand estimation reveals economically large and statistically significant effects of decision assistance on plan choice.
-For example, we estimate that individuals are `r round(as.numeric(metal.final[5,6]),2)*100`% more likely to select a silver plan when using some form of decision assistance.
-Since silver plans are the dominant plan for many choice sets, this finding suggests that decision assistance may improve plan choice.
+We also assess whether choice assistance reduces the probability that consumers choose a "dominated plan." Consumers with incomes below 250% of the federal povery level (FPL) can receive cost sharing subsidies (CSRs) if they purchase a silver tier plan.
+CSRs have the effect of increasing the actuarial value (AV) of the silver plan.
+For consumers with incomes below 150% of FPL, the AV of the silver plan exceeds the AV of more expensive plans from the gold and platinum tiers, and hence gold and platinum plans are dominated for this income group.
+We estimate the effect of decision assistance on making a dominated choice with a linear probability model, allowing for year, insurer, and region fixed effects.
 
-### Dominated choices:
-As a complementary empirical analysis, we identify specific instances in which the observed plan choice is dominated by some other plan in an individual's choice set, and we estimate the effects of decision assistance on the probability of making such a choice.
-For example, Gold and Platinum tier plans are dominated for any household that is eligible for cost-sharing subsidies and with incomes below 150% of the federal poverty level.
-We estimate the effect of decision assistance on dominated choices with a linear probability model, allowing for year, insurer, and region fixed effects.
-Analogous to our nested logit analysis, these results suggest that individuals with decision assistance are `r abs(round(reg1$coeff[1],4))*100` percentage points less likely to make a dominated choice.
+### Results:
+
+Our demand estimates reveal economically large and statistically significant effects of decision assistance on plan choice.
+We estimate that individuals are `r round(as.numeric(metal.final[5,6]),2)*100`% more likely to select a silver plan when using some form of decision assistance even when controlling for CSR eligibility.
+Individuals with decision assistance are `r abs(round(reg1$coeff[1],4))*100` percentage points less likely to make a dominated choice.
 On a base of `r round(mean.dom.choice,3)*100`%, this reflects a `r abs(round(reg1$coeff[1]/mean.dom.choice,2))*100`% decrease in the probability of making a dominated choice.
+These results suggest that assistors can help consumers avoid making poor health insurance decisions.
+We also find that firms, particularly the largest, have considerable ability to steer consumers' decisions using agent commissions.
+For small firms, a $1 increase in the plan commission has  the same effect as a $2 decrease in the plan premium on the probability of the plan being chosen.
+For large firms, a $1 increase in the plan commission has the same effect as a $3.50 increase in the plan premium on the probability of the plan being chosen.
 
-### Steering and welfare:
-We then supplement our nested logit demand analysis with data on commission payments to insurance brokers, and we incorporate a suppyl-side model of insurer commissions.
-Our strutural framework allows us to examine welfare implications of decision assistance and steering.
-Within this framework, we study several counterfactuals designed to approxmiate a variety of policy proposals, including flat commissions, banning of private insurance brokers in favor of public assistance only, and outright removal of all forms of decision assitance (e.g., defunding decision assistance entirely).
-Preliminary results suggest large welfare gains from removal of commission payments or restrictions to a flat commission schedule.
+Our strutural model allows us to simulate the welfare implications of decision assistance and firm steering.
+We study several counterfactuals designed to approximate a variety of policy proposals, including uniform commissions across firms, the banning of private insurance agents in favor of publicly-funded assistance, and removal of all forms of decision assistance (e.g., defunding decision assistance entirely).
+Preliminary results suggest large welfare gains from removal of commission payments or restrictions to a uniform commission schedule.
 
@@
 Our results provide strong evidence that decision assistance has a significant and economically meaningful effect on health insurance plan choice.
-Decision assistance in general tends to improve consumer welfare, increasing the probability that enrollees select a silver plan and dramatically decreasing the probability of making a dominated choice.
-Gains to consumer welfare may be offset somewhat by insurer steering.
+Decision assistance in general tends to improve consumer welfare, increasing the probability that enrollees select a silver plan and decreasing the probability of making a dominated choice.
+Gains to social welfare are somewhat offset by insurer steering.
+Alternative agent compensation schemes can provide welfare gains.
 
 In addition to continued structural work on commissions and steering, future work will exploit the Trump administration's removal of cost-sharing subisidies from the exchanges in 2018 and the subsequent response from insurers to increase premiums on their silver plans ("silver loading").
-This response significantly changed the prevalence of dominated choices in each household's choice set, and in this way, the removal of the cost-sharing subsidies offers an exogenous change to the set of dominated plans available to each household.
+This response significantly changed the prevalence of dominated choices in each household's choice set provides an exogenous change to the set of dominated plans available to each household.
 

### 2020-06-12 _Abstract_SHESG_202006.Rmd
Finalize abstract for SHESG

@@
 In some markets such as real estate, used automobiles, and insurance, consumers face significant cognitive challenges that may require the assistance of an agent or intermediary.
-How agents influence consumer decisions and firm incentives affect agents' advice to consumers have important implications for the efficiency of these markets.
-In this paper, we study the welfare impact of agent decision assistance and firm steering of agents in health insurance.
+The influence of agents on consumer decisions, and the firm's influence on the behaviors of its agents, have important implications for the efficiency of these markets.
+In this paper, we study the welfare effects of decision assistance and firm steering in health insurance.
 The complexity of choosing an optimal health insurance plan has been well-documented in studies of health insurance choice in the Medicare Advantage market [@abaluck2011; @ketcham2012; @gruber2017], among others.
-We expand on this literature by analyzing the effect of private insurance agents and publicly-financed assistors (known as navigators) on health insurance plan choices.
+We expand on this literature by analyzing the effect of private insurance agents and publicly-financed navigators on health insurance plan choices.
 We then examine the extent to which insurance firms steer consumer choices through agent commissions.
-We quantify the welfare impact of decision assistance and simulate the impact of alternative decision support policy regimes.
+We quantify the welfare impact of decision assistance and simulate the effects of alternative commission policies.
 
@@
 We obtain consumer-level enrollment data from the California Affordable Care Act (ACA) exchange.
-Our final data consist of (is this right?
-seems too low) `r format(tot.enroll, big.mark=",")` household-year observations from `r first.year` to `r last.year`.
+Our final data consist of `r format(tot.enroll, big.mark=",")` household-year observations from `r first.year` to `r last.year`.
 The data include a variety of household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any).
@@
 
-### Model and Estimation:
-To study the effect of choice assistance and firm steering, we use our data to estimate a structural model of the California ACA exchange.
-Our model endogenizes consumer plan choices,  premiums, and commissions.
-We estimate demand for health insurance using a nested logit discrete choice model, as in @saltzman2019, and derive estimates of the causal effect of decision assistance by embedding this discrete choice model into a standard potential outcomes framework.
+### Empirical approach:
+In our main empirical analysis, we estimate a structural model of the California ACA exchange.
+Our model endogenizes consumer plan choices, premiums, and commissions, which allows us to simulate the welfare implications of decision assistance and firm steering.
+We study several counterfactuals designed to approximate a variety of policy proposals, including uniform commissions across firms, the banning of private insurance agents in favor of publicly-funded assistance, and the removal of all forms of decision assistance (e.g., defunding decision assistance entirely).
+
+Before estimating the full structural model, we first establish a causal relationship between decision assistance and insurance choice by embedding a nested logit discrete choice model into a standard potential outcomes framework.
 This analysis proceeds in three steps: 1) we estimate utility parameters on the subset of individuals without decision assistance; 2) we incorporate these parameters into the closed-form nested logit choice probabilities to estimate choices for the subset of "treated" individuals (i.e., those with some form of decision assistance); and 3) we take the difference between observed and predicted values to form our estimate of the average treatment effect on the treated.
@@
 
-We also assess whether choice assistance reduces the probability that consumers choose a "dominated plan." Consumers with incomes below 250% of the federal povery level (FPL) can receive cost sharing subsidies (CSRs) if they purchase a silver tier plan.
-CSRs have the effect of increasing the actuarial value (AV) of the silver plan.
-For consumers with incomes below 150% of FPL, the AV of the silver plan exceeds the AV of more expensive plans from the gold and platinum tiers, and hence gold and platinum plans are dominated for this income group.
+As a complementary analysis, we also examine whether choice assistance reduces the probability that consumers choose a "dominated plan".
+Consumers with incomes below 250% of the federal povery level (FPL) can receive cost sharing subsidies if they purchase a silver tier plan.
+The subsidies have the effect of increasing the actuarial value of the silver plan.
+For consumers with incomes below 150% of FPL, the actuarial value of the silver plan exceeds that of more expensive plans from the gold and platinum tiers, and hence gold and platinum plans are dominated for this income group.
 We estimate the effect of decision assistance on making a dominated choice with a linear probability model, allowing for year, insurer, and region fixed effects.
@@
 ### Results:
+Our demand estimates reveal economically large and statistically significant effects of decision assistance on plan choice.
+We estimate that individuals are `r round(as.numeric(metal.final[5,6]),2)*100`% more likely to select a silver plan when using some form of decision assistance even when controlling for subsidies.
+We also find that individuals with decision assistance are `r abs(round(reg1$coeff[1],4))*100` percentage points less likely to make a dominated choice.
+On a base of `r round(mean.dom.choice,3)*100`%, this reflects a `r abs(round(reg1$coeff[1]/mean.dom.choice,2))*100`% decrease in the probability of making a dominated choice.
+These results suggest that decision assistance can help consumers avoid making poor health insurance decisions.
 
-Our demand estimates reveal economically large and statistically significant effects of decision assistance on plan choice.
-We estimate that individuals are `r round(as.numeric(metal.final[5,6]),2)*100`% more likely to select a silver plan when using some form of decision assistance even when controlling for CSR eligibility.
-Individuals with decision assistance are `r abs(round(reg1$coeff[1],4))*100` percentage points less likely to make a dominated choice.
-On a base of `r round(mean.dom.choice,3)*100`%, this reflects a `r abs(round(reg1$coeff[1]/mean.dom.choice,2))*100`% decrease in the probability of making a dominated choice.
-These results suggest that assistors can help consumers avoid making poor health insurance decisions.
-We also find that firms, particularly the largest, have considerable ability to steer consumers' decisions using agent commissions.
-For small firms, a $1 increase in the plan commission has  the same effect as a $2 decrease in the plan premium on the probability of the plan being chosen.
-For large firms, a $1 increase in the plan commission has the same effect as a $3.50 increase in the plan premium on the probability of the plan being chosen.
-
-Our strutural model allows us to simulate the welfare implications of decision assistance and firm steering.
-We study several counterfactuals designed to approximate a variety of policy proposals, including uniform commissions across firms, the banning of private insurance agents in favor of publicly-funded assistance, and removal of all forms of decision assistance (e.g., defunding decision assistance entirely).
+Turning to our steering analysis, we find that firms have considerable ability to steer consumers' decisions using agent commissions.
+For small firms, a \$1 increase in the plan commission has the same effect as a \$2 decrease in the plan premium on the probability of the plan being chosen.
+The effect is more pronounced for larger insurers, where a \$1 increase in the plan commission is equivalent to a \$3.50 decrease in the plan premium.
 Preliminary results suggest large welfare gains from removal of commission payments or restrictions to a uniform commission schedule.

### 2020-06-12 _Abstract_SHESG_202006.tex
Finalize abstract for SHESG

@@
 
-Health insurance markets are unique in many respects, not least of which is the increasing complexity of choosing an optimal health insurance plan.
-Such complexity has been well-documented in studies of health insurance choice in the Medicare Advantage market (Abaluck and Gruber 2011; Ketcham et al.
+In some markets such as real estate, used automobiles, and insurance, consumers face significant cognitive challenges that may require the assistance of an agent or intermediary.
+The influence of agents on consumer decisions, and the firm's influence on the behaviors of its agents, have important implications for the efficiency of these markets.
+In this paper, we study the welfare effects of decision assistance and firm steering in health insurance.
+The complexity of choosing an optimal health insurance plan has been well-documented in studies of health insurance choice in the Medicare Advantage market (Abaluck and Gruber 2011; Ketcham et al.
 2012; Gruber 2017), among others.
-One way to reduce the burden of this complexity is to provide professional decision support through private insurance agents or public assistance programs, both of which are available in the California health insurance exchanges created under the Affordable Care Act (ACA).
-The presence of private insurance brokers also introduces the potential for insurers to steer patients to insurance products indirectly through the brokers.
-In this paper, we examine the role of decision assistance on health insurance plan choice, the effects of commissions on insurer steering, and the broad implications of decision assistance for consumer welfare.
+We expand on this literature by analyzing the effect of private insurance agents and publicly-financed navigators on health insurance plan choices.
+We then examine the extent to which insurance firms steer consumer choices through agent commissions.
+We quantify the welfare impact of decision assistance and simulate the effects of alternative commission policies.
 
@@
 
-Our final dataset consists of 3,212,732 household/year observations from the California health insurance exhanges from 2014 to 2019.
-Our data include a variety of household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any).
-From these data, we can identify each household's set of possible health insurance plans, and we employ premium and cost sharing subsidy formulas to calculate health insurance costs for each possible plan for each household.
+We obtain consumer-level enrollment data from the California Affordable Care Act (ACA) exchange.
+Our final data consist of 3,212,732 household-year observations from 2014 to 2019.
+The data include a variety of household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any).
+Using these data, we can precisely identify each household's choice set, the premium paid for each plan in the choice set, and any premium and cost sharing subsidies for which the household is eligible.
 
-\hypertarget{demand-estimation}{%
-\subsubsection{Demand estimation:}\label{demand-estimation}}
+\hypertarget{empirical-approach}{%
+\subsubsection{Empirical approach:}\label{empirical-approach}}
 
-We model health insurance purchasing with a nested logit discrete choice model, as in Saltzman (2019), and we derive estimates of the causal effect of decision assistnce by embedding this discrete choice model into a standard potential outcomes framework.
+In our main empirical analysis, we estimate a structural model of the California ACA exchange.
+Our model endogenizes consumer plan choices, premiums, and commissions, which allows us to simulate the welfare implications of decision assistance and firm steering.
+We study several counterfactuals designed to approximate a variety of policy proposals, including uniform commissions across firms, the banning of private insurance agents in favor of publicly-funded assistance, and the removal of all forms of decision assistance (e.g., defunding decision assistance entirely).
+
+Before estimating the full structural model, we first establish a causal relationship between decision assistance and insurance choice by embedding a nested logit discrete choice model into a standard potential outcomes framework.
 This analysis proceeds in three steps: 1) we estimate utility parameters on the subset of individuals without decision assistance; 2) we incorporate these parameters into the closed-form nested logit choice probabilities to estimate choices for the subset of ``treated'' individuals (i.e., those with some form of decision assistance); and 3) we take the difference between observed and predicted values to form our estimate of the average treatment effect on the treated.
@@
 
-Our nested logit demand estimation reveals economically large and statistically significant effects of decision assistance on plan choice.
-For example, we estimate that individuals are 14\% more likely to select a silver plan when using some form of decision assistance.
-Since silver plans are the dominant plan for many choice sets, this finding suggests that decision assistance may improve plan choice.
+As a complementary analysis, we also examine whether choice assistance reduces the probability that consumers choose a ``dominated plan''.
+Consumers with incomes below 250\% of the federal povery level (FPL) can receive cost sharing subsidies if they purchase a silver tier plan.
+The subsidies have the effect of increasing the actuarial value of the silver plan.
+For consumers with incomes below 150\% of FPL, the actuarial value of the silver plan exceeds that of more expensive plans from the gold and platinum tiers, and hence gold and platinum plans are dominated for this income group.
+We estimate the effect of decision assistance on making a dominated choice with a linear probability model, allowing for year, insurer, and region fixed effects.
 
-\hypertarget{dominated-choices}{%
-\subsubsection{Dominated choices:}\label{dominated-choices}}
+\hypertarget{results}{%
+\subsubsection{Results:}\label{results}}
 
-As a complementary empirical analysis, we identify specific instances in which the observed plan choice is dominated by some other plan in an individual's choice set, and we estimate the effects of decision assistance on the probability of making such a choice.
-For example, Gold and Platinum tier plans are dominated for any household that is eligible for cost-sharing subsidies and with incomes below 150\% of the federal poverty level.
-We estimate the effect of decision assistance on dominated choices with a linear probability model, allowing for year, insurer, and region fixed effects.
-Analogous to our nested logit analysis, these results suggest that individuals with decision assistance are 1.4 percentage points less likely to make a dominated choice.
+Our demand estimates reveal economically large and statistically significant effects of decision assistance on plan choice.
+We estimate that individuals are 14\% more likely to select a silver plan when using some form of decision assistance even when controlling for subsidies.
+We also find that individuals with decision assistance are 1.4 percentage points less likely to make a dominated choice.
 On a base of 2.8\%, this reflects a 50\% decrease in the probability of making a dominated choice.
+These results suggest that decision assistance can help consumers avoid making poor health insurance decisions.
 
-\hypertarget{steering-and-welfare}{%
-\subsubsection{Steering and welfare:}\label{steering-and-welfare}}
-
-We then supplement our nested logit demand analysis with data on commission payments to insurance brokers, and we incorporate a suppyl-side model of insurer commissions.
-Our strutural framework allows us to examine welfare implications of decision assistance and steering.
-Within this framework, we study several counterfactuals designed to approxmiate a variety of policy proposals, including flat commissions, banning of private insurance brokers in favor of public assistance only, and outright removal of all forms of decision assitance (e.g., defunding decision assistance entirely).
-Preliminary results suggest large welfare gains from removal of commission payments or restrictions to a flat commission schedule.
+Turning to our steering analysis, we find that firms have considerable ability to steer consumers' decisions using agent commissions.
+For small firms, a \$1 increase in the plan commission has the same effect as a \$2 decrease in the plan premium on the probability of the plan being chosen.
+The effect is more pronounced for larger insurers, where a \$1 increase in the plan commission is equivalent to a \$3.50 decrease in the plan premium.
+Preliminary results suggest large welfare gains from removal of commission payments or restrictions to a uniform commission schedule.
 
@@
 Our results provide strong evidence that decision assistance has a significant and economically meaningful effect on health insurance plan choice.
-Decision assistance in general tends to improve consumer welfare, increasing the probability that enrollees select a silver plan and dramatically decreasing the probability of making a dominated choice.
-Gains to consumer welfare may be offset somewhat by insurer steering.
+Decision assistance in general tends to improve consumer welfare, increasing the probability that enrollees select a silver plan and decreasing the probability of making a dominated choice.
+Gains to social welfare are somewhat offset by insurer steering.
+Alternative agent compensation schemes can provide welfare gains.
 
 In addition to continued structural work on commissions and steering, future work will exploit the Trump administration's removal of cost-sharing subisidies from the exchanges in 2018 and the subsequent response from insurers to increase premiums on their silver plans (``silver loading'').
-This response significantly changed the prevalence of dominated choices in each household's choice set, and in this way, the removal of the cost-sharing subsidies offers an exogenous change to the set of dominated plans available to each household.
+This response significantly changed the prevalence of dominated choices in each household's choice set provides an exogenous change to the set of dominated plans available to each household.
 
@@
 ``Sinking, Swimming, or Learning to Swim in Medicare Part d.'' \emph{American Economic Review} 102 (6): 2639--73.
-
-\leavevmode\hypertarget{ref-saltzman2019}{}%
-Saltzman, Evan. 2019. ``Demand for Health Insurance: Evidence from the California and Washington Aca Exchanges.'' \emph{Journal of Health Economics} 63: 197--222.
 \end{cslreferences}

### 2020-09-02 Paper.Rmd
Add paper to github

--- 2019-11-07 _Abstract_ASHEcon_201910.Rmd
@@
 author: Ian McCarthy & Evan Saltzman
-date: October 2019
+date: '`r format(Sys.Date(), "%B %d, %Y")`'
 geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
@@
 output: 
-  pdf_document:
+  pdf_document2:
     keep_tex: TRUE
-bibliography: 'C:/Users/immccar/CloudStation/Professional/Bibliography/BibTeX_Library.bib'
+    toc: FALSE
+bibliography: 'BibTeX_Library.bib'
 ---
@@
                lfe)
+library(googledrive)
+drive_download("Bibliography/BibTeX_Library.bib", overwrite=TRUE, path='BibTeX_Library.bib')
 ```
@@
 ```
-### Background:
+# Introduction
 Health insurance markets are unique in many respects, not least of which is the increasing complexity of choosing an optimal health insurance plan.
@@
 
-### Data:
+# Background and Motivation
+
+# Data
 Our final dataset consists of `r format(tot.enroll, big.mark=",")` household/year observations from the California health insurance exhanges from `r first.year` to `r last.year`.
 Our data include a variety of household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any).
-From these data, we can identify each household's set of possible health insurance plans, and we employ premium and cost sharing subsidy formulas to calculate health insurance costs for each possible plan for each household.
+From these data, we can identify each household's set of possible health insurance plans, and we employ premium and cost sharing subsidy formulas to calculate health insurance costs for each possible plan for each household
 
-### Methods:
-We first estimate overall demand for health insurance using a nested logit discrete choice model, as in @saltzman2019.
-We then identify specific instances in which the observed plan choice is dominated by some other plan in an individual's choice set.
+# Methods
+Our overarching goal is to estimate the effect of decision assistance on health insurance decisions; however, there are perhaps many ways of measuring "health insurance decisions".
+One approach is to estimate demand for health insurance in a traditional discrete choice framework.
+This would allow us to quantify individuals' willingness to pay for decision assistance as well as the effect of decision assistance on choice probabilities.
+Another approach is to focus specifically on "dominated choices", which are relatively clearly defined and observable in our empirical context.
+This latter approach lacks the richness of the discrete choice demand framework but benefits from a focus on a specific outcome of obvious policy and welfare relevance.
+We consider both approaches in our analysis, as detailed in the remainder of this section.
+
+## Discrete Choice Framework
+We model health insurance purchasing with a nested logit discrete choice model, as in @saltzman2019, and we derive estimates of the effect of decision assistnce by embedding this discrete choice model into a standard potential outcomes framework.
+
+For our discrete choice model, we assume that household $i$ chooses the plan $j$ that maximizes their utility,
+\begin{equation}
+u_{ij} = \alpha_{i}p_{ij} + \beta x_{j} + \gamma d_{i} + \xi_{j} + \varepsilon_{ij}, (\#eq:utility)
+\end{equation}
+where $p_{ij}$ denotes the premium for plan $j$, $x_{j}$ denotes a vector of product characteristics, $d_{i}$ denotes a vector of household characteristics, $\xi_{j}$ captures unobserved product characteristics, and $\varepsilon_{ij}$ is an error term assumed to follow a type I extreme value distribution.
+We allow for heterogenities in price elasticities across households by parameterizing $\alpha_{i}$ in Equation \@ref(eq:utility), $$\alpha_{i} = \alpha + \theta d_{i}.$$ In our estimation, this amounts to including a full set of interactions between $d_{i}$ and $p_{ij}$.
+
+## Dominated Choices
+As a complementary empirical analysis, we identify specific instances in which the observed plan choice is dominated by some other plan in an individual's choice set, and we estimate the effects of decision assistance on the probability of making such a choice.
 For example, Gold and Platinum tier plans are dominated for any household that is eligible for cost-sharing subsidies and with incomes below 150% of the federal poverty level.
@@
 
-### Results:
+# Results
 Our nested logit models establish strong evidence that decision assistance matters for insurance choice.
@@
 
-### Discussion:
+# Conclusion
 Our current results provide strong evidence that decision assistance has a significant and economically meaningful effect on health insurance plan choice.

### 2020-09-02 Paper.tex
Add paper to github

--- 2019-10-28 _Abstract_ASHEcon_201910.tex
@@
-\documentclass[12pt,]{article}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  12pt,
+]{article}
 \usepackage{lmodern}
@@
 \usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
   \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
-\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
-\usepackage{hyperref}
-\hypersetup{unicode=true,
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
   pdftitle={Decision Support and Health Insurance Choice},
   pdfauthor={Ian McCarthy \& Evan Saltzman},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{graphicx,grffile}
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
+\usepackage{longtable,booktabs}
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
 \makeatletter
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-%%% Change title format to be more compact
-\usepackage{titling}
-
-% Create subtitle command for use in maketitle
-\providecommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
-
-\setlength{\droptitle}{-2em}
-
-  \title{Decision Support and Health Insurance Choice}
-    \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
-    \author{Ian McCarthy \& Evan Saltzman}
-    \preauthor{\centering\large\emph}
-  \postauthor{\par}
-      \predate{\centering\large\emph}
-  \postdate{\par}
-    \date{October 2019}
-
+\setcounter{secnumdepth}{5}
 \usepackage{setspace}
@@
 \titlespacing{\subsubsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newenvironment{cslreferences}%
+  {\setlength{\parindent}{0pt}%
+  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
+  {\par}
+
+\title{Decision Support and Health Insurance Choice}
+\author{Ian McCarthy \& Evan Saltzman}
+\date{April 30, 2020}
 
@@
 
-\hypertarget{background}{%
-\subsubsection{Background:}\label{background}}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-Health insurance markets are unique in many respects, not least of which
-is the increasing complexity of choosing an optimal health insurance
-plan. Such complexity has been well-documented in studies of health
-insurance choice in the Medicare Advantage market (Abaluck and Gruber
-2011; Ketcham et al. 2012; Gruber 2017). One way to reduce the burden of
-this complexity is to provide professional decision support through
-private insurance agents or public assistance programs, both of which
-are available in the California health insurance exchanges created under
-the Affordable Care Act (ACA). In this paper, we examine the role of
-this decision assistance on health insurance plan choice and its
-implications for consumer welfare.
+Health insurance markets are unique in many respects, not least of which is the increasing complexity of choosing an optimal health insurance plan.
+Such complexity has been well-documented in studies of health insurance choice in the Medicare Advantage market (Abaluck and Gruber 2011; Ketcham et al.
+2012; Gruber 2017).
+One way to reduce the burden of this complexity is to provide professional decision support through private insurance agents or public assistance programs, both of which are available in the California health insurance exchanges created under the Affordable Care Act (ACA).
+In this paper, we examine the role of this decision assistance on health insurance plan choice and its implications for consumer welfare.
+
+\hypertarget{background-and-motivation}{%
+\section{Background and Motivation}\label{background-and-motivation}}
 
 \hypertarget{data}{%
-\subsubsection{Data:}\label{data}}
+\section{Data}\label{data}}
 
-We have data on 6,401,473 enrollee/year observations from the California
-health insurance exhanges from 2014 to 2017. Our data include a variety
-of individual and household characteristics, plan choices and plan
-characteristics, and information on the type of decision assistance used
-by the enrollee (if any). From these data, we can identify each
-household's set of possible health insurance plans, and we employ
-premium and cost sharing subsidy formulas to calculate health insurance
-costs for each possible plan for each household.
+Our final dataset consists of 3,200,080 household/year observations from the California health insurance exhanges from 2014 to 2019.
+Our data include a variety of household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any).
+From these data, we can identify each household's set of possible health insurance plans, and we employ premium and cost sharing subsidy formulas to calculate health insurance costs for each possible plan for each household.
 
 \hypertarget{methods}{%
-\subsubsection{Methods:}\label{methods}}
+\section{Methods}\label{methods}}
 
-We first estimate overall demand for health insurance using a nested
-logit discrete choice model, as in Saltzman (2019). We then identify
-specific instances in which the observed plan choice is dominated by
-some other plan in an individual's choice set. For example, Gold and
-Platinum tier plans are dominated for any household that is eligible for
-cost-sharing subsidies and with incomes below 150\% of the federal
-poverty level. We estimate the effect of decision assistance on
-dominated choices with a linear probability model, allowing for year and
-household fixed effects.
+Our overarching goal is to estimate the effect of decision assistance on health insurance decisions; however, there are perhaps many ways of measuring ``health insurance decisions''.
+One approach is to estimate demand for health insurance in a traditional discrete choice framework.
+This would allow us to quantify individuals' willingness to pay for decision assistance as well as the effect of decision assistance on choice probabilities.
+Another approach is to focus specifically on ``dominated choices'', which are relatively clearly defined and observable in our empirical context.
+This latter approach lacks the richness of the discrete choice demand framework but benefits from a focus on a specific outcome of obvious policy and welfare relevance.
+We consider both approaches in our analysis, as detailed in the remainder of this section.
+
+\hypertarget{discrete-choice-framework}{%
+\subsection{Discrete Choice Framework}\label{discrete-choice-framework}}
+
+We model health insurance purchasing with a nested logit discrete choice model, as in Saltzman (2019), and we derive estimates of the effect of decision assistnce by embedding this discrete choice model into a standard potential outcomes framework.
+
+For our discrete choice model, we assume that household \(i\) chooses the plan \(j\) that maximizes their utility,
+\begin{equation}
+u_{ij} = \alpha_{i}p_{ij} + \beta x_{j} + \gamma d_{i} + \xi_{j} + \varepsilon_{ij}, \label{eq:utility}
+\end{equation}
+where \(p_{ij}\) denotes the premium for plan \(j\), \(x_{j}\) denotes a vector of product characteristics, \(d_{i}\) denotes a vector of household characteristics, \(\xi_{j}\) captures unobserved product characteristics, and \(\varepsilon_{ij}\) is an error term assumed to follow a type I extreme value distribution.
+We allow for heterogenities in price elasticities across households by parameterizing \(\alpha_{i}\) in Equation \eqref{eq:utility}, \[\alpha_{i} = \alpha + \theta d_{i}.\] In our estimation, this amounts to including a full set of interactions between \(d_{i}\) and \(p_{ij}\).
+
+\hypertarget{dominated-choices}{%
+\subsection{Dominated Choices}\label{dominated-choices}}
+
+As a complementary empirical analysis, we identify specific instances in which the observed plan choice is dominated by some other plan in an individual's choice set, and we estimate the effects of decision assistance on the probability of making such a choice.
+For example, Gold and Platinum tier plans are dominated for any household that is eligible for cost-sharing subsidies and with incomes below 150\% of the federal poverty level.
+We estimate the effect of decision assistance on dominated choices with a linear probability model, allowing for year, insurer, and region fixed effects.
 
 \hypertarget{results}{%
-\subsubsection{Results:}\label{results}}
+\section{Results}\label{results}}
 
-Our nested logit models establish strong evidence that decision
-assistance matters for insurance choice. Turning specifically to
-dominated choices, our baseline results suggest that individuals with
-decision assistance are 0.37 percentage points less likely to make a
-dominated choice. On a base of 1.9\%, this reflects a 20\% decrease in
-the probability of making a dominated choice.
+Our nested logit models establish strong evidence that decision assistance matters for insurance choice.
+Turning specifically to dominated choices, our baseline results suggest that individuals with decision assistance are 1.16 percentage points less likely to make a dominated choice.
+On a base of 2.8\%, this reflects a 41\% decrease in the probability of making a dominated choice.
 
-We also find strong heterogeneities in the effects of different forms of
-decision assistance. In particular, we find that individuals using
-publicly provided decision assistance are 0.43 percentage points less
-likely to select a dominated plan, while individuals using a private
-insurance agent are 0.16 percentage points less likely to select a
-dominated plan.
+We also find evidence fo heterogeneities in the effects of different forms of decision assistance.
+In particular, we find that individuals using publicly provided decision assistance are 0.91 percentage points less likely to select a dominated plan, while individuals using a private insurance agent are 1.26 percentage points less likely to select a dominated plan.
 
-\hypertarget{discussion}{%
-\subsubsection{Discussion:}\label{discussion}}
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
 
-Our current results provide strong evidence that decision assistance has
-a significant and economically meaningful effect on health insurance
-plan choice. In terms of dominated choices, our early results suggest
-that this change in decision-making is welfare improving, and we
-continue to explore other measures of choice dominance to further
-confirm this result.
+Our current results provide strong evidence that decision assistance has a significant and economically meaningful effect on health insurance plan choice.
+In terms of dominated choices, our early results suggest that this change in decision-making is welfare improving, and we continue to explore other measures of choice dominance to further confirm this result.
 
-In future work, our identification strategy will exploit the Trump
-administration's removal of cost-sharing subisidies from the exchanges
-in 2018 and the subsequent response from insurers to increase premiums
-on their silver plans (``silver loading''). This response significantly
-changed the prevalence of dominated choices in each household's choice
-set, and in this way, the removal of the cost-sharing subsidies offers
-an exogenous change to the set of dominated plans available to each
-household.
+In future work, our identification strategy will exploit the Trump administration's removal of cost-sharing subisidies from the exchanges in 2018 and the subsequent response from insurers to increase premiums on their silver plans (``silver loading'').
+This response significantly changed the prevalence of dominated choices in each household's choice set, and in this way, the removal of the cost-sharing subsidies offers an exogenous change to the set of dominated plans available to each household.
 
-We are also extending our analysis of the differential effects between
-public decision support versus assistance from private insurance
-agents/brokers. This analysis will determine whether insurance brokers
-are more likely to steer patients into plans offered by the sponsoring
-insurer.
+We are also extending our analysis of the differential effects between public decision support versus assistance from private insurance agents/brokers.
+This analysis will determine whether insurance brokers are more likely to steer patients into plans offered by the sponsoring insurer.
 
@@
 \hypertarget{refs}{}
+\begin{cslreferences}
 \leavevmode\hypertarget{ref-abaluck2011}{}%
-Abaluck, Jason, and Jonathan Gruber. 2011. ``Heterogeneity in Choice
-Inconsistencies Among the Elderly: Evidence from Prescription Drug Plan
-Choice.'' \emph{American Economic Review} 101 (3): 377--81.
+Abaluck, Jason, and Jonathan Gruber. 2011. ``Heterogeneity in Choice Inconsistencies Among the Elderly: Evidence from Prescription Drug Plan Choice.'' \emph{American Economic Review} 101 (3): 377--81.
 
 \leavevmode\hypertarget{ref-gruber2017}{}%
-Gruber, Jonathan. 2017. ``Delivering Public Health Insurance Through
-Private Plan Choice in the United States.'' \emph{Journal of Economic
-Perspectives} 31 (4): 3--22.
+Gruber, Jonathan. 2017. ``Delivering Public Health Insurance Through Private Plan Choice in the United States.'' \emph{Journal of Economic Perspectives} 31 (4): 3--22.
 
 \leavevmode\hypertarget{ref-ketcham2012}{}%
-Ketcham, Jonathan D, Claudio Lucarelli, Eugenio J Miravete, and M
-Christopher Roebuck. 2012. ``Sinking, Swimming, or Learning to Swim in
-Medicare Part d.'' \emph{American Economic Review} 102 (6): 2639--73.
+Ketcham, Jonathan D, Claudio Lucarelli, Eugenio J Miravete, and M Christopher Roebuck.
+2012.
+``Sinking, Swimming, or Learning to Swim in Medicare Part d.'' \emph{American Economic Review} 102 (6): 2639--73.
 
 \leavevmode\hypertarget{ref-saltzman2019}{}%
-Saltzman, Evan. 2019. ``Demand for Health Insurance: Evidence from the
-California and Washington Aca Exchanges.'' \emph{Journal of Health
-Economics} 63: 197--222.
+Saltzman, Evan. 2019. ``Demand for Health Insurance: Evidence from the California and Washington Aca Exchanges.'' \emph{Journal of Health Economics} 63: 197--222.
+\end{cslreferences}
 

### 2020-09-02 Paper.tex
change bibtex link

@@
 \author{Ian McCarthy \& Evan Saltzman}
-\date{April 30, 2020}
+\date{September 02, 2020}
 
@@
 
-Our final dataset consists of 3,200,080 household/year observations from the California health insurance exhanges from 2014 to 2019.
+Our final dataset consists of 3,212,732 household/year observations from the California health insurance exhanges from 2014 to 2019.
 Our data include a variety of household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any).
-From these data, we can identify each household's set of possible health insurance plans, and we employ premium and cost sharing subsidy formulas to calculate health insurance costs for each possible plan for each household.
+From these data, we can identify each household's set of possible health insurance plans, and we employ premium and cost sharing subsidy formulas to calculate health insurance costs for each possible plan for each household
 
@@
 Our nested logit models establish strong evidence that decision assistance matters for insurance choice.
-Turning specifically to dominated choices, our baseline results suggest that individuals with decision assistance are 1.16 percentage points less likely to make a dominated choice.
-On a base of 2.8\%, this reflects a 41\% decrease in the probability of making a dominated choice.
+Turning specifically to dominated choices, our baseline results suggest that individuals with decision assistance are 1.4 percentage points less likely to make a dominated choice.
+On a base of 2.8\%, this reflects a 50\% decrease in the probability of making a dominated choice.
 
 We also find evidence fo heterogeneities in the effects of different forms of decision assistance.
-In particular, we find that individuals using publicly provided decision assistance are 0.91 percentage points less likely to select a dominated plan, while individuals using a private insurance agent are 1.26 percentage points less likely to select a dominated plan.
+In particular, we find that individuals using publicly provided decision assistance are 1.09 percentage points less likely to select a dominated plan, while individuals using a private insurance agent are 1.54 percentage points less likely to select a dominated plan.
 

### 2021-03-17 finals/Paper.tex
Update decision assistance portion of code, remove Julia estimation from my end

--- 2020-09-02 Paper.tex
@@
 
+Discussion of poor decision making in health insurance and role of experts.
+
 \hypertarget{data}{%
@@
 
-Our overarching goal is to estimate the effect of decision assistance on health insurance decisions; however, there are perhaps many ways of measuring ``health insurance decisions''.
+Our overarching goal is to estimate the effect of decision assistance on health insurance decisions; however, there are many ways of measuring ``health insurance decisions''.
 One approach is to estimate demand for health insurance in a traditional discrete choice framework.

### 2021-03-17 finals/_Abstract_ASHEcon_201910.tex
Update decision assistance portion of code, remove Julia estimation from my end

--- 2019-10-28 _Abstract_ASHEcon_201910.tex
@@
 
-We have data on 6,401,473 enrollee/year observations from the California
-health insurance exhanges from 2014 to 2017. Our data include a variety
-of individual and household characteristics, plan choices and plan
+Our final dataset consists of 3,200,080 household/year observations from
+the California health insurance exhanges from 2014 to 2019. Our data
+include a variety of household characteristics, plan choices and plan
 characteristics, and information on the type of decision assistance used
@@
 poverty level. We estimate the effect of decision assistance on
-dominated choices with a linear probability model, allowing for year and
-household fixed effects.
+dominated choices with a linear probability model, allowing for year,
+insurer, and region fixed effects.
 
@@
 dominated choices, our baseline results suggest that individuals with
-decision assistance are 0.37 percentage points less likely to make a
-dominated choice. On a base of 1.9\%, this reflects a 20\% decrease in
+decision assistance are 1.16 percentage points less likely to make a
+dominated choice. On a base of 2.8\%, this reflects a 41\% decrease in
 the probability of making a dominated choice.
 
-We also find strong heterogeneities in the effects of different forms of
-decision assistance. In particular, we find that individuals using
-publicly provided decision assistance are 0.43 percentage points less
-likely to select a dominated plan, while individuals using a private
-insurance agent are 0.16 percentage points less likely to select a
-dominated plan.
+We also find evidence fo heterogeneities in the effects of different
+forms of decision assistance. In particular, we find that individuals
+using publicly provided decision assistance are 0.91 percentage points
+less likely to select a dominated plan, while individuals using a
+private insurance agent are 1.26 percentage points less likely to select
+a dominated plan.
 

### 2021-03-17 analysis/_ChoiceModel.R

@@ -1,125 +1,0 @@
-# Meta --------------------------------------------------------------------
-
-## Date Created:  3/4/2020
-## Date Edited:   5/12/2020
-## Description:   Create data for discrete choice model and estimate by year and 3-digit zip
-
-## Notes:         This file requires that we've already created the household data
-##                and the plan data.
-
-
-
-# Clean data --------------------------------------------------------------
-
-## Remove "flagged" households
-hh.clean <- data.hh %>% filter(flagged==0)
-data.clean <- data %>% filter(flagged==0)
-
-## Oldest person per household
-max.age <- data.ind %>%
-  group_by(household_id, year) %>%
-  summarize(oldest_member=max(AGE))
-
-## Add some variables
-hh.clean <- hh.clean %>%
-  mutate(FPL_bracket = case_when(
-    FPL <= 1.38 ~ "138orless",
-    FPL > 1.38 & FPL <= 2.50 ~ "138to250",
-    FPL > 2.50 & FPL <= 4 ~ "250to400",
-    FPL > 4 ~ "400ormore")) %>%
-  mutate(perc_18to34 = perc_18to25 + perc_26to34,
-         perc_35to54 = perc_35to44 + perc_45to54,
-         FPL_bracket=as.factor(FPL_bracket)) %>%
-  left_join(max.age, by=c("household_id","year"))
-
-  
-
-## Predict who left market
-hh.clean <- hh.clean %>%
-  add_predictions(outside_logit, "pred_oom", type="response") %>%
-  mutate(pred_oom = ifelse(is.na(plan_number_nocsr),pred_oom,NA),
-         unif_draw=runif(n(),0,1),
-         out_of_market = (pred_oom >= unif_draw)) %>%
-  filter(out_of_market == FALSE | !is.na(plan_number_nocsr))
-hh.clean <- as_tibble(hh.clean)
-  
-
-data.clean <- data.clean %>%
-  left_join(hh.clean %>% select(household_id, year, out_of_market), 
-            by=c("household_id","year")) %>%
-  filter(out_of_market == FALSE | !is.na(plan_number_nocsr))
-data.clean <- as_tibble(data.clean)
-
-
-# Form choice sets --------------------------------------------------------
-afford.threshold <- tibble(
-  cutoff = c(0.08, 0.0805, 0.0813, 0.0816, 0.0805, 0.0830),
[…]

### 2021-03-17 analysis/_DominatedChoices.R

@@ -1,38 +1,0 @@
-# Meta --------------------------------------------------------------------
-
-## Date Created:  3/4/2020
-## Date Edited:   6/5/2020
-## Description:   Simple regressions of dominated choices
-
-
-# Initial Regressions -----------------------------------------------------
-
-
-reg1 <- felm(dominated_choice ~ any_assist + lang_english + lang_spanish +
-               low_income + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
-               perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
-               perc_other + hh_single + SEP + new_enrollee 
-             | region + year + insurer | 0 | region, 
-     data=final.data)
-
-reg2 <- felm(dominated_choice ~ any_assist + lang_english + lang_spanish +
-               low_income + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
-               perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
-               perc_other + hh_single + SEP + new_enrollee
-             | household_id + year + insurer | 0 | household_id, 
-             data=final.data)
-
-reg1.b <- felm(dominated_choice ~ assist_agent + assist_other + lang_english + lang_spanish +
-                 low_income + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
-                 perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
-                 perc_other + hh_single + SEP + new_enrollee 
-               | region + year + insurer  | 0 | region, 
-               data=final.data)
-
-
-reg2.b <- felm(dominated_choice ~ assist_agent + assist_other + lang_english + lang_spanish +
-               low_income + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
-               perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
-               perc_other + hh_single + SEP + new_enrollee
-             | household_id + year + insurer | 0 | household_id, 
-             data=final.data)

### 2021-03-17 analysis/_SummaryStats.R

@@ -1,106 +1,0 @@
-# Meta --------------------------------------------------------------------
-
-## Date Created:  10/11/2019
-## Date Edited:   6/5/2020
-## Description:   Basic summary stats
-
-
-# Summary Statistics ------------------------------------------------------
-
-
-## metal by type of assistance (all enrollees)
-metal.assist.all <- final.data %>% group_by(channel, metal) %>%
-  summarize(metal_count=n()) %>%
-  mutate(metal_pct=metal_count/sum(metal_count),
-         metal_pct=round(metal_pct,3))
-
-## metal by type of assistance (new enrollees)
-metal.assist.new <- final.data %>% filter(new_enrollee==1) %>%
-  group_by(channel, metal) %>%
-  summarize(metal_count=n()) %>%
-  mutate(metal_pct=metal_count/sum(metal_count),
-         metal_pct=round(metal_pct))
-
-## table of assistance and tier choice
-kable(metal.assist.all[,2:4], "latex", booktabs=T, 
-      col.names=c("Tier"," Count", "Percent")) %>%
-  group_rows("Insurance Agent", 1, 5) %>%
-  group_rows("Other Assitance", 6, 10) %>%
-  group_rows("Unassisted", 11, 15)
-
-## figure of assistance and tier choice
-stack.all <- ggplot(final.data) +
-  geom_bar(mapping=aes(x=channel,fill=metal),
-           position="fill", color="black") +
-  labs(
-    x="Type of Assistance",
-    y="Relative Frequency",
-    title="Metal Tier by Type of Assistance"
-  ) + theme_bw() +
-  theme(legend.title=element_blank()) +
-  scale_fill_brewer(palette="Greys")
-ggsave("figures/metal_stack_all.png", stack.all)
-
-## data on enrollees per year
-enrollee.count.all <- final.data %>% count(year) %>%
-  rename(all_count=n)
-enrollee.count.new <- final.data %>% filter(new_enrollee==1) %>%
-  count(year) %>% rename(new_count=n)
-enrollee.count <- enrollee.count.all %>%
-  left_join(enrollee.count.new, by=c("year"))
-
-## graph of enrollees per year
-enrollee.count %>%
-  ggplot() + geom_line(aes(x=year,y=all_count)) +
-  geom_line(aes(x=year,y=new_count)) +
-  labs(
-    x="Year",
-    y="Enrollees"
-  )
-
-## count of years same household is observed
[…]

### 2021-03-17 analysis/archive/J_demand_est.jl

@@ -48,8 +48,8 @@
 	
 	# Save output
 	param_output = DataFrame();
-	param_output[:Variable] = cat(dims=1,all_covariates,"lambda");
-	param_output[:Coef] = min_beta;
+	param_output[!,:Variable] = cat(all_covariates,"lambda"; dims=1);
+	param_output[!,:Coef] = min_beta;
 		
 		
 		

### 2021-03-17 analysis/choice_est_function.R

@@ -1,170 +1,0 @@
-# Meta --------------------------------------------------------------------
-
-## Date Created:  5/12/2020
-## Date Edited:   5/25/2020
-## Description:   Function to estimate demand, calls Julia within function and reports
-##                mean predicted enrollments per plan as well as coefficient estimates
-
-
-# Estimation function -----------------------------------------------------
-
-dchoice.est <- function(time, area) {
-  
-  for (t in time) {
-    
-    a.thresh <- as.numeric(afford.threshold %>% filter(year==t) %>% select(cutoff))
-    
-    step=0
-    for (r in area) {
-      step=step+1
-      
-      julia.data <- get(paste0("julia.data.",r,".",t))
-      julia.oos <- get(paste0("julia.oos.",r,".",t))
-      
-      julia_assign("data",julia.data)
-      julia_assign("data_oos",julia.oos)
-      
-        
-      ## Terms for estimation (passed to Julia)
-      all_covars=c("intercept","premium", "AV", "HMO", "HSA", "silver")
-      beta_initial = array(0,dim=length(all_covars)+1)
-        
-      ins.offer <- c(0,0,0,0)
-      cml.share <- 0
-      tot.choice <- sum(julia.data$choice==1)
-      ins.offer[1] <- sum(julia.data$Anthem==1 & julia.data$choice==1)/tot.choice
-      ins.offer[2] <- sum(julia.data$Blue_Shield==1 & julia.data$choice==1)/tot.choice
-      ins.offer[3] <- sum(julia.data$Kaiser==1 & julia.data$choice==1)/tot.choice
-      ins.offer[4] <- sum(julia.data$Health_Net==1 & julia.data$choice==1)/tot.choice
-        
-      cml.share <- ins.offer[1]
-      if (ins.offer[1]>.1 & cml.share<.9) {
-        all_covars=c(all_covars, "Anthem")
-        beta_initial=c(beta_initial,0)
-      }
-      cml.share <- cml.share+ins.offer[2]
-      if (ins.offer[2]>.1 & cml.share<.9) {
-        all_covars=c(all_covars, "Blue_Shield")
-        beta_initial=c(beta_initial,0)
-      }
-      cml.share <- cml.share+ins.offer[3]
-      if (ins.offer[3]>.1 & cml.share<.9) {
-        all_covars=c(all_covars, "Kaiser")
-        beta_initial=c(beta_initial,0)
-      }
[…]

### 2021-03-17 analysis/decision-support/_ChoiceModel.R

@@ -1,0 +1,93 @@
+# Preliminaries -----------------------------------------------------------
+afford.threshold <- tibble(
+  cutoff = c(0.08, 0.0805, 0.0813, 0.0816, 0.0805, 0.0830),
+  year = c(2014, 2015, 2016, 2017, 2018, 2019)
+)
+
+## specify time periods and regions for estimation
+unique.region <- hh.clean %>% distinct(region)
+time.dat <- 2014:2019
+area.dat <- as.list(unique.region)$region
+
+# Estimate model ----------------------------------------------------------
+plan(multisession, workers=4)
+future.tracking <- c("time.dat","area.dat", "is.error")
+
+source('analysis/decision-support/choice_data_function.R')
+source('analysis/decision-support/choice_est_function.R')
+source('analysis/decision-support/choice_est_bs_function.R')
+for (t in time.dat) {
+  
+  step=0
+  for (r in area.dat) {
+    step=step+1
+    
+    choice.data <- choice.data.fnc(t=t,r=r)
+    assign(paste0("est.data.",r,".",t), choice.data$est.data)
+    assign(paste0("oos.data.",r,".",t), choice.data$oos.data)
+    choice.est <- dchoice.est(d=choice.data$est.data, oos=choice.data$oos.data, t=t, r=r)
+    
+    treated.dat <- choice.est$pred
+    coef.vals <- choice.est$coef
+    if (step==1) {
+      final.data <- treated.dat
+      final.coef <- coef.vals
+    } else {
+      final.data <- bind_rows(final.data, treated.dat)
+      final.coef <- bind_rows(final.coef, coef.vals)
+    }
+    future.tracking <- c(future.tracking, paste0("est.data.",r,".",t), paste0("oos.data.",r,".",t))      
+  }
+  
+  assign(paste0("final.data.",t),final.data)
+  assign(paste0("final.coef.",t),final.coef)
+  textme(msg=paste0(emo::ji("space"),"One small step for man...You've completed time: ",t))
+  
+}
+
+
+step=0
+for (t in time.dat) {
+  step=step+1
+  if (step==1) {
+    est.prob <- get(paste0("final.data.",t))
+    bs.starting <- get(paste0("final.coef.",t))
+  } else {
+    est.prob <- bind_rows(est.prob, get(paste0("final.data.",t)))
[…]

### 2021-03-17 analysis/decision-support/_DominatedChoices.R

@@ -1,0 +1,86 @@
+# Meta --------------------------------------------------------------------
+
+## Date Created:  3/4/2020
+## Date Edited:   3/17/2021
+## Description:   Simple regressions of dominated choices
+
+
+# Initial Regressions -----------------------------------------------------
+
+mod1 <- feols(dominated_choice ~ channel + english + spanish +
+                FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
+                perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
+                perc_other + household_size + new_enrollee 
+              | region + year + insurer, cluster="region",
+              data=hh.full)
+
+mod2 <- feols(dominated_choice ~ channel + english + spanish +
+               FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
+               perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
+               perc_other + household_size + SEP + new_enrollee 
+             | region + year + insurer, cluster="region",
+     data=hh.full)
+
+
+mod3 <- feols(dominated_choice ~ channel + english + spanish +
+                FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
+                perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
+                perc_other + household_size + new_enrollee 
+             | household_id + year + insurer, cluster="household_id", 
+             data=hh.full)
+
+mod4 <- feols(dominated_choice ~ channel + english + spanish +
+                FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
+                perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
+                perc_other + household_size + SEP + new_enrollee 
+              | household_id + year + insurer, cluster="household_id", 
+              data=hh.full)
+
+
+mod5 <- feols(dominated_choice ~ channel + english + spanish +
+                FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
+                perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
+                perc_other + household_size
+              | region + year + insurer, cluster="region",
+              data=hh.clean)
+
+mod6 <- feols(dominated_choice ~ channel + english + spanish +
+                FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
[…]

### 2021-03-17 analysis/decision-support/_SummaryStats.R

@@ -1,0 +1,86 @@
+# Meta --------------------------------------------------------------------
+
+## Date Created:  10/11/2019
+## Date Edited:   3/17/2021
+## Description:   Basic summary stats
+
+
+# Summary Statistics ------------------------------------------------------
+
+## metal by type of assistance (all enrollees)
+metal.assist.all <- hh.full %>% group_by(channel_detail, metal) %>%
+  summarize(metal_count=n()) %>%
+  mutate(metal_pct=metal_count/sum(metal_count),
+         metal_pct=round(metal_pct,3))
+
+## metal by type of assistance (new enrollees)
+metal.assist.new <- hh.clean %>%
+  group_by(channel_detail, metal) %>%
+  summarize(metal_count=n()) %>%
+  mutate(metal_pct=metal_count/sum(metal_count),
+         metal_pct=round(metal_pct))
+
+
+## table of assistance and tier choice
+kable(metal.assist.all[,2:4], format="latex",
+                       col.names=c("Type of Assistance"," Count", "Percent"),
+                       format.args=list(big.mark=","),
+                       booktabs=T) %>%
+  kable_styling(latex_options=c("HOLD_position")) %>%
+  group_rows("Agent or Broker", 1, 5) %>%
+  group_rows("Navigator", 6, 10) %>%
+  group_rows("Unassisted", 11, 15) %>%
+  save_kable("tables/metal_assistance.tex")
+
+## figure of assistance and tier choice
+ggplot(hh.full) +
+  geom_bar(mapping=aes(x=channel_detail,fill=metal),
+           position="fill", color="black", size=.1) +
+  labs(
+    x="Type of Assistance",
+    y="Relative Frequency",
+    title="Metal Tier by Type of Assistance"
+  ) + theme_bw() +
+  theme(legend.title=element_blank()) +
+  scale_fill_brewer(palette="Greys") + ggsave("figures/metal_stack_all.png")
+
+## data on enrollees per year
+enrollee.count.all <- hh.full %>% count(year) %>%
+  rename(enroll_count=n) %>%
+  mutate(Type="All Enrollees")
+enrollee.count.new <- hh.clean %>%
+  count(year) %>% rename(enroll_count=n) %>%
+  mutate(Type="New Enrollees")
+enrollee.count <- bind_rows(enrollee.count.all, enrollee.count.new) %>%
+  mutate(enroll_count=enroll_count/1000)
+
[…]

### 2021-03-17 analysis/decision-support/choice_data_function.R

@@ -1,8 +1,8 @@
 # Meta --------------------------------------------------------------------
 
 ## Date Created:  5/12/2020
-## Date Edited:   5/25/2020
-## Description:   Function to create choice-level datasets and save subset for future use
+## Date Edited:   3/15/2021
+## Description:   Function to create choice-level dataset for given year and area
 
 
 # Estimation function -----------------------------------------------------
@@ -16,8 +16,8 @@ choice.data.fnc <- function(t, r) {
     Issuer_Name="Outside_Option"
   )
   
-  choice.set <- plan.data %>% filter(ENROLLMENT_YEAR==t, region==r) %>%
-    select(plan_name=Plan_Name2, Issuer_Name, region, PLAN_NETWORK_TYPE, metal_level, metal, 
+  choice.set <- plan_data %>% filter(Year==t, region==r) %>%
+    select(plan_name=Plan_Name2, Issuer_Name=Insurer, region, PLAN_NETWORK_TYPE, metal_level=Metal_Level, metal, 
            Premium, MSP, HSA) %>%
     group_by(plan_name, region) %>%
     summarize(Issuer_Name=first(Issuer_Name),
@@ -142,7 +142,7 @@ choice.data.fnc <- function(t, r) {
            platinum, silver, gold, bronze, AV, plan_name) %>%
     left_join(hh.clean %>% select(household_id, year, hh_region=region, tax_unit_type, hh_size=household_size,
                                   starts_with('lang_'), starts_with('perc_'), starts_with('exempt'),
-                                  dominated_choice, service_channel, channel),
+                                  dominated_choice, navigator, broker, agent, channel),
               by=c("household_id", "year", "hh_region")) %>%
     mutate(metal=ifelse(is.na(metal),"Other",metal),
            plan_choice = case_when(
@@ -223,8 +223,8 @@ choice.data.fnc <- function(t, r) {
   sample.hh.oos <- sample_frac(unique.hh.oos, size=0.2, replace=FALSE)
   
     
-  ## Final data to Julia
-  julia.data <- untreated.dat %>%
+  ## Final data
+  est.data <- untreated.dat %>%
     inner_join(sample.hh, by=c("household_number")) %>%          
     select(plan_name, household_number, choice, premium,
            platinum, gold, silver, bronze, HSA, HMO, AV, uninsured_plan,
[…]

### 2021-03-17 analysis/decision-support/choice_est_bs_function.R

@@ -17,57 +17,56 @@ dchoice.bs <- function(time, area) {
     for (r in area) {
       step=step+1
     
-      julia.data <- get(paste0("julia.data.",r,".",t))
-      julia.oos <- get(paste0("julia.oos.",r,".",t))
+      #choice.bs <- choice.data.fnc(t=t,r=r)
+      #est.data <- choice.bs$est.data
+      #oos.data <- choice.bs$oos.data
+      est.data <- get(paste0("est.data.",r,".",t))
+      oos.data <- get(paste0("oos.data.",r,".",t))
 
-      # Select bootstrap sample (within area and year)
-      unique.hh <- julia.data %>%
+      ## Select bootstrap sample (within area and year)
+      unique.hh <- est.data %>%
         group_by(household_number) %>%
         mutate(hh_count=seq(n())) %>%
         filter(hh_count==1) %>%
         select(household_number) %>% ungroup()
       sample.hh <- sample_n(unique.hh, size=nrow(unique.hh), replace=TRUE)
-      julia.data <- julia.data %>%
+      est.data <- est.data %>%
         inner_join(sample.hh, by=c("household_number"))
       
       
-      # send sample to Julia and estimate with original starting values  
-      julia_assign("data",julia.data)
-      julia_assign("data_oos",julia.oos)
+      ## Set up model and starting values
+      all_covars <- as.list(bs.starting %>% filter(region==r, year==t) %>% select(variable))$variable
+      mclogit.formula <- formula(paste("cbind(choice, household_number) ~", paste(all_covars, collapse=" + ")))
+      beta_initial <- as.list(bs.starting %>% filter(region==r, year==t) %>% select(estimate))$estimate
+
+    
+      ## Estimate model and store results
+      test <- is.error(mclogit(mclogit.formula, data=est.data, start=beta_initial))
+      if (test==FALSE) {
+        mc.logit <- mclogit(mclogit.formula, data=est.data, start=beta_initial)  
+      } else {
+        mc.logit <- mclogit(mclogit.formula, data=est.data)
+      }
       
-      all_covars <- as.list(bs.starting %>% filter(region==r, year==t, value!="lambda") %>% select(value))$value
-      beta_initial <- as.list(bs.starting %>% filter(region==r, year==t) %>% select(value1))$value1
+      coef.name <- as_tibble(names(mc.logit$coefficients)) %>%
+        rename("variable"=value)
[…]

### 2021-03-17 analysis/decision-support/choice_est_function.R

@@ -1,0 +1,77 @@
+# Meta --------------------------------------------------------------------
+
+## Date Created:  5/12/2020
+## Date Edited:   3/15/2021
+## Description:   Function to estimate demand, reports mean predicted enrollments 
+##                per plan as well as coefficient estimates
+
+
+# Estimation function -----------------------------------------------------
+
+dchoice.est <- function(d, oos, t, r) {
+  a.thresh <- as.numeric(afford.threshold %>% filter(year==t) %>% select(cutoff))
+
+  ## Terms for estimation
+  all_covars=c("premium", "HMO", "HSA", "silver")
+  ins.offer <- c(0,0,0,0)
+  cml.share <- 0
+  tot.choice <- sum(d$choice==1)
+  ins.offer[1] <- sum(d$Anthem==1 & d$choice==1)/tot.choice
+  ins.offer[2] <- sum(d$Blue_Shield==1 & d$choice==1)/tot.choice
+  ins.offer[3] <- sum(d$Kaiser==1 & d$choice==1)/tot.choice
+  ins.offer[4] <- sum(d$Health_Net==1 & d$choice==1)/tot.choice
+  
+  cml.share <- ins.offer[1]
+  if (ins.offer[1]>.3 & cml.share<.9) {
+    all_covars=c(all_covars, "Anthem")
+  }
+  cml.share <- cml.share+ins.offer[2]
+  if (ins.offer[2]>.3 & cml.share<.9) {
+    all_covars=c(all_covars, "Blue_Shield")
+  }
+  cml.share <- cml.share+ins.offer[3]
+  if (ins.offer[3]>.3 & cml.share<.9) {
+    all_covars=c(all_covars, "Kaiser")
+  }
+  cml.share <- cml.share+ins.offer[4]
+  if (ins.offer[4]>.3 & cml.share<.9) {
+    all_covars=c(all_covars, "Health_Net")
+  }  
+  
+  mclogit.formula <- formula(paste("cbind(choice, household_number) ~", paste(all_covars, collapse=" + ")))
+  logit.formula <- formula(paste("choice ~", paste(all_covars, collapse=" + ")))
+  
+  ## Find initial values from logit and apply to mclogit
+  logit.start <- glm(logit.formula, data=d, family="binomial")
+  test <- is.error(mclogit(mclogit.formula, data=d))
+  if (test==FALSE) {
+    mc.logit <- mclogit(mclogit.formula, data=d)
+  } else {
[…]

### 2021-03-17 analysis/decision-support/decision-analysis.R

@@ -1,0 +1,140 @@
+
+# Meta --------------------------------------------------------------------
+
+## Title:         Decision Assistance and Health Insurance Choice
+## Author:        Ian McCarthy & Evan Saltzman
+## Date Created:  10/28/2019
+## Date Edited:   3/16/2021
+## Description:   This file calls all scripts necessary for estimating the effect of decision assistance on 
+##                health insurance choice.
+
+
+# Preliminaries -----------------------------------------------------------
+if (!require("pacman")) renv::install('pacman')
+pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stargazer, knitr, kableExtra,
+               lfe, modelr, mclogit, bookdown, future, parallel, nnet, mixl, fixest,
+               future.apply, gtsummary, emo, twilio, SAScii, data.table, scales,
+               modelsummary)
+
+source('paths.R')
+source(paste0(common,"/common_functions.R"))
+set.seed(84324) # set using random.seed(s=Sys.time()) 
+
+
+
+# Import and clean data ---------------------------------------------------
+
+plan_data <- get(load("data/final/plan_data"))
+data <- get(load("data/final/enroll_data"))
+households <- get(load("data/final/household_data"))
+outside_logit <- get(load("data/final/sipp_logit"))
+
+plan_data <- as_tibble(plan_data) %>%
+  mutate(metal = as.character(Metal_Level),
+         metal = replace(metal, metal %in% c("Silver - Enhanced 73",
+                                             "Silver - Enhanced 87",
+                                             "Silver - Enhanced 94"), 
+                         "Silver") )
+
+
+## Oldest person per household
+data <- as.data.table(data, key=c("household_id","year"))
+max.age <- data[, .(oldest_member = max(AGE, na.rm=T)), by=.(household_id,year)]
+
+## language spoken
+language <- data[, .(household_id, year, lang_english=(language_spoken=="English"), 
+                     lang_spanish=(language_spoken=="Spanish"),
+                     lang_other=(! language_spoken %in% c("English","Spanish")))]
+
+hh.language <- language[, .(english=max(lang_english, na.rm=T),
+                            spanish=max(lang_spanish, na.rm=T),
[…]

### 2021-03-17 data-code/build-data.R

@@ -4,7 +4,7 @@
 ## Title:         Decision Assistance and Health Insurance Choice
 ## Author:        Ian McCarthy & Evan Saltzman
 ## Date Created:  10/28/2019
-## Date Edited:   3/2/2021
+## Date Edited:   3/8/2021
 ## Description:   This file builds the final datasets for analysis
 
 
@@ -15,9 +15,12 @@ source('paths.R')
 
 # Import and clean data ---------------------------------------------------
 source('data-code/process.SIPP.R')
-rm(list=ls())
 source('data-code/impute.SIPP.R')
 source('data-code/process.COVCAL.data.R')
+
+
+# Build demand-side data --------------------------------------------------
+source('data-code/prepare.demand.data.R')
 
 
 # Call analysis and set workspace for knitr -------------------------------

### 2021-03-17 data-code/prepare.demand.data.R

@@ -118,7 +118,7 @@ gc()
 ##### Load All Other Data 
 acs_immigration <- get(load("data/final/acs_immigration"))
 acs_emp_offer <- get(load("data/final/acs_emp_offer"))
-ca_pumas <- read.csv("data/pumas.csv",header=TRUE) # PUMA definitions for California
+ca_pumas <- read.csv("data/PUMAs.csv",header=TRUE) # PUMA definitions for California
 sahie <- read.csv("data/sahie_2014.csv",header=TRUE) # 2014 CA SAHIE data
 contribution_percentages <- read.csv("data/contribution_percentages.csv",row.names = 1) # ACA contribution percentages
 poverty_guidelines <- read.csv("data/poverty_guidelines.csv",row.names=1) # Poverty guidelines

### 2021-03-17 data-code/prepare.supply.data.R

@@ -9,8 +9,7 @@
 
 ##### Load Data
 	
-	setwd("C:/Users/esaltzm/OneDrive - Emory University/Google Drive/Emory/Research/Navigators/Data")
-	mlr_data <- read.csv("mlr_data.csv",header=TRUE,row.names=1)
+	mlr_data <- read.csv("data/final/mlr_data.csv",header=TRUE,row.names=1)
 	#rate_data <- read.csv("ca_risk_adj_results.csv")
 	rate_data <- read.csv("convergence_analysis_updated.csv",row.names=1)
 	
@@ -898,7 +897,7 @@
 	plans_pmt[plans_pmt$Metal_Level == "Platinum","AV"] <- 0.9
 	
 	# Add proj_name and rate_name
-	rsdata <- read.csv("moments_data_V11_nav.csv",header=TRUE,row.names=1)
+	rsdata <- read.csv("data/final/moments_data.csv",header=TRUE,row.names=1)
 	plans_pmt$rate_name <- plans_pmt$pmt_name	
 	plans_pmt[!plans_pmt$rate_name %in% rsdata$pmt_name,"rate_name"]	<- 
 		paste(plans_pmt[!plans_pmt$rate_name %in% rsdata$pmt_name,"plan_name"],plans_pmt[!plans_pmt$rate_name %in% rsdata$pmt_name,"year"],0,sep="")

### 2021-03-17 data-code/process.MLR.data.R

@@ -1,0 +1,342 @@
+# Load Data
+
+	# 2014 Data
+	finsum_to_keep <- c("ï..MR_SUBMISSION_TEMPLATE_ID","ROW_LOOKUP_CODE",
+					"CMM_INDIVIDUAL_YEARLY","CMM_INDIVIDUAL_Q1",
+					"CMM_INDIVIDUAL_DEFERRED_PY","CMM_INDIVIDUAL_DEFERRED_CY","CMM_INDIVIDUAL_TOTAL","year")
+	mlr_to_keep <- c("ï..MR_SUBMISSION_TEMPLATE_ID","ROW_LOOKUP_CODE",
+					"CMM_INDIVIDUAL_PY2","CMM_INDIVIDUAL_PY1","CMM_INDIVIDUAL_CY",
+					"CMM_INDIVIDUAL_TOTAL","year")
+	
+	ins_data2014 <- read.csv("data/MLR/2014/MR_Submission_Template_Header.csv",header=TRUE)
+	ins_data2014$year <- 2014
+	ins_data2014 <- ins_data2014[ins_data2014$BUSINESS_STATE == "California",]
+	
+	finsum_data2014 <- read.csv("data/MLR/2014/Part1_2_Summary_Data_Premium_Claims.csv",header=TRUE)
+	finsum_data2014$year <- 2014
+	finsum_data2014 <- finsum_data2014[,finsum_to_keep]
+	
+	mlr_data2014 <- read.csv("data/MLR/2014/Part3_MLR_Rebate_Calculation.csv",header=TRUE)
+	mlr_data2014$year <- 2014
+	mlr_data2014 <- mlr_data2014[,mlr_to_keep]
+	gc()
+	
+	# 2015 data
+	ins_data2015 <- read.csv("data/MLR/2015/MR_Submission_Template_Header.csv",header=TRUE)
+	ins_data2015$year <- 2015
+	ins_data2015 <- ins_data2015[ins_data2015$BUSINESS_STATE == "California",]
+	
+	finsum_data2015 <- read.csv("data/MLR/2015/Part1_2_Summary_Data_Premium_Claims.csv",header=TRUE)
+	finsum_data2015$year <- 2015
+	finsum_data2015 <- finsum_data2015[,finsum_to_keep]
+	
+	mlr_data2015 <- read.csv("data/MLR/2015/Part3_MLR_Rebate_Calculation.csv",header=TRUE)
[…]

### 2021-03-17 data-code/process.rate.data.R

@@ -1,0 +1,2534 @@
+# Load Data
+
+	# Rate filing data
+		
+		#### NOTE: I need to ask Sam how he constructed the merged file
+	
+	load("data/2014-2020.RData")
+	library(plyr)
+	library(dplyr)
+
+	year_to_run <- 2018
+
+	data2014 <- data.frame(PUF_2014)
+	rm(PUF_2014)
+
+	data2015 <- data.frame(PUF_2015)
+	rm(PUF_2015)
+
+	data2016 <- data.frame(PUF_2016)
+	rm(PUF_2016)
+
+	data2017 <- data.frame(PUF_2017)
+	rm(PUF_2017)
+
+	data2018 <- data.frame(PUF_2018)
+	rm(PUF_2018)
+
+	data2019 <- data.frame(PUF_2019)
+	rm(PUF_2019)
+
+	data2020 <- data.frame(PUF_2020)
+	rm(PUF_2020)
+
+	gc()
+	
+	# MLR Data
+	mlr_data <- read.csv("data/final/mlr_data.csv",header=TRUE)
+	rownames(mlr_data) <- paste(mlr_data$HIOS_ISSUER_ID,mlr_data$year,sep="_")
+	
+#### Preliminary Data Cleaning	
+	
+	# Drop Small Group and NON-CA Plans
+
+	data2014 <- data2014[!data2014$MARKET == "Small Group" & data2014$STATE %in% c("CA"),]
+	data2015 <- data2015[!data2015$MARKET == "Small Group" & data2015$STATE %in% c("CA"),]
+	data2016 <- data2016[!data2016$MARKET == "Small Group" & data2016$STATE %in% c("CA"),]
+	data2017 <- data2017[!data2017$MARKET == "Small Group" & data2017$STATE %in% c("CA"),]
+	data2018 <- data2018[!data2018$MARKET == "Small Group" & data2018$STATE %in% c("CA"),]
+	data2019 <- data2019[!data2019$MARKET == "Small Group" & data2019$STATE %in% c("CA"),]
+	data2020 <- data2020[!data2020$MARKET == "Small Group" & data2020$STATE %in% c("CA"),]
+	
+	# Some missing HIOS
+	data2014[data2014$COMPANY == "California Physician's Service, dba Blue Shield of California","ISSUER_ID"] <- 70285
+	data2014[data2014$COMPANY == "Chinese Community Health Plan","ISSUER_ID"] <- 47579
[…]

### 2021-03-18 analysis/decision-support/decision-analysis.R
update figures and lock file

@@ -4,7 +4,7 @@
 ## Title:         Decision Assistance and Health Insurance Choice
 ## Author:        Ian McCarthy & Evan Saltzman
 ## Date Created:  10/28/2019
-## Date Edited:   3/16/2021
+## Date Edited:   3/17/2021
 ## Description:   This file calls all scripts necessary for estimating the effect of decision assistance on 
 ##                health insurance choice.
 

### 2021-03-18 analysis/decision-support/_ChoiceModel.R
summarize discrete choice model

@@ -82,11 +82,13 @@ max.boot <- 200
                          future.seed=TRUE)
 #sim.bs <- lapply(1:max.boot, bootsrp)
 
-bs.coef <- sim.bs[[1]]$coef
-bs.pred <- sim.bs[[1]]$pred
+bs.coef <- sim.bs[[1]]$coef %>%
+  mutate(boot=1)
+bs.pred <- sim.bs[[1]]$pred %>%
+  mutate(boot=1)
 for (i in 2:max.boot) {
-  bs.coef <- bind_rows(bs.coef, sim.bs[[i]]$coef)
-  bs.pred <- bind_rows(bs.pred, sim.bs[[i]]$pred)  
+  bs.coef <- bind_rows(bs.coef, sim.bs[[i]]$coef %>% mutate(boot=i))
+  bs.pred <- bind_rows(bs.pred, sim.bs[[i]]$pred %>% mutate(boot=i))  
 }
 
 

### 2021-03-18 analysis/decision-support/_ChoiceSummary.R

@@ -1,13 +1,13 @@
 # Meta --------------------------------------------------------------------
 
 ## Date Created:  6/5/2020
-## Date Edited:   6/8/2020
+## Date Edited:   3/18/2021
 ## Description:   Summarize results from discrete choice models
 
 
 # Average treatment effect on the treated ---------------------------------
 
-pred.purchase <- est.prob %>% ungroup() %>%
+pred.purchase <- all.prob %>% ungroup() %>%
   mutate(plan_name=str_replace(plan_name, "G.*","G"),
          plan_name=str_replace(plan_name, "P.*","P"),
          plan_name=str_replace(plan_name, "CAT.*","CAT"),
@@ -47,16 +47,6 @@ ins.summary <- pred.purchase %>%
 
 # 95% confidence intervals ------------------------------------------------
 
-bs.pred$boot <- 0
-bs.pred$boot[1] <- 1
-for (i in 2:nrow(bs.pred)) {
-  if (bs.pred$plan_name[i-1]=="Uninsured") {
-    bs.pred$boot[i] <- bs.pred$boot[i-1]+1    
-  } else {
-    bs.pred$boot[i] <- bs.pred$boot[i-1]
-  }
-}
-
 bs.pred.purchase <- bs.pred %>% ungroup() %>%
   mutate(plan_name=str_replace(plan_name, "G.*","G"),
          plan_name=str_replace(plan_name, "P.*","P"),
@@ -76,8 +66,10 @@ bs.metal.boot <- bs.pred.purchase %>%
 
 bs.metal.summary <- bs.metal.boot %>% ungroup() %>%
   group_by(metal) %>%
-  summarize(p05=quantile(att, 0.05),
-            p95=quantile(att, 0.95))
+  summarize(p01=quantile(att, 0.01),
+            p05=quantile(att, 0.05),
+            p95=quantile(att, 0.95),
+            p99=quantile(att, 0.99))
 
 
 bs.ins.boot <- bs.pred.purchase %>%   
@@ -92,23 +84,29 @@ bs.ins.boot <- bs.pred.purchase %>%
 
 bs.ins.summary <- bs.ins.boot %>% ungroup() %>%
   group_by(insurer) %>%
-  summarize(p05=quantile(att, 0.05),
-            p95=quantile(att, 0.95))
+  summarize(p01=quantile(att, 0.01),
+            p05=quantile(att, 0.05),
+            p95=quantile(att, 0.95),
[…]

### 2021-03-18 analysis/decision-support/decision-analysis.R

@@ -136,5 +136,7 @@ hh.clean <- hh.full %>%
 
 source('analysis/decision-support/_SummaryStats.R')
 source('analysis/decision-support/_DominatedChoices.R')
+
+rm("hh.full","households","max.age","language","hh.language","panel.length")
 source('analysis/decision-support/_ChoiceModel.R')
 source('analysis/decision-support/_ChoiceSummary.R')

### 2021-03-18 finals/Paper.tex

@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-  12pt,
-]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Decision Support and Health Insurance Choice},
-  pdfauthor={Ian McCarthy \& Evan Saltzman},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
-\usepackage{longtable,booktabs}
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-\usepackage{setspace}
-\doublespacing
-\usepackage{titlesec}
-\titlespacing{\section}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
-\titlespacing{\subsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
-\titlespacing{\subsubsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newenvironment{cslreferences}%
-  {\setlength{\parindent}{0pt}%
-  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
-  {\par}
+\documentclass[12pt]{article}
+\usepackage{graphicx,amssymb,amsmath,setspace,comment,verbatim,titling,pgf,lscape,color}
+\usepackage[left=2cm,right=2cm,top=2.5cm,bottom=2cm]{geometry}
+\usepackage[round]{natbib}
+\usepackage{hyperref}
+\usepackage{array}
+\usepackage{bbm}
+\usepackage{marginnote}
+\usepackage[justification=centering]{caption}
+%%\usepackage{breqn}
+\newcommand{\pderiv}[2]{\frac{\partial#1}{\partial#2}}
+%\usepackage{siunitx}
+\newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{#1}}
+\hypersetup{colorlinks,%
+						citecolor=black,%
+						filecolor=black,%
+						linkcolor=black,%
+						urlcolor=blue,%
+						}
+\setstretch{1.5}
 
+\setlength{\droptitle}{-50pt}
+
+\begin{document}
 \title{Decision Support and Health Insurance Choice}
 \author{Ian McCarthy \& Evan Saltzman}
-\date{September 02, 2020}
-
-\begin{document}
+\date{March 18, 2021}
 \maketitle
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\vspace{-2ex}
+\begin{abstract}
+\noindent Abstract
+\end{abstract}
+
+\clearpage
+
+\section{Introduction}
+\label{sec:introduction}
 
 Health insurance markets are unique in many respects, not least of which is the increasing complexity of choosing an optimal health insurance plan.
-Such complexity has been well-documented in studies of health insurance choice in the Medicare Advantage market (Abaluck and Gruber 2011; Ketcham et al.
-2012; Gruber 2017).
+Such complexity has been well-documented in studies of health insurance choice in the Medicare Advantage market \citep{abaluck2011, ketcham2012, gruber2017}.
 One way to reduce the burden of this complexity is to provide professional decision support through private insurance agents or public assistance programs, both of which are available in the California health insurance exchanges created under the Affordable Care Act (ACA).
@@
 
-\hypertarget{background-and-motivation}{%
-\section{Background and Motivation}\label{background-and-motivation}}
+\section{Background and Motivation}
+\label{sec:background-and-motivation}
 
@@
 
-\hypertarget{data}{%
-\section{Data}\label{data}}
+\section{Data}
+\label{sec:data}
 
@@
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
+\section{Methods}
+\label{sec:methods}
 
@@
 
-\hypertarget{discrete-choice-framework}{%
-\subsection{Discrete Choice Framework}\label{discrete-choice-framework}}
+\subsection{Discrete Choice Framework}
+\label{subsec:discrete-choice-framework}
 
-We model health insurance purchasing with a nested logit discrete choice model, as in Saltzman (2019), and we derive estimates of the effect of decision assistnce by embedding this discrete choice model into a standard potential outcomes framework.
+We model health insurance purchasing with a nested logit discrete choice model, as in \cite{saltzman2019}, and we derive estimates of the effect of decision assistance by embedding this discrete choice model into a standard potential outcomes framework.
 
@@
 
-\hypertarget{dominated-choices}{%
-\subsection{Dominated Choices}\label{dominated-choices}}
+\subsection{Dominated Choices}
+\label{subsec:dominated-choices}
 
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\section{Results}
+\label{sec:results}
 
@@
 
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
+\section{Conclusion}
+\label{sec:conclusion}
 
@@
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
+\pagebreak
+\bibliographystyle{authordate1}
+\bibliography{BibTeX_Library}
 
-\hypertarget{refs}{}
-\begin{cslreferences}
-\leavevmode\hypertarget{ref-abaluck2011}{}%
-Abaluck, Jason, and Jonathan Gruber. 2011. ``Heterogeneity in Choice Inconsistencies Among the Elderly: Evidence from Prescription Drug Plan Choice.'' \emph{American Economic Review} 101 (3): 377--81.
+\clearpage
+\newpage
 
-\leavevmode\hypertarget{ref-gruber2017}{}%
-Gruber, Jonathan. 2017. ``Delivering Public Health Insurance Through Private Plan Choice in the United States.'' \emph{Journal of Economic Perspectives} 31 (4): 3--22.
+\section*{Tables and Figures}
 
-\leavevmode\hypertarget{ref-ketcham2012}{}%
-Ketcham, Jonathan D, Claudio Lucarelli, Eugenio J Miravete, and M Christopher Roebuck.
-2012.
-``Sinking, Swimming, or Learning to Swim in Medicare Part d.'' \emph{American Economic Review} 102 (6): 2639--73.
-
-\leavevmode\hypertarget{ref-saltzman2019}{}%
-Saltzman, Evan. 2019. ``Demand for Health Insurance: Evidence from the California and Washington Aca Exchanges.'' \emph{Journal of Health Economics} 63: 197--222.
-\end{cslreferences}
+\begin{figure}[htb]\caption{Count of Enrollees in California Exchange}
+\centering
+ 		\hspace*{-1cm}\includegraphics[scale=.7]{figures/enrollee_count.png}
+ 		\begin{minipage}{\textwidth}
+		\bigskip
+			\footnotesize \textsc{Notes:} The coefficients for high ratings are shown with circles, those for middle ratings are shown with triangles, and no reviews are shown with diamonds.
+The main results are designated in blue along with an indicator for specification ``Main".
+Various specifications and required minimum number of reviews are also indicated.
+ 		\end{minipage}
+ 		\label{figure:SpecCurve}
+ \end{figure}
 

### 2021-03-18 analysis/decision-support/_ChoiceModel.R
add steering code files

@@ -80,9 +80,9 @@ max.boot <- 200
                          future.globals=future.tracking, 
                          future.packages=c("dplyr","mclogit","modelr"),
                          future.seed=TRUE)
-#sim.bs <- lapply(1:max.boot, bootsrp)
 
-bs.coef <- sim.bs[[1]]$coef %>%
+
+ bs.coef <- sim.bs[[1]]$coef %>%
   mutate(boot=1)
 bs.pred <- sim.bs[[1]]$pred %>%
   mutate(boot=1)

### 2021-03-18 analysis/steering/make.julia.learning.R

@@ -1,0 +1,82 @@
+setwd("C:/Users/esaltzm/OneDrive - Emory University/Google Drive/Emory/Research/Navigators/Data")  # Office computer directory
+choices <- get(load("ca_choice_matrix_FEB052021_small"))
+previous_choices <- get(load("ca_previous_choice_matrix_FEB052021_small"))	
+premiums <- get(load("ca_premium_matrix_FEB052021_small"))
+commissions <- get(load("ca_commissions_matrix_FEB052021_small"))
+renewals <- get(load("ca_renewals_matrix_FEB052021_small"))
+subsidies <- get(load("ca_subsidy_matrix_FEB052021_small"))
+households <- get(load("ca_household_characteristics_FEB052021_small"))
+	
+##### Initialize output object
+
+	valid_choices <- as.vector(!is.na(t(choices)))	
+	julia_output <- expand.grid(colnames(choices),1:nrow(choices))[valid_choices,]
+	gc()
+	
+##### Save year and weight from household object and then delete
+	
+	household_years <- rep(households[rownames(choices),"year"],each=ncol(choices))[valid_choices]	
+	weight <- rep(households[rownames(choices),"weight"],each=ncol(choices))[valid_choices]
+	penalties <- rep(households[rownames(choices),"penalty"]/12,each=ncol(choices))[valid_choices]
+	#rm(households)
+	gc()
+		
+##### Reduce memory of premium and choice objects
+	
+	num_households <- nrow(choices)
+	num_plans <- ncol(choices)
+	
+	# Reduce memory
+	choices <- as.vector(t(choices))[valid_choices]
+	gc()
+	
+	previous_choices <- as.vector(t(previous_choices))[valid_choices]
+	gc()
+	
+	premiums <- as.vector(t(premiums))[valid_choices] - penalties
+	gc()
+	
+	commissions <- as.vector(t(commissions))[valid_choices]
+	gc()
+	
+	renewals <- as.vector(t(renewals))[valid_choices]
+	gc()
+	
+	subsidies <- as.vector(t(subsidies))[valid_choices]
+	gc()
+	
+##### To send to Julia
+	
+	julia_output$choice <- choices
+	rm(choices)
+	gc()
+	
+	julia_output$previous_choice <- previous_choices
+	julia_output[is.na(julia_output$previous_choice),"previous_choice"] <- 0
+	
+	julia_output$premium <- premiums
+	julia_output$subsidy <- subsidies
[…]

### 2021-03-18 analysis/decision-support/_DominatedChoices.R
Update dominated choice regression tables and figures

@@ -7,14 +7,14 @@
 
 # Initial Regressions -----------------------------------------------------
 
-mod1 <- feols(dominated_choice ~ channel + english + spanish +
+mod1 <- feols(dominated_choice ~ assisted + english + spanish +
                 FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
                 perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
                 perc_other + household_size + new_enrollee 
               | region + year + insurer, cluster="region",
               data=hh.full)
 
-mod2 <- feols(dominated_choice ~ channel + english + spanish +
+mod2 <- feols(dominated_choice ~ assisted + english + spanish +
                FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
                perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
                perc_other + household_size + SEP + new_enrollee 
@@ -22,14 +22,14 @@ mod2 <- feols(dominated_choice ~ channel + english + spanish +
      data=hh.full)
 
 
-mod3 <- feols(dominated_choice ~ channel + english + spanish +
+mod3 <- feols(dominated_choice ~ assisted + english + spanish +
                 FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
                 perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
                 perc_other + household_size + new_enrollee 
              | household_id + year + insurer, cluster="household_id", 
              data=hh.full)
 
-mod4 <- feols(dominated_choice ~ channel + english + spanish +
+mod4 <- feols(dominated_choice ~ assisted + english + spanish +
                 FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
                 perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
                 perc_other + household_size + SEP + new_enrollee 
@@ -37,14 +37,14 @@ mod4 <- feols(dominated_choice ~ channel + english + spanish +
               data=hh.full)
 
 
-mod5 <- feols(dominated_choice ~ channel + english + spanish +
+mod5 <- feols(dominated_choice ~ assisted + english + spanish +
                 FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
[…]

### 2021-03-18 analysis/decision-support/decision-analysis.R

@@ -121,6 +121,7 @@ hh.full <- hh.full %>%
            broker==1 | agent==1 ~ "Agent",
            TRUE ~ "Unassisted"
          ),
+         assisted=ifelse(channel=="Assisted",1,0),
          channel_detail=as.factor(channel_detail),
          any_agent=ifelse(broker==1 | agent==1, 1, 0),
          new_enrollee=ifelse(is.na(previous_plan_offered),1,0))

### 2021-03-22 analysis/decision-support/_SummaryStats.R
update summary stats and graphs

@@ -44,6 +44,57 @@ ggplot(hh.full) +
   theme(legend.title=element_blank()) +
   scale_fill_brewer(palette="Greys") + ggsave("figures/metal_stack_all.png")
 
+ggplot(hh.full) +
+  geom_bar(mapping=aes(x=channel,fill=metal),
+           position="fill", color="black", size=.1) +
+  labs(
+    x=" ",
+    y="Relative Frequency",
+    title="Metal Tier by Assistance"
+  ) + theme_bw() +
+  theme(legend.title=element_blank()) +
+  scale_fill_brewer(palette="Greys") + ggsave("figures/metal_stack_any.png")
+
+
+## figure of assistance and insurer
+hh.full %>% mutate(insurer = case_when(
+  insurer=="Blue_Shield" ~ "BCBS",
+  insurer=="Health_Net" ~ "HealthNet",
+  insurer=="Anthem" ~ "Anthem",
+  insurer %in% c("Chinese_Community", "Contra_Costa", "Molina", "LA_Care","Oscar","SHARP","United","Valley","Western") ~ "Other",
+  insurer=="Kaiser" ~ "Kaiser",
+  TRUE ~ "Missing")) %>%
+  ggplot() + 
+  geom_bar(mapping=aes(x=channel_detail,fill=insurer),
+           position="fill", color="black", size=.1) +
+  labs(
+    x="Type of Assistance",
+    y="Relative Frequency",
+    title="Selected Insurer"
+  ) + theme_bw() +
+  theme(legend.title=element_blank()) +
+  scale_fill_brewer(palette="Greys") + ggsave("figures/insurer_stack_all.png")
+
+
+hh.full %>% mutate(insurer = case_when(
+  insurer=="Blue_Shield" ~ "BCBS",
+  insurer=="Health_Net" ~ "HealthNet",
+  insurer=="Anthem" ~ "Anthem",
+  insurer %in% c("Chinese_Community", "Contra_Costa", "Molina", "LA_Care","Oscar","SHARP","United","Valley","Western") ~ "Other",
+  insurer=="Kaiser" ~ "Kaiser",
+  TRUE ~ "Missing")) %>%
+  ggplot() + 
+  geom_bar(mapping=aes(x=channel,fill=insurer),
+           position="fill", color="black", size=.1) +
+  labs(
+    x=" ",
+    y="Relative Frequency",
+    title="Selected Insurer"
+  ) + theme_bw() +
[…]

### 2021-03-22 analysis/decision-support/decision-analysis.R

@@ -4,7 +4,7 @@
 ## Title:         Decision Assistance and Health Insurance Choice
 ## Author:        Ian McCarthy & Evan Saltzman
 ## Date Created:  10/28/2019
-## Date Edited:   3/17/2021
+## Date Edited:   3/21/2021
 ## Description:   This file calls all scripts necessary for estimating the effect of decision assistance on 
 ##                health insurance choice.
 

### 2021-03-22 finals/lunch-and-learn/lunch-learn-202103.Rmd
add presentation

---
title: "Insurance choice, decision assistance, and insurer steering"
subtitle: "Ian McCarthy & Evan Saltzman"
author: Emory University, Lunch and Learn
date: March 30, 2021 #"`r format(Sys.time(), '%d %B %Y')`"
header-includes: 
  - \usepackage{graphicx}
  - \usepackage{amsmath}
output:
#  html_document: default (toggle on for "simplified" view)
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, custom.css] 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      beforeInit: "macros.js"
#knit: pagedown::chrome_print
---

<!-- Adjust some CSS code for font size, maintain R code font size -->
<style type="text/css">
.remark-slide-content {
    font-size: 30px;
    padding: 1em 2em 1em 2em;    
}
.remark-code, .remark-inline-code { 
    font-size: 20px;
}
</style>

<!-- Set R options for how code chunks are displayed and load packages -->
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
options(dplyr.summarise.inform = FALSE)
library(knitr)
opts_chunk$set(
  fig.align="center",  
  fig.height=3, #fig.width=6,
  # out.width="748px", #out.length="520.75px",
  dpi=300, #fig.path='Figs/',
  cache=T#, echo=F, warning=F, message=F
  )

knitr::opts_hooks$set(fig.callout = function(options) {
  if(options$fig.callout) {
    options$echo = FALSE
  }
  options
})

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, xaringanExtra)
```

```{r xaringan-scribble, echo=FALSE}
xaringanExtra::use_scribble()
xaringanExtra::use_panelset()
```

# Insurance Choice is Confusing

.center[
  ![](slate-2017.png)
]

.footnote[
  [Slate, 2017](https://slate.com/business/2017/08/americans-are-overpaying-for-insurance-because-obamacare-is-confusing.html)
]

---
count: false

# Insurance Choice is Confusing
.center[
  ![](health-affairs-2017b.png)
]

.footnote[
  [Health Affairs, January, 2017](https://www.healthaffairs.org/doi/10.1377/hlthaff.2016.0472)
]

---
count: false

# Insurance Choice is Confusing
.center[
  ![](health-affairs-2017.png)
]

.footnote[
  [Health Affairs, August, 2017](https://www.healthaffairs.org/doi/full/10.1377/hlthaff.2017.0085)
]

---
count: false

# Insurance Choice is Confusing

  - "More than half of all uninsured (56%) say they are likely to go to the marketplace to find a health plan in the future. But there are knowledge gaps."
  - "Six in 10 are confused about or have not heard of the tax credit, and more than 7 in 10 want one-on-one help understanding their insurance options"

.footnote[
  [Robert Wood Johnson Foundation, **Understanding the Uninsured Now**, 2015](https://www.rwjf.org/en/library/research/2015/06/understanding-the-uninsured-now.html)
]

---
# Choice of plans has big consequences

### 2021-03-23 finals/lunch-and-learn/lunch-learn-202103.Rmd
update presentation

@@
 ```{r xaringan-scribble, echo=FALSE}
-xaringanExtra::use_scribble()
-xaringanExtra::use_panelset()
+xaringanExtra::use_scribble(rgb(0.9, 0.5, 0.5))
 ```
 
-# Insurance Choice is Confusing
+# Two motivating facts:
+
+1. Insurance choice is confusing, particularly on the ACA exchanges
+
+2. Size of the market introduces decision problems on a massive scale
+
+---
+# 1. Insurance choice is confusing
 
@@
 
-# Insurance Choice is Confusing
+# 1. Insurance choice is confusing
 .center[
@@
 
-# Insurance Choice is Confusing
+# 1. Insurance choice is confusing
+
 .center[
@@
 
-# Insurance Choice is Confusing
+# 1. Insurance choice is confusing
 
@@
 ---
-# Choice of plans has big consequences
+# 2. Potential scale
+
+- 12.7 million enrollees on exchanges in 2016
+- Down to 11.4 million in 2020
+- Over 27 million remain uninsured
+
+---
+count: false
+
+# 2. Potential scale
+
+.pull-left[
+Exchanges relatively large, but...
+
+- Large number of people still uninsured
+- Many eligible for some type of subsidy on exchanges
+]
+
+.pull-right[
+  ![:scale 150%](kff-uninsured.png)
+]
+
+.footnote[
+  [Kaiser Family Foundation, November, 2020](https://www.kff.org/policy-watch/millions-of-uninsured-americans-are-eligible-for-free-aca-health-insurance/)
+]
+
+---
+# This paper
+
+Lots of people participating in a very complicated decision. With this in mind, we ask the following questions:
+
+1. Does some form of decision assistance "help" in plan selection?
+2. Does the type of assistance matter (private versus public)?
+3. Do insurers use brokers/agents to steer people to different plans?
+4. What are the welfare effects of any such steering?
+
+---
+# Outline of talk
+
+1. [Background on the ACA](#background)
+2. [Data](#data)
+3. [Dominated choices](#dominated)
+4. [Effects of decision assistance](#decision-assist)
+5. [Insurer steering](#steering)
+
+---
+class: inverse, center, middle
+name: background
+
+# Background on the ACA exchanges
+
+<html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>
+
+---
+class: clear, center, middle
+
+![:scale 80%](https://media.giphy.com/media/Awb1k8lX8a3Re/giphy.gif)

### 2021-03-24 finals/lunch-and-learn/lunch-learn-202103.Rmd
update readme and add presentation link

@@
 
-# Two motivating facts:
+# Decisions are hard
+
+<iframe width="560" height="315" src="https://www.youtube.com/embed/oWXNf3JVWpI?start=146" frameborder="0" allowfullscreen></iframe>
+
+---
+# In the health insurance setting...
 
@@
 ![:scale 80%](https://media.giphy.com/media/Awb1k8lX8a3Re/giphy.gif)
+
+---
+# What are the exchanges?
+
+- Online marketplace to purchase private health insurance for those without insurance through their employers or other public programs
+
+- Intended to help fill the "coverage gap" for the 40+ million uninsured individuals in the U.S. (pre ACA)
+
+- Complicated program with various premium and cost-sharing subsidies, specific to a household
+
+---
+# Metal tiers
+
+.pull-left[
+To help with this complex decision, plans organized around tiers based on actuarial value
+]
+
+--
+
+.pull.right[
+  ![:scale 50%](metal_tiers.jpg)
+]
+
+---
+# Rating areas
+
+.pull-left[
+Insurers limited in ability to adjust premiums
+
+- Smoking
+- Age
+- Rating area
+]
+
+--
+
+.pull-right[
+  ![:scale 100%](CA_Rating_Regions2.jpg)
+]

### 2021-03-24 RunRender.R

@@ -1,63 +1,0 @@
-
-# Meta --------------------------------------------------------------------
-
-## Title:         Decision Assistance and Health Insurance Choice
-## Author:        Ian McCarthy & Evan Saltzman
-## Date Created:  10/28/2019
-## Date Edited:   2/3/2021
-## Description:   This file renders/runs all relevant R code for the project
-
-
-# Preliminaries -----------------------------------------------------------
-if (!require("pacman")) renv::install('pacman')
-pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stargazer, knitr, kableExtra,
-               lfe, modelr, mlogit, bookdown, future, parallel, nnet, mnlogit, mixl,
-               JuliaCall, future.apply, gtsummary, emo, twilio, SAScii, data.table)
-
-source('paths.R')
-source(paste0(common,"/common_functions.R"))
-julia_setup(JULIA_HOME=jsetup)
-
-
-# Import and clean data ---------------------------------------------------
-source('data-code/impute.SIPP.R')
-source('data-code/process.COVCAL.data.R')
-
-
-# Call analysis and set workspace for knitr -------------------------------
-source('analysis/_ChoiceModel.R')
-source('analysis/_SummaryStats.R')
-source('analysis/_DominatedChoices.R')
-source('analysis/_ChoiceSummary.R')
-
-
-julia.list=NULL
-for (i in 1:19) {
-  for (t in 2014:2017) {
-    julia.list <- c(julia.list, paste0("julia.data.",i,".",t), paste0("julia.oos.",i,".",t))
-  }
-}
-
-rm(list=c(julia.list, "data", "data.clean", "data.hh", "data.ind", "hh.clean", "hh.language",
-          "households", "max.age", "outside_logit", "plan.data", "sim.bs",
-          "choice.data"))
-save.image("data/R_workspace.Rdata")
-
-
-
-# Run abstract markdown ---------------------------------------------------
-load("data/R_workspace.Rdata")
-rmarkdown::render(input = '_Abstract_ASHEcon_201910.Rmd',
-                  output_format = 'all',
-                  output_file ='_Abstract_ASHEcon_201910')
-
-rmarkdown::render(input = '_Abstract_SHESG_202006.Rmd',
-                  output_format = 'all',
-                  output_file ='_Abstract_SHESG_202006')
-
-
-# Run paper markdown ---------------------------------------------------
-rmarkdown::render(input = 'Paper.Rmd',
-                  output_format = 'all',
-                  output_file ='Paper')
-

### 2021-03-24 finals/abstract-emory-lunchlearn-202103.tex

\documentclass[12pt]{article}
\usepackage{graphicx,amssymb,amsmath,setspace,comment,verbatim,titling,pgf,lscape,color}
\usepackage[left=2cm,right=2cm,top=2.5cm,bottom=2cm]{geometry}
\usepackage[round]{natbib}
\usepackage{hyperref}
\usepackage{array}
\usepackage{bbm}
\usepackage{marginnote}
\usepackage[justification=centering]{caption}
%%\usepackage{breqn}
\newcommand{\pderiv}[2]{\frac{\partial#1}{\partial#2}}
%\usepackage{siunitx}
\newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{#1}}
\hypersetup{colorlinks,%
						citecolor=black,%
						filecolor=black,%
						linkcolor=black,%
						urlcolor=blue,%
						}
\setstretch{1.5}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\setlength{\droptitle}{-50pt}

\title{Decision Assistance and Insurer Steering in Health Insurance}
\author{Ian McCarthy \& Evan Saltzman}
\date{March 2021}

\begin{document}
\maketitle

\subsubsection{Background:}
In some markets such as real estate, used automobiles, and insurance, consumers face significant cognitive challenges that may require the assistance of an agent or intermediary. The influence of agents on consumer decisions, and the firm's influence on the behaviors of its agents, have important implications for the efficiency of these markets. In this paper, we study the welfare effects of decision assistance and firm steering in health insurance. The complexity of choosing an optimal health insurance plan has been well-documented in studies of health insurance choice in the Medicare Advantage market, including \cite{abaluck2011}, \cite{ketcham2012}, and \cite{gruber2017}, among others. We expand on this literature by analyzing the effect of private insurance agents and publicly-financed navigators on health insurance plan choices. We then examine the extent to which insurance firms steer consumer choices through agent commissions. We quantify the welfare impact of decision assistance and simulate the effects of alternative commission policies.

\subsubsection{Data:}
We use consumer-level enrollment data from the California Affordable Care Act (ACA) exchange. Our final data consist of 8.3 million household-year observations from 2014 to 2019. The data include a variety of household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any). Using these data, we can precisely identify each household's choice set, the premium paid for each plan in the choice set, and any premium and cost sharing subsidies for which the household is eligible.

\subsubsection{Effects of decision assistance:}
Our initial analysis of the effects of decision assistance exploits the presence of ``dominated plans'' in the ACA exchanges. Specifically, consumers with incomes below 250\% of the federal povery level (FPL) can receive cost sharing subsidies if they purchase a silver tier plan. The subsidies have the effect of increasing the actuarial value of the silver plan. For consumers with incomes below 150\% of FPL, the actuarial value of the silver plan exceeds that of more expensive plans from the gold and platinum tiers, and hence gold and platinum plans are dominated for this income group. As a summary statistic, we estimate the relationship between decision assistance and dominated choices with a linear probability model, allowing for year, insurer, and region fixed effects. These results show that new enrollees using some form of decision assistance (agents or navigators) are approximately 0.9 percentage points less likely to make a dominated choice. On a base of 3.2\%, this reflects a 28\% decrease in the probability of making a dominated choice.

We then establish a causal relationship between decision assistance and insurance choice by embedding a nested logit discrete choice model into a standard potential outcomes framework. This analysis proceeds in three steps: 1) we estimate utility parameters on the subset of individuals without decision assistance; 2) we incorporate these parameters into the closed-form nested logit choice probabilities to estimate choices for the subset of ``treated'' individuals (i.e., those with some form of decision assistance); and 3) we take the difference between observed and predicted values to form our estimate of the average treatment effect on the treated. Standard errors are bootstrapped and clustered at the year/region level.

Consistent with our dominated choice analysis, we find that decision assistance has a statistically significant and economically meaningful effect on plan choice. We estimate that individuals are 50\% more likely to select a silver plan when using some form of decision assistance. The majority of this increase comes from a reduction in the selection of bronze plans, such that those using some decision assistance appear to be substituting out of bronze plans and into silver plans. We also find that individuals with decision assistance are about 12\% more likely to select a Kaiser plan and about 8\% more likely to select a Blue Cross Blue Shield plan. This is offset by over a 20\% decrease in the probability that an individual is uninsured, and about a 5\% reduction in the probability of selecting one of the many smaller health insurers in the exchanges.

Collectively, these results suggest that decision assistance can help consumers avoid making poor health insurance decisions. People with some assistance are much more likely to select a silver tier plan, and they are much less likely to remain uninsured. This is consistent with other documented patterns among enrollees on the exchanges, in which a large share of individuals either choose a dominated plan or remain uninsured despite having affordable plans available to them.

\subsubsection{Insurer steering:}
To examine the welfare effects of decision assistance and the presence of steering, we estimate a structural model of the California ACA exchange. Our model endogenizes consumer plan choices, premiums, and commissions, which allows us to simulate the welfare implications of decision assistance and firm steering. We study several counterfactuals designed to approximate a variety of policy proposals, including uniform commissions across firms, the banning of private insurance agents in favor of publicly-funded assistance, and the removal of all forms of decision assistance (e.g., defunding decision assistance entirely).

Preliminary results suggest that firms have considerable ability to steer consumers' decisions using agent commissions. For small firms, a \$1 increase in the plan commission has the same effect as a \$2 decrease in the plan premium on the probability of the plan being chosen. The effect is more pronounced for larger insurers, where a \$1 increase in the plan commission is equivalent to a \$3.50 decrease in the plan premium.

\subsubsection{Discussion:}
Our results provide strong evidence that decision assistance has a significant and economically meaningful effect on health insurance plan choice. Decision assistance in general tends to improve plan choices, increasing the probability that enrollees select a silver plan and decreasing the probability of making a dominated choice. Gains to social welfare are potentially offset by insurer steering, which introduces the potential for alternative agent compensation schemes to improve welfare in this market.

\pagebreak
\bibliographystyle{authordate1}
\bibliography{BibTeX_Library}

\clearpage
\newpage

\end{document}

### 2021-03-24 finals/lunch-and-learn/lunch-learn-202103.Rmd
center video slide
change iframe size
update presentation

@@
 
-# Decisions are hard
+# Some decisions are hard
 
-<iframe width="560" height="315" src="https://www.youtube.com/embed/oWXNf3JVWpI?start=146" frameborder="0" allowfullscreen></iframe>
+.center[
+<iframe width="800" height="500" src="https://www.youtube.com/embed/oWXNf3JVWpI?start=146&end=271" frameborder="0" allowfullscreen></iframe>
+]
 
@@
 ---
+class: inverse
+
 # Outline of talk
@@
 ]
+
+---
+# Popularity of the exchanges
+
+.center[
+![:scale 85%](aca-enrollment-graph.png)
+]
+
+---
+class: inverse, center, middle
+name: data
+
+# Data
+
+<html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>
+
+---
+class: inverse, center, middle
+name: dominated
+
+# Analysis of dominated choices
+
+<html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>
+
+---
+class: inverse, center, middle
+name: decision-assist
+
+# Effect of decision assistance
+
+<html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>
+
+---
+# Consumer choice model
+
+Household i's Utility for Plan j<br>
+
+$\begin{eqnarray}U_{ij} &=& \alpha_i \underbrace{p_{ij}}_{cons.\\prem.} \hspace{0.075in} + \hspace{0.075in} \underbrace{x'_{j}}_{obs.\\prod.} \beta \hspace{0.075in} + \hspace{0.075in} \underbrace{d'_{i}}_{dem.\\char.} \varphi \hspace{0.075in} + \hspace{0.075in} \underbrace{\xi_{j}}_{unobs.\\prod.} \hspace{0.075in} + \hspace{0.075in} \underbrace{\epsilon_{ij}}_{error} \nonumber\end{eqnarray}$
+
+where<br>
+
+$\begin{eqnarray*}\alpha_i &=& \alpha + d'_i \gamma \end{eqnarray*}$
+
+$\begin{eqnarray*}\underbrace{p_{ij}}_{cons.\\prem.} &=& \underbrace{r_{i}}_{rating\\ fact.} \underbrace{p_j}_{full\\prem.} \hspace{0.075in} - \hspace{0.075in} \underbrace{\max\{p_b - \mathrm{cap}_i,0\}}_{subsidy} \end{eqnarray*}$
+
+---
+count: false
+
+# Consumer choice model
+
+Utility for Outside Option (Uninsured)<br>
+
+$\begin{eqnarray*} U_{i0} &=& \alpha_i \underbrace{\rho_i}_{\textrm{penalty}} \hspace{0.075in} + \hspace{0.075in}  \underbrace{\epsilon_{i0}}_{error} \end{eqnarray*}$
+
+---
+class: inverse, center, middle
+name: steering
+
+# Analysis of insurer steering
+
+<html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>

### 2021-03-25 finals/lunch-and-learn/lunch-learn-202103.Rmd
update figures and presentation

@@
       ratio: "16:9"
-      beforeInit: "macros.js"
+      beforeInit: ["macros.js","https://platform.twitter.com/widgets.js"]
 #knit: pagedown::chrome_print
@@
 - "More than half of all uninsured (56%) say they are likely to go to the marketplace to find a health plan in the future. But there are knowledge gaps."
+
 - "Six in 10 are confused about or have not heard of the tax credit, and more than 7 in 10 want one-on-one help understanding their insurance options"
@@
 - 12.7 million enrollees on exchanges in 2016
+
 - Down to 11.4 million in 2020
+
 - Over 27 million remain uninsured
@@
 - Large number of people still uninsured
+
 - Many eligible for some type of subsidy on exchanges
@@
 1. Does some form of decision assistance "help" in plan selection?
-2. Does the type of assistance matter (private versus public)?
-3. Do insurers use brokers/agents to steer people to different plans?
-4. What are the welfare effects of any such steering?
+
+2. Do insurers use brokers/agents to steer people to different plans?
+
+3. What are the welfare effects of any such steering?
 
@@
 ---
+# Sources
+
+Main enrollment come from Covered California under FOIA. This includes:
+- Individual demographics and income
+- Plan purchases
+- Information on type of assistance (if any)
+
+Supplemental data include:
+- ACS and SIPP for predicting uninsured
+- ACA program data (contribution percentages, rating areas, etc.)
+
+---
+# Final data
+
+All analysis done at the household level...
+
+- **Initial data:** 16.9 million households from 2014-2019
+- Remove households with missing or inconsistent data
+  - 14.6 million remaining
+- Remove households predicted to be insured elsewhere
+  - 8.3 million remaining
+  - 4.5 million of which are new enrollees
+
+---
+# Enrollees over time
+
+.center[
+  ![:scale 50%](../../figures/enrollee_count.png)
+]
+
+---
+# Insurers
+
+.pull-left[
+  ![](../../figures/insurer_stack_any.png)
+]
+
+.pull-right[
+  ![](../../figures/insurer_stack_all.png)
+]
+
+---
+# Metal tier
+
+.pull-left[
+  ![](../../figures/metal_stack_any.png)
+]
+
+.pull-right[
+  ![](../../figures/metal_stack_all.png)
+
+]
+
+---
 class: inverse, center, middle
@@
 <html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>
+
+---
+# What is a dominated choice?
+
+.center[
+  ![](https://twitter.com/DaveEvansPhD/status/1234506064470716416?s=20)
+]
 

### 2021-03-25 analysis/decision-support/_SummaryStats.R

@@ -38,8 +38,7 @@ ggplot(hh.full) +
            position="fill", color="black", size=.1) +
   labs(
     x="Type of Assistance",
-    y="Relative Frequency",
-    title="Metal Tier by Type of Assistance"
+    y="Relative Frequency"
   ) + theme_bw() +
   theme(legend.title=element_blank()) +
   scale_fill_brewer(palette="Greys") + ggsave("figures/metal_stack_all.png")
@@ -49,8 +48,7 @@ ggplot(hh.full) +
            position="fill", color="black", size=.1) +
   labs(
     x=" ",
-    y="Relative Frequency",
-    title="Metal Tier by Assistance"
+    y="Relative Frequency"
   ) + theme_bw() +
   theme(legend.title=element_blank()) +
   scale_fill_brewer(palette="Greys") + ggsave("figures/metal_stack_any.png")
@@ -69,8 +67,7 @@ hh.full %>% mutate(insurer = case_when(
            position="fill", color="black", size=.1) +
   labs(
     x="Type of Assistance",
-    y="Relative Frequency",
-    title="Selected Insurer"
+    y="Relative Frequency"
   ) + theme_bw() +
   theme(legend.title=element_blank()) +
   scale_fill_brewer(palette="Greys") + ggsave("figures/insurer_stack_all.png")
@@ -88,8 +85,7 @@ hh.full %>% mutate(insurer = case_when(
            position="fill", color="black", size=.1) +
   labs(
     x=" ",
-    y="Relative Frequency",
-    title="Selected Insurer"
+    y="Relative Frequency"
   ) + theme_bw() +
   theme(legend.title=element_blank()) +
   scale_fill_brewer(palette="Greys") + ggsave("figures/insurer_stack_any.png")

### 2021-03-25 finals/lunch-and-learn/lunch-learn-202103.Rmd
update lunch and learn presentation

@@
 author: Emory University, Lunch and Learn
-date: March 30, 2021 #"`r format(Sys.time(), '%d %B %Y')`"
+date: March 29, 2021 #"`r format(Sys.time(), '%d %B %Y')`"
 header-includes: 
@@
 
+<center>
+<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr"><a href="https://twitter.com/DaveEvansPhD/status/1234506064470716416">March 2, 2020</a></blockquote><script async src="//platform.twitter.com/widgets.js" charset="utf-8"></script>
+</center>
+
+---
+count: false
+
+# What is a dominated choice?
+
+In our context...
+
+- Subsidies available for households with incomes below 250% of the FPL
+- At 150% of the FPL, larger subsidies are such that actuarial value of silver plans exceeds that of gold and platinum plans
+- Gold and platinum plans dominated by silver plans for incomes $\leq$ 150% FPL
+
+--
+
+About 3.2% of households make a dominated choice in our data
+
+---
+# Analysis of dominated choices
+
 .center[
-  ![](https://twitter.com/DaveEvansPhD/status/1234506064470716416?s=20)
+  ![](../../figures/dominated_choice_regression.png)
 ]
@@
 ---
+# Estimand of interest
+
+- Want to identify the Average Treatment Effect on the Treated (ATT) of decision assistance
+
+- Denote by $Pr[Y_{ij}^{1}]$ the probability of household $i$ selecting plan $j$ with decision assistance
+
+- Denote by $Pr[Y_{ij}^{0}]$ the probability of household $i$ selecting plan $j$ without decision assistance
+
+--
+
+$$ATT = Pr[Y_{ij}^{1} | \text{Assist}] - Pr[Y_{ij}^{0} | \text{Assist}]$$
+
+---
+# Estimation
+
+1. Estimate nested logit model among those without any decision assistance, $\hat{\theta}$
+
+2. Use $\hat{\theta}$ to form predicted counterfactual, $\widehat{Pr[Y_{ij}^{0} | \text{Assist}]}$
+
+3. Use predicted value in ATT estimate: $$\underbrace{Pr[Y_{ij}^{1} | \text{Assist}]}_{Observed} - \underbrace{\widehat{Pr[Y_{ij}^{0} | \text{Assist}]}}_{Predicted}$$
+
+4. Aggregate to level of insurer and metal
+
+---
+count: false
+
+# Estimation
+
+- Focus only on new enrollees to avoid presence of inertia
+
+- Estimate separately by year and rating area
+
+---
+# Inference
+
+- Clustered bootstrap, by year and rating area
+
+- 200 bootstrap replications
+
+- Confidence interval based on the 5th and 95th percentile of bootstrap replications
+
+---
+# Effects of decision assistance
+
+.pull-left[
+  ![](../../figures/choice_metals.png)
+]
+
+.pull-right[
+  ![](../../figures/choice_insurer.png)
+]
+
+---
 class: inverse, center, middle

### 2021-03-26 finals/lunch-and-learn/lunch-learn-202103.Rmd
fix scale of results figures
update slides

@@
 ---
-# Rating areas
+# Community rating rules
 
@@
 
-- Smoking
+- Smoking (not in CA)
 - Age
@@
 - Gold and platinum plans dominated by silver plans for incomes $\leq$ 150% FPL
+- Gold plans dominated by silver plans for incomes between 150% and 200% FPL
 
@@
 .center[
-  ![](../../figures/dominated_choice_regression.png)
+  ![:scale 50%](../../figures/dominated_choice_regression.png)
 ]

### 2021-03-29 finals/lunch-and-learn/lunch-learn-202103.Rmd
add switching analysis and update slides

@@
 ---
+# Analysis of switching
+
+.center[
+  ![:scale 50%](../../figures/switching_regression.png)
+]
+
+---
 class: inverse, center, middle
@@
 <html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>
+
+---
+# This is preliminary!
+
+.center[
+  ![:scale 50%](https://media.giphy.com/media/3o6Yg9rDXHL8Zrdlza/giphy.gif)
+]
+
+---
+# Agent compensation
+
+.pull-left[
+**Compensation schemes**
+
+- Flat commission 
+- Fixed amount from <span>&#36;</span>0 to <span>&#36;</span>264
+
+]
+
+.pull-right[
+  ![](flat_comm.jpg)
+]
+
+---
+count: false
+
+# Agent compensation
+
+.pull-left[
+**Compensation schemes**
+
+- Percentage commission
+- Percent of annual premium, from 1% to 5%
+]
+
+.pull-right[
+  ![](perc_comm.jpg)
+]
+
+---
+count: false
+
+# Agent compensation
+
+.pull-left[
+**Compensation schemes**
+
+- Flat commission, from <span>&#36;</span>0 to <span>&#36;</span>264
+- Percentage commission, from 1% to 5% of annual premium
+
+]
+
+--
+
+.pull-right[
+**Sources of variation**
+
+- Insurer
+- New enrollee versus renewal
+- Network type (e.g., HMO vs PPO)
+
+]
+
+---
+# Quantifying steering effect
+
+**Calculate commission elasticities of demand**
+
+1. Estimate nested logit choice model with commission as covariate
+2. Compute commission elasticity (percent change in demand for a 1% increase in commission)
+
+--
+
+|                | Agent Users   | All Enrollees  |
+| -------------- |:-------------:| --------------:|
+| Overall        | 11.18         | 5.39           |
+| Large Insurers | 11.94         | 5.75           |
+| Small Insurers | 6.33          | 3.08           |

### 2021-03-29 analysis/decision-support/_Switching.R

@@ -1,0 +1,63 @@
+# Meta --------------------------------------------------------------------
+
+## Date Created:  3/4/2020
+## Date Edited:   3/17/2021
+## Description:   Simple regressions of dominated choices
+
+
+# Initial Regressions -----------------------------------------------------
+
+mod1 <- feols(switch ~ assisted + english + spanish +
+                FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
+                perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
+                perc_other + household_size
+              | region + year + insurer, cluster="region",
+              data=hh.full)
+
+mod2 <- feols(switch ~ assisted + english + spanish +
+                FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
+                perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
+                perc_other + household_size
+             | household_id + year + insurer, cluster="household_id", 
+             data=hh.full)
+
+mod3 <- feols(dominated_choice ~ assisted + english + spanish +
+                FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
+                perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
+                perc_other + household_size
+              | region + year + insurer, cluster="region",
+              data=hh.full %>% filter(switch==1))
+
+
+dom.regs <- list("Switching \nRegion FE"=mod1, 
+                 "Switching \nHH FE"=mod2, 
+                 "Dominated choice \namong switchers"=mod3)
+
+modelplot(dom.regs, coef_map= c("assisted"="Assistance"), facet=TRUE, size=.1) + 
+  theme(strip.text.y=element_blank()) +
+  scale_x_continuous(limits=c(-0.050,0.3)) +
+  ggsave("figures/switching_regression.png")
+  
+  
+modelsummary(list("1"=mod1, "2"=mod2, "3"=mod3), 
+             coef_rename=c("assisted"="Assistance",
+                           "english"="English Speaking HH",
+                           "spanish"="Spanish Speacking HH",
+                           "FPL" = "Poverty Line",
+                           "perc_0to17" = "Share of HH < 18",
+                           "perc_18to25" = "Share of HH 18 to 25",
+                           "perc_26to34" = "Share of HH 26 to 34",
+                           "perc_35to44" = "Share of HH 35 to 44",
[…]

### 2021-03-29 analysis/decision-support/decision-analysis.R

@@ -124,7 +124,12 @@ hh.full <- hh.full %>%
          assisted=ifelse(channel=="Assisted",1,0),
          channel_detail=as.factor(channel_detail),
          any_agent=ifelse(broker==1 | agent==1, 1, 0),
-         new_enrollee=ifelse(is.na(previous_plan_offered),1,0))
+         new_enrollee=ifelse(is.na(previous_plan_offered),1,0),
+         switch=case_when(
+           new_enrollee==0 & !is.na(plan_number_nocsr) & !is.na(previous_plan_number) & plan_number_nocsr!=previous_plan_number ~ 1,
+           new_enrollee==0 & !is.na(plan_number_nocsr) & !is.na(previous_plan_number) & plan_number_nocsr==previous_plan_number ~ 0,
+           TRUE ~ NA_real_
+         ))
 
 
 ## Filter for only new purchases for plan choice analysis

### 2021-03-29 finals/lunch-and-learn/lunch-learn-202103.Rmd
update slides

@@
 .center[
-<iframe width="800" height="500" src="https://www.youtube.com/embed/oWXNf3JVWpI?start=146&end=271" frameborder="0" allowfullscreen></iframe>
+<iframe width="800" height="500" src="https://www.youtube.com/embed/oWXNf3JVWpI?start=146&end=272" frameborder="0" allowfullscreen></iframe>
 ]

### 2021-05-03 finals/abstract-ashecon-assa-2022.tex
Updates from Overleaf

--- 2021-03-24 finals/abstract-emory-lunchlearn-202103.tex
@@
 
-\subsubsection{Background:}
 In some markets such as real estate, used automobiles, and insurance, consumers face significant cognitive challenges that may require the assistance of an agent or intermediary.
@@
 In this paper, we study the welfare effects of decision assistance and firm steering in health insurance.
-The complexity of choosing an optimal health insurance plan has been well-documented in studies of health insurance choice in the Medicare Advantage market, including \cite{abaluck2011}, \cite{ketcham2012}, and \cite{gruber2017}, among others.
-We expand on this literature by analyzing the effect of private insurance agents and publicly-financed navigators on health insurance plan choices.
-We then examine the extent to which insurance firms steer consumer choices through agent commissions.
-We quantify the welfare impact of decision assistance and simulate the effects of alternative commission policies.
 
-\subsubsection{Data:}
-We use consumer-level enrollment data from the California Affordable Care Act (ACA) exchange.
-Our final data consist of 8.3 million household-year observations from 2014 to 2019.
+We use consumer-level enrollment data from the California Affordable Care Act (ACA) exchange, with 8.3 million household-year observations from 2014 to 2019.
 The data include a variety of household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any).
@@
 
-\subsubsection{Effects of decision assistance:}
-Our initial analysis of the effects of decision assistance exploits the presence of ``dominated plans'' in the ACA exchanges.
-Specifically, consumers with incomes below 250\% of the federal povery level (FPL) can receive cost sharing subsidies if they purchase a silver tier plan.
-The subsidies have the effect of increasing the actuarial value of the silver plan.
-For consumers with incomes below 150\% of FPL, the actuarial value of the silver plan exceeds that of more expensive plans from the gold and platinum tiers, and hence gold and platinum plans are dominated for this income group.
-As a summary statistic, we estimate the relationship between decision assistance and dominated choices with a linear probability model, allowing for year, insurer, and region fixed effects.
-These results show that new enrollees using some form of decision assistance (agents or navigators) are approximately 0.9 percentage points less likely to make a dominated choice.
-On a base of 3.2\%, this reflects a 28\% decrease in the probability of making a dominated choice.
+Our initial analysis exploits the presence of "dominated plans" in the ACA exchanges, where we find that new enrollees using some form of decision assistance (agents or navigators) are approximately 28\% less likely to make a dominated choice.
+We then examine the causal effect of decision assistance on health insurance choice.
+Here, we find that decision assistance has a statistically significant and economically meaningful effect on plan choice, with enrollees 50\% more likely to select a silver plan when using some form of decision assistance and 20\% less likely to be uninsured.
 
-We then establish a causal relationship between decision assistance and insurance choice by embedding a nested logit discrete choice model into a standard potential outcomes framework.
-This analysis proceeds in three steps: 1) we estimate utility parameters on the subset of individuals without decision assistance; 2) we incorporate these parameters into the closed-form nested logit choice probabilities to estimate choices for the subset of ``treated'' individuals (i.e., those with some form of decision assistance); and 3) we take the difference between observed and predicted values to form our estimate of the average treatment effect on the treated.
-Standard errors are bootstrapped and clustered at the year/region level.
-
-Consistent with our dominated choice analysis, we find that decision assistance has a statistically significant and economically meaningful effect on plan choice.
-We estimate that individuals are 50\% more likely to select a silver plan when using some form of decision assistance.
-The majority of this increase comes from a reduction in the selection of bronze plans, such that those using some decision assistance appear to be substituting out of bronze plans and into silver plans.
-We also find that individuals with decision assistance are about 12\% more likely to select a Kaiser plan and about 8\% more likely to select a Blue Cross Blue Shield plan.
-This is offset by over a 20\% decrease in the probability that an individual is uninsured, and about a 5\% reduction in the probability of selecting one of the many smaller health insurers in the exchanges.
-
-Collectively, these results suggest that decision assistance can help consumers avoid making poor health insurance decisions.
-People with some assistance are much more likely to select a silver tier plan, and they are much less likely to remain uninsured.
-This is consistent with other documented patterns among enrollees on the exchanges, in which a large share of individuals either choose a dominated plan or remain uninsured despite having affordable plans available to them.
-
-\subsubsection{Insurer steering:}
-To examine the welfare effects of decision assistance and the presence of steering, we estimate a structural model of the California ACA exchange.
-Our model endogenizes consumer plan choices, premiums, and commissions, which allows us to simulate the welfare implications of decision assistance and firm steering.
-We study several counterfactuals designed to approximate a variety of policy proposals, including uniform commissions across firms, the banning of private insurance agents in favor of publicly-funded assistance, and the removal of all forms of decision assistance (e.g., defunding decision assistance entirely).
-
+We then turn to a structural analysis of insurer steering, commissions, and premiums.
 Preliminary results suggest that firms have considerable ability to steer consumers' decisions using agent commissions.
@@
 
-\subsubsection{Discussion:}
 Our results provide strong evidence that decision assistance has a significant and economically meaningful effect on health insurance plan choice.
@@
 
-\pagebreak
-\bibliographystyle{authordate1}
-\bibliography{BibTeX_Library}
-
-\clearpage
-\newpage
-
 \end{document}

### 2021-05-03 finals/creed/creed-202105.Rmd
update presentations and filenames

--- 2021-03-29 finals/lunch-and-learn/lunch-learn-202103.Rmd
@@
 subtitle: "Ian McCarthy & Evan Saltzman"
-author: Emory University, Lunch and Learn
-date: March 29, 2021 #"`r format(Sys.time(), '%d %B %Y')`"
+author: Carolina Region Empirical Economics Day
+date: May 3, 2021 #"`r format(Sys.time(), '%d %B %Y')`"
 header-includes: 
@@
 .center[
-  ![](slate-2017.png)
+  ![](../pics/slate-2017.png)
 ]
@@
 .center[
-  ![](health-affairs-2017b.png)
+  ![](../pics/health-affairs-2017b.png)
 ]
@@
 .center[
-  ![](health-affairs-2017.png)
+  ![](../pics/health-affairs-2017.png)
 ]
@@
 .pull-right[
-  ![:scale 150%](kff-uninsured.png)
+  ![:scale 150%](../pics/kff-uninsured.png)
 ]
@@
 3. What are the welfare effects of any such steering?
+
+---
+# What's new?
+
+- Large literature on choice inconsistencies
+  - Abaluck and Gruber, *AER*, 2011
+  - Ketcham et al., *AER*, 2012
+  - Gruber, *JEP*, 2017
+
+- What's new here?
+  - Role of decision assistance in health
+  - Commissions and steering
 
@@
 .pull.right[
-  ![:scale 50%](metal_tiers.jpg)
+  ![:scale 50%](../pics/metal_tiers.jpg)
 ]
@@
 .pull-right[
-  ![:scale 100%](CA_Rating_Regions2.jpg)
+  ![:scale 100%](../pics/CA_Rating_Regions2.jpg)
 ]
@@
 .center[
-![:scale 85%](aca-enrollment-graph.png)
+![:scale 85%](../pics/aca-enrollment-graph.png)
 ]
@@
 .pull-right[
-  ![](flat_comm.jpg)
+  ![](../pics/flat_comm.jpg)
 ]
@@
 .pull-right[
-  ![](perc_comm.jpg)
+  ![](../pics/perc_comm.jpg)
 ]

### 2021-05-03 analysis/decision-support/_SummaryStats.R

@@ -150,8 +150,12 @@ hh.full <- hh.full %>%
     year==2019 ~ pred_assist_2019,
     TRUE ~ NA_real_
   )) %>%
-  select(-starts_with("pred_assist_"))
-
+  select(-starts_with("pred_assist_")) %>%
+  mutate(ipweight=case_when(
+    assisted==1 ~ 1,
+    assisted==0 ~ pred_assist/(1-pred_assist),
+    TRUE ~ NA_real_
+  ))
 
 hh.clean <- hh.clean %>%
   mutate(pred_assist=case_when(
@@ -163,7 +167,12 @@ hh.clean <- hh.clean %>%
     year==2019 ~ pred_assist_2019,
     TRUE ~ NA_real_
   )) %>%
-  select(-starts_with("pred_assist_"))
+  select(-starts_with("pred_assist_")) %>%
+  mutate(ipweight=case_when(
+    assisted==1 ~ 1,
+    assisted==0 ~ pred_assist/(1-pred_assist),
+    TRUE ~ NA_real_
+  ))
 
 ggplot(hh.full, aes(x=pred_assist)) + 
   geom_histogram() + 
@@ -191,11 +200,40 @@ ggplot(hh.clean, aes(x=pred_assist)) +
   theme_bw() + ggsave("figures/ps_assist_clean.png")
 
 
-## use bal.tab in love.plot with pred_assist as weights from prior estimation
-set.cobalt.options(binary="std")
-new.names <- c(FPL = "Federal Poverty Line")
 
-love.plot(assisted~)
+set.cobalt.options(binary="std")
+new.names <- c(FPL = "Federal Poverty Level",
+               perc_0to17 = "Percent below 18",
+               perc_18to25 = "Percent 18 to 25",
+               perc_65plus = "Percent 65+",
+               perc_black = "Percent Black",
+               perc_hispanic = "Percent Hispanic",
+               perc_asian = "Percent Asian",
+               perc_male = "Percent Male",
+               household_size = "HH Size")
+
+covs <- hh.full %>% select(FPL, perc_0to17, perc_18to25, perc_65plus, 
+                   perc_black, perc_hispanic, perc_asian, perc_male, 
+                   household_size)
+
+love.plot(bal.tab(covs, treat = hh.full$assisted, weights = hh.full$ipweight),
+          data=hh.full,
+          estimand="ATT",
+          stats=c("mean.diffs", "ks.statistics"),
+          var.order="unadjusted",
+          abs=TRUE,
+          line=FALSE,
[…]

### 2021-05-03 analysis/decision-support/_SummaryStats.R
update summary stats calculations

@@ -1,7 +1,7 @@
 # Meta --------------------------------------------------------------------
 
 ## Date Created:  10/11/2019
-## Date Edited:   3/17/2021
+## Date Edited:   5/3/2021
 ## Description:   Basic summary stats
 
 

### 2021-05-03 finals/creed/creed-202105.Rmd
update slides for creed

@@
 ---
-count: false
-
-# 1. Insurance choice is confusing
-
-- "More than half of all uninsured (56%) say they are likely to go to the marketplace to find a health plan in the future. But there are knowledge gaps."
-
-- "Six in 10 are confused about or have not heard of the tax credit, and more than 7 in 10 want one-on-one help understanding their insurance options"
-
-.footnote[
-  [Robert Wood Johnson Foundation, **Understanding the Uninsured Now**, 2015](https://www.rwjf.org/en/library/research/2015/06/understanding-the-uninsured-now.html)
-]
-
----
 # 2. Potential scale
@@
 
-1. [Background on the ACA](#background)
-2. [Data](#data)
-3. [Dominated choices](#dominated)
-4. [Effects of decision assistance](#decision-assist)
-5. [Insurer steering](#steering)
-
----
-class: inverse, center, middle
-name: background
-
-# Background on the ACA exchanges
-
-<html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>
-
----
-class: clear, center, middle
-
-![:scale 80%](https://media.giphy.com/media/Awb1k8lX8a3Re/giphy.gif)
-
----
-# What are the exchanges?
-
-- Online marketplace to purchase private health insurance for those without insurance through their employers or other public programs
-
-- Intended to help fill the "coverage gap" for the 40+ million uninsured individuals in the U.S. (pre ACA)
-
-- Complicated program with various premium and cost-sharing subsidies, specific to a household
-
----
-# Metal tiers
-
-.pull-left[
-To help with this complex decision, plans organized around tiers based on actuarial value
-]
-
---
-
-.pull.right[
-  ![:scale 50%](../pics/metal_tiers.jpg)
-]
-
----
-# Community rating rules
-
-.pull-left[
-Insurers limited in ability to adjust premiums
-
-- Smoking (not in CA)
-- Age
-- Rating area
-]
-
---
-
-.pull-right[
-  ![:scale 100%](../pics/CA_Rating_Regions2.jpg)
-]
-
----
-# Popularity of the exchanges
-
-.center[
-![:scale 85%](../pics/aca-enrollment-graph.png)
-]
+1. [Data](#data)
+2. [Dominated choices](#dominated)
+3. [Effects of decision assistance](#decision-assist)
+4. [Insurer steering](#steering)
 
@@
 - Information on type of assistance (if any)
+- 8.3 million households, 4.5 million new enrollees
 
@@
 - ACA program data (contribution percentages, rating areas, etc.)
-
----
-# Final data
-
-All analysis done at the household level...
-
-- **Initial data:** 16.9 million households from 2014-2019
-- Remove households with missing or inconsistent data
-  - 14.6 million remaining
-- Remove households predicted to be insured elsewhere
-  - 8.3 million remaining
-  - 4.5 million of which are new enrollees
-
----
-# Enrollees over time
-
-.center[
-  ![:scale 50%](../../figures/enrollee_count.png)
-]
 
@@
 
-- Denote by $Pr[Y_{ij}^{1}]$ the probability of household $i$ selecting plan $j$ with decision assistance
+- Denote by $N_{j}^{1} = \sum_{i} 1(Y_{ij}^{1}=1 | \text{Assist})$ the the count of enrollees in plan $j$ had they received decision assistance, conditional on receiving assistance
 
-- Denote by $Pr[Y_{ij}^{0}]$ the probability of household $i$ selecting plan $j$ without decision assistance
+- Denote by $N_{j}^{0} = \sum_{i} 1(Y_{ij}^{0}=1 | \text{Assist})$ the count of enrollees in plan $j$ had they not received decision assistance, conditional on receiving assistance
 
@@
 
-$$ATT = Pr[Y_{ij}^{1} | \text{Assist}] - Pr[Y_{ij}^{0} | \text{Assist}]$$
+$$ATT = N_{j}^{1} - N_{j}^{0} $$
 
@@
 
-2. Use $\hat{\theta}$ to form predicted counterfactual, $\widehat{Pr[Y_{ij}^{0} | \text{Assist}]}$
+2. Use $\hat{\theta}$ to form predicted counterfactual, $\hat{N}_{j}^{0} = \sum_{i} \widehat{Pr[Y_{ij}^{0} | \text{Assist}]}$
 
-3. Use predicted value in ATT estimate: $$\underbrace{Pr[Y_{ij}^{1} | \text{Assist}]}_{Observed} - \underbrace{\widehat{Pr[Y_{ij}^{0} | \text{Assist}]}}_{Predicted}$$
+3. Use predicted value in ATT estimate: $$\underbrace{N_{j}^{1}}_{Observed} - \underbrace{\hat{N}_{j}^{0}}_{Predicted}$$
 
-4. Aggregate to level of insurer and metal
+4. Aggregate to level of insurer and metal tier
 
@@
 - Estimate separately by year and rating area
+
+---
+# Selection on observables
+
+.pull-left[
+  ![](../../figures/cov_balance.png)
+]
+
+.pull-right[
+  ![](../../figures/ps_assist_full.png)
+
+]
 

### 2021-05-03 finals/creed/creed-202105.Rmd
update slides
creed slides

@@
 
-.pull-left[
-Exchanges relatively large, but...
-
-- Large number of people still uninsured
-
-- Many eligible for some type of subsidy on exchanges
-]
-
-.pull-right[
-  ![:scale 150%](../pics/kff-uninsured.png)
+.center[
+  ![:scale 200%](../pics/kff-uninsured.png)
 ]
@@
 ---
-# Analysis of dominated choices
+# Estimation and identification
+
+- Linear probability model of dominated choices or switching
+- Dummy variable for receiving any assistance
+- Selection on observables assumption (for now)
+
+---
+# Selection on observables
+
+.pull-left[
+  ![](../../figures/cov_balance.png)
+]
+
+.pull-right[
+  ![](../../figures/ps_assist_full.png)
+
+]
+
+---
+# Decision assistance and dominated choices
 
@@
 ---
-# Analysis of switching
+# Decision assistance and switching
 
@@
 
-# Effect of decision assistance
+# Effect of decision assistance on plan choice
 
@@
 - Estimate separately by year and rating area
-
----
-# Selection on observables
-
-.pull-left[
-  ![](../../figures/cov_balance.png)
-]
-
-.pull-right[
-  ![](../../figures/ps_assist_full.png)
-
-]
 

### 2021-05-03 finals/creed/creed-202105.Rmd
creed slides

@@
 .center[
-  ![:scale 200%](../pics/kff-uninsured.png)
-]
-
-.footnote[
-  [Kaiser Family Foundation, November, 2020](https://www.kff.org/policy-watch/millions-of-uninsured-americans-are-eligible-for-free-aca-health-insurance/)
+  ![:scale 75%](../pics/kff-uninsured.png)
 ]
@@
 ---
-# Consumer choice model
-
-Household i's Utility for Plan j<br>
-
-$\begin{eqnarray}U_{ij} &=& \alpha_i \underbrace{p_{ij}}_{cons.\\prem.} \hspace{0.075in} + \hspace{0.075in} \underbrace{x'_{j}}_{obs.\\prod.} \beta \hspace{0.075in} + \hspace{0.075in} \underbrace{d'_{i}}_{dem.\\char.} \varphi \hspace{0.075in} + \hspace{0.075in} \underbrace{\xi_{j}}_{unobs.\\prod.} \hspace{0.075in} + \hspace{0.075in} \underbrace{\epsilon_{ij}}_{error} \nonumber\end{eqnarray}$
-
-where<br>
-
-$\begin{eqnarray*}\alpha_i &=& \alpha + d'_i \gamma \end{eqnarray*}$
-
-$\begin{eqnarray*}\underbrace{p_{ij}}_{cons.\\prem.} &=& \underbrace{r_{i}}_{rating\\ fact.} \underbrace{p_j}_{full\\prem.} \hspace{0.075in} - \hspace{0.075in} \underbrace{\max\{p_b - \mathrm{cap}_i,0\}}_{subsidy} \end{eqnarray*}$
-
----
-count: false
-
-# Consumer choice model
-
-Utility for Outside Option (Uninsured)<br>
-
-$\begin{eqnarray*} U_{i0} &=& \alpha_i \underbrace{\rho_i}_{\textrm{penalty}} \hspace{0.075in} + \hspace{0.075in}  \underbrace{\epsilon_{i0}}_{error} \end{eqnarray*}$
+# Estimand of interest
 
@@
 
-- Denote by $N_{j}^{1} = \sum_{i} 1(Y_{ij}^{1}=1 | \text{Assist})$ the the count of enrollees in plan $j$ had they received decision assistance, conditional on receiving assistance
+- Denote by $Pr[Y_{ij}^{1}]$ the probability of household $i$ selecting plan $j$ with decision assistance
 
-- Denote by $N_{j}^{0} = \sum_{i} 1(Y_{ij}^{0}=1 | \text{Assist})$ the count of enrollees in plan $j$ had they not received decision assistance, conditional on receiving assistance
+- Denote by $Pr[Y_{ij}^{0}]$ the probability of household $i$ selecting plan $j$ without decision assistance
 
@@
 
-$$ATT = N_{j}^{1} - N_{j}^{0} $$
+$$ATT = Pr[Y_{ij}^{1} | \text{Assist}] - Pr[Y_{ij}^{0} | \text{Assist}]$$
 
@@
 
-1. Estimate nested logit model among those without any decision assistance, $\hat{\theta}$
+1. Estimate multinomial logit model among those without any decision assistance, $\hat{\theta}$
 
-2. Use $\hat{\theta}$ to form predicted counterfactual, $\hat{N}_{j}^{0} = \sum_{i} \widehat{Pr[Y_{ij}^{0} | \text{Assist}]}$
+2. Use $\hat{\theta}$ to form predicted counterfactual, $\widehat{Pr[Y_{ij}^{0} | \text{Assist}]}$
 
-3. Use predicted value in ATT estimate: $$\underbrace{N_{j}^{1}}_{Observed} - \underbrace{\hat{N}_{j}^{0}}_{Predicted}$$
+3. Use predicted value in ATT estimate: $$\underbrace{Pr[Y_{ij}^{1} | \text{Assist}]}_{Observed} - \underbrace{\widehat{Pr[Y_{ij}^{0} | \text{Assist}]}}_{Predicted}$$
 
-4. Aggregate to level of insurer and metal tier
+4. Aggregate to level of insurer and metal
 

### 2021-05-26 analysis/decision-support/_ChoiceModel.R
major update - manual loops to deal with mmlogit nest errors

@@ -10,12 +10,11 @@ time.dat <- 2014:2019
 area.dat <- as.list(unique.region)$region
 
 # Estimate model ----------------------------------------------------------
-plan(multisession, workers=4)
-future.tracking <- c("time.dat","area.dat", "is.error")
-
 source('analysis/decision-support/choice_data_function.R')
 source('analysis/decision-support/choice_est_function.R')
 source('analysis/decision-support/choice_est_bs_function.R')
+
+
 for (t in time.dat) {
   
   step=0
@@ -28,6 +27,8 @@ for (t in time.dat) {
     nest.names <- unique(choice.data$est.data$plan_name)
     nest.in <- nest.names[nest.names != "Uninsured"]
     nest.out <- nest.names[nest.names == "Uninsured"]
+    assign(paste0("nest.in.",r,".",t), nest.in)
+    assign(paste0("nest.out.",r,".",t), nest.out)
     
     choice.est <- dchoice.est(d=choice.data$est.data, oos=choice.data$oos.data, t=t, r=r)
     
@@ -40,7 +41,6 @@ for (t in time.dat) {
       final.data <- bind_rows(final.data, treated.dat)
       final.coef <- bind_rows(final.coef, coef.vals)
     }
-    future.tracking <- c(future.tracking, paste0("est.data.",r,".",t), paste0("oos.data.",r,".",t), "nest.in", "nest.out")      
   }
   
   assign(paste0("final.data.",t),final.data)
@@ -65,35 +65,66 @@ for (t in time.dat) {
 all.coef <- bs.starting
 all.prob <- est.prob
 
-future.tracking <- c(future.tracking, "bs.starting")
-
 
 # Bootstrap Standard Errors -----------------------------------------------
-bootsrp <- function(j) {
+max.boot <- 200
+
+for (b in 1:max.boot) {
+
   t.samp <- sample_n(as.data.frame(time.dat), size=length(time.dat), replace=T)
   a.samp <- sample_n(as.data.frame(area.dat), size=length(area.dat), replace=T)
-  bs.choice <- dchoice.bs(time=as.list(t.samp)$time.dat, area=as.list(a.samp)$area.dat)
-  return(list("coef"=bs.choice$coef, "pred"=bs.choice$pred))
+  
+  tlist=as.list(t.samp)$time.dat
+  rlist=as.list(a.samp)$area.dat
+  for (t in tlist) {
[…]

### 2021-05-26 analysis/decision-support/_DominatedChoices.R

@@ -12,51 +12,18 @@ mod1 <- feols(dominated_choice ~ assisted + english + spanish +
                 perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
                 perc_other + household_size + new_enrollee 
               | region + year + insurer, cluster="region",
-              data=hh.full)
+              data=hh.full, weights=hh.full$ipweight)
+
 
 mod2 <- feols(dominated_choice ~ assisted + english + spanish +
-               FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
-               perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
-               perc_other + household_size + SEP + new_enrollee 
-             | region + year + insurer, cluster="region",
-     data=hh.full)
-
-
-mod3 <- feols(dominated_choice ~ assisted + english + spanish +
-                FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
-                perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
-                perc_other + household_size + new_enrollee 
-             | household_id + year + insurer, cluster="household_id", 
-             data=hh.full)
-
-mod4 <- feols(dominated_choice ~ assisted + english + spanish +
-                FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
-                perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
-                perc_other + household_size + SEP + new_enrollee 
-              | household_id + year + insurer, cluster="household_id", 
-              data=hh.full)
-
-
-mod5 <- feols(dominated_choice ~ assisted + english + spanish +
                 FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +
                 perc_45to54 + perc_male + perc_asian + perc_black + perc_hispanic +
                 perc_other + household_size
               | region + year + insurer, cluster="region",
-              data=hh.clean)
+              data=hh.clean, weights=hh.clean$ipweight)
 
-mod6 <- feols(dominated_choice ~ assisted + english + spanish +
[…]

### 2021-05-26 analysis/decision-support/choice_data_function_map.R

@@ -7,19 +7,17 @@
 
 # Estimation function -----------------------------------------------------
 
-choice.data.fnc <- function(t, r) {
-  
-  a.thresh <- as.numeric(afford.threshold %>% filter(year==t) %>% select(cutoff))
+choice.data.fnc2 <- function(plans, hhs) {
+
   outside=tibble(
     plan_name="Uninsured",
-    region=r,
     Issuer_Name="Outside_Option"
   )
   
-  choice.set <- plan_data %>% filter(Year==t, region==r) %>%
-    select(plan_name=Plan_Name2, Issuer_Name=Insurer, region, PLAN_NETWORK_TYPE, metal_level=Metal_Level, metal, 
+  choice.set <- as_tibble(plans) %>% 
+    select(plan_name=Plan_Name2, Issuer_Name=Insurer, PLAN_NETWORK_TYPE, metal_level=Metal_Level, metal, 
            Premium, MSP, HSA) %>%
-    group_by(plan_name, region) %>%
+    group_by(plan_name) %>%
     summarize(Issuer_Name=first(Issuer_Name),
               PLAN_NETWORK_TYPE=first(PLAN_NETWORK_TYPE),
               metal_level=first(metal_level),
@@ -32,11 +30,11 @@ choice.data.fnc <- function(t, r) {
     bind_rows(outside)
   
   
-  full.choice.data <- hh.clean %>% filter(year==t, region==r) %>%
-    select(household_id, year, zip3, FPL, subsidized_members, hh_region=region, hh_rating=rating_factor,
+  full.choice.data <- as_tibble(hhs) %>% 
+    select(household_id, zip3, FPL, subsidized_members, hh_rating=rating_factor,
            hh_plan_number = plan_number_nocsr, hh_plan_id=plan_id, penalty, hh_insurer=insurer,
-           hh_plan_name = plan_name, oldest_member, cheapest_premium, subsidy, poverty_threshold) %>%
-    full_join(choice.set, by=c("hh_region"="region")) 
+           hh_plan_name = plan_name, oldest_member, cheapest_premium, subsidy, poverty_threshold, cutoff) %>%
+    merge(choice.set) 
   
   
   ## Remove plans that are not available for specific households.
@@ -61,7 +59,7 @@ choice.data.fnc <- function(t, r) {
       eff_premium = case_when(
         subsidized_members>0 ~ (cheapest_premium-subsidy)*12,
[…]

### 2021-05-26 analysis/decision-support/choice_est_bs_function.R

@@ -7,113 +7,54 @@
 
 # Estimation function -----------------------------------------------------
 
-dchoice.bs <- function(time, area) {
+dchoice.bs <- function(t, r) {
   
-  for (t in time) {
-    
-    a.thresh <- as.numeric(afford.threshold %>% filter(year==t) %>% select(cutoff))
-    
-    step=0
-    for (r in area) {
-      step=step+1
-    
-      #choice.bs <- choice.data.fnc(t=t,r=r)
-      #est.data <- choice.bs$est.data
-      #oos.data <- choice.bs$oos.data
-      est.data <- get(paste0("est.data.",r,".",t))
-      oos.data <- get(paste0("oos.data.",r,".",t))
+  est.data <- get(paste0("est.data.",r,".",t))
+  oos.data <- get(paste0("oos.data.",r,".",t))
 
-      ## Select bootstrap sample (within area and year)
-      unique.hh <- est.data %>%
-        group_by(household_number) %>%
-        mutate(hh_count=seq(n())) %>%
-        filter(hh_count==1) %>%
-        select(household_number) %>% ungroup()
-      sample.hh <- sample_n(unique.hh, size=nrow(unique.hh), replace=TRUE)
-      est.data <- est.data %>%
-        inner_join(sample.hh, by=c("household_number"))
-      
-      
-      ## Set up model and starting values
-      all_covars <- as.list(bs.starting %>% filter(region==r, year==t) %>% select(variable))$variable
-      mclogit.formula <- formula(paste("cbind(choice, household_number) ~", paste(all_covars, collapse=" + ")))
-      beta_initial <- as.list(bs.starting %>% filter(region==r, year==t) %>% select(estimate))$estimate
+  ## Set up model and starting values
+  all_covars <- as.list(bs.starting %>% filter(region==r, year==t, variable!="iv") %>% select(variable))$variable
+  mclogit.formula <- formula(paste("cbind(choice, household_number) ~", paste(all_covars, collapse=" + ")))
+  beta_initial <- as.list(bs.starting %>% filter(region==r, year==t, variable!="iv") %>% select(estimate))$estimate
 
-      nested.data <- mlogit.data(est.data, choice="choice", shape="long", chid.var = "household_number", alt.var="plan_name")
-      nested.formula <- formula(paste("choice ~", paste(all_covars, collapse=" + "),"| 0"))  
[…]

### 2021-05-26 analysis/decision-support/choice_est_function_map.R

@@ -8,7 +8,7 @@
 
 # Estimation function -----------------------------------------------------
 
-dchoice.est <- function(d, oos, t, r) {
+dchoice.reg <- function(d, names) {
 
   ## Terms for estimation
   all_covars=c("premium", "silver")
@@ -51,54 +51,42 @@ dchoice.est <- function(d, oos, t, r) {
   nested.formula <- formula(paste("choice ~", paste(all_covars, collapse=" + "),"| 0"))  
   logit.formula <- formula(paste("choice ~", paste(all_covars, collapse=" + ")))
   
-
-  ## Find initial values from logit and apply to mclogit
+  ## Find initial values from logit and apply to nested logit
   logit.start <- glm(logit.formula, data=d, family="binomial")
-  test <- is.error(mlogit(nested.formula, data=nested.data, weights=ipweight, nests=list(insured=nest.in, uninsured=nest.out), un.nest.el=TRUE))
+  test <- is.error(mlogit(nested.formula, data=nested.data, weights=ipweight, nests=list(insured=names, uninsured="Uninsured"), un.nest.el=TRUE))
   if (test==FALSE) {
-#    mc.logit <- mclogit(mclogit.formula, data=d)
-    nested.logit <- mlogit(nested.formula, data=nested.data, weights=ipweight, nests=list(insured=nest.in, uninsured=nest.out), un.nest.el=TRUE)
+    nested.logit <- mlogit(nested.formula, data=nested.data, weights=ipweight, nests=list(insured=names, uninsured="Uninsured"), un.nest.el=TRUE)
   } else {
-#    mc.logit <- mclogit(mclogit.formula, data=d, start=logit.start$coefficients[2:length(logit.start$coefficients)])
-    nested.logit <- mlogit(nested.formula, data=nested.data, weights=ipweight, nests=list(insured=nest.in, uninsured=nest.out), un.nest.el=TRUE,
+    nested.logit <- mlogit(nested.formula, data=nested.data, weights=ipweight, nests=list(insured=names, uninsured="Uninsured"), un.nest.el=TRUE,
                            start=logit.start$coefficients[2:length(logit.start$coefficients)])    
   }
 
-
-  ## MCLogit estimation
-  coef.name <- as_tibble(names(nested.logit$coefficients)) %>%
-    rename("variable"=value)
-  coef.est <- as_tibble(nested.logit$coefficients) %>%
-    rename("estimate"=value)
[…]

### 2021-05-26 analysis/decision-support/decision-analysis.R

@@ -4,7 +4,7 @@
 ## Title:         Decision Assistance and Health Insurance Choice
 ## Author:        Ian McCarthy & Evan Saltzman
 ## Date Created:  10/28/2019
-## Date Edited:   4/28/2021
+## Date Edited:   5/18/2021
 ## Description:   This file calls all scripts necessary for estimating the effect of decision assistance on 
 ##                health insurance choice.
 
@@ -12,9 +12,9 @@
 # Preliminaries -----------------------------------------------------------
 if (!require("pacman")) renv::install('pacman')
 pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stargazer, knitr, kableExtra,
-               lfe, modelr, mclogit, bookdown, future, parallel, nnet, mixl, fixest,
+               lfe, modelr, mclogit, bookdown, parallel, nnet, mixl, fixest,
                future.apply, gtsummary, emo, twilio, SAScii, data.table, scales, mlogit,
-               modelsummary, cobalt, WeightIt)
+               modelsummary, cobalt, WeightIt, broom, tidymodels)
 
 source('paths.R')
 source(paste0(common,"/common_functions.R"))
@@ -137,13 +137,13 @@ hh.clean <- hh.full %>%
   filter(is.na(previous_plan_offered))
   
 
-
 # Run analysis scripts ----------------------------------------------------
 
 source('analysis/decision-support/_SummaryStats.R')
 source('analysis/decision-support/_DominatedChoices.R')
 
-rm("hh.full","households","max.age","language","hh.language","panel.length")
+rm("hh.full","households","max.age","language","hh.language","panel.length",
+   "hh.nest","mod.full","bs.hh.data","sim.bs")
 source('analysis/decision-support/_ChoiceModel.R')
 source('analysis/decision-support/_ChoiceSummary.R')
 

### 2021-06-08 analysis/decision-support/_ChoiceModel.R
update estimation with nested logit and purrr, add summary stats

@@ -9,122 +9,261 @@ unique.region <- hh.clean %>% distinct(region)
 time.dat <- 2014:2019
 area.dat <- as.list(unique.region)$region
 
-# Estimate model ----------------------------------------------------------
-source('analysis/decision-support/choice_data_function.R')
-source('analysis/decision-support/choice_est_function.R')
-source('analysis/decision-support/choice_est_bs_function.R')
 
 
-for (t in time.dat) {
+# Estimate with purrr -----------------------------------------------------
+
+hh.nest <- hh.clean %>%
+  left_join(afford.threshold, by="year") %>%
+  nest(-c(region, year))
+
+plan.nest <- plan_data %>%
+  rename(year=Year) %>%
+  nest(-c(region, year))
+
+region.year <- as_tibble(merge(time.dat, area.dat)) %>%
+  rename(region=y, year=x)
+
+source('analysis/decision-support/choice_data_function_map.R')
+source('analysis/decision-support/choice_est_function_map.R')
+full.nest <- region.year %>%
+  left_join(hh.nest, by=c("region","year")) %>%
+  rename(hh_nest=data) %>%
+  left_join(plan.nest, by=c("region", "year")) %>%
+  rename(plan_nest=data) %>%
+  group_by(region, year) %>%
+  mutate(data_full = map2(hh_nest, plan_nest, ~choice.data.fnc2(hhs=.x, plans=.y)),
+         data.est=map(data_full,~filter(., assisted==0)),
+         data.oos=map(data_full,~filter(., assisted==1))) 
+
+choice.regs <- full.nest %>%
+  mutate(nest_names = map(data.est, ~unique(.x$plan_name)),
+         nest1=map(nest_names, ~.x[.x !="Uninsured"])) %>%
+  mutate( regs = map2(data.est, nest1, ~dchoice.reg(d=.x, nest.names=.y)),
+          tidied = map(regs, tidy),
+          pred = data.est)
+
+for (i in nrow(choice.regs)) {
+  oos.nest <- mlogit.data(choice.regs$data_full[[i]], choice="choice", shape="long", chid.var = "household_number", alt.var="plan_name")
+  nest.coef <- choice.regs$regs[[i]]
+  nest.names <- choice.regs$nest1[[i]]
+  nested.pred <- predict(nest.coef, newdata=oos.nest)  
[…]

### 2021-06-08 analysis/decision-support/_DominatedChoices.R

@@ -79,17 +79,12 @@ mod.full <- hh.nest %>%
 
 ## bootstrap standard errors
 max.boot <- 200
-bs.hh.data <- bootstraps(hh.nest, times=max.boot)
-
 bootsrp.dom <- function(j) {
-  bs.dom.dat <- analysis(bs.hh.data$splits[[j]]) %>% 
-    unnest(data) %>%
-    nest(-c(region,year))
-  
-  bs.dom.run <- bs.dom.dat %>%
-    mutate(data.est=map(data,~filter(., assisted==0)),
-           data.oos=map(data,~filter(., assisted==1))) %>%
-    select(-data) %>%
+  bs.dom.run <- hh.nest %>%
+    mutate(data.bs=map(data, ~slice_sample(.x, n=nrow(.x), replace=TRUE)),
+           data.est=map(data.bs,~filter(., assisted==0)),
+           data.oos=map(data.bs,~filter(., assisted==1))) %>%
+    select(-c(data, data.bs)) %>%
     mutate( regs = map(data.est, 
                        ~feglm(dominated_choice ~ english + spanish +
                                 FPL + perc_0to17 + perc_18to25 + perc_26to34 + perc_35to44 +

### 2021-06-08 analysis/decision-support/_SummaryStats.R

@@ -239,9 +239,118 @@ ggsave("figures/cov_balance.png")
 
 summary(panel.length$year_obs)
 mean.dom.choice <- mean(hh.clean$dominated_choice, na.rm=T)
-tot.enroll <- sum(enrollee.count.all$enroll_count)*1000
-tot.enroll.new <- sum(enrollee.count.new$enroll_count)*1000
-unique.enroll <- nrow(hh.full %>% distinct(household_id))
+tot.enroll <- sum(enrollee.count.all$enroll_count)
+tot.enroll.new <- sum(enrollee.count.new$enroll_count)
 first.year <- min(enrollee.count$year)
 last.year <- max(enrollee.count$year)
+
+
+
+# # Summary tables ----------------------------------------------------------
+
+## household summary statistics
+sum.stats.data <- hh.full %>% ungroup() %>%
+  mutate(FPL_low=if_else(FPL_bracket=="138orless",1,0),
+         FPL_250=if_else(FPL_bracket=="138to250",1,0),
+         FPL_400=if_else(FPL_bracket=="250to400",1,0),
+         FPL_high=if_else(FPL_bracket=="400ormore",1,0),
+         Kaiser=if_else(insurer=="Kaiser",1,0),
+         Anthem=if_else(insurer=="Anthem",1,0),
+         BlueShield=if_else(insurer=="Blue_Shield",1,0),
+         HealthNet=if_else(insurer=="Health_Net",1,0),
+         Other=if_else(insurer %in% c("Kaiser","Anthem","Blue_Shield","Health_Net"),0,1),
+         Bronze=if_else(metal=="Bronze",1,0),
+         Silver=if_else(metal=="Silver",1,0),
+         Gold=if_else(metal=="Gold",1,0),         
+         Platinum=if_else(metal=="Platinum",1,0),
+         Catastrophic=if_else(metal=="Catastrophic",1,0),
+         HMO=if_else(plan_network_type=="HMO",1,0),
+         PPO=if_else(plan_network_type=="PPO",1,0),
+         EPO=if_else(plan_network_type=="EPO",1,0),
+         HSP=if_else(plan_network_type=="HSP",1,0)) %>%
+  select(starts_with("FPL_"),Kaiser, Anthem, BlueShield, HealthNet, Other, Bronze, Silver, Gold, Platinum, Catastrophic, HMO, PPO, EPO, HSP,
+         assisted, navigator, any_agent, household_size, num_children_subject, perc_black, perc_hispanic, perc_white)
[…]

### 2021-06-08 analysis/decision-support/choice_data_function_map.R

@@ -216,7 +216,7 @@ choice.data.fnc2 <- function(plans, hhs) {
     mutate(hh_count=seq(n())) %>%
     filter(hh_count==1) %>%
     select(household_number) %>% ungroup()
-  sample.hh.oos <- sample_frac(unique.hh.oos, size=0.2, replace=FALSE)
+  sample.hh.oos <- sample_frac(unique.hh.oos, size=0.15, replace=FALSE)
   
     
   ## Final data

### 2021-06-08 analysis/decision-support/choice_est_bs_function.R

@@ -12,26 +12,42 @@ dchoice.bs <- function(t, r) {
   est.data <- get(paste0("est.data.",r,".",t))
   oos.data <- get(paste0("oos.data.",r,".",t))
 
+
+  # oos.data <- oos.data %>%
+  #   inner_join(est.data.bs %>% distinct(plan_name),
+  #              by="plan_name") %>%
+  #   group_by(household_number) %>%
+  #   mutate(any_choice=max(choice)) %>%
+  #   filter(any_choice==1) %>%
+  #   ungroup() %>%
+  #   select(-any_choice)
+  
   ## Set up model and starting values
   all_covars <- as.list(bs.starting %>% filter(region==r, year==t, variable!="iv") %>% select(variable))$variable
-  mclogit.formula <- formula(paste("cbind(choice, household_number) ~", paste(all_covars, collapse=" + ")))
-  beta_initial <- as.list(bs.starting %>% filter(region==r, year==t, variable!="iv") %>% select(estimate))$estimate
-
-  nested.data <- mlogit.data(est.data, choice="choice", shape="long", chid.var = "household_number", alt.var="plan_name")
   nested.formula <- formula(paste("choice ~", paste(all_covars, collapse=" + "),"| 0")) 
-    
+  beta_initial <- as.list(bs.starting %>% filter(region==r, year==t, variable!="iv") %>% select(estimate))$estimate
+  
   ## Estimate model and store results
-  test <- is.error(mlogit(nested.formula, data=nested.data, weights=ipweight, 
-                          nests=list(insured=nest.in, uninsured=nest.out), un.nest.el=TRUE, start=beta_initial))
-  if (test==FALSE) {
-    nested.logit <- mlogit(nested.formula, data=nested.data, weights=ipweight,
-                           nests=list(insured=nest.in, uninsured=nest.out), un.nest.el=TRUE,
-                           start=beta_initial)        
-  } else {
-    nested.logit <- mlogit(nested.formula, data=nested.data, weights=ipweight,
-                           nests=list(insured=nest.in, uninsured=nest.out), un.nest.el=TRUE)        
+  test <- TRUE
+  while (test==TRUE) {
+    est.data.bs <- est.data %>%
+      nest(-household_number)
+        
+    est.data.bs <- slice_sample(est.data.bs, n=nrow(est.data.bs), replace=TRUE) %>%
+      mutate(household_number=cur_group_rows()) %>%
+      unnest(data)
+
[…]

### 2021-06-08 analysis/decision-support/choice_est_function.R

@@ -11,8 +11,8 @@
 dchoice.est <- function(d, oos, t, r) {
 
   ## Terms for estimation
-  all_covars=c("premium", "silver")
-  ins.offer <- c(0,0)
+  all_covars=c("premium", "silver","hh_size_prem","AV")
+  ins.offer <- c(0,0,0,0)
   cml.share <- 0
   tot.choice <- sum(d$choice==1)
   ins.offer[1] <- sum(d$Anthem==1 & d$choice==1)/tot.choice

### 2021-06-08 analysis/decision-support/choice_est_function_map.R

@@ -8,10 +8,10 @@
 
 # Estimation function -----------------------------------------------------
 
-dchoice.reg <- function(d, names) {
+dchoice.reg <- function(d, nest.names) {
 
   ## Terms for estimation
-  all_covars=c("premium", "silver")
+  all_covars=c("premium", "silver", "AV")
   ins.offer <- c(0,0)
   cml.share <- 0
   tot.choice <- sum(d$choice==1)
@@ -53,40 +53,15 @@ dchoice.reg <- function(d, names) {
   
   ## Find initial values from logit and apply to nested logit
   logit.start <- glm(logit.formula, data=d, family="binomial")
-  test <- is.error(mlogit(nested.formula, data=nested.data, weights=ipweight, nests=list(insured=names, uninsured="Uninsured"), un.nest.el=TRUE))
+  test <- is.error(mlogit(nested.formula, data=nested.data, weights=ipweight, nests=list(insured=nest.names, uninsured="Uninsured"), un.nest.el=TRUE))
   if (test==FALSE) {
-    nested.logit <- mlogit(nested.formula, data=nested.data, weights=ipweight, nests=list(insured=names, uninsured="Uninsured"), un.nest.el=TRUE)
+    nested.logit <- mlogit(nested.formula, data=nested.data, weights=ipweight, nests=list(insured=nest.names, uninsured="Uninsured"), un.nest.el=TRUE)
   } else {
-    nested.logit <- mlogit(nested.formula, data=nested.data, weights=ipweight, nests=list(insured=names, uninsured="Uninsured"), un.nest.el=TRUE,
+    nested.logit <- mlogit(nested.formula, data=nested.data, weights=ipweight, nests=list(insured=nest.names, uninsured="Uninsured"), un.nest.el=TRUE,
                            start=logit.start$coefficients[2:length(logit.start$coefficients)])    
   }
 
   ## Finalize data for output
   return(nested.logit)
         
-}
-  
-dchoice.pred <- function(data, regcoef) {
-  
-  ## Out of sample predictions (predicted values for treated group)
-  oos.nest <- mlogit.data(data, choice="choice", shape="long", chid.var = "household_number", alt.var="plan_name")
-  oos <- data %>%
-    filter(assisted==0)
-  
-  nested.pred <- predict(regcoef, newdata=oos.nest)  
-  return(nested.pred)
-}  
-  
-  
[…]

### 2021-06-08 analysis/decision-support/decision-analysis.R

@@ -4,7 +4,7 @@
 ## Title:         Decision Assistance and Health Insurance Choice
 ## Author:        Ian McCarthy & Evan Saltzman
 ## Date Created:  10/28/2019
-## Date Edited:   5/18/2021
+## Date Edited:   6/1/2021
 ## Description:   This file calls all scripts necessary for estimating the effect of decision assistance on 
 ##                health insurance choice.
 
@@ -140,10 +140,10 @@ hh.clean <- hh.full %>%
 # Run analysis scripts ----------------------------------------------------
 
 source('analysis/decision-support/_SummaryStats.R')
-source('analysis/decision-support/_DominatedChoices.R')
+#source('analysis/decision-support/_DominatedChoices.R')
 
 rm("hh.full","households","max.age","language","hh.language","panel.length",
-   "hh.nest","mod.full","bs.hh.data","sim.bs")
+   "hh.nest","mod.full", "sim.bs")
 source('analysis/decision-support/_ChoiceModel.R')
 source('analysis/decision-support/_ChoiceSummary.R')
 

### 2021-06-08 finals/paper.tex
Updates from Overleaf

\documentclass[12pt]{article}
\usepackage{graphicx,amssymb,amsmath,setspace,comment,verbatim,titling,pgf,lscape,color}
\usepackage[left=2cm,right=2cm,top=2.5cm,bottom=2cm]{geometry}
\usepackage[round]{natbib}
\usepackage{hyperref}
\usepackage{array}
\usepackage{bbm}
\usepackage{marginnote}
\usepackage[justification=centering]{caption}
%%\usepackage{breqn}
\newcommand{\pderiv}[2]{\frac{\partial#1}{\partial#2}}
%\usepackage{siunitx}
\newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{#1}}
\hypersetup{colorlinks,%
						citecolor=black,%
						filecolor=black,%
						linkcolor=black,%
						urlcolor=blue,%
						}
\setstretch{1.5}

\setlength{\droptitle}{-50pt}

\begin{document}
\title{Decision Assistance and Steering in Health Insurance}
\author{Ian McCarthy \& Evan Saltzman}
\date{May 2021}
\maketitle

\vspace{-2ex}
\begin{abstract}
\noindent 
\end{abstract}

\clearpage

\section{Introduction}
\label{sec:introduction}

Health insurance markets are unique in many respects, not least of which is the increasing complexity of choosing an optimal health insurance plan. Such complexity has been well-documented in studies of health insurance choice in the Medicare Advantage market \citep{abaluck2011, ketcham2012, gruber2017}. One way to reduce the burden of this complexity is to provide professional decision support through private insurance agents or public assistance programs, both of which are available in the California health insurance exchanges created under the Affordable Care Act (ACA). Such decision assistance, however, also introduces the potential for private insurers to steer enrollees into potentially suboptimal plans. Commissions paid to facilitate any steering may also increase plan premiums for all enrollees. In this paper, we examine the role of decision assistance on health insurance plan choice and its implications for consumer welfare.

Our analysis is based on household enrollment data from the California ACA exchange. Our final data consist of over 3.2 million household-year observations from 2014 to 2019. The data include a variety of household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any). Using these data, we can precisely identify each household's choice set, the premium paid for each plan in the choice set, and any premium and cost sharing subsidies for which the household is eligible.

Our empirical analysis proceeds as follows. First, we examine whether decision assistance affects plan choice. Our estimand of interest is the average treatment effect on the treated (ATT) for enrollees receiving decision assistance. We employ as our estimator an augmented inverse propensity weighted nested logit regression, as discussed in more detail in Section \ref{sec:causal}, and we limit the analysis to newly enrolled households. We estimate that such households are 50\% more likely to select a silver plan and 20\% less likely to remain uninsured when using some form of decision assistance. We also find strong evidence of heterogeneous effects depending on the type of assistance used, wherein households using public decision assistance ...

Second, we consider the potential for decision assistance to ``improve'' plan choice. While identifying ``improvement'' is not generally feasible in our data, we can identify specific instances in which the observed plan choice is dominated by some other plan in an individual's choice set. For example, Gold and Platinum tier plans are dominated for any household that is eligible for cost-sharing subsidies and with incomes below 150\% of the federal poverty level. We can therefore identify dominated choices and examine whether those with decision assistance appear less likely to select a dominated plan. As with our initial nested logit model of plan choice, our estimand is the ATT for households receiving decision assistance, and our estimator is an augmented inverse propensity weighted logit regression.

Regarding dominated choices, our results suggest that individuals with decision assistance are over 1 percentage point less likely to make a dominated choice. On a base of 3.5\%, this reflects a 30\% decrease in the probability of making a dominated choice. We again find evidence of heterogeneities in the effects of different forms of decision assistance. In particular, we find that individuals using publicly provided decision assistance are around 0.76 percentage points less likely to select a dominated plan, while individuals using a private insurance agent are 1.2 percentage points less likely to select a dominated plan.

Third,

We contribute to two distinct literatures. First, our examination of decision assistance and health insurance relates to the literature on the role of experts in decision making.

A related literature considers the effects of recommendations, sometimes automated via an algorithmic recommendation, on decisions. \cite{bundorf2019}, for example, show that offering additional information alongside an algorithmic expert recommendation significantly affects an individual's choice of prescription drug plans.

Second, we contribute to the literature examining the prevalence and underlying mechanisms of poor decision making in health insurance. In the employer-provided insurance market, \cite{liu2021} documents that over half of employers offer a dominated plan among their menu of insurance options available to their employees, and \cite{sinaiko2011} and \cite{bhargava2017} find that a large share of employees regularly select such dominated insurance plans. \cite{abaluck2011}, \cite{ketcham2012}, \cite{zhou2012}, \cite{heiss2013}, \cite{gruber2017}, \cite{ho2017rand} and many others similarly examine poor decisions when selecting a Medicare prescription drug (Part D) plan. The consensus from this literature is that individuals regularly make \textit{ex ante} very bad health insurance decisions, often selecting plans that are either financially dominated by other plan options or most likely suboptimal given the enrollee's existing medical conditions.

Specifically in the context of the ACA, \cite{orzol2018} find that an ``Enroll America,'' a national non-profit organization designed to expand health insurance enrollment in the U.S., significantly increased enrollment in the ACA exchange plans. \cite{myerson2019} also finds that federally funded assistance programs significantly increased the probability of enrollment in Medicaid, although they found little effect of such federal funding on enrollment in exchange plans. \cite{sommers2015} similarly show that access to navigators is highly correlated with Medicaid enrollment, mirroring earlier findings from \cite{aizer2003} in her study of Medicaid enrollment and application assistants in California.

\cite{aizawa2021}

While not definitive, a common theme in this literature is that poor health insurance decisions are due in-part to an inability or unwillingness of enrollees to accurately evaluate their plan options \citep{bhargava2017, hanoch2009}. Even still, \cite{ketcham2012} find that any such poor decision making will tend to improve over time, thereby partially alleviating the need for any explicit intervention.

\section{Background and Institutional Details}
\label{sec:background}

One of the pillars of the Affordable Care Act (ACA) was the creation of regulated state insurance exchanges in which insurers sell private insurance plans directly to consumers. Although all state exchanges must adhere to a minimum set of regulations, there exists significant variation across states in terms of how they manage and regulate their exchanges. Since our analysis uses data from the California exchange, we focus our discussion on California.

There are three general aspects of the California insurance exchange that are particularly relevant for our analysis: 1) enrollee choice sets and the types of plans available; 2) variation in premiums across individuals on the exchange; and 3) the presence of navigators and brokers to assist individuals when considering an exchange plan. We discuss the institutional details of each of these areas in more detail throughout the remainder of this section.

\subsection{Choice Sets and Plan Types}
Exchange plans are classified by a ``metal'' tier intended to easily summarize the actuarial value (AV) of a plan. Bronze plans reflect an AV of 60\%, silver plans an AV of 70\%, gold plans an AV of 80\%, and platinum plans an AV of 90\%. For plans on the California exchange, other cost sharing parameters are standardized within a metal tier, such that the enrollee's financial burden across plans within a given metal tier is relatively homogeneous.\footnote{In other states, insurers can generally design plans with different cost sharing provisions within a metal tier, but the regulations on the California exchange are more stringent.} Each state also defines geographic rating areas, usually composed of counties, in which an insurer's premiums must be the same for consumers of the same age.

Most households face the same choice set based on their region and year of enrollment; however, some individuals (mainly those under age 30) are also eligible for basic catastrophic coverage. Insurers can also choose to serve only a part of a rating area. Such ``partial'' rating area coverage is relatively uncommon in California, and \cite{fang2020} show that insurers' decisions to enter a subset of counties in a rating area appears to be determined by entry costs and risk pools rather than strategic competitive behavior.

\subsection{Premiums and Cost-sharing}
Premium variation within a plan is more tightly regulated in California than in other state exchanges, with insurer price discrimination only allowed based on an enrollee's age and geographic residence. For example, insurers can charge a 64-year old up to 3 times as much as a 21-year old according to the default age rating curve.

The ACA also provides premium and cost-sharing subsidies to eligible enrollees.\footnote{Premium subsidies are available to consumers who meet the following criteria: 1) income between 100 and 400\% of the federal poverty level (FPL); 2) citizenship or legal resident status; 3) ineligible for public insurance such as Medicare or Medicaid; and 4) lack access to an ``affordable plan offer'' through employer-sponsored insurance either as an employee or as a dependent. Cost-sharing subsidies are available to anyone with income $\leq$ 250\% of FPL and serve to increase the actuarial value of a plan from 70\% up to 94\% (income $<$ 150\% of FPL), 87\% (income between 150\% and 200\% of FPL), and 73\% (incomes between 200\% and 250\% of FPL).} The premium subsidy is set to the difference between: 1) the premium of the benchmark plan, defined as the second-cheapest silver plan available to a given enrollee; and 2) and the enrollee's income contribution cap, defined as the maximum percent of a person's income spent on premiums. Consumers can apply the premium subsidy towards the premium of any metal plan, whereas cost-sharing subsidies only apply to the purchase of a silver tier plan.

\subsection{Decision Assistance}
There are two forms of formal decision assistance available to potential enrollees on the California exchange: publicly funded ``navigators;'' and private insurance agents or brokers. For states participating in the federal exchange, navigators are mandated under the ACA and federally funded. Navigators are voluntary for state-based exchanges, although most states offer such assistance to potential enrollees, including California.

A navigator is essentially a public employee available to help potential enrollees better understand their insurance options. Access to navigators has been shown to have a particularly large effect on Medicaid enrollment \citep{myerson2019, sommers2015, aizer2003}. Relatedly, navigators tend to work with households of lower incomes, currently uninsured, and non-native english speakers.

\section{Data}
\label{sec:data}
We have detailed individual and household-level administrative data from California's ACA exchange (i.e., Covered California) from 2014-2019. The data indicate each enrollee's selected plan and key demographic information, including age, income, county of residence, subsidy eligibility, and household composition. We also collect data on plan characteristics and rate filings, including the plan premium, metal tier, cost sharing requirements (e.g., deductible, coinsurance, and maximum out-of-pocket limit), and network type (e.g., HMO, PPO). Demographic and plan characteristics allow the construction of each household's menu of plan choices and household-specific premiums, $p_{ij}$. Individual and household identifiers allow consumers to be grouped into household units and tracked across time.\footnote{To form the universe of \textit{potential} exchange consumers, we supplement the Covered California data with data from the American Community Survey (ACS). From the full ACS data, we exclude individuals enrolled in or eligible for another source of insurance coverage as well as those ineligible to purchase insurance on the exchanges. Details of ACS data are described in the supplemental appendix.}

Our final data consist of 8.3 million total annual enrollments from 2014-2019. Of these, 4.5 million are newly enrolled (e.g., not enrolled in any California exchange plan in the prior year). Table~\ref{tab:summary-stats} displays summary statistics for Covered California households, separately between those that used and did not use decision assistance. The silver tier is the most commonly selected option because consumers eligible for cost sharing reductions (CSRs) must choose a silver plan to receive CSRs.  Approximately 68 percent of California enrollees and 61 percent of Washington enrollees are eligible for CSRs, while 91 percent of California enrollees and 85 percent of Washington enrollees are eligible for premium subsidies.  The proportion of consumers exempt from the individual mandate is small, but is notably higher among those who are uninsured.  The uninsured rate is substantially higher among young adults and males in both states. Individuals with incomes between 250 and 400 percent of FPL, who receive relatively small subsidies, and those with incomes above 400 percent of FPL, who are ineligible for subsidies, make up a relatively large share of the uninsured population.

\begin{table}[h]
\centering	
\caption{Summary Statistics for Covered California Enrollees}
\input{tables/summary-stats.tex}
\footnote{Something}
\label{tab:summary-stats}
\end{table}

\section{Decision Assistance and Plan Choice}
\label{sec:causal}

\subsection{Estimation}
\label{subsec:causal-methods}
We model health insurance purchasing with a nested logit discrete choice model, as in \cite{saltzman2019}, and we derive estimates of the effect of decision assistance by embedding this discrete choice model into a potential outcomes framework \citep{rubin1974, imbens2009}.

For our nested logit discrete choice model, we assume that household $i$ chooses the plan $j$ that maximizes their utility,
\begin{equation}
u_{ij} = \alpha_{i}p_{ij} + \beta x_{j} + \gamma d_{i} + \xi_{j} + \varepsilon_{ij}, \label{eq:utility}
\end{equation}
where $p_{ij}$ denotes the premium for plan $j$, $x_{j}$ denotes a vector of product characteristics, $d_{i}$ denotes a vector of household characteristics, $\xi_{j}$ captures unobserved product characteristics, and $\varepsilon_{ij}$ is an error term assumed to follow a type I extreme value distribution. We allow for heterogenities in price elasticities across households by parameterizing $\alpha_{i}$ in Equation \eqref{eq:utility}, $\alpha_{i} = \alpha + \theta d_{i}.$ In our estimation, this amounts to including a full set of interactions between $d_{i}$ and $p_{ij}$.

this estimator proceeds in four steps: 1) estimate a logit regression of decision assistance, the predicted probabilities of which enter as weights in the second stage; 2) estimate a weighted nested logit model of plan choice, limiting the sample to those observed to \textbf{not} have used any form of decision assistance; 3) use the results of our choice model to predict the counterfactual outcome of plan choice among those that \textbf{did} use some form of decision assistance; and 4) take the difference in predicted plan choices versus observed plan choices, conditional on receiving assistance.

\subsection{Results}
\label{subsec:causal-results}

Interpreting our results as an estimate of the ATT assumes that individuals receiving decision assistance do not seek assistance due to some unobserved factors that also affect their plan choice. Conditional on household characteristics as well as insurer fixed effects, interacted with a full set of region and year fixed effects, we argue that this assumption is plausible.

\section{Dominated Choices}
\label{sec:dominated}
As a complementary empirical analysis, we identify specific instances in which the observed plan choice is dominated by some other plan in an individual's choice set, and we estimate the effects of decision assistance on the probability of making such a choice. For example, Gold and Platinum tier plans are dominated for any household that is eligible for cost-sharing subsidies and with incomes below 150\% of the federal poverty level. We estimate the effect of decision assistance on dominated choices with a linear probability model, allowing for year, insurer, and region fixed effects.

\section{Welfare and Insurer Steering}
\label{sec:steering}

\subsection{Model of Commissions and Steering}
\label{subsec:steering-model}

\subsection{Structural Estimation}
\label{subsec:steering-methods}

\subsection{Welfare Results}
\label{subsec:steering-results}

\section{Conclusion}
\label{sec:conclusion}

Our current results provide strong evidence that decision assistance has a significant and economically meaningful effect on health insurance plan choice. In terms of dominated choices, our early results suggest that this change in decision-making is welfare improving, and we continue to explore other measures of choice dominance to further confirm this result.

In future work, our identification strategy will exploit the Trump administration's removal of cost-sharing subisidies from the exchanges in 2018 and the subsequent response from insurers to increase premiums on their silver plans (``silver loading''). This response significantly changed the prevalence of dominated choices in each household's choice set, and in this way, the removal of the cost-sharing subsidies offers an exogenous change to the set of dominated plans available to each household.

We are also extending our analysis of the differential effects between public decision support versus assistance from private insurance agents/brokers. This analysis will determine whether insurance brokers are more likely to steer patients into plans offered by the sponsoring insurer.

\pagebreak
\bibliographystyle{authordate1}
\bibliography{BibTeX_Library}

\clearpage
\newpage

\section*{Tables and Figures}

\begin{figure}[htb]\caption{Count of Enrollees in California Exchange}
\centering
 		\hspace*{-1cm}\includegraphics[scale=.7]{figures/enrollee_count.png}
 		\begin{minipage}{\textwidth}
		\bigskip
			\footnotesize \textsc{Notes:} The coefficients for high ratings are shown with circles, those for middle ratings are shown with triangles, and no reviews are shown with diamonds. The main results are designated in blue along with an indicator for specification ``Main". Various specifications and required minimum number of reviews are also indicated. 
 		\end{minipage}
 		\label{figure:SpecCurve}
 \end{figure}

\end{document}

### 2021-06-08 analysis/decision-support/_SummaryStats.R
update summary stats

@@ -326,10 +326,10 @@ final.sum.stats <- mean.stats.assist %>%
   left_join(mean.stats.unassist, by="name") %>%
   left_join(mean.stats.all, by="name") %>%
   mutate(name=case_when(
-    name=="FPL_low" ~ "< 138%",
+    name=="FPL_low" ~ "below 138%",
     name=="FPL_250" ~ "between 138 and 250%",
     name=="FPL_400" ~ "between 250 and 400%",
-    name=="FPL_high" ~ "> 400%",
+    name=="FPL_high" ~ "above 400%",
     name=="BlueShield" ~ "Blue Shield",
     name=="HealthNet" ~ "Health Net",
     name=="any_agent" ~ "Agent or Broker",
@@ -343,6 +343,7 @@ final.sum.stats <- mean.stats.assist %>%
     TRUE ~ name
   ))
 
+options(knitr.kable.NA = '')
 kable(final.sum.stats, format="latex",
       col.names = c("Variable","Assisted","Unassisted","Overall"),
       digits=c(0,2,2,2),

### 2021-06-11 analysis/decision-support/_ChoiceModel.R
update choice model estimation and bootstraps

@@ -11,7 +11,7 @@ area.dat <- as.list(unique.region)$region
 
 
 
-# Estimate with purrr -----------------------------------------------------
+# Estimation --------------------------------------------------------------
 
 hh.nest <- hh.clean %>%
   left_join(afford.threshold, by="year") %>%
@@ -40,10 +40,9 @@ choice.regs <- full.nest %>%
   mutate(nest_names = map(data.est, ~unique(.x$plan_name)),
          nest1=map(nest_names, ~.x[.x !="Uninsured"])) %>%
   mutate( regs = map2(data.est, nest1, ~dchoice.reg(d=.x, nest.names=.y)),
-          tidied = map(regs, tidy),
-          pred = data.est)
+          tidied = map(regs, tidy))
 
-for (i in nrow(choice.regs)) {
+for (i in 1:nrow(choice.regs)) {
   oos.nest <- mlogit.data(choice.regs$data_full[[i]], choice="choice", shape="long", chid.var = "household_number", alt.var="plan_name")
   nest.coef <- choice.regs$regs[[i]]
   nest.names <- choice.regs$nest1[[i]]
@@ -55,13 +54,22 @@ for (i in nrow(choice.regs)) {
     group_by(plan_name) %>% 
     summarize(tot_nonmiss=sum(!is.na(pred_purchase)),
               obs_purchase=sum(choice, na.rm=TRUE),
-              pred_purchase=sum(pred_purchase, na.rm=TRUE))
+              pred_purchase=sum(pred_purchase, na.rm=TRUE)) %>%
+    mutate(region=choice.regs$region[[i]],
+           year = choice.regs$year[[i]])
   
-  choice.regs$pred[[i]] <- treated.dat
+  if (i==1) {
+    all.prob <- treated.dat
+  } else {
+    all.prob <- bind_rows(all.prob, treated.dat)
+  }
+  
 }
 
 
-## start back here trying the bootstrap with purrr
+
+# Bootstrap standard errors -----------------------------------------------
+
 bs.choice.data <- full.nest %>% 
   mutate(hh.final = map(data_full, ~.x %>% distinct(.x$household_number)))
 
@@ -129,141 +137,6 @@ for (b in 1:max.boot) {
     sim.bs.pred <- bind_rows(sim.bs.pred, bs.pred)  
   }
   
+  print(paste0("finished bootstrap: ", b, "at time ", Sys.time()))
 } 
     
-
-
-
-
[…]

### 2021-06-11 analysis/decision-support/_ChoiceSummary.R

@@ -11,7 +11,8 @@ pred.purchase <- all.prob %>% ungroup() %>%
   mutate(plan_name=str_replace(plan_name, "G.*","G"),
          plan_name=str_replace(plan_name, "P.*","P"),
          plan_name=str_replace(plan_name, "CAT.*","CAT"),
-         plan_name=str_replace(plan_name, "BR.*","BR"))
+         plan_name=str_replace(plan_name, "BR.*","BR"),
+         plan_name=str_replace(plan_name, "SIL.*","SIL"))
 
 plan.summary <- pred.purchase %>%
   group_by(plan_name) %>%
@@ -31,6 +32,19 @@ metal.summary <- pred.purchase %>%
          e_y0 = pred_purchase/sum(pred_purchase),
          att = e_y1 - e_y0)
 
+metal.summary.cond <- pred.purchase %>%
+  separate(plan_name, c("insurer","metal"), sep="_") %>%
+  mutate(metal=if_else(is.na(metal),"Uninsured",metal)) %>%
+  filter(metal!="Uninsured") %>%
+  group_by(metal) %>%
+  summarize(obs_purchase=sum(obs_purchase, na.rm=TRUE), 
+            pred_purchase=sum(pred_purchase, na.rm=TRUE)) %>%
+  ungroup() %>%
+  mutate(e_y1 = obs_purchase/sum(obs_purchase),
+         e_y0 = pred_purchase/sum(pred_purchase),
+         att = e_y1 - e_y0)
+
+
 ## by insurer
 ins.summary <- pred.purchase %>%
   separate(plan_name, c("insurer","metal"), sep="_") %>%
@@ -42,12 +56,22 @@ ins.summary <- pred.purchase %>%
          e_y0 = pred_purchase/sum(pred_purchase),
          att = e_y1 - e_y0)
 
+ins.summary.cond <- pred.purchase %>%
+  separate(plan_name, c("insurer","metal"), sep="_") %>%
+  filter(insurer!="Uninsured") %>%  
+  group_by(insurer) %>%
+  summarize(obs_purchase=sum(obs_purchase, na.rm=TRUE), 
+            pred_purchase=sum(pred_purchase, na.rm=TRUE)) %>%
+  ungroup() %>%
+  mutate(e_y1 = obs_purchase/sum(obs_purchase),
+         e_y0 = pred_purchase/sum(pred_purchase),
+         att = e_y1 - e_y0)
 
 
 
[…]

### 2021-06-11 analysis/decision-support/_SummaryStats.R

@@ -254,48 +254,49 @@ sum.stats.data <- hh.full %>% ungroup() %>%
          FPL_250=if_else(FPL_bracket=="138to250",1,0),
          FPL_400=if_else(FPL_bracket=="250to400",1,0),
          FPL_high=if_else(FPL_bracket=="400ormore",1,0),
-         Kaiser=if_else(insurer=="Kaiser",1,0),
-         Anthem=if_else(insurer=="Anthem",1,0),
-         BlueShield=if_else(insurer=="Blue_Shield",1,0),
-         HealthNet=if_else(insurer=="Health_Net",1,0),
-         Other=if_else(insurer %in% c("Kaiser","Anthem","Blue_Shield","Health_Net"),0,1),
-         Bronze=if_else(metal=="Bronze",1,0),
-         Silver=if_else(metal=="Silver",1,0),
-         Gold=if_else(metal=="Gold",1,0),         
-         Platinum=if_else(metal=="Platinum",1,0),
-         Catastrophic=if_else(metal=="Catastrophic",1,0),
-         HMO=if_else(plan_network_type=="HMO",1,0),
-         PPO=if_else(plan_network_type=="PPO",1,0),
-         EPO=if_else(plan_network_type=="EPO",1,0),
-         HSP=if_else(plan_network_type=="HSP",1,0)) %>%
-  select(starts_with("FPL_"),Kaiser, Anthem, BlueShield, HealthNet, Other, Bronze, Silver, Gold, Platinum, Catastrophic, HMO, PPO, EPO, HSP,
-         assisted, navigator, any_agent, household_size, num_children_subject, perc_black, perc_hispanic, perc_white)
+         Kaiser=if_else(insurer=="Kaiser" & !is.na(plan_number_nocsr),1,0),
+         Anthem=if_else(insurer=="Anthem" & !is.na(plan_number_nocsr),1,0),
+         BlueShield=if_else(insurer=="Blue_Shield" & !is.na(plan_number_nocsr),1,0),
+         HealthNet=if_else(insurer=="Health_Net" & !is.na(plan_number_nocsr),1,0),
+         Uninsured=if_else(is.na(plan_number_nocsr),1,0),
+         Other=if_else( (!insurer %in% c("Kaiser","Anthem","Blue_Shield","Health_Net")) & !is.na(plan_number_nocsr),1,0),
+         Bronze=if_else(metal=="Bronze" & !is.na(plan_number_nocsr),1,0),
[…]

### 2021-06-11 analysis/decision-support/choice_data_function.R

@@ -1,251 +1,0 @@
-# Meta --------------------------------------------------------------------
-
-## Date Created:  5/12/2020
-## Date Edited:   3/15/2021
-## Description:   Function to create choice-level dataset for given year and area
-
-
-# Estimation function -----------------------------------------------------
-
-choice.data.fnc <- function(t, r) {
-  
-  a.thresh <- as.numeric(afford.threshold %>% filter(year==t) %>% select(cutoff))
-  outside=tibble(
-    plan_name="Uninsured",
-    region=r,
-    Issuer_Name="Outside_Option"
-  )
-  
-  choice.set <- plan_data %>% filter(Year==t, region==r) %>%
-    select(plan_name=Plan_Name2, Issuer_Name=Insurer, region, PLAN_NETWORK_TYPE, metal_level=Metal_Level, metal, 
-           Premium, MSP, HSA) %>%
-    group_by(plan_name, region) %>%
-    summarize(Issuer_Name=first(Issuer_Name),
-              PLAN_NETWORK_TYPE=first(PLAN_NETWORK_TYPE),
-              metal_level=first(metal_level),
-              metal=first(metal),
-              Premium=mean(Premium, na.rm=TRUE),
-              MSP=min(MSP, na.rm=TRUE),
-              HSA=min(HSA, na.rm=TRUE)) %>%
-    ungroup() %>%
-    mutate(plan_name=as.character(plan_name)) %>%
-    bind_rows(outside)
-  
-  
-  full.choice.data <- hh.clean %>% filter(year==t, region==r) %>%
-    select(household_id, year, zip3, FPL, subsidized_members, hh_region=region, hh_rating=rating_factor,
-           hh_plan_number = plan_number_nocsr, hh_plan_id=plan_id, penalty, hh_insurer=insurer,
-           hh_plan_name = plan_name, oldest_member, cheapest_premium, subsidy, poverty_threshold) %>%
-    full_join(choice.set, by=c("hh_region"="region")) 
-  
-  
-  ## Remove plans that are not available for specific households.
-  ## 1. ACS eligible households not eligible for "unenhanced silver plans"
-  clean.choice.data <- full.choice.data %>%
-    mutate(acs_eligible73 = ifelse(FPL>2 & FPL<=2.5 & subsidized_members>0,1,0),
[…]

### 2021-06-11 analysis/decision-support/choice_data_function_map.R

@@ -99,7 +99,7 @@ choice.data.fnc2 <- function(plans, hhs) {
   clean.choice.large <- clean.choice.data %>%
     filter(Issuer_Name %in% c('Anthem', 'Blue_Shield', 'Kaiser', 'Health_Net', 'Outside_Option')) %>%
     mutate(monthly_penalty=penalty/12) %>%
-    select(household_id, FPL, hh_plan_name, oldest_member, hh_insurer,
+    select(household_id, FPL, hh_plan_name, oldest_member, hh_insurer, hh_plan_number,
            cheapest_premium, Issuer_Name, PLAN_NETWORK_TYPE, MSP, HMO, HSA,
            metal_level, metal, plan_name,
            final_subsidy, final_premium, plan_choice, insured, monthly_penalty,
@@ -110,7 +110,7 @@ choice.data.fnc2 <- function(plans, hhs) {
     group_by(household_id, metal) %>%
     summarize(final_premium=min(final_premium, na.rm=TRUE),
               plan_choice=max(plan_choice,na.rm=TRUE),
-              FPL=first(FPL), hh_plan_name=first(hh_plan_name),
+              FPL=first(FPL), hh_plan_name=first(hh_plan_name), hh_plan_number=first(hh_plan_number),
               oldest_member=first(oldest_member),
               cheapest_premium=first(cheapest_premium), insured=first(insured),
               penalty=first(penalty),
@@ -119,7 +119,7 @@ choice.data.fnc2 <- function(plans, hhs) {
               silver=mean(silver, na.rm=TRUE), bronze=mean(bronze, na.rm=TRUE),
               AV=mean(AV, na.rm=TRUE))%>%
     mutate(monthly_penalty=penalty/12) %>%      
-    select(household_id, FPL, hh_plan_name, oldest_member,
+    select(household_id, FPL, hh_plan_name, oldest_member, hh_plan_number,
            cheapest_premium, plan_choice, insured, final_premium, monthly_penalty,
            platinum, gold, silver, bronze, AV, metal) %>%
     mutate(Issuer_Name='Small_Insurer', hh_insurer="Small_Insurer",
@@ -134,7 +134,7 @@ choice.data.fnc2 <- function(plans, hhs) {
   
   ## Final dataset (for zip and year)
   choices <- bind_rows(clean.choice.large,clean.choice.small) %>%
[…]

### 2021-06-11 analysis/decision-support/choice_est_bs_function.R

@@ -1,76 +1,0 @@
-# Meta --------------------------------------------------------------------
-
-## Date Created:  5/12/2020
-## Date Edited:   5/20/2020
-## Description:   Function to estimate standard errors using bootstrap
-
-
-# Estimation function -----------------------------------------------------
-
-dchoice.bs <- function(t, r) {
-  
-  est.data <- get(paste0("est.data.",r,".",t))
-  oos.data <- get(paste0("oos.data.",r,".",t))
-
-
-  # oos.data <- oos.data %>%
-  #   inner_join(est.data.bs %>% distinct(plan_name),
-  #              by="plan_name") %>%
-  #   group_by(household_number) %>%
-  #   mutate(any_choice=max(choice)) %>%
-  #   filter(any_choice==1) %>%
-  #   ungroup() %>%
-  #   select(-any_choice)
-  
-  ## Set up model and starting values
-  all_covars <- as.list(bs.starting %>% filter(region==r, year==t, variable!="iv") %>% select(variable))$variable
-  nested.formula <- formula(paste("choice ~", paste(all_covars, collapse=" + "),"| 0")) 
-  beta_initial <- as.list(bs.starting %>% filter(region==r, year==t, variable!="iv") %>% select(estimate))$estimate
-  
-  ## Estimate model and store results
-  test <- TRUE
-  while (test==TRUE) {
-    est.data.bs <- est.data %>%
-      nest(-household_number)
-        
-    est.data.bs <- slice_sample(est.data.bs, n=nrow(est.data.bs), replace=TRUE) %>%
-      mutate(household_number=cur_group_rows()) %>%
-      unnest(data)
-
-    nested.data <- mlogit.data(est.data.bs, choice="choice", shape="long", chid.var = "household_number", alt.var="plan_name")
-    test <- is.error(mlogit(nested.formula, data=nested.data, weights=ipweight, 
-                            nests=list(insured=nest.in, uninsured=nest.out), un.nest.el=TRUE, start=beta_initial))
-    if (test==FALSE) {
-      nested.logit <- mlogit(nested.formula, data=nested.data, weights=ipweight,
-                             nests=list(insured=nest.in, uninsured=nest.out), un.nest.el=TRUE)
-    } else {
-      test <- TRUE
-    }
-  }
-   
-  coef.name <- as_tibble(names(nested.logit$coefficients)) %>%
-    rename("variable"=value)
[…]

### 2021-06-11 analysis/decision-support/choice_est_function.R

@@ -1,104 +1,0 @@
-# Meta --------------------------------------------------------------------
-
-## Date Created:  5/12/2020
-## Date Edited:   3/15/2021
-## Description:   Function to estimate demand, reports mean predicted enrollments 
-##                per plan as well as coefficient estimates
-
-
-# Estimation function -----------------------------------------------------
-
-dchoice.est <- function(d, oos, t, r) {
-
-  ## Terms for estimation
-  all_covars=c("premium", "silver","hh_size_prem","AV")
-  ins.offer <- c(0,0,0,0)
-  cml.share <- 0
-  tot.choice <- sum(d$choice==1)
-  ins.offer[1] <- sum(d$Anthem==1 & d$choice==1)/tot.choice
-  ins.offer[2] <- sum(d$Blue_Shield==1 & d$choice==1)/tot.choice
-  ins.offer[3] <- sum(d$Kaiser==1 & d$choice==1)/tot.choice
-  ins.offer[4] <- sum(d$Health_Net==1 & d$choice==1)/tot.choice
-
-  all.hmo <- sum(d$HMO==1 & d$choice==1)/tot.choice
-  if (all.hmo>.1) {
-    all_covars=c(all_covars, "HMO")
-  }
-  all.hsa <- sum(d$HSA==1 & d$choice==1)/tot.choice
-  if (all.hsa>.1) {
-    all_covars=c(all_covars, "HSA")
-  }
-  
-  cml.share <- ins.offer[1]
-  if (ins.offer[1]>.4 & cml.share<.9) {
-    all_covars=c(all_covars, "Anthem")
-  }
-  cml.share <- cml.share+ins.offer[2]
-  if (ins.offer[2]>.4 & cml.share<.9) {
-    all_covars=c(all_covars, "Blue_Shield")
-  }
-  cml.share <- cml.share+ins.offer[3]
-  if (ins.offer[3]>.4 & cml.share<.9) {
-    all_covars=c(all_covars, "Kaiser")
-  }
-  cml.share <- cml.share+ins.offer[4]
-  if (ins.offer[4]>.4 & cml.share<.9) {
-    all_covars=c(all_covars, "Health_Net")
-  }  
-  
-  nested.data <- mlogit.data(d, choice="choice", shape="long", chid.var = "household_number", alt.var="plan_name")
-  mclogit.formula <- formula(paste("cbind(choice, household_number) ~", paste(all_covars, collapse=" + ")))
[…]

### 2021-06-11 finals/paper.tex
Updates from Overleaf

@@
 %%\usepackage{breqn}
+\usepackage{booktabs}
 \newcommand{\pderiv}[2]{\frac{\partial#1}{\partial#2}}
@@
 \author{Ian McCarthy \& Evan Saltzman}
-\date{May 2021}
+\date{June 2021}
 \maketitle
@@
 
-Our final data consist of 8.3 million total annual enrollments from 2014-2019.
-Of these, 4.5 million are newly enrolled (e.g., not enrolled in any California exchange plan in the prior year).
-Table~\ref{tab:summary-stats} displays summary statistics for Covered California households, separately between those that used and did not use decision assistance.
-The silver tier is the most commonly selected option because consumers eligible for cost sharing reductions (CSRs) must choose a silver plan to receive CSRs.
-Approximately 68 percent of California enrollees and 61 percent of Washington enrollees are eligible for CSRs, while 91 percent of California enrollees and 85 percent of Washington enrollees are eligible for premium subsidies.
-The proportion of consumers exempt from the individual mandate is small, but is notably higher among those who are uninsured.
-The uninsured rate is substantially higher among young adults and males in both states.
-Individuals with incomes between 250 and 400 percent of FPL, who receive relatively small subsidies, and those with incomes above 400 percent of FPL, who are ineligible for subsidies, make up a relatively large share of the uninsured population.
+Our final data consist of 8.3 million total households from 2014-2019.
+Of these, 4.5 million were not previously enrolled in any Covered California plan in the prior year.
+Table~\ref{tab:summary-stats} displays summary statistics for all households in our data.
+Since the key independent variable throughout much of our analysis is whether a household used some form of decision assistance, we present summary statistics separately between those that used and did not use decision assistance.
 
-\begin{table}[h]
-\centering	
-\caption{Summary Statistics for Covered California Enrollees}
-\input{tables/summary-stats.tex}
-\footnote{Something}
-\label{tab:summary-stats}
-\end{table}
+We see from Table~\ref{tab:summary-stats} that enrollees using decision assistance are of lower income and larger household size.
+Among types of plans purchased, we see little difference between those with and without decision assistance, with the exception of Kaiser plans for which individuals using decision assistance are less likely to purchase.
+Overall, the silver tier is the most commonly selected option, and this is particularly true for those using decision assistance.
+Enrollees with decision assistance are also less likely to select an HMO and relatively more likely to select a PPO.
+Finally, among those using some form of decision assistance, about 70\% of households used a private agent or broker while the remaining 30\% used a public navigator.
 
@@
 \begin{equation}
-u_{ij} = \alpha_{i}p_{ij} + \beta x_{j} + \gamma d_{i} + \xi_{j} + \varepsilon_{ij}, \label{eq:utility}
+u_{ij} = \alpha_{i}p_{ij} + \beta x_{j} + \gamma d_{i} + \xi_{j} + \varepsilon_{ij}, 
+\label{eqn:utility}
 \end{equation}
 where $p_{ij}$ denotes the premium for plan $j$, $x_{j}$ denotes a vector of product characteristics, $d_{i}$ denotes a vector of household characteristics, $\xi_{j}$ captures unobserved product characteristics, and $\varepsilon_{ij}$ is an error term assumed to follow a type I extreme value distribution.
-We allow for heterogenities in price elasticities across households by parameterizing $\alpha_{i}$ in Equation \eqref{eq:utility}, $\alpha_{i} = \alpha + \theta d_{i}.$ In our estimation, this amounts to including a full set of interactions between $d_{i}$ and $p_{ij}$.
+We allow for heterogenities in price elasticities across households by parameterizing $\alpha_{i}$ in Equation~\eqref{eqn:utility}, $\alpha_{i} = \alpha + \theta d_{i}.$ In our estimation, this amounts to including interactions between $d_{i}$ and $p_{ij}$.
 
-this estimator proceeds in four steps: 1) estimate a logit regression of decision assistance, the predicted probabilities of which enter as weights in the second stage; 2) estimate a weighted nested logit model of plan choice, limiting the sample to those observed to \textbf{not} have used any form of decision assistance; 3) use the results of our choice model to predict the counterfactual outcome of plan choice among those that \textbf{did} use some form of decision assistance; and 4) take the difference in predicted plan choices versus observed plan choices, conditional on receiving assistance.
+Using the nested logit model in Equation~\eqref{eqn:utility}, our goal is to estimate the average treatment effect on the treated (ATT), which in our case reflects the average treatment effect among those using some form of decision assistance.
+To allow for general heterogeneous treatment effects, we estimate the ATT with a four-step process:
+\begin{enumerate}
+    \item Estimate the nested logit model of plan choice from Equation~\eqref{eqn:utility}, limiting the sample to those observed to \textbf{not} have used any form of decision assistance.
+We estimate Equation~\eqref{eqn:utility} separately for each year and region, implicitly allowing for a full set of region/year interactions among all covariates.
+For this reason, we select a relatively small set of covariates, including household-specific premiums, the interaction between premiums and household size, the actuarial value of the plan, the metal tier, indicators for network type (HMO or PPO), and insurer fixed effects.
+We then obtain a set of coefficient estimates, $\hat{\theta} = \{\hat{\alpha}, \hat{\beta}, \hat{\gamma}, \hat{\xi} \}$.\footnote{These coefficient estimates differ by region and year, but we supress that notation for brevity.}
+
+    \item Use $\hat{\theta}$ to form the predicted counterfactual, $\widehat{Pr[Y_{ij}^{0} | \text{Assistance}]}$.
+In other words, we use the results of our choice model, estimated only among those without decision assistance, to predict the counterfactual outcome of plan choice among those that \textbf{did} use some form of decision assistance.
+
+    \item Sum the predicted probabilities across individuals, $$\widehat{N_{j}^{0}} = \sum_{ i \in \Omega} \widehat{Pr[Y_{ij}^{0} | \text{Assistance}]},$$ where $\Omega$ denotes the set of all enrollees that used decision assistance.
+Among such enrollees, this reflects the predicted number of enrollments if enrollees had not used any assistance.
+
+    \item Sum the observed number of enrollments, $N_{j}^{1}$, and take the difference between this and the counterfactual prediction,
+    \begin{equation}
+        ATT_{j} = \underbrace{N^{1}_{j}}_{Observed} - \underbrace{\widehat{N_{j}^{0}}}_{Predicted}.
+    \label{eqn:att}
+    \end{equation}
+\end{enumerate}
+
+Interpreting Equation~\eqref{eqn:att} as an estimate of the ATT assumes that individuals receiving decision assistance do not seek assistance due to some unobserved factors that also affect their plan choice.
+Conditional on household characteristics as well as insurer fixed effects, (implicitly) interacted with a full set of region and year fixed effects, we argue that this assumption is plausible; however, our estimation strategy employs untreated households (i.e., those without decision assistance) to predict counterfactual choices for treated households and therefore requires sufficient balance between treated and untreated households.
+As is evident from Table~\ref{tab:summary-stats}, there is reason to suspect that such balance does not hold in our data.
+
+To ensure balance among observed covariates, we employ an augmented inverse propensity weighted regression estimate \cite{wooldridge2010}, in which the weights in the nested logit estimation derive from a preliminary logit regression of decision assistance status for each household.
+The outcome in this preliminary regression is an indicator variable, set to one if a household used decision assistance (i.e., the treatment group) and 0 otherwise (i.e., the control group).
+Denoting the resulting predicted probability of decision assistance by $\hat{p}_{i}$, we then assign a weight of $\frac{\hat{p}_{i}}{1-\hat{p}_{i}}$ to each observation in the control group and proceed with step (1) above using these weights in the nested logit regression.
+Conceptually, this approach assigns more weight to households without decision assistance that are ``most similar'' to households that use decision assistance.
 
@@
 
-Interpreting our results as an estimate of the ATT assumes that individuals receiving decision assistance do not seek assistance due to some unobserved factors that also affect their plan choice.
-Conditional on household characteristics as well as insurer fixed effects, interacted with a full set of region and year fixed effects, we argue that this assumption is plausible.
+Figure~\ref{fig:ps-balance} presents the resulting propensity scores from our preliminary logit regression of decision assistance against observable household demographics.
+As is evident from the figure, we observe substantial overlap in propensity scores between the treated and control groups.
+In Figure~\ref{fig:cov-balance}, we present a comparison of observable household characteristics between the treatment and control groups.
+The hollow circles in Figure~\ref{fig:cov-balance} reflect the unadjusted differences in means, while the solid circles reflect the difference in means when weighting households.
+Weights for treated households are set to 1, and weights for untreated households are set to  $\frac{\hat{p}_{i}}{1-\hat{p}_{i}}$ based on the preliminary logistic regression.
+We see from Figure~\ref{fig:cov-balance} that our treated and control groups are well-balanced after weighting.
 
@@
 \label{sec:dominated}
-As a complementary empirical analysis, we identify specific instances in which the observed plan choice is dominated by some other plan in an individual's choice set, and we estimate the effects of decision assistance on the probability of making such a choice.
+The results in Section~\ref{subsec:causal-results} reveal large effects of decision assistance on plan choice; however, it is not clear from those results whether decision assistance \textit{improves} plan choice or simply reallocates households into different, perhaps worse, plans.
+
+we identify specific instances in which the observed plan choice is dominated by some other plan in an individual's choice set, and we estimate the effects of decision assistance on the probability of making such a choice.
 For example, Gold and Platinum tier plans are dominated for any household that is eligible for cost-sharing subsidies and with incomes below 150\% of the federal poverty level.
@@
 
-\subsection{Model of Commissions and Steering}
+\subsection{Model}
 \label{subsec:steering-model}
 
-\subsection{Structural Estimation}
-\label{subsec:steering-methods}
+Consider a two-stage  game where  (1) firms set premiums and commissions simultaneously to maximize their expected profit and (2) consumers select a plan to maximize their expected utility.
+In the following three subsections, we detail how we (1) model the decisions of firms; (2) model the decisions of consumers; and (3) find the model equilibrium.
+
+Given our available data, we do not explicitly model the actions of individual insurance agents.
+However, we do model how firms use agent compensation to steer an agent's clients to their plans.
+Our approach assumes that the consumer's decision to seek agent assistance is independent of the firms' commission levels.
+This identifying assumption is valid if commissions incentivize agents to recommend certain plans to their clients, but do not induce agents to change advertising levels or marketing efforts to  seek new clients.
+Advertising and marketing by both insurers and agents are tightly regulated, particularly in Covered California.
+We therefore believe our identifying assumption is relatively  innocuous.
+
+\subsubsection{Firms Set Premiums and Commissions}
+
+\paragraph{Defining Firm Decision Variables}
+
+Firms set premiums and commissions to maximize their expected profit.
+Let $p_{jmt}$ be the base premium decision for each plan $j$ sold in market $m$ in period $t$ and the \textit{commission decision} $n_{gjt}$
+
+	\vspace{-0.4in}		
+		\singlespacing
+
+				\begin{eqnarray*}
+	n_{gjt}  \equiv \begin{cases} 
+		\delta_{gjt} & \mathrm{\% \,\, commission} \\		
+		\eta_{gjt} & \mathrm{\$ \,\, commission} \\
+		0 & \mathrm{o/w}
+   \end{cases}
+	\end{eqnarray*}
+
+\doublespacing
+
+\noindent for each plan $j$ sold at time $t$ with renewal status $g$ (i.e., new or existing customer).
+Agents are either paid a percentage $\delta_{gjt}$  of the consumer's unsubsidized premium  or a flat amount $\eta_{gjt}$ that is independent of the premium.
+We assume the firm's decision to pay a percentage commission or flat commission is exogenous because switching agent compensation methods is costly.
+The only firm that switched between compensation methods during our six-year study timeframe was Health Net following its acquisition by Centene.
+The \textit{commission paid} to household $i$'s insurance agent is
+
+		\vspace{-0.4in}		
+		\singlespacing
+
+			\begin{eqnarray*}
+	\eta_{gijt}(\textit{p},\textit{n})  \equiv \begin{cases} 
+		n_{gjt} \left(\sigma_{it}p_{jmt}\right) & \mathrm{\% \,\, commission} \\		
+		n_{gjt} & \mathrm{\$ \,\, commission}
+   \end{cases}
+	\end{eqnarray*}
+
+\doublespacing
+
+\noindent where $\textit{p} = {\bf p}_t$ is the vector of plan base premiums set by all insurers in each market in year $t$, $\textit{n} = {\bf n}_t$ is the vector of commission decision variables in period $t$, and the household's (unsubsidized) premium is the product of the household's rating factor $\sigma_{it}$  and the plan's base premium $p_{jmt}$.
+In California, the rating factor can vary by age and geographic residence of the household's members.\footnote{The ACA also permits rating by tobacco usage, but California prohibits tobacco rating.}  Insurers can charge a 64-year-old up to 3 times as much as a 21-year-old.
+Figure~\ref{rating_area_partitions} shows the partition of California into rating areas.
+In each rating area,  an insurer's premium must be the same for all consumers of the same age.
+Total commissions paid by firm $f$  are
+
+	\vspace{-0.2in}
+
+		$$
+		\mathcal{C}_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) = \sum_{g \in G, i \in I, m\in M, k \in J_{fmt}} \left( \mathbb{I}_{n,i,t} \right)  q_{ikt}(\textit{p},\textit{n};\boldsymbol{\beta}) \eta_{gikt}(\textit{p},\textit{n})
+		$$
+
+\noindent where $\mathbb{I}_{n,i,t}$ indicates whether household $i$ is assisted by an agent in year $t$, $q_{ikt}(\cdot)$ is the probability household $i$ chooses plan $k$ at time $t$, and $J_{fmt}$ is the set of plans offered by firm $f$ in market $m$ at time $t$.
+The model parameters $\boldsymbol{\theta} \equiv (\boldsymbol{\beta},\boldsymbol{\gamma},\boldsymbol{\mu})$, where $\boldsymbol{\beta}$ are the demand parameters, $\boldsymbol{\gamma}$ are the risk score parameters, and $\boldsymbol{\mu}$ are the average claims parameters.
+
+\begin{figure}[htbp]
+\caption{Premium Rating Regions in California}
+\label{rating_area_partitions}
+\centering
+\includegraphics[scale=.45]{finals/pics/CA_Rating_Regions2.jpg}
+
+\begin{footnotesize}
+ \begin{flushleft}
+Notes: Figure shows the premium rating regions in the California exchange \citep{CARATE2016}. California's 58 counties are divided into 19 rating areas. 
+\end{flushleft}
+\end{footnotesize}
+
+\end{figure}
+
+\paragraph{Calculating Risk Adjustment Transfers}
+
+We now discuss the ACA's risk adjustment program, which directly affects firm profit.
+\citet{Pope2014} derive the ACA risk adjustment transfer formula.\footnote{We start with \citet{Pope2014}'s transfer formula as derived in their first appendix, which allows plans to vary only by their actuarial values (and not by differences in firm efficiency, geographic costs, allowable rating factors, or moral hazard).
+We start with this formula because we want to capture  all differences in expected risk, except for cost sharing and any associated moral hazard, in the plan's risk score (i.e., cost sharing and moral hazard are addressed through the utilization share).
+In contrast, the plan liability risk score   $PLRS_j$ as defined in \citet{Pope2014}'s second appendix does not account for certain differences such as variation in geographic cost.
+Instead, \citet{Pope2014} account for these differences by applying factors in the transfer formula.}  In our notation, the per-member per-month risk adjustment transfer $ra_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta})$ for plan $j$ is
+
+\vspace{-0.2in}
+
+	$$
+	ra_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) = \left(\frac{r_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta})\sum_{m \in M, l \in J_{mt}} q_{lmt}(\textit{p},\textit{n};\boldsymbol{\beta})}{\sum_{m \in M, l \in J_{mt}} r_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) q_{lmt}(\textit{p},\textit{n};\boldsymbol{\beta})}    -     \frac{h_j\sum_{m \in M, l \in J_{mt}} q_{lmt}(\textit{p},\textit{n};\boldsymbol{\beta})}{\sum_{m \in M, l \in J_{mt}} h_l q_{lmt}(\textit{p},\textit{n};\boldsymbol{\beta})}\right)\overline{p}
+	$$
+
+\noindent where $r_{jmt}(\cdot)$ is the plan risk score, $h_j$ is an exogenous expected utilization factor set by regulation that accounts for the plan AV and any associated moral hazard, and $\overline{p}$ is the weighted average premium in the market.
+The plan's total risk adjustment transfer $RA_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta})$ equals
+
+	\vspace{-0.4in}
+
+	\begin{eqnarray}\label{ra_formula}
+	RA_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) &=& ra_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta})  q_{jmt}(\textit{p},\textit{n};\boldsymbol{\beta}) \nonumber \\
+	&= & \left[rs_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta})  - us_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta})  \right] R_t(\textit{p},\textit{n};\boldsymbol{\beta}) 
+	\end{eqnarray}
+
+	\vspace{-0.2in}
+
+\noindent where $rs_{jmt}(\cdot)$ is the plan's ``risk share'' of total claims, $us_{jmt}(\cdot)$ is the plan's ``utilization share'' of total claims, and $R_t(\cdot) = \sum_f R_{ft}(\cdot)$ is total premium revenue across all plans.
+The total risk adjustment transfer for the firm equals the sum of the risk adjustment transfers for the plans that it sells (i.e., $RA_{ft}(\cdot) = \sum_{m \in M, j \in J_{fmt}} RA_{jmt}(\cdot)$.
+
+The plan's risk share includes the combined effects of adverse selection, moral hazard, and plan AV, whereas the plan's utilization share only includes the effects of moral hazard and plan AV.
+Thus, the difference between the risk share and utilization share captures the plan's relative risk due to adverse selection only.
+The risk share equals
+
+\vspace{-0.1in}
+
+	$$
+	rs_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) = \frac{ r_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) q_{jmt}(\textit{p},\textit{n};\boldsymbol{\beta})}{\sum_{m \in M, l \in J_{mt}}  r_{lmt}(\textit{p},\textit{n};\boldsymbol{\theta}) q_{lmt}(\textit{p},\textit{n};\boldsymbol{\beta})}
+	$$
+
+\noindent where $J_{mt}$ is the set of all plans offered in market $m$ and year $t$, and the plan risk score $r_{jmt}(\cdot)$ is a function of enrollee characteristics and the plan AV.
+We do not directly observe plan risk scores in the insurer rate filing data.
+However, we observe all other variables in formula~(\ref{ra_formula}) including each plan's risk adjustment transfer and can therefore solve formula~(\ref{ra_formula}) for the plan risk scores.
+The plan's utilization share $us_{jmt}(\cdot)$ equals
+
+\vspace{-0.1in}
+
+	$$
+	us_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) =  \frac{ h_j q_{jmt}(\textit{p},\textit{n};\boldsymbol{\beta})}{\sum_{m \in M, l \in J_{mt}} h_l q_{lmt}(\textit{p},\textit{n};\boldsymbol{\beta})}
+	$$
+
+\noindent A positive difference between the risk share and the utilization share indicates that a plan has high risk relative to its expected utilization and results in the plan receiving a risk adjustment transfer; a negative difference indicates that a plan has low risk relative to its expected utilization and results in the plan paying a risk adjustment transfer.
+
+\paragraph{Calculating Variable Profit}
+
+ Firms choose premiums and commissions to maximize expected variable profit
+
+	\vspace{-0.4in}		
+	\begin{footnotesize}
+
+	\begin{eqnarray}\label{profit}
+	\pi_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) &=&  R_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) -  C_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) - \mathcal{C}_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) + RA_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) +  RI_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})  - V_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})  \nonumber \\
+	&=& R_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) - (1 - \iota_{ft}) C_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) - \mathcal{C}_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) + RA_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})   - V_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})
+	\end{eqnarray}
+
+	\end{footnotesize}
+
+	\vspace{-0.1in}
+
+\noindent where $R_{ft}(\cdot)$ is total premium revenue, $C_{ft}(\cdot)$ is total claims, $RI_{ft}(\cdot)$ is reinsurance received, $V_{ft}(\cdot)$  is variable administrative cost (excluding commissions), and $\iota_{ft}$ is the actuarial value of the reinsurance contract (i.e., the expected percentage of claims paid by the reinsurer).
+Total commissions paid $\mathcal{C}_{ft}(\cdot)$ and risk adjustment received  $RA_{ft}(\cdot)$ are as above.
+
+\subsubsection{Households Choose Plans}
+
+Households choose the plan that maximizes their (indirect) utility function
+
+	\vspace{-0.4in}
+
+	\begin{eqnarray}\label{demand_model}
+	U_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta}) &\equiv& \beta_{i}^p p_{ijt}(\textit{p}) + \beta_j^{\eta} \eta_{gijt}(\textit{p},\textit{n})   + \beta_i^y y_{ij(t-1)} + x'_{ij}\beta^x + \xi_{j} + \epsilon_{ijt}^d
+	\end{eqnarray}
+
+	\vspace{-0.1in}
+
+\noindent where $\textit{p} = {\bf p}_t$ is the vector of plan base premiums set by all insurers in each market in year $t$, $p_{ijt}(\textit{p})$ is household $i$'s premium for plan $j$ in year $t$, $y_{ij(t-1)}$ indicates whether household $i$ chose plan $j$ in the previous year, $x_{ij}$ is a vector of observed product characteristics including the plan AV,  $\xi_{j}$ is a vector of unobserved product characteristics, and $\epsilon_{ijt}^d$ is an error term.
+We allow the household's premium parameter $\beta_{i}^p = \beta^p + w'_{it} \phi$ to vary with household characteristics $w_{it}$ and the household's inertia parameter $\beta_i^y = \beta^y +  x'_{ij} \kappa + w'_{it} \nu$ to vary with household and product characteristics.
+CSRs enter utility equation (\ref{demand_model}) through the plan AV and premium subsidies reduce the household's premium $p_{ijt}(\textit{p})$.
+The utility of the outside option $U_{i0t} = \beta_i^p \rho_{it} + \epsilon_{i0t}$, where $\rho_{it}$ is the household's penalty for not having insurance in year $t$.
+
+\paragraph{Calculating Household Premiums}
+
+Households choose the plan that maximizes their (indirect) utility function
+
+	\vspace{-0.4in}
+
+	\begin{eqnarray}\label{demand_model}
+	U_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta}) &\equiv& \beta_{i}^p p_{ijt}(\textit{p}) + \beta_j^{\eta} \eta_{gijt}(\textit{p},\textit{n})  \mathbb{I}_{n,i,t}   + \beta_i^y y_{ij(t-1)} + x'_{ij}\beta^x + \xi_{j} + \epsilon_{ijt}^d
+	\end{eqnarray}
+
+	\vspace{-0.1in}
+
+\noindent where $p_{ijt}(\textit{p})$ is household $i$'s (subsidized) premium for plan $j$ in year $t$, $\eta_{gijt}(\textit{p},\textit{n})$ is the commission paid to household $i$'s insurance agent, $y_{ij(t-1)}$ indicates whether household $i$ chose plan $j$ in the previous year, $x_{ij}$ is a vector of observed product characteristics including the plan AV,  $\xi_{j}$ is a vector of unobserved product characteristics, and $\epsilon_{ijt}^d$ is an error term.
+CSRs enter utility equation (\ref{demand_model}) through the plan AV and premium subsidies reduce the household's premium $p_{ijt}(\textit{p})$.
+The utility of the outside option $U_{i0t} = \beta_i^p \rho_{it} + \epsilon_{i0t}$, where $\rho_{it}$ is the household's penalty for not having insurance in year $t$.
+
+\paragraph{Choice Model Parameters}
+
+We define the vector of demand parameters $\boldsymbol{\beta} \equiv (\beta_i^p,\beta_j^{\eta},\beta_i^y,\beta^x)$ to accommodate heterogeneous consumer preferences.
+The household's premium parameter $\beta_{i}^p \equiv \beta^p + w'_{it} \phi$ varies with household characteristics $w_{it}$.
+The household's inertia parameter $\beta_i^y = \beta^y +  x'_{ij} \kappa + w'_{it} \nu$ varies with both household and product characteristics.
+The steering parameter $\beta_j^{\eta}$ captures the degree to which agent compensation steers  an agent's clients to particular plans.
+A high value of $\beta_j^{\eta}$ would indicate that agent compensation is effective in steering consumers.
+Because smaller firms offer agents considerably higher commissions, we allow the steering parameter to vary with firm size.
+
+\paragraph{Calculating Demand}
+
+ We assume equation (\ref{demand_model}) is a nested logit model such that the vector of error terms $\epsilon_i$ has the generalized extreme value distribution.
+The first nest contains all exchange plans and  the second nest contains only the outside option.
+This two-nest structure captures the key observed substitution pattern between the silver tier and the outside option resulting from the ACA's linkage of CSRs to the purchase of silver plans.
+Under the assumption that $\epsilon_i$ has the generalized extreme value distribution, the household choice probabilities are
+
+	\vspace{-0.4in}
+
+	\begin{eqnarray}\label{choice_probs}
+	q_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta}) &=&  \frac{e^{V_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta})/\lambda}\left(\sum_{j } e^{V_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta})/\lambda}\right)^{\lambda-1}}{1 + \left(\sum_{j} e^{V_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta})/\lambda}\right)^{\lambda}}
+	\end{eqnarray}
+
+	\vspace{-0.1in}
+
+\noindent where $V_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta}) \equiv \beta_{i}^p p_{ijt}(\textit{p}) + \beta_j^{\eta} \eta_{gijt}(\textit{p},\textit{n})   + \beta_i^y y_{ij(t-1)} + x'_{ij}\beta^x + \xi_{j}$ and $\lambda$ is the nesting parameter.
+The household choice probabilities in equation~(\ref{choice_probs}) converge to the standard logit choice probabilities when $\lambda \rightarrow 1$.
+
+The sensitivity of a subsidized consumer's demand $q_{ijt}(\textit{p})$ to a premium change is given by
+
+	\vspace{-0.4in}
+
+	\begin{eqnarray*}
+	\frac{\partial q_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta})}{\partial p_{jmt}} &=& \sum_{l \in J_{mt}} \frac{ \partial q_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta})}{\partial p_{ilt}(\textit{p})}\frac{ \partial p_{ilt}(\textit{p})}{\partial p_{jmt}}
+	\end{eqnarray*}
+
+	\vspace{-0.1in}
+
+\noindent for all plans $j,k$ in the set of available plans $J_{mt}$.
+Assuming a strictly positive subsidy that does not exceed the full, unsubsidized premium, it follows from equation (\ref{cons_premium}) that
+
+	\vspace{-0.4in}
+	\singlespacing
+
+	\begin{eqnarray}\label{price_partial_formula}
+	 \frac{\partial p_{ilt}(\textit{p})}{\partial p_{jmt}} = \begin{cases} 
+		0 & l=j, j = b \\		
+		\sigma_{it} & l = j, j \neq b \\     
+		-\sigma_{it} & l \neq j, j = b \\
+		0 & l \neq j, j \neq b
+
+   \end{cases}
+	\end{eqnarray}
+
+	\doublespacing
+
+	%\vspace{-0.1in}
+
+\noindent For a non-benchmark plan, an infinitesimal premium increase results in consumers paying more for that plan only.
+An infinitesimal increase in the benchmark premium does not affect what subsidized consumers pay for the benchmark plan, but reduces what consumers pay for all other plans because of the larger subsidy.
+The complex relationship between insurer and consumer premiums, endogenous determination of the benchmark premium, and variation in the benchmark plan across consumers due to heterogeneous entry create significant computational challenges for estimation.
+We carefully model the endogenous subsidy design despite the high computational cost because of the critical role premium subsidies play in addressing adverse selection.
+
+\subsubsection{Equilibrium}
+
+Now we find the first-order necessary conditions for a Nash equilibrium.  Differentiating equation (\ref{profit}) with respect to the premium and the commission yields the  first-order conditions
+
+\vspace{-0.4in}	
+\begin{footnotesize}
+
+	\begin{eqnarray}\label{acara_foc_short}
+	\frac{\partial R_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} + \frac{\partial RA_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} &=& (1-\iota_{ft}) \frac{\partial C_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} + \frac{\partial \mathcal{C}_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} + \frac{\partial V_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} \nonumber \\
+	\frac{\partial R_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}} + \frac{\partial RA_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}} &=& (1-\iota_{ft}) \frac{\partial C_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}} + \frac{\partial \mathcal{C}_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}} + \frac{\partial V_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}}
+	\end{eqnarray}
+
+\end{footnotesize}
+
+	\vspace{-0.1in}
+
+\noindent for all renewal groups $g$ and markets $m$ in which plan $j$ is offered by the firm in year $t$.
+In Appendix~\ref{app::model_formulas}, we write every variable in equations~(\ref{profit}) and (\ref{acara_foc_short})  in terms of three estimable variables: (1) household choice probabilities $q_{ijt}(\textit{p},\textit{n};\boldsymbol{\theta})$; (2) plan risk scores $r_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta})$; and (3) average claims $c_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta})$.
+Household choice probabilities are computed using equation (\ref{choice_probs}).
+We calculate plan risk scores as a function of observable enrollee characteristics   and the plan generosity using the estimating equation
+
+\vspace{-0.4in}
+
+	\begin{eqnarray}\label{risk_score_estimation}
+	\ln r_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) &=& \sum_{d \in D} \gamma^d s_{djmt}(\textit{p},\textit{n};\boldsymbol{\theta}) + MT'_j \gamma^{MT} + \epsilon_{jmt}^r
+	\end{eqnarray}
+
+\vspace{-0.1in}
+
+\noindent The predicted demographic share $s_{djmt}(\cdot)$ is the share of plan $j$'s enrollment in market $m$ and year $t$ with demographic characteristic $d$, $MT_j$ is a vector metal tier fixed effects,  $\epsilon_{jmt}^r$ is an error term, and the vector of risk score parameters $\boldsymbol{\gamma} = (\gamma^d,\gamma^{MT},\gamma^{n})$.
+The demographic shares are computed by aggregating the household choice probabilities.
+We calculate plan average claims as a function of the plan risk score using the estimating equation
+
+\vspace{-0.4in}
+
+	\begin{eqnarray}\label{avg_claims_estimation}
+	\ln c_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) &=& \mu^r \ln r_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) + x'_j  \mu^{x}  + \mu^l l_t +   n'_m \mu^{n} + \epsilon_{jmt}^c
+	\end{eqnarray}
+
+\vspace{-0.1in}
+
+\noindent where $r_{jmt}(\cdot)$ is the predicted risk score computed using equation (\ref{risk_score_estimation}), $x_j$ are product characteristics (not including plan AV), $l_t$ is a linear trend, $n'_m$ are market fixed effects, $\epsilon_{jmt}^c$ is an error term, and  $\boldsymbol{\mu} = (\mu^r,\mu^x,\mu^l,\mu^n)$ are the claims parameters.
+
+\subsection{Estimation}\label{subsec:steering-methods}
+
+In this section, we explain how we use the generalized method of moments (GMM) to estimate the parameter vector $\boldsymbol{\theta}$.
+We construct four sets of moment conditions: (1) demand moments that match observed choices and predicted household choice probabilities; (2) risk score moments that match observed and predicted plan risk scores; and (3) average claims moments that match observed and predicted plan average claims; and (4) the first-order conditions for profit maximization in equation~\ref{acara_foc_short}.
+These moment conditions are summarized below:
+
+	\vspace{-0.4in}
+
+	\begin{eqnarray}\label{moment_conditions}
+	\frac{1}{N^{IJT}} \sum_{i\in I, j \in J, t \in T} \frac{ \chi_{ijt} \partial  \ln  q_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta})}{\partial \boldsymbol{\beta}} &=& {\bf 0} \nonumber \\
+	\frac{1}{N^{JMT}} \sum_{j \in J,m \in M,t \in T} {\bf z}_{jmt}^r(\textit{p},\textit{n};\boldsymbol{\theta}) \left(\ln r_{jmt} - \boldsymbol{\gamma}'   {\bf z}_{jmt}^r(\textit{p},\textit{n};\boldsymbol{\theta}) \right)  &=& {\bf 0} \nonumber  \\
+	\frac{1}{N^{JMT}} \sum_{j \in J,m \in M,t \in T} {\bf z}_{jmt}^c(\textit{p},\textit{n};\boldsymbol{\theta}) \left(\ln c_{jmt} - \boldsymbol{\mu}'   {\bf z}_{jmt}^c(\textit{p},\textit{n};\boldsymbol{\theta}) \right)  &=& {\bf 0} \nonumber  \\
+	\frac{1}{N_{jt}^M} \sum_{m \in M} g_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) &=& 0,  \hspace{0.3in} \forall j \in J_t,t \in T \nonumber \\
+	\frac{1}{N_{jt}^M} \sum_{m \in M} g'_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) &=& 0,  \hspace{0.3in} \forall j \in J_t,t \in T 
+	\end{eqnarray}
+
+\noindent where $N^{IJT}$ is the number of plans available to all households in all years, $N^{JMT}$ is the number of plans available in all markets and years, $N_{jt}^M$ is the number of markets where plan $j$ is offered in year $t$, $\chi_{ijt}$ indicates whether household $i$ chose plan $j$ at time $t$, $r_{jmt}$ is the observed plan risk score, $c_{jmt}$ is the observed plan average claims, the risk score covariates ${\bf z}_{jmt}^r(\textit{p};\boldsymbol{\beta}) \equiv (s_{djmt}(\textit{p},\boldsymbol{\beta}),MT_j)$, the average claims covariates ${\bf z}_{jmt}^c(\textit{p};\boldsymbol{\theta}) \equiv (\ln r_{jmt}(\textit{p};\boldsymbol{\theta}),x_j,u_t,n_m)$, and the first-order condition values
+
+	\vspace{-0.4in}
+	\begin{footnotesize}
+	\begin{eqnarray*}
+	g_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) &\equiv& \frac{\partial R_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} + \frac{\partial RA_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} - (1-\iota_{ft}) \frac{\partial C_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} - \frac{\partial \mathcal{C}_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} - \frac{\partial V_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} \\
+	g'_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) &\equiv& 	\frac{\partial R_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}} + \frac{\partial RA_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}} - (1-\iota_{ft}) \frac{\partial C_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}} - \frac{\partial \mathcal{C}_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}} - \frac{\partial V_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}}
+	\end{eqnarray*}
+	\end{footnotesize}
+
+	\vspace{-0.1in}
+
+\noindent Because model (\ref{moment_conditions}) over-identifies the model parameters, we use two-step feasible GMM to find the values of $\boldsymbol{\theta}$ that minimize the GMM objective $[{\bf m}(\boldsymbol{\theta})]'{\bf W}^{-1}[{\bf m}(\boldsymbol{\theta})]$, where ${\bf m}(\boldsymbol{\theta})$ is the vector of moment values in model (\ref{moment_conditions}) and the optimal weight matrix ${\bf W}$ is a consistent estimate of the variance-covariance matrix of the moment values.
+
+A significant estimation challenge is to identify the effect of premiums on household choices (i.e., the parameter $\beta_i^p$).
+Several sources of exogenous variation are used to identify the premium parameter $\beta_i^p$, including: (1) exogenous variation in absolute premiums (i.e., relative to the outside option) that results from the phasing-in of the mandate penalty between 2014 and 2016 and zeroing out of the penalty in 2019; (2) exogenous variation in relative premiums (i.e., between plans) that results from kinks in the household premium formula (\ref{cons_premium}).
+Because of these kinks, some bronze plans may be ``free'' to low-income consumers if the subsidy exceeds the full premium (i.e., the second-cheapest silver plan available to the consumer may exceed the premium of some bronze plans).
+The set of free plans varies by market, time, and consumer characteristics such as income, age, and household composition.
+Unobservables at the insurer's discretion such as provider networks and formularies may also be correlated with premiums.
+We address this concern by estimating  equation (\ref{demand_model}) with insurer-market fixed effects.
+\citet{Ho2014} and \citet{Tebaldi2020} follow a similar approach.
+Our estimates are  similar when including insurer-market fixed effects.
+
+We also need to identify the steering parameter in equation~(\ref{choice_probs}).
+Unobservables such as customer service, brand image, and other forms of advertising could be correlated with commission payments.
+Commission payments may also be correlated with competition in a given market.
+We control for these variables by including insurer fixed effects and market fixed effects.
+
+***NOTE: we still need to deal with the selection issue (i.e., do people who seek agent assistance have different preferences than those who do not).  ***
+
+Another identification challenge is that we lack data on patient medical conditions to predict plan risk scores.
+Omitting medical conditions may bias estimates of the parameter vector $\gamma^d$.
+To address this potential source of bias, we compute predicted demographic shares using the estimated consumer-level choice probabilities from equation (\ref{choice_probs}) instead of the observed demographic shares, which are likely to be endogenous.
+Choice model (\ref{choice_probs}) can be interpreted as the first-stage of an IV regression for computing unbiased estimates of plan risk scores.
+A similar empirical strategy is widely used in the hospital choice literature to compute measures of hospital market concentration (e.g., \citet{Kessler2000}).
+The identifying assumption is that the predicted demographic shares are based on exogenous determinants of consumer plan demand.
+
+A third identification challenge is to obtain an unbiased estimate of the risk score parameter $\mu^r$ to predict plan average claims.
+We compute predicted plan risk scores using equation (\ref{risk_score_estimation}) instead of the observed plan risk scores, which are likely to be endogenous.
+If the ACA risk score perfectly captures plan claims risk, then enrollee characteristics should only affect plan average claims through the plan risk score and not directly affect average claims.
+Imperfections in the ACA risk score are reflected in the estimated risk score parameter.
 
@@
 
-\begin{figure}[htb]\caption{Count of Enrollees in California Exchange}
+\begin{table}[h!]
 \centering
- 		\hspace*{-1cm}\includegraphics[scale=.7]{figures/enrollee_count.png}
- 		\begin{minipage}{\textwidth}
-		\bigskip
-			\footnotesize \textsc{Notes:} The coefficients for high ratings are shown with circles, those for middle ratings are shown with triangles, and no reviews are shown with diamonds.
-The main results are designated in blue along with an indicator for specification ``Main".
-Various specifications and required minimum number of reviews are also indicated.
+\footnotesize
+\begin{minipage}[h]{6in}
+\caption[caption]{\textbf{Summary Statistics for Covered California Enrollees}\footnote{Statistics based on the population of households enrolled in a Covered California plan at any point from 2014-2019.}}
+\centerline{%
+    \input{tables/summary_stats.tex}
+}
+\label{tab:summary-stats}
 \end{minipage}
- 		\label{figure:SpecCurve}
+\end{table}
+
+\newpage
+\begin{figure}[htb]
+\caption{\textbf{Count of Enrollees in California Exchange}}
+\centering
+\begin{minipage}[h]{6in}
+\centerline{%
+    \includegraphics[scale=0.75]{figures/enrollee_count.png}
+}
+\label{fig:enrollee-count}
+\end{minipage}
 \end{figure}
 
+\newpage
+\begin{figure}[htb]
+\centering
+\footnotesize
+\begin{minipage}[h]{6in}
+\caption[caption]{\textbf{Histogram of Propensity Scores}\footnote{Propensity scores derived from a logistic regression of decision assistance on household characteristics, including the racial and ethnic makeup of the household, age of household members, gender of household members, household size, and household income.
+Regression analysis is limited to newly enrolled households, although results are comparable when considering all exchange households.}}
+\centerline{%
+    \includegraphics[scale=0.75]{figures/ps_assist_clean.png}
+}
+\label{fig:ps-balance}
+\end{minipage}
+\end{figure}
+
+\newpage
+\begin{figure}[htb]
+\centering
+\footnotesize
+\begin{minipage}[h]{6in}
+\caption[caption]{\textbf{Covariate Balance}\footnote{Standardized mean differences with and without inverse-propensity weighting, limited to newly enrolled households.
+``IPW-ATT'' reflects weighted mean differences where treated households receive a weight of 1 and untreated households receive a weight of $p/(1-p)$ and where $p$ denotes the estimated propensity score from a logistic regression of decision assistance on observable household demographics (see Figure~\ref{fig:ps-balance}).}}
+\centerline{%
+    \includegraphics[scale=0.75]{figures/cov_balance.png}
+}
+\label{fig:cov-balance}
+\end{minipage}
+\end{figure}
+
+\clearpage
+\vspace{30pt}
+{\centering \textbf{ELECTRONIC APPENDICES -- NOT FOR PRINT PUBLICATION}}
+%\noindent\textbf{\Large{Appendices}}
+\appendix
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+\renewcommand{\thefigure}{A\arabic{figure}}
+
+\section{Constructing the Outside Option}\label{outside_option}
+
+In this study, we model dynamic switching both between plans and into and out of the exchange market (any plan, vs.
+remaining uninsured) using five years of longitudinal data on exchange customers.
+Previous studies of the exchanges have treated demand as static, typically merging administrative data on exchange enrollees with survey data such as the American Community Survey (ACS) on the uninsured  to form the universe of potential exchange consumers \citep{Tebaldi2020,Domurat2017,saltzman2019}.
+In contrast, we form the uninsured population using data on consumers in our Covered California data for years in which they did not have exchange coverage, and using panel survey data on dynamics of consumers' exchange market eligibility.
+For example, within our data, consumers with exchange coverage in 2015 and 2016 are considered uninsured (the outside option) in 2014, 2017, and 2018, provided they remained eligible for the exchange market.
+Consumers might lose exchange market eligibility if they gain access to employer-sponsored insurance or public insurance such as Medicaid or Medicare.
+Because our data do not indicate when enrollees lose exchange market eligibility, we use the Survey of Income and Program Participation (SIPP) to impute consumer eligibility \citep{SIPP2019}.
+
+To impute consumer exchange market eligibility, we use data from the SIPP.
+The SIPP is well-suited for the imputation because (1) it asks the insurance status of respondents for every month over a three-year period (2013-2015) and (2) it includes detailed information on the chief reasons for consumers' coverage status, such as whether the respondent obtained or lost an offer of employer-sponsored insurance, moved in or out of California, or became eligible or ineligible for Medicare or Medicaid.
+For SIPP respondents who newly obtained or gave up individual market coverage, we construct a \textit{transitioned} variable that indicates whether the respondent gained or lost eligibility for the individual market.
+The \textit{transitioned} variable takes value 1 if the respondent (1) belongs to a household that obtained or lost an offer of employer-sponsored insurance; (2) moved out of or into California; (3) the respondent turned 65 and qualified for Medicare; and (4) the respondent became eligible for Medicaid following a drop in income.
+We estimate a logit model regression of the \textit{transitioned} variable on the demographic variables available in both the SIPP and the Covered California data, including age, income, gender, race, and household size.
+We use the estimated logit to predict whether Covered California consumers observed for only some years of our study timeframe transitioned into or out of the exchange market.
+Consumers transitioning into or out of the exchange market are removed from our study population during years when they are not enrolled in an exchange plan.
+
+\newpage
+
+\section{Mathematical Formulas in the ACA Exchange Model}\label{app::model_formulas}
+
+\noindent In this appendix, we write all model variables in terms of the following three variables and associated partial derivatives: (1) the household choice probabilities $q_{ijt}(\textit{p},\textit{n})$ with partial derivatives $\frac{ \partial q_{ikt}(\textit{p},\textit{n})}{\partial p_{ijt}(\textit{p},\textit{n})}$ and $\frac{\partial q_{ikt}(\textit{p},\textit{n})}{\partial \eta_{gijt}(\textit{p},\textit{n})}$; (2) the plan risk scores $r_{jmt}(\textit{p},\textit{n})$ with partial derivatives $\frac{\partial r_{kmt}(\textit{p},\textit{n})}{\partial p_{jmt}(\textit{p},\textit{n})}$ and $\frac{\partial r_{kmt}(\textit{p},\textit{n})}{\partial \eta_{gijt}(\textit{p},\textit{n})}$; and (3) plan average claims $c_{jmt}(\textit{p},\textit{n})$ with partial derivatives $ \frac{\partial c_{kmt}(\textit{p},\textit{n})}{\partial p_{jmt}(\textit{p},\textit{n})}$ and $\frac{\partial c_{kmt}(\textit{p},\textit{n})}{\partial \eta_{gijt}(\textit{p},\textit{n})}$.
+
+\noindent \textit{\bf Demand partial derivatives}:
+
+\noindent The demand partial derivatives with respect to the firm's base plan premium $p_{jmt}$ and commission decision $n_{gjt}$ are
+
+\vspace{-0.4in}
+
+		\begin{eqnarray*}
+		\frac{\partial q_{ikt}(\textit{p},\textit{n})}{\partial p_{jmt}} &=& \begin{cases} \sum_{l \in J_{mt}} \left[ \frac{ \partial q_{ikt}(\textit{p},\textit{n})}{\partial p_{ilt}(\textit{p})}\frac{ \partial p_{ilt}(\textit{p})}{\partial p_{jmt}} +  \delta_{glt} \sigma_{it} \frac{ \partial q_{ikt}(\textit{p},\textit{n})}{\partial \eta_{gilt}(\textit{p})}  \right] & $l= j$, \mathrm{\% \,\, commission} \\
+		\sum_{l \in J_{mt}}  \frac{ \partial q_{ikt}(\textit{p},\textit{n})}{\partial p_{ilt}(\textit{p})}\frac{ \partial p_{ilt}(\textit{p})}{\partial p_{jmt}}  & \mathrm{o/w} 
+		\end{cases}
+		\end{eqnarray*}
+
+	\vspace{-0.4in}
+	\singlespacing
+
+		 \begin{eqnarray*}
+	\frac{\partial q_{ikt}(\textit{p},\textit{n})}{\partial n_{gjt}} &=& \begin{cases} 
+		\sigma_{it} p_{jmt} \frac{\partial q_{ikt}(\textit{p},\textit{n})}{\partial \eta_{gijt}(\textit{p},\textit{n})}  & \mathrm{\% \,\, commission} \\		
+		\frac{\partial q_{ikt}(\textit{p},\textit{n})}{\partial \eta_{gijt}(\textit{p},\textit{n})} & \mathrm{\$ \,\, commission}
+   \end{cases}
+	\end{eqnarray*}
+
+		\doublespacing
+
+	\noindent	where $\frac{\partial p_{ilt}(\textit{p})}{\partial p_{jmt}}$ is given in equation~(\ref{price_partial_formula}).
+
+\noindent \textit{\bf Revenue}:
+
+\noindent Total premium revenue earned by the firm is
+
+		\vspace{-0.3in}
+
+		$$
+		R_{ft}(\textit{p},\textit{n}) = \sum_{i \in I, m \in M, k \in J_{fmt}} \sigma_{it} p_{kmt} q_{ikt}(\textit{p},\textit{n})
+		$$
+
+\noindent and the partial derivatives with respect to the firm's base plan premium $p_{jmt}$ and commission decision $n_{gjt}$ are
+
+		\vspace{-0.4in}
+
+		\begin{eqnarray*}
+		\frac{\partial R_{ft}(\textit{p},\textit{n})}{\partial p_{jmt}} &=&  \sum_{i \in I, m \in M, k \in J_{fmt}} \sigma_{it} \left(q_{ijt}(\textit{p},\textit{n}) + p_{kmt} \frac{\partial q_{ikt}(\textit{p},\textit{n})}{\partial p_{jmt}} \right) \\
+		\frac{\partial R_{ft}(\textit{p},\textit{n})}{\partial n_{gjt}} &=& \sum_{i \in I, m \in M, k \in J_{fmt}} \sigma_{it} p_{kmt}  \frac{\partial q_{ikt}(\textit{p},\textit{n})}{\partial n_{gjt}} 
+		\end{eqnarray*}
+
+	\vspace{-0.1in}
+
+\noindent \textit{\bf Claims}:
+
+\noindent Total claims paid by the firm are
+
+	\vspace{-0.3in}
+
+		$$
+		C_{ft}(\textit{p},\textit{n}) = \sum_{k \in J_{fmt}} c_{kmt}(\textit{p},\textit{n}) q_{kmt}(\textit{p},\textit{n})
+		$$
+
+\noindent where total plan demand $q_{kmt}(\textit{p},\textit{n}) = \sum_{i\in I} \left(\mathbb{I}_{i,m,t} \right) q_{ikt}(\textit{p},\textit{n})$  and the partial derivatives with respect to the firm's base plan premium $p_{jmt}$ and commission decision $n_{gjt}$ are
+
+		\vspace{-0.4in}
+		\begin{eqnarray*}
+		\frac{\partial C_{ft}(\textit{p},\textit{n})}{\partial p_{jmt}} &=& \sum_{k \in J_{fmt}} \left[ c_{kmt}(\textit{p},\textit{n})\frac{ \partial q_{kmt}(\textit{p},\textit{n})}{\partial p_{jmt}}   +  q_{kmt}(\textit{p},\textit{n})\frac{ \partial c_{kmt}(\textit{p},\textit{n})}{\partial p_{jmt}} \right] \\
+		\frac{\partial C_{ft}(\textit{p},\textit{n})}{\partial n_{gjt}} &=& \sum_{k \in J_{fmt}} \left[ c_{kmt}(\textit{p},\textit{n})\frac{ \partial q_{kmt}(\textit{p},\textit{n})}{\partial n_{gjt}}   +  q_{kmt}(\textit{p},\textit{n})\frac{ \partial c_{kmt}(\textit{p},\textit{n})}{\partial n_{gjt}} \right]
+		\end{eqnarray*}
+
+	\vspace{-0.1in}
+
+\noindent \textit{\bf Commissions}:
+
+\noindent Total commissions paid by the firm are
+
+	\vspace{-0.3in}
+
+		$$
+		\mathcal{C}_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) = \sum_{g \in G, i \in I, m \in M, k \in J_{fmt}} \left( \mathbb{I}_{n,i,t} \right)   \eta_{gikt}(\textit{p},\textit{n}) q_{ikt}(\textit{p},\textit{n};\boldsymbol{\beta})
+		$$
+
+\noindent and the partial derivatives with respect to the firm's base plan premium $p_{jmt}$ and commission decision $n_{gjt}$ are
+
+\vspace{-0.4in}
+
+		\begin{eqnarray*}
+		\frac{\partial \mathcal{C}_{ft}(\textit{p},\textit{n})}{\partial p_{jmt}} &=& \begin{cases} \sum_{g \in G, i \in I,m \in M, k \in J_{fmt}} \mathbb{I}_{n,i,t} \left[ \eta_{gikt}(\textit{p},\textit{n}) \frac{ \partial q_{ikt}(\textit{p},\textit{n})}{\partial p_{jmt}} +  \left(\delta_{gjt} \sigma_{it} \right)  q_{ikt}(\textit{p},\textit{n})  \right] &  \mathrm{\% \,\, commission} \\
+		  \sum_{g \in G, i \in I, m \in M, k \in J_{fmt}} \left( \mathbb{I}_{n,i,t}\right) \eta_{gikt}(\textit{p},\textit{n}) \frac{ \partial q_{ikt}(\textit{p},\textit{n})}{\partial p_{jmt}}  & \mathrm{\$ \,\, commission}
+		\end{cases}
+		\end{eqnarray*}
+
+\vspace{-0.4in}
+	\singlespacing
+
+		 \begin{eqnarray*}
+	\frac{\partial \mathcal{C}_{ft}(\textit{p},\textit{n})}{\partial n_{gjt}} &=& \begin{cases} 
+		\sum_{g \in G, i \in I, m \in M, k \in J_{fmt}} \mathbb{I}_{n,i,t} \left[\eta_{gikt}(\textit{p},\textit{n}) \frac{\partial q_{ikt}(\textit{p},\textit{n})}{\partial n_{gjt}} +  \left(\sigma_{it} p_{jmt} \right) q_{ikt}(\textit{p},\textit{n})   \right]   & \mathrm{\% \,\, commission} \\
+		\sum_{g \in G, i \in I, m \in M, k \in J_{fmt}} \mathbb{I}_{n,i,t} \left[\eta_{gikt}(\textit{p},\textit{n}) \frac{\partial q_{ikt}(\textit{p},\textit{n})}{\partial n_{gjt}} + q_{ikt}(\textit{p},\textit{n})  \right]  & \mathrm{\$ \,\, commission}
+   \end{cases}
+	\end{eqnarray*}
+
+		\doublespacing
+
+\noindent \textit{\bf Risk adjustment}:
+
+\noindent As defined in equation~(\ref{ra_formula}), the firm's risk adjustment transfer is
+
+	\vspace{-0.3in}
+
+	$$
+	RA_{ft}(\textit{p},\textit{n}) =  R_t(\textit{p},\textit{n}) \sum_{m \in M, k \in J_{fmt}} \left[ rs_{kmt}(\textit{p},\textit{n}) - us_{kmt}(\textit{p},\textit{n})  \right]
+	$$
+
+\noindent and the partial derivatives with respect to the firm's base plan premium $p_{jmt}$ and commission decision $n_{gjt}$ are
+
+		\vspace{-0.4in}
+
+		\begin{eqnarray*}
+		\frac{\partial RA_{ft}(\textit{p},\textit{n})}{\partial p_{jmt}} &=& \sum_{k \in J_{fmt}}  \left[\frac{\partial R_t(\textit{p},\textit{n})}{\partial p_{jmt}}\left( rs_{kmt}(\textit{p},\textit{n}) - us_{kmt}(\textit{p},\textit{n})  \right) \right.
+\nonumber \\ && \left.
++ \,\,\,  R_t(\textit{p},\textit{n}) \left( \frac{\partial rs_{kmt}(\textit{p},\textit{n})}{\partial p_{jmt}} - \frac{\partial  us_{kmt}(\textit{p},\textit{n})}{\partial p_{jmt}} \right) \right] \\
+		\frac{\partial RA_{ft}(\textit{p},\textit{n})}{\partial n_{gjt}} &=& \sum_{k \in J_{fmt}}  \left[\frac{\partial R_t(\textit{p},\textit{n})}{\partial n_{gjt}}\left( rs_{kmt}(\textit{p},\textit{n}) - us_{kmt}(\textit{p},\textit{n})  \right) \right.
+\nonumber \\ && \left.
++ \,\,\,  R_t(\textit{p},\textit{n}) \left( \frac{\partial rs_{kmt}(\textit{p},\textit{n})}{\partial n_{gjt}} - \frac{\partial  us_{kmt}(\textit{p},\textit{n})}{\partial n_{gjt}} \right) \right]
+		\end{eqnarray*}
+
+		\vspace{-0.1in}
+
+\noindent where
+
+\vspace{-0.4in}
+
+	\begin{eqnarray*}
+	\frac{\partial R_t(\textit{p},\textit{n})}{\partial p_{jmt}} &=& \sum_{f \in F} \frac{\partial R_{ft}(\textit{p},\textit{n})}{\partial p_{jmt}} \\
+	\frac{\partial R_t(\textit{p},\textit{n})}{\partial n_{gjt}} &=& \sum_{f \in F} \frac{\partial R_{ft}(\textit{p},\textit{n})}{\partial n_{gjt}}
+	\end{eqnarray*}
+
+\vspace{-0.4in}
+
+	\begin{eqnarray*}
+	\frac{ \partial us_{kmt}(\textit{p},\textit{n})}{\partial p_{jmt}} 
+	&=& \left(\sum_{m\in M,l \in J_{mt}} h_l q_{lmt}(\textit{p},\textit{n}) \right)^{-1}  \\ && \times \,\,\, \left[h_k \frac{\partial q_{kmt}(\textit{p},\textit{n})}{\partial p_{jmt}} - \frac{h_k q_{kmt}(\textit{p},\textit{n})}{\sum_{m\in M,l \in J_{mt}} h_l q_{lmt}(\textit{p},\textit{n})}  \sum_{l \in J_{mt}} h_l \frac{\partial q_{lmt}(\textit{p},\textit{n})}{\partial p_{jmt} } \right] \\
+	\frac{ \partial us_{kmt}(\textit{p},\textit{n})}{\partial n_{gjt}} 
+	&=& \left(\sum_{m\in M,l \in J_{mt}} h_l q_{lmt}(\textit{p},\textit{n}) \right)^{-1}  \\ && \times \,\,\, \left[h_k \frac{\partial q_{kmt}(\textit{p},\textit{n})}{\partial n_{gjt}} - \frac{h_k q_{kmt}(\textit{p},\textit{n})}{\sum_{m\in M,l \in J_{mt}} h_l q_{lmt}(\textit{p},\textit{n})}  \sum_{l \in J_{mt}} h_l \frac{\partial q_{lmt}(\textit{p},\textit{n})}{\partial n_{gjt} } \right]
+	\end{eqnarray*}
+
+\vspace{-0.4in}
+
+	\begin{eqnarray*}
+	\frac{ \partial rs_{kmt}(\textit{p},\textit{n})}{\partial p_{jmt}} 
+	&=& \left(\sum_{m\in M,l \in J_{mt}} r_{lmt}(\textit{p},\textit{n}) q_{lmt}(\textit{p},\textit{n})\right)^{-1}\left[\left(r_{kmt}(\textit{p},\textit{n})\frac{\partial q_{kmt}(\textit{p},\textit{n})}{\partial p_{jmt}} + q_{kmt}(\textit{p},\textit{n})\frac{\partial r_{kmt}(\textit{p},\textit{n})}{\partial p_{jmt}} \right) \right.\\
+	&& - \,\,\, \left.
+\frac{r_{jmt}(\textit{p},\textit{n}) q_{jmt}(\textit{p},\textit{n})}{\sum_{m\in M,l \in J_{mt}} r_{lmt}(\textit{p},\textit{n}) q_{lmt}(\textit{p},\textit{n})}\sum_{l \in J_{mt}} \left[r_{lmt}(\textit{p},\textit{n})\frac{\partial q_{lmt}(\textit{p},\textit{n})}{\partial p_{jmt}} + q_{lmt}(\textit{p},\textit{n})\frac{\partial r_{lmt}(\textit{p},\textit{n})}{\partial p_{jmt}} \right]\right] \\
+	\frac{ \partial rs_{kmt}(\textit{p},\textit{n})}{\partial n_{gjt}} 
+	&=& \left(\sum_{m\in M,l \in J_{mt}} r_{lmt}(\textit{p},\textit{n}) q_{lmt}(\textit{p},\textit{n})\right)^{-1}\left[\left(r_{kmt}(\textit{p},\textit{n})\frac{\partial q_{kmt}(\textit{p},\textit{n})}{\partial n_{gjt}} + q_{kmt}(\textit{p},\textit{n})\frac{\partial r_{kmt}(\textit{p},\textit{n})}{\partial n_{gjt}} \right) \right.\\
+	&& - \,\,\, \left.
+\frac{r_{jmt}(\textit{p},\textit{n}) q_{jmt}(\textit{p},\textit{n})}{\sum_{m\in M,l \in J_{mt}} r_{lmt}(\textit{p},\textit{n}) q_{lmt}(\textit{p},\textit{n})}\sum_{l \in J_{mt}} \left[r_{lmt}(\textit{p},\textit{n})\frac{\partial q_{lmt}(\textit{p},\textit{n})}{\partial n_{gjt}} + q_{lmt}(\textit{p},\textit{n})\frac{\partial r_{lmt}(\textit{p},\textit{n})}{\partial n_{gjt}} \right]\right]
+	\end{eqnarray*}
+
+\noindent \textit{\bf Variable administrative cost}:
+
+\noindent Total variable administrative cost is
+
+	\vspace{-0.3in}
+
+		$$
+		V_{ft}(\textit{p},\textit{n}) = v_{ft} q_{ft}(\textit{p},\textit{n})
+		$$
+
+\noindent where $v_{ft}$ is the variable administrative cost per-member per-month and total firm demand $q_{ft}(\textit{p},\textit{n}) = \sum_{i \in I, j \in J_f} q_{ijt}(\textit{p},\textit{n})$.
+The partial derivatives with respect to the firm's base plan premium $p_{jmt}$ and commission decision $n_{gjt}$ are
+
+		\vspace{-0.4in}
+
+	\begin{eqnarray*}
+	\frac{ \partial V_{ft}(\textit{p},\textit{n})}{\partial p_{jmt}} &=& v_{ft} \frac{\partial q_{ft}(\textit{p},\textit{n})}{\partial p_{jmt}} \\
+	\frac{ \partial V_{ft}(\textit{p},\textit{n})}{\partial n_{gjt}} &=& v_{ft} \frac{\partial q_{ft}(\textit{p},\textit{n})}{\partial n_{gjt}}
+	\end{eqnarray*}
+
 \end{document}

### 2021-06-14 analysis/decision-support/_ChoiceSummary.R
update figures and temp fix for confidence intervals

@@ -194,12 +194,12 @@ choice.metals <- metal.final.cond %>%
 choice.insurer <- ins.final.cond %>%
   mutate(insurer = case_when(
     insurer=="ANT" ~ "Anthem",
-    insurer=="BS" ~ "BCBS",
-    insurer=="HN" ~ "HealthNet",
+    insurer=="BS" ~ "Blue Shield",
+    insurer=="HN" ~ "Health Net",
     insurer=="KA" ~ "Kaiser",
     insurer=="Small" ~ "Other"
   )) %>%
-  mutate(insurer = factor(insurer, levels=c("Anthem","BCBS","HealthNet","Kaiser","Other"))) %>%
+  mutate(insurer = factor(insurer, levels=c("Anthem","Blue Shield","Health Net","Kaiser","Other"))) %>%
   ggplot(aes(x=as.factor(insurer),y=att)) +
   geom_hline(aes(yintercept=0),linetype="dashed") +
   geom_errorbar(aes(ymin=p05, ymax=p95),

### 2021-06-14 finals/paper.tex

--- 2021-06-08 finals/paper.tex
@@
 \begin{abstract}
-\noindent 
+\noindent In many markets, consumers have access to an agent or some other intermediary to aid in decision making.
+The influence of such agents on consumer decisions, and the firm's influence on the behaviors of its agents, have important implications for the efficiency of these markets.
+In this paper, we study the welfare effects of decision assistance and firm steering in health insurance using the population of enrollments from the California Affordable Care Act (ACA) exchange from 2014 to 2019.
+We find that enrollees are nearly 2x more likely to select a silver plan when using some form of decision assistance and 30\% less likely to select a ``dominated'' plan.
+Preliminary results suggest that firms have considerable ability to steer consumers' decisions using agent commissions, where a \$1 increase in commissions paid to agents has the same effect as a \$2 or \$3 increase in plan premiums.
 \end{abstract}
@@
 While identifying ``improvement'' is not generally feasible in our data, we can identify specific instances in which the observed plan choice is dominated by some other plan in an individual's choice set.
-For example, Gold and Platinum tier plans are dominated for any household that is eligible for cost-sharing subsidies and with incomes below 150\% of the federal poverty level.
+For example, gold and platinum tier plans are dominated for any household that is eligible for cost-sharing subsidies and with incomes below 150\% of the federal poverty level.
 We can therefore identify dominated choices and examine whether those with decision assistance appear less likely to select a dominated plan.
@@
 We again find evidence of heterogeneities in the effects of different forms of decision assistance.
-In particular, we find that individuals using publicly provided decision assistance are around 0.76 percentage points less likely to select a dominated plan, while individuals using a private insurance agent are 1.2 percentage points less likely to select a dominated plan.
+In particular, we find that individuals using publicly provided decision assistance are around 0.8 percentage points less likely to select a dominated plan, while individuals using a private insurance agent are 1.2 percentage points less likely to select a dominated plan.
 
@@
 \subsection{Decision Assistance}
-There are two forms of formal decision assistance available to potential enrollees on the California exchange: publicly funded ``navigators;'' and private insurance agents or brokers.
+There are two forms of formal decision assistance available to potential enrollees on the California exchange: publicly funded ``navigators'' and private insurance agents or brokers.
 For states participating in the federal exchange, navigators are mandated under the ACA and federally funded.
@@
 Relatedly, navigators tend to work with households of lower incomes, currently uninsured, and non-native english speakers.
+Among individuals receiving some form of assistance in our data, about 30\% of households used a navigator.
+
+Potential enrollees on the California exchange may also use a traditional private insurance agent or broker (hereafter, agents).
+Agents are not generally tied to any specific insurer and can enroll individuals in any available plans.
+Agents are also not restricted to any specific geography or region and can enroll individuals in the relevant rating area regardless of the physical office in which the agent resides.
+Among individusl receiving some form of assistance in our data, 70\% used a private insurance agent.
+
+Unlike navigators, agents are paid commissions for each enrollment into an exchange plan.
+The amount of commission varies by insurer and is generally set as a flat fee per enrollee or as a percentage of the premium paid by that enrollee.
+For new enrollees, flat fee commissions typically range between \$100 and \$200, with percent commissions ranging between 2\% and 5\%.
+Figure~\ref{fig:commissions} presents the observed commission rates by insurer over time, separately among insurers offering a flat fee commission versus those offering a percentage commission.
+As is evident from the figure, there exists relatively large variation in commissions across insurers, as well as within-variation over time for large insurers such as Anthem, Health Net, and Blue Shield.
 
@@
 
-Our final data consist of 8.3 million total annual enrollments from 2014-2019.
-Of these, 4.5 million are newly enrolled (e.g., not enrolled in any California exchange plan in the prior year).
-Table~\ref{tab:summary-stats} displays summary statistics for Covered California households, separately between those that used and did not use decision assistance.
-The silver tier is the most commonly selected option because consumers eligible for cost sharing reductions (CSRs) must choose a silver plan to receive CSRs.
-Approximately 68 percent of California enrollees and 61 percent of Washington enrollees are eligible for CSRs, while 91 percent of California enrollees and 85 percent of Washington enrollees are eligible for premium subsidies.
-The proportion of consumers exempt from the individual mandate is small, but is notably higher among those who are uninsured.
-The uninsured rate is substantially higher among young adults and males in both states.
-Individuals with incomes between 250 and 400 percent of FPL, who receive relatively small subsidies, and those with incomes above 400 percent of FPL, who are ineligible for subsidies, make up a relatively large share of the uninsured population.
+Our final data consist of 8.3 million total households from 2014-2019.
+Of these, 4.5 million were not previously enrolled in any Covered California plan in the prior year.
+Table~\ref{tab:summary-stats} displays summary statistics for all households in our data.
+Since the key independent variable throughout much of our analysis is whether a household used some form of decision assistance, we present summary statistics separately between those that used and did not use decision assistance.
 
-\begin{table}[h]
-\centering	
-\caption{Summary Statistics for Covered California Enrollees}
-\input{tables/summary-stats.tex}
-\footnote{Something}
-\label{tab:summary-stats}
-\end{table}
+We see from Table~\ref{tab:summary-stats} that enrollees using decision assistance are of lower income and larger household size.
+Among types of plans purchased, we see little difference between those with and without decision assistance, with the exception of Kaiser plans for which individuals using decision assistance are less likely to purchase.
+Overall, the silver tier is the most commonly selected option, and this is particularly true for those using decision assistance.
+Enrollees with decision assistance are also much more likely to select an HMO and relatively more likely to select a PPO.
 
@@
 
-Interpreting our results as an estimate of the ATT assumes that individuals receiving decision assistance do not seek assistance due to some unobserved factors that also affect their plan choice.
-Conditional on household characteristics as well as insurer fixed effects, interacted with a full set of region and year fixed effects, we argue that this assumption is plausible.
+Figure~\ref{fig:ps-balance} presents the resulting propensity scores from our preliminary logit regression of decision assistance against observable household demographics.
+As is evident from the figure, there exists common support in propensity scores for the treated and control groups.
+In Figure~\ref{fig:cov-balance}, we present a comparison of observable household characteristics between the treatment and control groups.
+The hollow circles in Figure~\ref{fig:cov-balance} reflect the unadjusted differences in means, while the solid circles reflect the difference in means when weighting households.
+Weights for treated households are set to 1, and weights for untreated households are set to  $\frac{\hat{p}_{i}}{1-\hat{p}_{i}}$ based on the preliminary logistic regression.
+We see from Figure~\ref{fig:cov-balance} that our treated and control groups are well-balanced after weighting.
+
+We summarize our ATT estimates by insurer and metal tier, presented in Figures~\ref{fig:choice-insurer} and \ref{fig:choice-metal} respectively.
+Figure~\ref{fig:choice-insurer} shows that individuals using decision assistance are significantly more likely to select a plan offered by Blue Shield, Health Net, or another smaller insurer, and much less likely to select a plan offered by Anthem or Kaiser.
+Of note, Anthem and Kaiser are similar in that they both offer flat commission payments.
+Kaiser sets the lowest of all such flat commissions in all years, while Anthem dropped their commission payments dramatically beginning in 2015.
+We investigate the issue of commission and plan choice more fully in Section \ref{sec:steering}.
 
@@
 \label{sec:dominated}
-As a complementary empirical analysis, we identify specific instances in which the observed plan choice is dominated by some other plan in an individual's choice set, and we estimate the effects of decision assistance on the probability of making such a choice.
-For example, Gold and Platinum tier plans are dominated for any household that is eligible for cost-sharing subsidies and with incomes below 150\% of the federal poverty level.
-We estimate the effect of decision assistance on dominated choices with a linear probability model, allowing for year, insurer, and region fixed effects.
+The results in Section~\ref{subsec:causal-results} reveal large effects of decision assistance on plan choice; however, it is not clear from those results whether decision assistance \textit{improves} plan choice or simply reallocates households into different, perhaps worse, plans.
+
+To examine this question, we first identify specific instances in which the observed plan choice is dominated by some other plan in an individual's choice set, and we estimate the effects of decision assistance on the probability of making such a choice.
+For example, for any household that is eligible for cost-sharing subsidies and with incomes below 150\% of the federal poverty level (FPL), silver plans will have lower premiums and lower out-of-pocket costs compared to gold or platinum tier plans such that the actuarial value of silver plans exceeds that of gold and platinum plans.
+Since provider networks are not allowed to vary across metal tiers for the same plan type, gold and platinum plans are strictly dominated by silver plans for such households.
+Gold plans are similarly dominated by silver plans for households with incomes between 150\% and 200\% of the FPL.
+
+We estimate the effect of decision assistance on dominated choices with a logistic regression, in which the outcome is an indicator for whether the enrollee made a dominated choice.
+Individuals that do not have a dominated plan in their choice set are excluded.
+Following the process laid out in Section~\ref{sec:causal}, we estimate a weighted logistic regression model only among individuals without any decision assistance, with weights derived from a preliminary logit regression of decision assistance against observable household characteristics.
+We then use the coefficient estimates to form predicted counterfactual probabilities for dominated choices among individuals that did use decision assistance.
+Finally, again limiting to those with decision assistance, our estimate of the ATT is the average probability of a dominated choice less the average predicted probability of a dominated choice.
+
+Results are presented in Figure~\ref{fig:dom-choice}, where we show the point estimate and 95\% confidence interval for the ATT.
+We also report the mean proportion of dominated choices observed in the data.
+We present different ATTs for people with any decision assistance and for those specifically using public navigators versus private insurance agents.
+We estimate that individuals are just over 1 percentage point less likely to make a dominated choice when using any form of decision assistance.
+On a base of 3.5\%, this reflects a nearly 30\% reduction in the prevalence of dominated choices.
+These effects are largest among those using a private insurance agent, where we estimate an ATT of -1.2 percentage points compared to an ATT of -0.8 percentage points for individuals using a navigator.
 
@@
 
-\subsection{Model of Commissions and Steering}
+\subsection{Model}
 \label{subsec:steering-model}
 
-\subsection{Structural Estimation}
+Consider a two-stage  game where  (1) firms set premiums and commissions simultaneously to maximize their expected profit and (2) consumers select a plan to maximize their expected utility.
+In the following three subsections, we detail how we (1) model the decisions of firms; (2) model the decisions of consumers; and (3) find the model equilibrium.
+
+Given our available data, we do not explicitly model the actions of individual insurance agents.
+However, we do model how firms use agent compensation to steer an agent's clients to their plans.
+Our approach assumes that the consumer's decision to seek agent assistance is independent of the firms' commission levels.
+This identifying assumption is valid if commissions incentivize agents to recommend certain plans to their clients, but do not induce agents to change advertising levels or marketing efforts to  seek new clients.
+Advertising and marketing by both insurers and agents are tightly regulated, particularly in Covered California.
+We therefore believe our identifying assumption is relatively  innocuous.
+
+\subsubsection{Stage 1: Firms Set Premiums and Commissions}
+
+\paragraph{Firm Decision Variables:}
+Firms set premiums and commissions to maximize their expected profit.
+Let $p_{jmt}$ be the base premium decision for each plan $j$ sold in market $m$ in period $t$ and the \textit{commission decision} $n_{gjt}$
+
+\vspace{-0.4in}		
+\singlespacing
+\begin{eqnarray*}
+    n_{gjt}  \equiv 
+    \begin{cases} 
+	    \delta_{gjt} & \mathrm{\% \,\, commission} \\		
+	    \eta_{gjt} & \mathrm{\$ \,\, commission} \\
+	    0 & \mathrm{o/w}
+    \end{cases}
+\end{eqnarray*}		   
+\doublespacing
+\noindent for each plan $j$ sold at time $t$ with renewal status $g$ (i.e., new or existing customer).
+Agents are either paid a percentage $\delta_{gjt}$  of the consumer's unsubsidized premium  or a flat amount $\eta_{gjt}$ that is independent of the premium.
+We assume the firm's decision to pay a percentage commission or flat commission is exogenous because switching agent compensation methods is costly.
+The only firm that switched between compensation methods during our six-year study timeframe was Health Net following its acquisition by Centene.
+The \textit{commission paid} to household $i$'s insurance agent is
+
+\vspace{-0.4in}		
+\singlespacing			
+\begin{eqnarray*}
+	\eta_{gijt}(\textit{p},\textit{n})  \equiv 
+	\begin{cases} 
+		n_{gjt} \left(\sigma_{it}p_{jmt}\right) & \mathrm{\% \,\, commission} \\		
+		n_{gjt} & \mathrm{\$ \,\, commission}
+    \end{cases},
+\end{eqnarray*}
+\doublespacing
+\noindent where $\textit{p} = {\bf p}_t$ is the vector of plan base premiums set by all insurers in each market in year $t$, $\textit{n} = {\bf n}_t$ is the vector of commission decision variables in period $t$, and the household's (unsubsidized) premium is the product of the household's rating factor $\sigma_{it}$  and the plan's base premium $p_{jmt}$.
+In California, the rating factor can vary by age and geographic residence of the household's members.\footnote{The ACA also permits rating by tobacco usage, but California prohibits tobacco rating.}  Insurers can charge a 64-year-old up to 3 times as much as a 21-year-old.
+Figure~\ref{rating_area_partitions} shows the partition of California into rating areas.
+In each rating area,  an insurer's premium must be the same for all consumers of the same age.
+Total commissions paid by firm $f$  are
+
+\vspace{-0.2in}		
+\begin{equation*}
+    \mathcal{C}_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) = \sum_{g \in G, i \in I, m\in M, k \in J_{fmt}} \left( \mathbb{I}_{n,i,t} \right)  q_{ikt}(\textit{p},\textit{n};\boldsymbol{\beta}) \eta_{gikt}(\textit{p},\textit{n}),
+\end{equation*}
+where $\mathbb{I}_{n,i,t}$ indicates whether household $i$ is assisted by an agent in year $t$, $q_{ikt}(\cdot)$ is the probability household $i$ chooses plan $k$ at time $t$, and $J_{fmt}$ is the set of plans offered by firm $f$ in market $m$ at time $t$.
+The model parameters $\boldsymbol{\theta} \equiv (\boldsymbol{\beta},\boldsymbol{\gamma},\boldsymbol{\mu})$, where $\boldsymbol{\beta}$ are the demand parameters, $\boldsymbol{\gamma}$ are the risk score parameters, and $\boldsymbol{\mu}$ are the average claims parameters.
+
+\paragraph{Risk Adjustment Transfers:} 
+\citet{Pope2014} derive the ACA risk adjustment transfer formula.\footnote{We start with \citet{Pope2014}'s transfer formula as derived in their first appendix, which allows plans to vary only by their actuarial values (and not by differences in firm efficiency, geographic costs, allowable rating factors, or moral hazard).
+We start with this formula because we want to capture all differences in expected risk, except for cost sharing and any associated moral hazard, in the plan's risk score (i.e., cost sharing and moral hazard are addressed through the utilization share).
+In contrast, the plan liability risk score   $PLRS_j$ as defined in \citet{Pope2014}'s second appendix does not account for certain differences such as variation in geographic cost.
+Instead, \citet{Pope2014} account for these differences by applying factors in the transfer formula.}  In our notation, the per-member per-month risk adjustment transfer $ra_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta})$ for plan $j$ is
+
+\vspace{-0.2in}
+\begin{equation*}
+	ra_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) = \left(\frac{r_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta})\sum_{m \in M, l \in J_{mt}} q_{lmt}(\textit{p},\textit{n};\boldsymbol{\beta})}{\sum_{m \in M, l \in J_{mt}} r_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) q_{lmt}(\textit{p},\textit{n};\boldsymbol{\beta})}    -     \frac{h_j\sum_{m \in M, l \in J_{mt}} q_{lmt}(\textit{p},\textit{n};\boldsymbol{\beta})}{\sum_{m \in M, l \in J_{mt}} h_l q_{lmt}(\textit{p},\textit{n};\boldsymbol{\beta})}\right)\overline{p},
+\end{equation*}
+where $r_{jmt}(\cdot)$ is the plan risk score, $h_j$ is an exogenous expected utilization factor set by regulation that accounts for the plan AV and any associated moral hazard, and $\overline{p}$ is the weighted average premium in the market.
+The plan's total risk adjustment transfer $RA_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta})$ equals
+
+\vspace{-0.4in}
+\begin{eqnarray}
+\label{eqn:ra_formula}
+	RA_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) &=& ra_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta})  q_{jmt}(\textit{p},\textit{n};\boldsymbol{\beta}) \nonumber \\
+	&= & \left[rs_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta})  - us_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta})  \right] R_t(\textit{p},\textit{n};\boldsymbol{\beta}),
+\end{eqnarray}
+where $rs_{jmt}(\cdot)$ is the plan's ``risk share'' of total claims, $us_{jmt}(\cdot)$ is the plan's ``utilization share'' of total claims, and $R_t(\cdot) = \sum_f R_{ft}(\cdot)$ is total premium revenue across all plans.
+The total risk adjustment transfer for the firm equals the sum of the risk adjustment transfers for the plans that it sells (i.e., $RA_{ft}(\cdot) = \sum_{m \in M, j \in J_{fmt}} RA_{jmt}(\cdot)$.
+
+The plan's risk share includes the combined effects of adverse selection, moral hazard, and plan AV, whereas the plan's utilization share only includes the effects of moral hazard and plan AV.
+Thus, the difference between the risk share and utilization share captures the plan's relative risk due to adverse selection only.
+The risk share equals
+
+\vspace{-0.1in}
+\begin{equation*}
+	rs_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) = \frac{ r_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) q_{jmt}(\textit{p},\textit{n};\boldsymbol{\beta})}{\sum_{m \in M, l \in J_{mt}}  r_{lmt}(\textit{p},\textit{n};\boldsymbol{\theta}) q_{lmt}(\textit{p},\textit{n};\boldsymbol{\beta})},
+\end{equation*}
+where $J_{mt}$ is the set of all plans offered in market $m$ and year $t$, and the plan risk score $r_{jmt}(\cdot)$ is a function of enrollee characteristics and the plan AV.
+We do not directly observe plan risk scores in the insurer rate filing data.
+However, we observe all other variables in Equation~\eqref{eqn:ra_formula}, including each plan's risk adjustment transfer, and can therefore solve for the plan risk scores.
+The plan's utilization share $us_{jmt}(\cdot)$ equals
+
+\vspace{-0.1in}
+\begin{equation*}
+	us_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) =  \frac{ h_j q_{jmt}(\textit{p},\textit{n};\boldsymbol{\beta})}{\sum_{m \in M, l \in J_{mt}} h_l q_{lmt}(\textit{p},\textit{n};\boldsymbol{\beta})}.
+\end{equation*}
+A positive difference between the risk share and the utilization share indicates that a plan has high risk relative to its expected utilization and results in the plan receiving a risk adjustment transfer; a negative difference indicates that a plan has low risk relative to its expected utilization and results in the plan paying a risk adjustment transfer.
+
+\paragraph{Calculating Variable Profit:} 
+Firms choose premiums and commissions to maximize expected variable profit
+
+\vspace{-0.4in}		
+\begin{footnotesize}
+\begin{eqnarray}
+\label{eqn:profit}
+	\pi_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) &=&  R_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) -  C_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) - \mathcal{C}_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) + RA_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) +  RI_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})  - V_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})  \nonumber \\
+	&=& R_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) - (1 - \iota_{ft}) C_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) - \mathcal{C}_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}) + RA_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})   - V_{ft}(\textit{p},\textit{n};\boldsymbol{\theta}),
+\end{eqnarray}
+\end{footnotesize}
+
+\noindent where $R_{ft}(\cdot)$ is total premium revenue, $C_{ft}(\cdot)$ is total claims, $RI_{ft}(\cdot)$ is reinsurance received, $V_{ft}(\cdot)$  is variable administrative cost (excluding commissions), and $\iota_{ft}$ is the actuarial value of the reinsurance contract (i.e., the expected percentage of claims paid by the reinsurer).
+Total commissions paid $\mathcal{C}_{ft}(\cdot)$ and risk adjustment received  $RA_{ft}(\cdot)$ are as above.
+
+\subsubsection{Stage 2: Household Plan Choice}
+Households choose the plan that maximizes their (indirect) utility function
+
+\vspace{-0.4in}
+\begin{eqnarray}
+\label{eqn:demand_model}
+	U_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta}) &\equiv& \beta_{i}^p p_{ijt}(\textit{p}) + \beta_j^{\eta} \eta_{gijt}(\textit{p},\textit{n})   + \beta_i^y y_{ij(t-1)} + x'_{ij}\beta^x + \xi_{j} + \epsilon_{ijt}^d,
+\end{eqnarray}
+where $p_{ijt}(\textit{p})$ is household $i$'s (subsidized) premium for plan $j$ in year $t$, $\eta_{gijt}(\textit{p},\textit{n})$ is the commission paid to household $i$'s insurance agent, $y_{ij(t-1)}$ indicates whether household $i$ chose plan $j$ in the previous year, $x_{ij}$ is a vector of observed product characteristics including the plan AV,  $\xi_{j}$ is a vector of unobserved product characteristics, and $\epsilon_{ijt}^d$ is an error term.
+CSRs enter utility through the plan AV and premium subsidies reduce the household's premium $p_{ijt}(\textit{p})$.
+The utility of the outside option $U_{i0t} = \beta_i^p \rho_{it} + \epsilon_{i0t}$, where $\rho_{it}$ is the household's penalty for not having insurance in year $t$.
+
+The household's premium is calculated as
+
+\vspace{-0.4in}
+\begin{eqnarray}
+\label{eqn:cons_premium}
+	p_{ijt}(\textit{p}) &=& \max \left \lbrace \underbrace{\sigma_{it} p_{jmt}}_{\text{\scriptsize{full premium}}}  - \underbrace{\max\{\sigma_{it} p_{bmt} - \zeta_{it},0\}}_{\text{\scriptsize{premium subsidy}}},0 \right \rbrace,
+\end{eqnarray}
+where $\sigma_{it}$ is the household's rating factor as before, $p_{bmt}$ is the base premium of the benchmark plan in market $m$ and year $t$, and $\zeta_{it}$ is the household's income contribution cap.
+The household's premium subsidy equals the difference between what the household would pay for the benchmark plan (i.e., $\sigma_{it} p_{bmt}$) and the household's income contribution cap $\zeta_{it}$.
+The benchmark plan is the second-cheapest silver plan available to the household and varies between consumers because of heterogeneous firm entry.
+The income contribution cap ranged from $2\%$ of annual income for consumers earning $100\%$ of the federal poverty level (FPL) and $9.5\%$ of annual income for consumers earning $400\%$ of FPL in 2014.
+The income contribution caps increase slightly each year.
+Subsidies can be applied to any plan except a catastrophic plan.
+For some low-income consumers, the premium subsidy may exceed the full premium of certain bronze plans.
+The subsidy is reduced in these cases to ensure nonnegativity of the premium.
+
+We define the vector of demand parameters $\boldsymbol{\beta} \equiv (\beta_i^p,\beta_j^{\eta},\beta_i^y,\beta^x)$ to accommodate heterogeneous consumer preferences.
+The household's premium parameter $\beta_{i}^p \equiv \beta^p + w'_{it} \phi$ varies with household characteristics $w_{it}$.
+The household's inertia parameter $\beta_i^y = \beta^y +  x'_{ij} \kappa + w'_{it} \nu$ varies with both household and product characteristics.
+The steering parameter $\beta_j^{\eta}$ captures the degree to which agent compensation steers  an agent's clients to particular plans.
+A high value of $\beta_j^{\eta}$ would indicate that agent compensation is effective in steering consumers.
+Because smaller firms offer agents considerably higher commissions, we allow the steering parameter to vary with firm size.
+
+\paragraph{Calculating Demand}
+We assume Equation~\eqref{eqn:demand_model}) is a nested logit model such that the vector of error terms $\epsilon_i$ has the generalized extreme value distribution.
+The first nest contains all exchange plans and the second nest contains only the outside option.
+This two-nest structure captures the key observed substitution pattern between the silver tier and the outside option resulting from the ACA's linkage of CSRs to the purchase of silver plans.
+Under the assumption that $\epsilon_i$ has the generalized extreme value distribution, the household choice probabilities are
+
+\vspace{-0.4in}		
+\begin{eqnarray}
+\label{eqn:choice_probs}
+	q_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta}) &=&  \frac{e^{V_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta})/\lambda}\left(\sum_{j } e^{V_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta})/\lambda}\right)^{\lambda-1}}{1 + \left(\sum_{j} e^{V_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta})/\lambda}\right)^{\lambda}},
+\end{eqnarray}
+\noindent where $V_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta}) \equiv \beta_{i}^p p_{ijt}(\textit{p}) + \beta_j^{\eta} \eta_{gijt}(\textit{p},\textit{n})   + \beta_i^y y_{ij(t-1)} + x'_{ij}\beta^x + \xi_{j}$ and $\lambda$ is the nesting parameter.
+The household choice probabilities in Equation~\eqref{eqn:choice_probs} converge to the standard logit choice probabilities when $\lambda \rightarrow 1$.
+
+The sensitivity of a subsidized consumer's demand $q_{ijt}(\textit{p})$ to a premium change is given by
+
+\vspace{-0.4in}
+\begin{eqnarray*}
+	\frac{\partial q_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta})}{\partial p_{jmt}} &=& \sum_{l \in J_{mt}} \frac{ \partial q_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta})}{\partial p_{ilt}(\textit{p})}\frac{ \partial p_{ilt}(\textit{p})}{\partial p_{jmt}}
+\end{eqnarray*}
+\noindent for all plans $j,k$ in the set of available plans $J_{mt}$.
+Assuming a strictly positive subsidy that does not exceed the full, unsubsidized premium, it follows from Equation~\eqref{eqn:cons_premium} that
+
+\vspace{-0.4in}
+\singlespacing
+\begin{eqnarray}
+\label{eqn:price_partial_formula}
+    \frac{\partial p_{ilt}(\textit{p})}{\partial p_{jmt}} = 
+    \begin{cases} 
+	    0 & l=j, j = b \\		
+		\sigma_{it} & l = j, j \neq b \\     
+		-\sigma_{it} & l \neq j, j = b \\
+		0 & l \neq j, j \neq b  
+    \end{cases}.
+\end{eqnarray}
+\doublespacing
+For a non-benchmark plan, an infinitesimal premium increase results in consumers paying more for that plan only.
+An infinitesimal increase in the benchmark premium does not affect what subsidized consumers pay for the benchmark plan, but reduces what consumers pay for all other plans because of the larger subsidy.
+The complex relationship between insurer and consumer premiums, endogenous determination of the benchmark premium, and variation in the benchmark plan across consumers due to heterogeneous entry create significant computational challenges for estimation.
+We carefully model the endogenous subsidy design despite the high computational cost because of the critical role premium subsidies play in addressing adverse selection.
+
+\subsubsection*{Equilibrium}
+
+Now we find the first-order necessary conditions for a Nash equilibrium.  Differentiating Equation~\eqref{eqn:profit} with respect to the premium and the commission yields the  first-order conditions
+
+\vspace{-0.4in}	
+\begin{footnotesize}
+\begin{eqnarray}
+\label{eqn:acara_foc_short}
+	\frac{\partial R_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} + \frac{\partial RA_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} &=& (1-\iota_{ft}) \frac{\partial C_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} + \frac{\partial \mathcal{C}_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} + \frac{\partial V_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} \nonumber \\
+	\frac{\partial R_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}} + \frac{\partial RA_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}} &=& (1-\iota_{ft}) \frac{\partial C_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}} + \frac{\partial \mathcal{C}_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}} + \frac{\partial V_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}}
+\end{eqnarray}
+\end{footnotesize}
+
+\noindent for all renewal groups $g$ and markets $m$ in which plan $j$ is offered by the firm in year $t$.
+In the supplemental appendix, we write every variable in Equations~\eqref{eqn:profit} and \eqref{eqn:acara_foc_short} in terms of three estimable variables: (1) household choice probabilities $q_{ijt}(\textit{p},\textit{n};\boldsymbol{\theta})$; (2) plan risk scores $r_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta})$; and (3) average claims $c_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta})$.
+Household choice probabilities are computed using Equation~\eqref{eqn:choice_probs}.
+We calculate plan risk scores as a function of observable enrollee characteristics and the plan generosity using the estimating equation,
+
+\vspace{-0.4in}
+\begin{eqnarray}
+\label{eqn:risk_score_estimation}
+	\ln r_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) &=& \sum_{d \in D} \gamma^d s_{djmt}(\textit{p},\textit{n};\boldsymbol{\theta}) + MT'_j \gamma^{MT} + \epsilon_{jmt}^r.
+\end{eqnarray}
+The predicted demographic share $s_{djmt}(\cdot)$ is the share of plan $j$'s enrollment in market $m$ and year $t$ with demographic characteristic $d$, $MT_j$ is a vector metal tier fixed effects,  $\epsilon_{jmt}^r$ is an error term, and the vector of risk score parameters $\boldsymbol{\gamma} = (\gamma^d,\gamma^{MT},\gamma^{n})$.
+The demographic shares are computed by aggregating the household choice probabilities.
+We calculate plan average claims as a function of the plan risk score using the estimating equation
+
+\vspace{-0.4in}	
+\begin{eqnarray}
+\label{eqn:avg_claims_estimation}
+	\ln c_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) &=& \mu^r \ln r_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) + x'_j  \mu^{x}  + \mu^l l_t +   n'_m \mu^{n} + \epsilon_{jmt}^c,
+\end{eqnarray}
+where $r_{jmt}(\cdot)$ is the predicted risk score computed using Equation~\eqref{eqn:risk_score_estimation}, $x_j$ are product characteristics (not including plan AV), $l_t$ is a linear trend, $n'_m$ are market fixed effects, $\epsilon_{jmt}^c$ is an error term, and  $\boldsymbol{\mu} = (\mu^r,\mu^x,\mu^l,\mu^n)$ are the claims parameters.
+
+\subsection{Estimation}
 \label{subsec:steering-methods}
+
+In this section, we explain how we use the generalized method of moments (GMM) to estimate the parameter vector $\boldsymbol{\theta}$.
+We construct four sets of moment conditions: (1) demand moments that match observed choices and predicted household choice probabilities; (2) risk score moments that match observed and predicted plan risk scores; and (3) average claims moments that match observed and predicted plan average claims; and (4) the first-order conditions for profit maximization in Equation~\eqref{eqn:acara_foc_short}.
+These moment conditions are summarized below:
+
+\vspace{-0.4in}
+\begin{eqnarray}
+\label{eqn:moment_conditions}
+	\frac{1}{N^{IJT}} \sum_{i\in I, j \in J, t \in T} \frac{ \chi_{ijt} \partial  \ln  q_{ijt}(\textit{p},\textit{n};\boldsymbol{\beta})}{\partial \boldsymbol{\beta}} &=& {\bf 0} \nonumber \\
+	\frac{1}{N^{JMT}} \sum_{j \in J,m \in M,t \in T} {\bf z}_{jmt}^r(\textit{p},\textit{n};\boldsymbol{\theta}) \left(\ln r_{jmt} - \boldsymbol{\gamma}'   {\bf z}_{jmt}^r(\textit{p},\textit{n};\boldsymbol{\theta}) \right)  &=& {\bf 0} \nonumber  \\
+	\frac{1}{N^{JMT}} \sum_{j \in J,m \in M,t \in T} {\bf z}_{jmt}^c(\textit{p},\textit{n};\boldsymbol{\theta}) \left(\ln c_{jmt} - \boldsymbol{\mu}'   {\bf z}_{jmt}^c(\textit{p},\textit{n};\boldsymbol{\theta}) \right)  &=& {\bf 0} \nonumber  \\
+	\frac{1}{N_{jt}^M} \sum_{m \in M} g_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) &=& 0,  \hspace{0.3in} \forall j \in J_t,t \in T \nonumber \\
+	\frac{1}{N_{jt}^M} \sum_{m \in M} g'_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) &=& 0,  \hspace{0.3in} \forall j \in J_t,t \in T ,
+\end{eqnarray}
+where $N^{IJT}$ is the number of plans available to all households in all years, $N^{JMT}$ is the number of plans available in all markets and years, $N_{jt}^M$ is the number of markets where plan $j$ is offered in year $t$, $\chi_{ijt}$ indicates whether household $i$ chose plan $j$ at time $t$, $r_{jmt}$ is the observed plan risk score, $c_{jmt}$ is the observed plan average claims, the risk score covariates ${\bf z}_{jmt}^r(\textit{p};\boldsymbol{\beta}) \equiv (s_{djmt}(\textit{p},\boldsymbol{\beta}),MT_j)$, the average claims covariates ${\bf z}_{jmt}^c(\textit{p};\boldsymbol{\theta}) \equiv (\ln r_{jmt}(\textit{p};\boldsymbol{\theta}),x_j,u_t,n_m)$, and the first-order condition values
+
+\vspace{-0.4in}
+\begin{footnotesize}
+\begin{eqnarray*}
+	g_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) &\equiv& \frac{\partial R_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} + \frac{\partial RA_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} - (1-\iota_{ft}) \frac{\partial C_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} - \frac{\partial \mathcal{C}_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} - \frac{\partial V_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial p_{jmt}} \\
+	g'_{jmt}(\textit{p},\textit{n};\boldsymbol{\theta}) &\equiv& 	\frac{\partial R_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}} + \frac{\partial RA_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}} - (1-\iota_{ft}) \frac{\partial C_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}} - \frac{\partial \mathcal{C}_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}} - \frac{\partial V_{ft}(\textit{p},\textit{n};\boldsymbol{\theta})}{\partial n_{gjt}}.
+\end{eqnarray*}
+\end{footnotesize}
+\vspace{-0.4in}
+
+\noindent Because our moment conditions in \eqref{eqn:moment_conditions} over-identify the model parameters, we use two-step feasible GMM to find the values of $\boldsymbol{\theta}$ that minimize the GMM objective $[{\bf m}(\boldsymbol{\theta})]'{\bf W}^{-1}[{\bf m}(\boldsymbol{\theta})]$, where ${\bf m}(\boldsymbol{\theta})$ is the vector of moment values in \eqref{eqn:moment_conditions} and the optimal weight matrix ${\bf W}$ is a consistent estimate of the variance-covariance matrix of the moment values.
+
+A significant estimation challenge is to identify the effect of premiums on household choices (i.e., the parameter $\beta_i^p$).
+Several sources of exogenous variation are used to identify the premium parameter $\beta_i^p$, including: (1) exogenous variation in absolute premiums (i.e., relative to the outside option) that results from the phasing-in of the mandate penalty between 2014 and 2016 and zeroing out of the penalty in 2019; (2) exogenous variation in relative premiums (i.e., between plans) that results from kinks in the household premium formula (\ref{eqn:cons_premium}).
+Because of these kinks, some bronze plans may be ``free'' to low-income consumers if the subsidy exceeds the full premium (i.e., the second-cheapest silver plan available to the consumer may exceed the premium of some bronze plans).
+The set of free plans varies by market, time, and consumer characteristics such as income, age, and household composition.
+Unobservables at the insurer's discretion such as provider networks and formularies may also be correlated with premiums.
+We address this concern by estimating Equation~\eqref{eqn:demand_model} with insurer-market fixed effects.
+\citet{Ho2014} and \citet{Tebaldi2020} follow a similar approach.
+Our estimates are similar when including insurer-market fixed effects.
+
+We also need to identify the steering parameter in Equation~\eqref{eqn:choice_probs}.
+Unobservables such as customer service, brand image, and other forms of advertising could be correlated with commission payments.
+Commission payments may also be correlated with competition in a given market.
+We control for these variables by including insurer fixed effects and market fixed effects.
+
+Another identification challenge is that we lack data on patient medical conditions to predict plan risk scores.
+Omitting medical conditions may bias estimates of the parameter vector $\gamma^d$.
+To address this potential source of bias, we compute predicted demographic shares using the estimated consumer-level choice probabilities from Equation~\eqref{eqn:choice_probs}) instead of the observed demographic shares, which are likely to be endogenous.
+The choice model in Equation~\eqref{eqn:choice_probs} can be interpreted as the first-stage of an IV regression for computing unbiased estimates of plan risk scores.
+A similar empirical strategy is widely used in the hospital choice literature to compute measures of hospital market concentration (e.g., \citet{Kessler2000}).
+The identifying assumption is that the predicted demographic shares are based on exogenous determinants of consumer plan demand.
+
+A third identification challenge is to obtain an unbiased estimate of the risk score parameter $\mu^r$ to predict plan average claims.
+We compute predicted plan risk scores using Equation~\eqref{eqn:risk_score_estimation} instead of the observed plan risk scores, which are likely to be endogenous.
+If the ACA risk score perfectly captures plan claims risk, then enrollee characteristics should only affect plan average claims through the plan risk score and not directly affect average claims.
+Imperfections in the ACA risk score are reflected in the estimated risk score parameter.
 
@@
 
-\section{Conclusion}
+\section{Conclusion and Discussion}
 \label{sec:conclusion}
@@
 Our current results provide strong evidence that decision assistance has a significant and economically meaningful effect on health insurance plan choice.
-In terms of dominated choices, our early results suggest that this change in decision-making is welfare improving, and we continue to explore other measures of choice dominance to further confirm this result.
+In avoiding a dominated choice, our results also suggest that decision assistance is welfare improving at least for some enrollees; however, the net welfare effects are unclear given the upward pressure placed on premiums due to commission payments made to private insurance agents.
+Estimation of our full structural model in Section~\ref{sec:steering} will ultimately provide insight into the net welfare effects.
 
-In future work, our identification strategy will exploit the Trump administration's removal of cost-sharing subisidies from the exchanges in 2018 and the subsequent response from insurers to increase premiums on their silver plans (``silver loading'').
-This response significantly changed the prevalence of dominated choices in each household's choice set, and in this way, the removal of the cost-sharing subsidies offers an exogenous change to the set of dominated plans available to each household.
-
-We are also extending our analysis of the differential effects between public decision support versus assistance from private insurance agents/brokers.
-This analysis will determine whether insurance brokers are more likely to steer patients into plans offered by the sponsoring insurer.
+To aid in discussion, we note three major limitations and concerns in our current work: 
+\begin{enumerate}
+    \item Selection and identification
+    \item Uninsurance and unobserved assistance
+\end{enumerate}
 
@@
 
-\begin{figure}[htb]\caption{Count of Enrollees in California Exchange}
+\begin{table}[h!]
 \centering
- 		\hspace*{-1cm}\includegraphics[scale=.7]{figures/enrollee_count.png}
- 		\begin{minipage}{\textwidth}
-		\bigskip
-			\footnotesize \textsc{Notes:} The coefficients for high ratings are shown with circles, those for middle ratings are shown with triangles, and no reviews are shown with diamonds.
-The main results are designated in blue along with an indicator for specification ``Main".
-Various specifications and required minimum number of reviews are also indicated.
+\footnotesize
+\begin{minipage}[h]{6in}
+\caption[caption]{\textbf{Summary Statistics for Covered California Enrollees}\footnote{Statistics based on the population of households enrolled in a Covered California plan at any point from 2014-2019.}}
+\centerline{%
+    \input{tables/summary_stats.tex}
+}
+\label{tab:summary-stats}
 \end{minipage}
- 		\label{figure:SpecCurve}
+\end{table}
+
+\newpage
+\begin{figure}[htb]
+\caption{\textbf{Plan Commissions}}
+\centering
+\begin{minipage}[h]{6in}
+\centerline{%
+    \begin{tabular}{cc}
+        \includegraphics[scale=0.5]{finals/pics/flat_comm.jpg} \\
+        \includegraphics[scale=0.5]{finals/pics/perc_comm.jpg}
+    \end{tabular}
+}
+\label{fig:commissions}
+\end{minipage}
+\end{figure}
+
+\newpage
+\begin{figure}[htb]
+\caption{\textbf{Count of Enrollees in California Exchange}}
+\centering
+\begin{minipage}[h]{6in}
+\centerline{%
+    \includegraphics[scale=0.75]{figures/enrollee_count.png}
+}
+\label{fig:enrollee-count}
+\end{minipage}
+\end{figure}
+
+\newpage
+\begin{figure}[htb]
+\centering
+\footnotesize
+\begin{minipage}[h]{6in}
+\caption[caption]{\textbf{Histogram of Propensity Scores}\footnote{Propensity scores derived from a logistic regression of decision assistance on household characteristics, including the racial and ethnic makeup of the household, age of household members, gender of household members, household size, and household income.
+Regression analysis is limited to newly enrolled households, although results are comparable when considering all exchange households.}}
+\centerline{%
+    \includegraphics[scale=0.75]{figures/ps_assist_clean.png}
+}
+\label{fig:ps-balance}
+\end{minipage}
+\end{figure}
+
+\newpage
+\begin{figure}[htb]
+\centering
+\footnotesize
+\begin{minipage}[h]{6in}
+\caption[caption]{\textbf{Covariate Balance}\footnote{Standardized mean differences with and without inverse-propensity weighting, limited to newly enrolled households.
+``IPW-ATT'' reflects weighted mean differences where treated households receive a weight of 1 and untreated households receive a weight of $p/(1-p)$ and where $p$ denotes the estimated propensity score from a logistic regression of decision assistance on observable household demographics (see Figure~\ref{fig:ps-balance}).}}
+\centerline{%
+    \includegraphics[scale=0.75]{figures/cov_balance.png}
+}
+\label{fig:cov-balance}
+\end{minipage}
+\end{figure}
+
+\newpage
+\begin{figure}[htb]
+\centering
+\footnotesize
+\begin{minipage}[h]{6in}
+\caption[caption]{\textbf{ATT of Decision Assistance on Insurer}\footnote{Estimated ATT as described in Section~\ref{sec:causal} aggregated to the insurer level.
+Confidence intervals derived from a paired bootstrap with 200 iterations.}}
+\centerline{%
+    \includegraphics[scale=0.75]{figures/choice_insurer.png}
+}
+\label{fig:choice-insurer}
+\end{minipage}
+\end{figure}
+
+\newpage
+\begin{figure}[htb]
+\centering
+\footnotesize
+\begin{minipage}[h]{6in}
+\caption[caption]{\textbf{ATT of Decision Assistance on Metal Tier}\footnote{Estimated ATT as described in Section~\ref{sec:causal} aggregated to the level of metal tier.
+Confidence intervals derived from a paired bootstrap with 200 iterations.}}
+\centerline{%
+    \includegraphics[scale=0.75]{figures/choice_metals.png}
+}
+\label{fig:choice-metal}
+\end{minipage}
+\end{figure}
+
+\newpage
+\begin{figure}[htb]
+\centering
+\footnotesize
+\begin{minipage}[h]{6in}
+\caption[caption]{\textbf{ATT of Decision Assistance on Dominated Choices}\footnote{Estimated ATT as described in Section~\ref{sec:dominated}.
+Confidence intervals derived from a paired bootstrap with 200 iterations.}}
+\centerline{%
+    \includegraphics[scale=0.75]{figures/dom_choice.png}
+}
+\label{fig:dom-choice}
+\end{minipage}
+\end{figure}
+
+\newpage
+\begin{figure}[htbp]
+\centering
+\footnotesize
+\begin{minipage}[h]{6in}
+\caption[caption]{\textbf{Premium Rating Regions in California}\footnote{Premium rating regions in the California exchange \citep{CARATE2016}.
+California's 58 counties are divided into 19 rating areas.}}
+\centerline{%
+    \includegraphics[scale=.45]{finals/pics/CA_Rating_Regions2.jpg}	
+}
+\label{rating_area_partitions}
+\end{minipage}
 \end{figure}

### 2021-06-14 analysis/decision-support/_ChoiceModel.R
update estimation functions and summary stats table)

@@ -73,6 +73,8 @@ for (i in 1:nrow(choice.regs)) {
 bs.choice.data <- full.nest %>% 
   mutate(hh.final = map(data_full, ~.x %>% distinct(.x$household_number)))
 
+poss.tidy <- possibly(.f = tidy, otherwise=NULL)
+
 max.boot <- 200
 for (b in 1:max.boot) {  
   bs.choice.run <- bs.choice.data %>%

### 2021-06-14 analysis/decision-support/_ChoiceSummary.R

@@ -104,14 +104,16 @@ bs.metal.boot.cond <- bs.pred.purchase %>%
 
 bs.metal.summary <- bs.metal.boot %>% ungroup() %>%
   group_by(metal) %>%
-  summarize(p01=quantile(att, 0.01),
+  summarize(mean=mean(att,na.rm=TRUE),
+            p01=quantile(att, 0.01),
             p05=quantile(att, 0.05),
             p95=quantile(att, 0.95),
             p99=quantile(att, 0.99))
 
 bs.metal.summary.cond <- bs.metal.boot.cond %>% ungroup() %>%
   group_by(metal) %>%
-  summarize(p01=quantile(att, 0.01),
+  summarize(mean=mean(att,na.rm=TRUE),
+            p01=quantile(att, 0.01),
             p05=quantile(att, 0.05),
             p95=quantile(att, 0.95),
             p99=quantile(att, 0.99))
@@ -142,7 +144,8 @@ bs.ins.boot.cond <- bs.pred.purchase %>%
 
 bs.ins.summary <- bs.ins.boot %>% ungroup() %>%
   group_by(insurer) %>%
-  summarize(p01=quantile(att, 0.01),
+  summarize(mean=mean(att,na.rm=TRUE),
+            p01=quantile(att, 0.01),
             p05=quantile(att, 0.05),
             p95=quantile(att, 0.95),
             p99=quantile(att, 0.99))
@@ -150,7 +153,8 @@ bs.ins.summary <- bs.ins.boot %>% ungroup() %>%
 
 bs.ins.summary.cond <- bs.ins.boot.cond %>% ungroup() %>%
   group_by(insurer) %>%
-  summarize(p01=quantile(att, 0.01),
+  summarize(mean=mean(att,na.rm=TRUE),
+            p01=quantile(att, 0.01),
             p05=quantile(att, 0.05),
             p95=quantile(att, 0.95),
             p99=quantile(att, 0.99))

### 2021-06-14 analysis/decision-support/_SummaryStats.R

@@ -283,15 +283,24 @@ sum.stats.assist <- sum.stats.data %>% filter(assisted==1) %>%
             na.rm=TRUE,
             .names="{col}_{fn}"))
 
-sum.stats.unassist <- sum.stats.data %>% filter(assisted==0) %>%
+sum.stats.unassist1 <- sum.stats.data %>% filter(assisted==0) %>%
   summarize(across(c("household_size","num_children_subject", "perc_black", "perc_hispanic", "perc_white",
-                     "FPL_low","FPL_250","FPL_400","FPL_high","Kaiser","Anthem","BlueShield","HealthNet",
-                     "Uninsured","Other","Bronze","Gold","Silver","Platinum","Catastrophic","HMO","PPO","EPO","HSP"),
+                     "FPL_low","FPL_250","FPL_400","FPL_high","Uninsured"),
                    list(Mean=mean, N=~n(),
                         q1=~quantile(., probs=0.10, na.rm=TRUE),
                         q9=~quantile(., probs=0.90, na.rm=TRUE)),
                    na.rm=TRUE,
                    .names="{col}_{fn}"))
+sum.stats.unassist2 <- sum.stats.data %>% filter(assisted==0, Uninsured==0) %>%
+  summarize(across(c("Kaiser","Anthem","BlueShield","HealthNet",
+                     "Other","Bronze","Gold","Silver","Platinum","Catastrophic","HMO","PPO","EPO","HSP"),
+                   list(Mean=mean, N=~n(),
+                        q1=~quantile(., probs=0.10, na.rm=TRUE),
+                        q9=~quantile(., probs=0.90, na.rm=TRUE)),
+                   na.rm=TRUE,
+                   .names="{col}_{fn}"))
+
+
 
 sum.stats.all <- sum.stats.data %>%
   summarize(across(c("household_size","num_children_subject", "perc_black", "perc_hispanic", "perc_white",
@@ -306,6 +315,7 @@ sum.stats.all <- sum.stats.data %>%
 tot.count <- nrow(sum.stats.data)/1000000
 assist.count <- nrow(sum.stats.data %>% filter(assisted==1))/1000000
 unassist.count <- nrow(sum.stats.data %>% filter(assisted==0))/1000000
+tot.unins <- nrow(sum.stats.data %>% filter(Uninsured==1))/1000000
[…]

### 2021-06-14 analysis/decision-support/choice_data_function_map.R

@@ -209,14 +209,14 @@ choice.data.fnc2 <- function(plans, hhs) {
     mutate(hh_count=seq(n())) %>%
     filter(hh_count==1) %>%
     select(household_number) %>% ungroup()
-  sample.hh <- sample_frac(unique.hh, size=0.1, replace=FALSE)
+  sample.hh <- sample_frac(unique.hh, size=0.2, replace=FALSE)
   
   unique.hh.oos <- treated.dat %>%
     group_by(household_number) %>%
     mutate(hh_count=seq(n())) %>%
     filter(hh_count==1) %>%
     select(household_number) %>% ungroup()
-  sample.hh.oos <- sample_frac(unique.hh.oos, size=0.15, replace=FALSE)
+  sample.hh.oos <- sample_frac(unique.hh.oos, size=0.2, replace=FALSE)
   
     
   ## Final data

### 2021-06-14 analysis/decision-support/choice_est_function_map.R

@@ -11,7 +11,7 @@
 dchoice.reg <- function(d, nest.names) {
 
   ## Terms for estimation
-  all_covars=c("premium", "silver", "AV")
+  all_covars=c("premium", "silver", "gold", "platinum")
   ins.offer <- c(0,0)
   cml.share <- 0
   tot.choice <- sum(d$choice==1)

### 2021-06-14 finals/paper.tex
Updates from Overleaf

@@
 We investigate the issue of commission and plan choice more fully in Section \ref{sec:steering}.
+
+With regard to metal tier, Figure~\ref{fig:choice-metal} shows that individuals with decision assistance are about 16 percentage points more likely to select a silver tier plan.
+With xx\% of unassisted households selecting a silver plan, this reflects a relative increase of xx\% in the probability of selecting a silver plan.
+Most of this increase comes from a reduction in the probability of selecting a bronze plan, with a smaller (but still significant) reduction in selecting gold plans.
 
@@
 
+\clearpage
 \newpage
-\begin{figure}[htbp]
+\begin{figure}[htb]
 \centering

### 2021-06-14 analysis/decision-support/_SummaryStats.R
correct summary stats table)

@@ -276,7 +276,7 @@ sum.stats.data <- hh.full %>% ungroup() %>%
 sum.stats.assist <- sum.stats.data %>% filter(assisted==1) %>%
   summarize(across(c("household_size","num_children_subject", "perc_black", "perc_hispanic", "perc_white",
                      "FPL_low","FPL_250","FPL_400","FPL_high","Kaiser","Anthem","BlueShield","HealthNet",
-                     "Uninsured","Other","Bronze","Gold","Silver","Platinum","Catastrophic","HMO","PPO","EPO","HSP"),
+                     "Other","Bronze","Gold","Silver","Platinum","Catastrophic","HMO","PPO","EPO","HSP"),
                    list(Mean=mean, N=~n(),
                     q1=~quantile(., probs=0.10, na.rm=TRUE),
                     q9=~quantile(., probs=0.90, na.rm=TRUE)),
@@ -285,7 +285,7 @@ sum.stats.assist <- sum.stats.data %>% filter(assisted==1) %>%
 
 sum.stats.unassist1 <- sum.stats.data %>% filter(assisted==0) %>%
   summarize(across(c("household_size","num_children_subject", "perc_black", "perc_hispanic", "perc_white",
-                     "FPL_low","FPL_250","FPL_400","FPL_high","Uninsured"),
+                     "FPL_low","FPL_250","FPL_400","FPL_high"),
                    list(Mean=mean, N=~n(),
                         q1=~quantile(., probs=0.10, na.rm=TRUE),
                         q9=~quantile(., probs=0.90, na.rm=TRUE)),
@@ -325,23 +325,24 @@ mean.stats.assist <- sum.stats.assist %>% select(ends_with("_Mean")) %>%
   pivot_longer(cols=ends_with("_Mean"),
                values_to="Assisted") %>%
   mutate(name=str_remove(name,"_Mean")) %>%
-  bind_rows(as_tibble(assist.count) %>% mutate(name="Obs") %>% rename(Assisted=value))  
+  bind_rows(as_tibble(assist.count) %>% mutate(name="Obs") %>% rename(Assisted=value))
 mean.stats.unassist1 <- sum.stats.unassist1 %>% select(ends_with("_Mean")) %>%
   pivot_longer(cols=ends_with("_Mean"),
                values_to="Unassisted") %>%
[…]

### 2021-06-14 finals/paper.tex
update draft

--- 2021-06-14 finals/paper.tex
@@
 In this paper, we study the welfare effects of decision assistance and firm steering in health insurance using the population of enrollments from the California Affordable Care Act (ACA) exchange from 2014 to 2019.
-We find that enrollees are nearly 2x more likely to select a silver plan when using some form of decision assistance and 30\% less likely to select a ``dominated'' plan.
+We find that enrollees 30\% more likely to select a silver plan when using some form of decision assistance and 30\% less likely to select a ``dominated'' plan.
 Preliminary results suggest that firms have considerable ability to steer consumers' decisions using agent commissions, where a \$1 increase in commissions paid to agents has the same effect as a \$2 or \$3 increase in plan premiums.
@@
 We employ as our estimator an augmented inverse propensity weighted nested logit regression, as discussed in more detail in Section \ref{sec:causal}, and we limit the analysis to newly enrolled households.
-We estimate that such households are 50\% more likely to select a silver plan and 20\% less likely to remain uninsured when using some form of decision assistance.
-We also find strong evidence of heterogeneous effects depending on the type of assistance used, wherein households using public decision assistance ...
+We estimate that such households are just over 30\% more likely to select a silver plan, the majority of which comes from a reduction in the probability of selecting a bronze plan.
 
@@
 
-Third,
+Third, we incorporate insurer commission payments alongside premium-setting and demand estimation as part of a structural model of insurer steering.
+Results from this analysis are pending; however, preliminary analysis of commission payments and plan choice suggests that commissions are a larger factor in plan choice than premiums.
+For example, we estimate that a \$1 increase in commissions paid to private insurance agents is equivalent to a \$2 to \$3 increase in premiums.
+In other words, private insurance agents appear to have significant influence on plan choice, with commission payments having 2x the effect of premiums.
 
-We contribute to two distinct literatures. First, our examination of decision assistance and health insurance relates to the literature on the role of experts in decision making.
+We contribute to two distinct literatures.
+First, our examination of decision assistance and health insurance relates to the literature on the role of experts in decision making.\footnote{A broader literature considers ``persuasion'', which includes the role of advertising and media reports.
+We are interested in the more narrow literature specifically dealing with decision assistance in the form of third-party ``experts'' or advice.
+See \cite{dellavigna2010} for a general survey of the empirical evidence on persuasion.} Theoretical models of the role of experts and advice in a principal-agent framework include \cite{szalay2005}, \cite{alonzo2008}, and \cite{armstrong2010}.
+In an experimental setting, \cite{schotter2003} finds that individuals are much more likely to follow the advice of an expert and that such behavior is welfare-improving.
+In education, \cite{borghans2015} find large effects of high school counselors on students' college field choices, and \cite{bettinger2012} estimate large effects of personal assistance on the probability of applying for and receiving college financial aid, with subsequently large effects on college attendance.
+\cite{finkelstein2019} similarly find large effects of both improved information and personal assistance on probability of enrollment in the Supplemental Nutrition Assistance Program among eligible households.
 
@@
 \cite{bundorf2019}, for example, show that offering additional information alongside an algorithmic expert recommendation significantly affects an individual's choice of prescription drug plans.
+\cite{kling2012} also estimates large effects of personalized cost information on plan switching in the Medicare Part D market.
+To our knowledge, the literature on experts and decision-making in the context of health insurance focuses on unbiased and often anonymous ``experts'' (e.g., an algorithm suggesting the best plan for an individual).
+Our setting is unique in that individuals have access to a public ``navigator,'' who receives no compensation for any plan choice, and a private insurance agent who receives a commission that varies by plan.
 
@@
 The consensus from this literature is that individuals regularly make \textit{ex ante} very bad health insurance decisions, often selecting plans that are either financially dominated by other plan options or most likely suboptimal given the enrollee's existing medical conditions.
+While not definitive, a common theme in this literature is that poor health insurance decisions are due in-part to an inability or unwillingness of enrollees to accurately evaluate their plan options \citep{bhargava2017, hanoch2009}.
 
-Specifically in the context of the ACA, \cite{orzol2018} find that an ``Enroll America,'' a national non-profit organization designed to expand health insurance enrollment in the U.S., significantly increased enrollment in the ACA exchange plans.
+There is less consensus, however, in terms of how best to improve health insurance plan choice.
+For example, \cite{ketcham2012} find that observed poor health insurance decision making will tend to improve over time, thereby partially alleviating the need for any explicit intervention.
+In the context of the ACA, \cite{orzol2018} find that an ``Enroll America,'' a national non-profit organization designed to expand health insurance enrollment in the U.S., significantly increased enrollment in the ACA exchange plans.
 \cite{myerson2019} also finds that federally funded assistance programs significantly increased the probability of enrollment in Medicaid, although they found little effect of such federal funding on enrollment in exchange plans.
 \cite{sommers2015} similarly show that access to navigators is highly correlated with Medicaid enrollment, mirroring earlier findings from \cite{aizer2003} in her study of Medicaid enrollment and application assistants in California.
+\cite{aizawa2021} distinguish between ``public'' provision (via government advertising) versus private provision (via insurer advertising) on plan choice, where they find that both forms of advertising affect participation in the market and that private advertising has a particularly large effect on the intensive margin of plan choice; however, the welfare effects of private advertising are unclear due to business stealing and costs of advertising.
 
-\cite{aizawa2021}
-
-While not definitive, a common theme in this literature is that poor health insurance decisions are due in-part to an inability or unwillingness of enrollees to accurately evaluate their plan options \citep{bhargava2017, hanoch2009}.
-Even still, \cite{ketcham2012} find that any such poor decision making will tend to improve over time, thereby partially alleviating the need for any explicit intervention.
+Our contribution to this literature is most closely related to \cite{aizawa2021} in that we consider both private and public decision assistance; however, we examine this in the context of one-on-one assistance rather than general exposure to advertising.
+We also consider the potential for private agents to improve health insurance decisions while also allowing for potential bias introduced through commissions (i.e., steering), and we compare outcomes from the use of private agents to those of public navigators.
+In this sense, our analysis follows in the spirit of \cite{ketcham2012} in that we envision private agents as helping to resolve an information problem, the costs of which include potential steering into sub-optimal plans and spillover effects of commission payments onto premiums.
+Whether the costs of such private agents exceed the benefits or are best borne by public agents without steering incentives is an empirical question which we pursue in Section \ref{sec:steering}.
 
@@
 We see from Table~\ref{tab:summary-stats} that enrollees using decision assistance are of lower income and larger household size.
-Among types of plans purchased, we see little difference between those with and without decision assistance, with the exception of Kaiser plans for which individuals using decision assistance are less likely to purchase.
+Among types of plans purchased, we see relatively minor differences between those with and without decision assistance, with the exception of Kaiser plans for which individuals using decision assistance are less likely to purchase.
 Overall, the silver tier is the most commonly selected option, and this is particularly true for those using decision assistance.
-Enrollees with decision assistance are also much more likely to select an HMO and relatively more likely to select a PPO.
+Enrollees with decision assistance are also slightly more likely to select a PPO relative to those without assistance.
 
@@
 We investigate the issue of commission and plan choice more fully in Section \ref{sec:steering}.
+
+With regard to metal tier, Figure~\ref{fig:choice-metal} shows that individuals with decision assistance are about 16 percentage points more likely to select a silver tier plan.
+With 50\% of unassisted households selecting a silver plan, this reflects a relative increase of 32\% in the probability of selecting a silver plan.
+Most of this increase comes from the 50\% reduction in the probability of selecting a bronze plan, with a smaller (but still significant) reduction in selecting gold plans.
 
@@
 \begin{minipage}[h]{6in}
-\caption[caption]{\textbf{Summary Statistics for Covered California Enrollees}\footnote{Statistics based on the population of households enrolled in a Covered California plan at any point from 2014-2019.}}
+\caption[caption]{\textbf{Summary Statistics for Covered California Enrollees}\footnote{Statistics based on the population of households enrolled in a Covered California plan at any point from 2014-2019.
+Household demographics and income summary statistics are based on all households, while summaries for insurer, metal tier, and network type are conditional on being insured.}}
 \centerline{%

### 2021-06-18 finals/ashecon/ashecon-202106.Rmd
Update slides for ashecon

--- 2021-05-03 finals/creed/creed-202105.Rmd
@@
 subtitle: "Ian McCarthy & Evan Saltzman"
-author: Carolina Region Empirical Economics Day
-date: May 3, 2021 #"`r format(Sys.time(), '%d %B %Y')`"
+author: ASHEcon Annual Conference
+date: June 23, 2021 #"`r format(Sys.time(), '%d %B %Y')`"
 header-includes: 
@@
   - \usepackage{amsmath}
+  - \usepackage{booktabs}
+  - \usepackage{caption}
 output:
@@
                scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
-               ggrepel, xaringanExtra)
+               ggrepel, xaringanExtra, kableExtra, knitr, htmltools)
 ```
@@
 
-# Some decisions are hard
+# Decisions are hard
 
 .center[
-<iframe width="800" height="500" src="https://www.youtube.com/embed/oWXNf3JVWpI?start=146&end=272" frameborder="0" allowfullscreen></iframe>
+  ![](https://media.giphy.com/media/Lp9wng87dsScq2owim/giphy.gif)
 ]
@@
 
-1. Does some form of decision assistance "help" in plan selection?
+1. Does some form of decision assistance affect plan selection?
 
-2. Do insurers use brokers/agents to steer people to different plans?
+2. Does decision assistance "improve" plan selection?
 
-3. What are the welfare effects of any such steering?
+3. Do insurers use brokers/agents to steer people to different plans?
+
+4. (not today) What are the welfare effects?
 
@@
 1. [Data](#data)
-2. [Dominated choices](#dominated)
-3. [Effects of decision assistance](#decision-assist)
+2. [Effects of decision assistance](#decision-assist)
+3. [Dominated choices](#dominated)
 4. [Insurer steering](#steering)
@@
 ---
-# Insurers
+# Households
+
+```{r, include=FALSE}
+load('final_summary.Rdata')
+```
+
+```{r sum-stats, echo=FALSE}
+kable(final.sum.stats %>% filter(name %in% c("Household Size", "No. of Children",
+                                             "Percent Black", "Percent White",
+                                             "Percent Hispanic","below 138%", "between 138 and 250%",
+                                             "between 250 and 400%", "above 400%",
+                                             "Total HHs (millions)", "Total Uninsured (millions)")), 
+      format="html",
+      col.names = c("Variable","Assisted","Unassisted","Overall"),
+      digits=c(0,2,2,2),
+      booktabs=T) %>%
+  pack_rows("Household Demographics", 1, 5) %>%  
+  pack_rows("Income relative to FPL", 6, 9) %>%
+  kable_styling(full_width=F,
+                font_size=17)
+```
+
+---
+# Plan choice: Insurers
 
@@
 ---
-# Metal tier
+# Plan choice: Metal tiers
 
@@
 
+]
+
+---
+class: inverse, center, middle
+name: decision-assist
+
+# Effect of decision assistance on plan choice
+
+<html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>
+
+---
+# Estimand of interest
+
+- Want to identify the Average Treatment Effect on the Treated (ATT) of decision assistance
+
+- Denote by $Pr[Y_{ij}^{1}]$ the probability of household $i$ selecting plan $j$ with decision assistance
+
+- Denote by $Pr[Y_{ij}^{0}]$ the probability of household $i$ selecting plan $j$ without decision assistance
+
+--
+
+$$ATT = Pr[Y_{ij}^{1} | \text{Assist}] - Pr[Y_{ij}^{0} | \text{Assist}]$$
+
+---
+# Estimation
+
+1. Calculate predicted probability of decision assistance from logit model
+
+--
+
+.pull-left[
+  ![:scale 80%](../../figures/ps_assist_full.png)
+]
+
+.pull-right[
+  ![:scale 80%](../../figures/cov_balance.png)
+]
+
+---
+count: false
+
+# Estimation
+
+1. Calculate predicted probability of decision assistance from logit model
+2. Estimate weighted multinomial logit model among those without any decision assistance, $\hat{\theta}$, with weights $\frac{\hat{p}}{1-\hat{p}}$
+3. Use $\hat{\theta}$ to form predicted counterfactual, $\widehat{Pr[Y_{ij}^{0} | \text{Assist}]}$
+4. Use predicted value in ATT estimate: $$\underbrace{Pr[Y_{ij}^{1} | \text{Assist}]}_{Observed} - \underbrace{\widehat{Pr[Y_{ij}^{0} | \text{Assist}]}}_{Predicted}$$
+5. Aggregate to level of insurer and metal
+
+---
+count: false
+
+# Estimation
+
+- Focus only on new enrollees to avoid presence of inertia
+
+- Estimate separately by year and rating area
+
+---
+# Inference
+
+- 200 bootstrap replications
+
+- Confidence interval based on the 5th and 95th percentile of bootstrap replications
+
+---
+# Effects of decision assistance
+
+.pull-left[
+  ![](../../figures/choice_metals.png)
+]
+
+.pull-right[
+  ![](../../figures/choice_insurer.png)
 ]
@@
 
-- Linear probability model of dominated choices or switching
-- Dummy variable for receiving any assistance
-- Selection on observables assumption (for now)
+1. Calculate predicted probability, $\hat{p}$, of decision assistance from logit model
 
----
-# Selection on observables
+2. Estimate weighted logit model of dominated choice among those without any decision assistance, $\hat{\beta}$, with weights given by  $\frac{\hat{p}}{1-\hat{p}}$
 
-.pull-left[
-  ![](../../figures/cov_balance.png)
-]
+3. Use $\hat{\beta}$ to form predicted counterfactual, $\widehat{Pr[Y_{i}^{0} | \text{Assist}]}$
 
-.pull-right[
-  ![](../../figures/ps_assist_full.png)
-
-]
+4. Use predicted value in ATT estimate: $$\underbrace{Pr[Y_{i}^{1} | \text{Assist}]}_{Observed} - \underbrace{\widehat{Pr[Y_{i}^{0} | \text{Assist}]}}_{Predicted}$$
 
@@
 .center[
-  ![:scale 50%](../../figures/dominated_choice_regression.png)
-]
-
----
-# Decision assistance and switching
-
-.center[
-  ![:scale 50%](../../figures/switching_regression.png)
-]
-
----
-class: inverse, center, middle
-name: decision-assist
-
-# Effect of decision assistance on plan choice
-
-<html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>
-
----
-# Estimand of interest
-
----
-# Estimand of interest
-
-- Want to identify the Average Treatment Effect on the Treated (ATT) of decision assistance
-
-- Denote by $Pr[Y_{ij}^{1}]$ the probability of household $i$ selecting plan $j$ with decision assistance
-
-- Denote by $Pr[Y_{ij}^{0}]$ the probability of household $i$ selecting plan $j$ without decision assistance
-
---
-
-$$ATT = Pr[Y_{ij}^{1} | \text{Assist}] - Pr[Y_{ij}^{0} | \text{Assist}]$$
-
----
-# Estimation
-
-1. Estimate multinomial logit model among those without any decision assistance, $\hat{\theta}$
-
-2. Use $\hat{\theta}$ to form predicted counterfactual, $\widehat{Pr[Y_{ij}^{0} | \text{Assist}]}$
-
-3. Use predicted value in ATT estimate: $$\underbrace{Pr[Y_{ij}^{1} | \text{Assist}]}_{Observed} - \underbrace{\widehat{Pr[Y_{ij}^{0} | \text{Assist}]}}_{Predicted}$$
-
-4. Aggregate to level of insurer and metal
-
----
-count: false
-
-# Estimation
-
-- Focus only on new enrollees to avoid presence of inertia
-
-- Estimate separately by year and rating area
-
----
-# Inference
-
-- Clustered bootstrap, by year and rating area
-
-- 200 bootstrap replications
-
-- Confidence interval based on the 5th and 95th percentile of bootstrap replications
-
----
-# Effects of decision assistance
-
-.pull-left[
-  ![](../../figures/choice_metals.png)
-]
-
-.pull-right[
-  ![](../../figures/choice_insurer.png)
+  ![:scale 50%](../../figures/dom_choice.png)
 ]
@@
 
-# Analysis of insurer steering
+# *Preliminary* analysis of insurer steering
 
 <html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>
-
----
-# This is preliminary!
-
-.center[
-  ![:scale 50%](https://media.giphy.com/media/3o6Yg9rDXHL8Zrdlza/giphy.gif)
-]
 
@@
 
-**Calculate commission elasticities of demand**
-
 1. Estimate nested logit choice model with commission as covariate
@@
 | -------------- |:-------------:| --------------:|
-| Overall        | 11.18         | 5.39           |
-| Large Insurers | 11.94         | 5.75           |
-| Small Insurers | 6.33          | 3.08           |
+| Overall        | 7.70          | 3.69           |
+| Large Insurers | 8.07          | 3.86           |
+| Small Insurers | 5.30          | 2.57           |

### 2021-06-18 analysis/decision-support/_SummaryStats.R

@@ -33,7 +33,7 @@ kable(metal.assist.all[,2:4], format="latex",
   save_kable("tables/metal_assistance.tex")
 
 ## figure of assistance and tier choice
-ggplot(hh.full) +
+ggplot(hh.ins) +
   geom_bar(mapping=aes(x=channel_detail,fill=metal),
            position="fill", color="black", size=.1) +
   labs(
@@ -43,7 +43,7 @@ ggplot(hh.full) +
   theme(legend.title=element_blank()) +
   scale_fill_brewer(palette="Greys") + ggsave("figures/metal_stack_all.png")
 
-ggplot(hh.full) +
+ggplot(hh.ins) +
   geom_bar(mapping=aes(x=channel,fill=metal),
            position="fill", color="black", size=.1) +
   labs(
@@ -55,7 +55,7 @@ ggplot(hh.full) +
 
 
 ## figure of assistance and insurer
-hh.full %>% mutate(insurer = case_when(
+hh.ins %>% mutate(insurer = case_when(
   insurer=="Blue_Shield" ~ "BCBS",
   insurer=="Health_Net" ~ "HealthNet",
   insurer=="Anthem" ~ "Anthem",
@@ -73,7 +73,7 @@ hh.full %>% mutate(insurer = case_when(
   scale_fill_brewer(palette="Greys") + ggsave("figures/insurer_stack_all.png")
 
 
-hh.full %>% mutate(insurer = case_when(
+hh.ins %>% mutate(insurer = case_when(
   insurer=="Blue_Shield" ~ "BCBS",
   insurer=="Health_Net" ~ "HealthNet",
   insurer=="Anthem" ~ "Anthem",
@@ -302,24 +302,38 @@ sum.stats.unassist2 <- sum.stats.data %>% filter(assisted==0, Uninsured==0) %>%
 
 
 
-sum.stats.all <- sum.stats.data %>%
+sum.stats.all1 <- sum.stats.data %>%
   summarize(across(c("household_size","num_children_subject", "perc_black", "perc_hispanic", "perc_white",
-                     "FPL_low","FPL_250","FPL_400","FPL_high","Kaiser","Anthem","BlueShield","HealthNet",
-                     "Uninsured","Other","Bronze","Gold","Silver","Platinum","Catastrophic","HMO","PPO","EPO","HSP"),
+                     "FPL_low","FPL_250","FPL_400","FPL_high"),
+                   list(Mean=mean, N=~n(),
+                        q1=~quantile(., probs=0.10, na.rm=TRUE),
[…]

### 2021-06-18 analysis/decision-support/choice_est_function_map.R

@@ -11,7 +11,7 @@
 dchoice.reg <- function(d, nest.names) {
 
   ## Terms for estimation
-  all_covars=c("premium", "silver", "gold", "platinum")
+  all_covars=c("premium", "silver", "bronze","hh_size_prem")
   ins.offer <- c(0,0)
   cml.share <- 0
   tot.choice <- sum(d$choice==1)

### 2021-06-18 analysis/decision-support/decision-analysis.R

@@ -14,7 +14,7 @@ if (!require("pacman")) renv::install('pacman')
 pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stargazer, knitr, kableExtra,
                lfe, modelr, mclogit, bookdown, parallel, nnet, mixl, fixest,
                future.apply, gtsummary, emo, twilio, SAScii, data.table, scales, mlogit,
-               modelsummary, cobalt, WeightIt, broom, tidymodels)
+               modelsummary, cobalt, WeightIt, broom, tidymodels, webshot)
 
 source('paths.R')
 source(paste0(common,"/common_functions.R"))
@@ -135,7 +135,8 @@ hh.full <- hh.full %>%
 ## Filter for only new purchases for plan choice analysis
 hh.clean <- hh.full %>% 
   filter(is.na(previous_plan_offered))
-  
+
+hh.ins <- hh.full %>% filter(!is.na(plan_number_nocsr))  
 
 # Run analysis scripts ----------------------------------------------------
 

### 2021-06-23 finals/ashecon/ashecon-202106.Rmd
update slides
update ashecon slides

@@
 
-2. Size of the market introduces decision problems on a massive scale
+2. Size of the market introduces decision problems on a large scale
 
@@
   - Role of decision assistance in health
+  - Public and private decision assistance in the same market
   - Commissions and steering
@@
 - ACA program data (contribution percentages, rating areas, etc.)
+
+---
+# What is "decision assistance"?
+
+- Public decision assistance in the form of "navigators"
+- Private brokers and agents (majority are brokers)
+
+---
+# Agent compensation
+
+.pull-left[
+**Compensation schemes**
+
+- Flat commission 
+- Fixed amount from <span>&#36;</span>0 to <span>&#36;</span>264
+
+]
+
+.pull-right[
+  ![](../pics/flat_comm.jpg)
+]
+
+---
+count: false
+
+# Agent compensation
+
+.pull-left[
+**Compensation schemes**
+
+- Percentage commission
+- Percent of annual premium, from 1% to 5%
+]
+
+.pull-right[
+  ![](../pics/perc_comm.jpg)
+]
 
@@
 ---
-# Agent compensation
-
-.pull-left[
-**Compensation schemes**
-
-- Flat commission 
-- Fixed amount from <span>&#36;</span>0 to <span>&#36;</span>264
-
-]
-
-.pull-right[
-  ![](../pics/flat_comm.jpg)
-]
-
----
-count: false
-
-# Agent compensation
-
-.pull-left[
-**Compensation schemes**
-
-- Percentage commission
-- Percent of annual premium, from 1% to 5%
-]
-
-.pull-right[
-  ![](../pics/perc_comm.jpg)
-]
-
----
-count: false
-
-# Agent compensation
-
-.pull-left[
-**Compensation schemes**
-
-- Flat commission, from <span>&#36;</span>0 to <span>&#36;</span>264
-- Percentage commission, from 1% to 5% of annual premium
-
-]
-
---
-
-.pull-right[
-**Sources of variation**
-
-- Insurer
-- New enrollee versus renewal
-- Network type (e.g., HMO vs PPO)
-
-]
-
----
 # Quantifying steering effect

### 2021-06-23 finals/ashecon/ashecon-202106.Rmd
update ashecon slides

@@
 
-- Public decision assistance in the form of "navigators"
-- Private brokers and agents (majority are brokers)
+- Public decision assistance in the form of "navigators", no commissions
+- Private assistance that receives commissions:
+  - "certified insurance agent", acts as independent broker (97\%)
+  - "plan-based enroller", acts as agent for insurer (3/%)
+  - all listed as "agent" in our analysis
 

### 2021-06-23 finals/ashecon/ashecon-202106.Rmd
update ashecon slides and summary figures

--- 2021-06-23 finals/ashecon/ashecon-202106.Rmd
@@
 - What's new here?
-  - Role of decision assistance in health
+  - Role of decision assistance in health insurance choice
   - Public and private decision assistance in the same market
@@
 
-- Public decision assistance in the form of "navigators"
-- Private brokers and agents (majority are brokers)
+- Public decision assistance in the form of "navigators", no commissions
+- Private assistance that receives commissions:
+  - "certified insurance agent", acts as independent broker (97%)
+  - "plan-based enroller", acts as agent for insurer (3%)
+  - all listed as "agent" in our analysis
 

### 2021-06-23 analysis/decision-support/_SummaryStats.R

@@ -56,7 +56,7 @@ ggplot(hh.ins) +
 
 ## figure of assistance and insurer
 hh.ins %>% mutate(insurer = case_when(
-  insurer=="Blue_Shield" ~ "BCBS",
+  insurer=="Blue_Shield" ~ "Blue Shield",
   insurer=="Health_Net" ~ "HealthNet",
   insurer=="Anthem" ~ "Anthem",
   insurer %in% c("Chinese_Community", "Contra_Costa", "Molina", "LA_Care","Oscar","SHARP","United","Valley","Western") ~ "Other",
@@ -74,7 +74,7 @@ hh.ins %>% mutate(insurer = case_when(
 
 
 hh.ins %>% mutate(insurer = case_when(
-  insurer=="Blue_Shield" ~ "BCBS",
+  insurer=="Blue_Shield" ~ "Blue Shield",
   insurer=="Health_Net" ~ "HealthNet",
   insurer=="Anthem" ~ "Anthem",
   insurer %in% c("Chinese_Community", "Contra_Costa", "Molina", "LA_Care","Oscar","SHARP","United","Valley","Western") ~ "Other",

### 2021-06-23 finals/ashecon/ashecon-202106.Rmd
correct ashecon slides
update ashecon slides

@@
 2. Size of the market introduces decision problems on a large scale
-
----
-# 1. Insurance choice is confusing
-
-.center[
-  ![](../pics/slate-2017.png)
-]
-
-.footnote[
-  [Slate, 2017](https://slate.com/business/2017/08/americans-are-overpaying-for-insurance-because-obamacare-is-confusing.html)
-]
-
----
-count: false
-
-# 1. Insurance choice is confusing
-.center[
-  ![](../pics/health-affairs-2017b.png)
-]
-
-.footnote[
-  [Health Affairs, January, 2017](https://www.healthaffairs.org/doi/10.1377/hlthaff.2016.0472)
-]
-
----
-count: false
-
-# 1. Insurance choice is confusing
-
-.center[
-  ![](../pics/health-affairs-2017.png)
-]
-
-.footnote[
-  [Health Affairs, August, 2017](https://www.healthaffairs.org/doi/full/10.1377/hlthaff.2017.0085)
-]
-
----
-# 2. Potential scale
-
-- 12.7 million enrollees on exchanges in 2016
-
-- Down to 11.4 million in 2020
-
-- Over 27 million remain uninsured
-
----
-count: false
-
-# 2. Potential scale
-
-.center[
-  ![:scale 75%](../pics/kff-uninsured.png)
-]
 
@@
 1. Calculate predicted probability of decision assistance from logit model
-2. Estimate weighted multinomial logit model among those without any decision assistance, $\hat{\theta}$, with weights $\frac{\hat{p}}{1-\hat{p}}$
+2. Estimate weighted nested logit model among those without any decision assistance, $\hat{\theta}$, with weights $\frac{\hat{p}}{1-\hat{p}}$
 3. Use $\hat{\theta}$ to form predicted counterfactual, $\widehat{Pr[Y_{ij}^{0} | \text{Assist}]}$
